### 2018-08-02 main.tex
Start the draft

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{mathrsfs}
\usepackage{float}
% ======    PACKAGES
\usepackage{slivkins-setup,slivkins-theorems}
%\usepackage{amsmath, amsfonts, amssymb, amsthm, amsbsy, amscd, bm, bbm}
\usepackage{amsbsy, amscd, bm, bbm}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[small,bf]{caption}
\setlength{\captionmargin}{30pt}
\usepackage{subcaption}
\captionsetup[sub]{margin=10pt,font=small}
\usepackage{color}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
\usepackage{url}
\usepackage{tocbibind}
\usepackage{enumerate}
\usepackage{mdframed}
\usepackage{comment}

\DeclareMathOperator*{\argmin}{argmin}

% a very useful package for edits and comments, from David Kempe (USC)
\usepackage{color-edits}
%\usepackage[suppress]{color-edits}  % use this to suppress the package
\addauthor{as}{red}      % as for Alex
\addauthor{jm}{blue}     % jm for Jieming
\addauthor{ni}{green}     % ni for Nicole
\addauthor{sw}{magenta}     % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{conjecture}[theorem]{Conjecture}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{remark}{Remark}[section]
%\newtheorem{claim}{Claim}[section]
%\newtheorem{example}{Example}[section]

\newcommand{\term}[1]{\ensuremath{\mathtt{#1}}}
\newcommand{\thread}{\term{thread}}

\newcommand{\DT}{\mD} % Alex' notation for distribution over types.

\def\DKL{\textbf{D}_{\term{KL}}}
\def\D{\mathbb{D}}
\def\E{\mathbb{E}}

\def\A{\mathcal{A}}
\def\M{\mathcal{M}}
\def\S{\mathcal{S}}
\def\X{\mathcal{X}}
\def\EX{\term{EX}}
\def\Ds{*}
\def\EE{\mathcal{E}}
\def\varTheta{\bold{\Theta}}
\def\varOmega{\bold{\Omega}}

\def\ALGG{Greedy }
\def\ALGPG{Parallel Greedy }
\def\2LEVEL{Two-level Policy}
\def\Ber{\emph{Ber} }

\title{Bayesian Exploration with Unbiased History}

\author{
}
\begin{document}
\begin{titlepage}
\maketitle

\thispagestyle{empty}
\begin{abstract}
aaa
\end{abstract}
\end{titlepage}

\input{model}

\section{Social Learning}
\begin{lemma}
\ALGG of $T_c$ rounds pulls each arm w.p. at least $p_c$. 
\end{lemma}

\begin{corollary}
\ALGPG of $c \cdot T_c \cdot \frac{1}{p_c} \cdot \log(1/\delta)$ rounds pulls each at least once w.p. $1-\delta$. \jmcomment{Do we actually need this?}
\end{corollary}

\section{Two-level Recommendation Policy}
Run $T_2$ \ALGG in parallel and then show the later agents the entire history.

\begin{lemma}
For each arm $i$, any $t > 0$ and $\varepsilon \leq 1/2$, let $p$ be the probability that there exists $t \leq \tau \leq T$ such that the empirical mean of the first $\tau$ pulls of arm $i$ is $\varepsilon$ away from $\mu_i$. Then we have 
\[
p \leq \frac{2}{\varepsilon^2} \exp(-2\varepsilon^2 t).
\]
\end{lemma}

\begin{proof}
For each $\tau \in \{t,...,T\}$, let $p_{\tau}$ be the probability that the empirical mean of the first $\tau$ pulls of arm $i$ is $\varepsilon$ away from $\mu_i$. By Chernoff bound, we have
\[
p_{\tau} \leq 2 \exp(-2\varepsilon^2 \tau).
\]

By union bound,
\[
p \leq \sum_{\tau = t}^T p_{\tau} \leq 2 \exp(-2\varepsilon^2 t)  \cdot \frac{1}{1-\exp(-2\varepsilon^2)}.
\]

We know that for any $ x \in [0,1]$, $e^{-x} \leq 1-x/2$. There we have
\[
p \leq  2 \exp(-2\varepsilon^2 t)  \cdot \frac{1}{1-(1-\varepsilon^2)} =  \frac{2}{\varepsilon^2} \exp(-2\varepsilon^2 t).
\]
\end{proof}

\begin{theorem}
\2LEVEL gets expected regret $O(T^{2/3} \log(T)^{1/3})$. If $\delta$, the expected regret is $O(\log(T) \cdot \delta^{-2})$. 
\end{theorem}

\begin{proof}
We will analyze the case when agents after \ALGG only uses empirical mean.
\end{proof}

\section{Multi-level Recommendation Policy}
The $r$-th level of $l$-level policy has number of agents equal to
\[
T^{(2^{l-1}+\cdots+2^{l-r})/(2^{l-1}+2^{l-2}+\cdots + 1)}.
\]
\end{document}

### 2018-08-02 model.tex
Start the draft

%!TEX root = main.tex
\section{Model and Preliminaries}
\label{sec:model}

\emph{Bayesian Exploration} is a game between a principal and $T$ agents who arrive one by one. Each round $t$ proceeds as follows: a new agent $t$ arrives, receives a message $m_t$ from the principal, chooses an action $a_t$ from a fixed action space $\A = \{1,...,K\}$, and collects a reward $r_t\in \{0,1\}$ that is immediately observed by the principal.

Each action $a \in \A$ has a state $\mu_a$ drawn from $\D_a$ before the game starts. For agent in round $t$ who takes action $a_t$, the reward $r_t$ is distributed as $\Ber(\mu_{a_t})$.

The messages $m_t$ are generated according to a randomized online algorithm $\pi$ termed ``recommendation policy".

### 2018-08-13 2level.tex
Update about posterior mean

--- 2018-08-02 main.tex
@@
-\documentclass[11pt]{article}
-\usepackage{fullpage}
-\usepackage{mathrsfs}
-\usepackage{float}
-% ======    PACKAGES
-\usepackage{slivkins-setup,slivkins-theorems}
-%\usepackage{amsmath, amsfonts, amssymb, amsthm, amsbsy, amscd, bm, bbm}
-\usepackage{amsbsy, amscd, bm, bbm}
-\usepackage{array}
-\usepackage{booktabs}
-\usepackage{graphicx}
-\usepackage[small,bf]{caption}
-\setlength{\captionmargin}{30pt}
-\usepackage{subcaption}
-\captionsetup[sub]{margin=10pt,font=small}
-\usepackage{color}
-\usepackage{ifthen}
-\usepackage{xspace}
-\usepackage[noend]{algorithmic}
-\usepackage{algorithm}
-\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
-\usepackage{url}
-\usepackage{tocbibind}
-\usepackage{enumerate}
-\usepackage{mdframed}
-\usepackage{comment}
-
-\DeclareMathOperator*{\argmin}{argmin}
-
-% a very useful package for edits and comments, from David Kempe (USC)
-\usepackage{color-edits}
-%\usepackage[suppress]{color-edits}  % use this to suppress the package
-\addauthor{as}{red}      % as for Alex
-\addauthor{jm}{blue}     % jm for Jieming
-\addauthor{ni}{green}     % ni for Nicole
-\addauthor{sw}{magenta}     % sw for Steven
-% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newtheorem{theorem}{Theorem}[section]
-%\newtheorem{corollary}[theorem]{Corollary}
-%\newtheorem{conjecture}[theorem]{Conjecture}
-%\newtheorem{proposition}[theorem]{Proposition}
-%\newtheorem{definition}[theorem]{Definition}
-%\newtheorem{lemma}[theorem]{Lemma}
-%\newtheorem{remark}{Remark}[section]
-%\newtheorem{claim}{Claim}[section]
-%\newtheorem{example}{Example}[section]
-
-\newcommand{\term}[1]{\ensuremath{\mathtt{#1}}}
-\newcommand{\thread}{\term{thread}}
-
-\newcommand{\DT}{\mD} % Alex' notation for distribution over types.
-
-\def\DKL{\textbf{D}_{\term{KL}}}
-\def\D{\mathbb{D}}
-\def\E{\mathbb{E}}
-
-\def\A{\mathcal{A}}
-\def\M{\mathcal{M}}
-\def\S{\mathcal{S}}
-\def\X{\mathcal{X}}
-\def\EX{\term{EX}}
-\def\Ds{*}
-\def\EE{\mathcal{E}}
-\def\varTheta{\bold{\Theta}}
-\def\varOmega{\bold{\Omega}}
-
-\def\ALGG{Greedy }
-\def\ALGPG{Parallel Greedy }
-\def\2LEVEL{Two-level Policy}
-\def\Ber{\emph{Ber} }
-
-\title{Bayesian Exploration with Unbiased History}
-
-\author{
-}
-\begin{document}
-\begin{titlepage}
-\maketitle
-
-\thispagestyle{empty}
-\begin{abstract}
-aaa
-\end{abstract}
-\end{titlepage}
-
-\input{model}
-
-\section{Social Learning}
-\begin{lemma}
-\ALGG of $T_c$ rounds pulls each arm w.p. at least $p_c$. 
-\end{lemma}
-
-\begin{corollary}
-\ALGPG of $c \cdot T_c \cdot \frac{1}{p_c} \cdot \log(1/\delta)$ rounds pulls each at least once w.p. $1-\delta$. \jmcomment{Do we actually need this?}
-\end{corollary}
-
+%!TEX root = main.tex
 \section{Two-level Recommendation Policy}
-Run $T_2$ \ALGG in parallel and then show the later agents the entire history.
+Run $T_2$ \ALGG in parallel and then show the later agents the history of first $T_2$ rounds.
 
@@
 \end{proof}
-
-\section{Multi-level Recommendation Policy}
-The $r$-th level of $l$-level policy has number of agents equal to
-\[
-T^{(2^{l-1}+\cdots+2^{l-r})/(2^{l-1}+2^{l-2}+\cdots + 1)}.
-\]
-\end{document}

### 2018-08-13 3level.tex
Update about posterior mean

%!TEX root = main.tex

\section{Three-level Recommendation Policy}
The $r$-th level of $l$-level policy has number of agents equal to
\[
T^{(2^{l-1}+\cdots+2^{l-r})/(2^{l-1}+2^{l-2}+\cdots + 1)}.
\]

### 2018-08-13 main.tex
Update about posterior mean

@@
 
+\def\pmn{\hat{\mu}}
+\def\emn{\bar{\mu}}
+
 \title{Bayesian Exploration with Unbiased History}
@@
 
-\section{Two-level Recommendation Policy}
-Run $T_2$ \ALGG in parallel and then show the later agents the entire history.
+\input{2level}
 
-\begin{lemma}
-For each arm $i$, any $t > 0$ and $\varepsilon \leq 1/2$, let $p$ be the probability that there exists $t \leq \tau \leq T$ such that the empirical mean of the first $\tau$ pulls of arm $i$ is $\varepsilon$ away from $\mu_i$.
-Then we have
-\[
-p \leq \frac{2}{\varepsilon^2} \exp(-2\varepsilon^2 t).
-\]
-\end{lemma}
+\input{3level}
 
-\begin{proof}
-For each $\tau \in \{t,...,T\}$, let $p_{\tau}$ be the probability that the empirical mean of the first $\tau$ pulls of arm $i$ is $\varepsilon$ away from $\mu_i$. By Chernoff bound, we have
-\[
-p_{\tau} \leq 2 \exp(-2\varepsilon^2 \tau).
-\]
+\appendix
 
-By union bound,
-\[
-p \leq \sum_{\tau = t}^T p_{\tau} \leq 2 \exp(-2\varepsilon^2 t)  \cdot \frac{1}{1-\exp(-2\varepsilon^2)}.
-\]
-
-We know that for any $ x \in [0,1]$, $e^{-x} \leq 1-x/2$. There we have
-\[
-p \leq  2 \exp(-2\varepsilon^2 t)  \cdot \frac{1}{1-(1-\varepsilon^2)} =  \frac{2}{\varepsilon^2} \exp(-2\varepsilon^2 t).
-\]
-\end{proof}
-
-\begin{theorem}
-\2LEVEL gets expected regret $O(T^{2/3} \log(T)^{1/3})$. If $\delta$, the expected regret is $O(\log(T) \cdot \delta^{-2})$. 
-\end{theorem}
-
-\begin{proof}
-We will analyze the case when agents after \ALGG only uses empirical mean.
-\end{proof}
-
-\section{Multi-level Recommendation Policy}
-The $r$-th level of $l$-level policy has number of agents equal to
-\[
-T^{(2^{l-1}+\cdots+2^{l-r})/(2^{l-1}+2^{l-2}+\cdots + 1)}.
-\]
+\input{posterior}
 \end{document}

### 2018-08-13 posterior.tex
Update about posterior mean

%!TEX root = main.tex
\section{Posterior Mean}

\begin{example}
Let the prior distribution be the uniform distribution over two Bernoulli distributions. Suppose there are $a$ 1's in $n$ samples. Then the posterior mean is $\frac{a+1}{n+2}$ and the empirical mean is $\frac{a}{n}$. Their difference is at most $\frac{1}{n+2}$. 
\end{example}

\begin{example}
Let the prior distribution be the sum of two independent 0-mean Gaussians. The first Gaussian is sampled once and has variance $\alpha^2$. The second Gaussian is sampled for each sample and has variance $\beta^2$. Suppose there are $n$ samples with empirical mean $m$. The posterior mean is $\frac{n \cdot m \cdot \alpha^2}{n \cdot \alpha^2 + \beta^2}$. The difference between the posterior mean and the empirical mean is $\frac{m\beta^2}{n\cdot \alpha^2 + \beta^2}$.
\end{example}

\begin{assumption}
\label{ass:post}
For any arm $i$ and any $m >0$, let $H_m$ be the random variables of $m$ pulls of arm $i$. Let $\emn(H_m)$ be the empirical mean and $\pmn(H_m)$ be the posterior mean. With probability at least $1 - \exp(m)$, we have $|\emn(H_m) - \pmn(H_m)| \leq \frac{1}{m}$. 
\end{assumption}

\begin{lemma}
\label{lem:post}
For any arbitrary strategy of pulling arms for $T$ rounds, let its history to be $G_T$. We allow this strategy to be adaptive based on history. Fix an arm $i$. Let $m_i(G_T)$ be the number of pulls of arm $i$, $\pmn_i(G_T)$ be the posterior mean of arm $i$. Let $H_{m(G_T)}$ be the sub history of arm $i$ in $G_T$. Then $\pmn_i(G_T)$ is the same as the posterior mean of seeing $H_{m_i(G_T)}$ after $m_i(G_T)$ pulls of arm $i$.
\end{lemma}

\begin{proof}
Let's assume there are $m^0_i(G_T)$ 0's and $m^1_i(G_T)$ 1's among of $m_i(G_T)$ pulls of arm $i$ in $G_T$. By the definition of posterior mean, we have
\[
\pmn_i(G_T) = \E[\mu_i|G_T] = \frac{\sum_{x_i} x_i \cdot \Pr[\mu_i=x_i, G_T]}{\sum_{x_i} \Pr[\mu_i=x_i, G_T]}.
\]

We also know that 
\[
\frac{\Pr[\mu_i = x_i, G_T]}{\Pr[\mu_i = x_i', G_T]} = \frac{\Pr[\mu_i = x_i] \cdot  (1-x_i)^{m^0_i(G_T)}x_i^{m^1_i(G_T)}}{\Pr[\mu_i = x_i'] \cdot (1-x_i)^{m^0_i(G_T)}(x_i')^{m^1_i(G_T)} }.
\]

Therefore ,
\[
\pmn_i(G_T) = \frac{\sum_{x_i} x_i \cdot \Pr[\mu_i = x_i] \cdot  (1-x_i)^{m^0_i(G_T)}x_i^{m^1_i(G_T)}}{\sum_{x_i}\Pr[\mu_i = x_i] \cdot  (1-x_i)^{m^0_i(G_T)}x_i^{m^1_i(G_T)}}
\]

Finally, by the definition of posterior mean, the posterior mean of seeing $H_{m_i(G_T)}$ after $m_i(G_T)$ pulls of arm $i$ is
\[
\frac{\sum_{x_i} x_i \cdot \Pr[\mu_i = x_i] \cdot  (1-x_i)^{m^0_i(G_T)}x_i^{m^1_i(G_T)}}{\sum_{x_i}\Pr[\mu_i = x_i] \cdot  (1-x_i)^{m^0_i(G_T)}x_i^{m^1_i(G_T)}} = \pmn_i(G_T).
\]
\end{proof}

\begin{corollary}
\label{cor:post}
For any arbitrary strategy of pulling arms for $T$ rounds, let its history to be $G_T$. We allow this strategy to be adaptive based on history. Fix an arm $i$. Let $m(G_T)$ be the number of pulls of arm $i$, $\emn(G_T)$ be the empirical mean of arm $i$ and $\pmn(G_T)$ be the posterior mean of arm $i$. Let $p_0$ be the probability that $m(G_T) \geq m_0$. With probability $p_0 - 2\exp(m_0)$, $|\emn(G_T) - \pmn(G_T)| \leq \frac{1}{m(G_T)}$.
\end{corollary}

\begin{proof}
Simply by applying Assumption \ref{ass:post}, Lemma \ref{lem:post} and union bound.
\end{proof}

### 2018-08-14 2level.tex
2level

@@
 \section{Two-level Recommendation Policy}
-Run $T_2$ \ALGG in parallel and then show the later agents the history of first $T_2$ rounds.
+Run $T_1$ \ALGG in parallel and then show the later agents the history of first $T_1$ rounds. We will pick $T_1$ in Theorem \ref{thm:2level}.
 
 \begin{lemma}
+\label{lem:2level1}
 For each arm $i$, any $t > 0$ and $\varepsilon \leq 1/2$, let $p$ be the probability that there exists $t \leq \tau \leq T$ such that the empirical mean of the first $\tau$ pulls of arm $i$ is $\varepsilon$ away from $\mu_i$.
@@
 \begin{theorem}
-\2LEVEL gets expected regret $O(T^{2/3} \log(T)^{1/3})$. If $\delta$, the expected regret is $O(\log(T) \cdot \delta^{-2})$. 
+\label{thm:2level}
+With proper setting of $T_1$, \2LEVEL gets expected regret $O(T^{2/3} \log(T)^{1/3})$.
+If we know the gap between the means of the best arm and second best arm is at least $\delta$, the expected regret is $O(\log(T) \cdot \delta^{-2})$.
 \end{theorem}
@@
 \begin{proof}
-We will analyze the case when agents after \ALGG only uses empirical mean.
+The first $T_1 \cdot \GdT$ rounds will get total regret at most $T_1 \cdot \GdT$.
+We focus on the regret of the rest $T - T_1 \cdot \GdT$ rounds.
+We will analyze the regret assuming in these rounds agents just pick the arm with the best empirical mean during the first $T_1 \cdot \GdT$.
+This will give an upper bound to the actual regret as agents choosing the arm with the best posterior mean will get no worse regret.
+
+Let $H$ be the random variable of the history of first $T_1 \cdot \GdT$ rounds.
+By Lemma \ref{lem:greedy}, we know that each arm $i$ has at least $T_1 \cdot \GdP$  pulls in $H$ in expectation.
+By multiplicative Chernoff bound, with probability at least $1 - K \cdot \exp(T_1 \cdot \GdP/8)$, each arm gets at least $\frac{1}{2} \cdot T_1 \cdot \GdP$ pulls in $H$.
+
+Suppose we are in the case that each arm gets at least $\frac{1}{2} \cdot T_1 \cdot \GdP$ pulls in $H$.
+By Lemma \ref{lem:2level1}, we know that, with probability $1- \frac{2K}{\varepsilon^2} \cdot \exp(-\varepsilon^2 \cdot T_1 \cdot \GdP)$, for all arm $i$, the empirical mean of arm $i$ in $H$, $\emn_i(H)$ satisfies that $|\emn_i(H) - \mu_i| < \varepsilon$.
+
+Therefore with probability at least $ 1- K \cdot \exp(T_1 \cdot \GdP/8) - \frac{2K}{\varepsilon^2} \cdot \exp(-\varepsilon^2 \cdot T_1 \cdot \GdP)$, the regret in the last $T - T_1 \cdot \GdT$ rounds is at most $(T-T_1 \cdot \GdT) \cdot (2\varepsilon )$.
+Therefore the total regret in expectation is at most
+\[
+T_1 \cdot \GdT + 2T\varepsilon + T \cdot \left(K \cdot \exp(T_1 \cdot \GdP/8) + \frac{2K}{\varepsilon^2} \cdot \exp(-\varepsilon^2 \cdot T_1 \cdot \GdP)\right).
+\]
+By setting $T_1 =\frac{2}{\GdP}\cdot T^{2/3} \log(T)^{1/3}$ and $\varepsilon = T^{-1/3} \log(T)^{1/3}$, the above term is $O(T^{2/3}\log(T)^{1/3})$.
+
+Suppose we know the gap between the means of the best arm and second best arm is at least $\delta$, we can set $\varepsilon = \delta/2$ and with probability at least $1- K \cdot \exp(T_1 \cdot \GdP/8) - \frac{2K}{\varepsilon^2} \cdot \exp(-\varepsilon^2 \cdot T_1 \cdot \GdP)$, the arm with the best empirical mean in the first $T_1 \cdot \GdT$ rounds is the arm with the highest mean.
+Therefore the regret in expectation is at most
+\[
+T_1 \cdot \GdT + \cdot \left(K \cdot \exp(T_1 \cdot \GdP/8) + \frac{2K}{\varepsilon^2} \cdot \exp(-\varepsilon^2 \cdot T_1 \cdot \GdP)\right).
+\]
+By setting $T_1 = \frac{3\log(T) }{\varepsilon^2 \GdP}$, the above term is $O(\log(T) \cdot \delta^{-2})$. 
 \end{proof}

### 2018-08-21 posterior.tex
Some change to posterior part

@@
 \begin{example}
-Let the prior distribution be the uniform distribution over two Bernoulli distributions.
+Let the prior distribution be the uniform distribution over Bernoulli distributions.
 Suppose there are $a$ 1's in $n$ samples.
@@
 Their difference is at most $\frac{1}{n+2}$.
+\end{example}
+
+\begin{example}
+Let the prior distribution be the uniform distribution over Bernoulli distributions with mean between $1/3$ and $2/3$.
+Suppose we have $n$ samples.
+With probability at least $\Omega(1/\sqrt{n})$, the difference between empirical mean and posterior mean is larger than $1/\sqrt{n}$.
 \end{example}

### 2018-08-30 3level.tex
3-level proof

@@
 \section{Three-level Recommendation Policy}
-The $r$-th level of $l$-level policy has number of agents equal to
+In this section, we show how to get $o(T^{2/3})$ regret with a 3-level recommendation policy. For simplicity, we assume there are only 2 arms.
+
+For 3-level recommendation policy, set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 = T^{6/7}\log^{-5/7}(T)$.
+The first level has $S = 2^10\log(T)$ groups of agents.
+Each group runs $T_1$ \ALGG of $T_G$ rounds in parallel.
+The second level also has $S$ groups of agents.
+Each group has $T_2$ agents and they observe the history of corresponding group in the first level.
+All the rest agents are in the third level and they observe the entire history of the first two levels.
+
+Needs to draw a figure here.
+
+\begin{theorem}
+The 3-level recommendation policy gets expected regret $O(T^{4/7} \log^{6/7}(T))$. 
+\end{theorem}
+
+\begin{proof}
+Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We do a case analysis based on $\mu_1-\mu_2$. (some intuition and explanation of these cases?)
+
+Before we start with the case analysis, we first define several clean events and show that the intersection of them happens with high probability. 
+\begin{itemize}
+\item For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
+By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$ group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$.
+By Chernoff bound,
 \[
-T^{(2^{l-1}+\cdots+2^{l-r})/(2^{l-1}+2^{l-2}+\cdots + 1)}.
+\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
 \]
+Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
+\[
+\Pr[W_1] \geq 1- \frac{4S}{T^2}.
+\]
+\item For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$.
+For the $s$-th first-level group and arm $a$, define $W_2^{s,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away from $\mu_a$.
+By Chernoff bound,
+\[
+\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
+\]
+
+Define $W_2$ to be the intersection of all these events (i.e. $W_2 = \bigcap_{a,s,t_1,t_2} W_2^{s,a,t_1,t_2}$). By union bound, we have
+\[
+\Pr[W_2] \geq 1- \frac{4S}{T^2}.
+\]
+
+\item For all the groups in the first two levels and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in the first two levels pull arm $a$.
+Define $W_3^{a,t}$ to be the event that the mean of the first $t$ pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.
+
+By Chernoff bound, 
+\[
+\Pr[W_3^{a,t}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
+\]
+Define $W_3$ to be the intersection of all these events (i.e. $W_3 = \bigcap_{a,t} W_3^{a,t}$). By union bound, we have
+\[
+\Pr[W_3] \geq 1- \frac{4}{T^3}.
+\]
+
+\item Consider the tapes defined in the second bullet again.
+For the $s$-th first-level group and arm $a$, define $W_4^{s,a,high}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1}$ and define  $W_4^{s,a,low}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1}$.
+By Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
+\[
+\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1}} > 1/4.
+\]
+The last inequality follows when $T$ is large than some constant.
+Similarly we also have 
+\[
+\Pr[W_4^{s,a,low}] > 1/4.
+\]
+Since $W_4^{s,a,high}$ is independent with $W_4^{s,3-a,low}$, we have
+\[
+\Pr[W_4^{s,a,high} \cap W_4^{s,3-a,low}] =\Pr[W_4^{s,a,high}] \cdot  \Pr[W_4^{s,3-a,low}]>(1/4)^2 = 1/16.
+\]
+Now define $W_4$ as $\bigcap_a \bigcup_s (W_4^{s,a,high} \cap W_4^{s,3-a,low})$. Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent across different $s$'s. So by union bound, we have
+\[
+\Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
+\]
+\end{itemize}
+
+By union bound, the intersection of these clean events (i.e.
+$\bigcap_{i=1}^4 W_i$) happens with probability $1-O(1/T)$.
+When this intersection does not happen, since the probability is $O(1/T)$, it cost expected regret $O(1/T) \cdot T = O(1)$.
+
+Now we assume the intersection of clean events happens and we summarize what these clean events imply.
+
+\begin{itemize}
+\item For the $s$-th first-level group and arm $a$, define $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in this group.
+$W_1^{a,s}$, $W_2^{a,s,1,t}$ for $ = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1- \GdT \sqrt{T_1\log(T)}$ together imply that
+\[
+|\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_a T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
+\]
+The last inequality holds when $T$ is larger than some constant.
+\item For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of arm $a$ pulls in the first two levels.
+$W_1^{a,s}$ for $s=1,...,S$ and $W_3^{a,t}$ for $t \geq  (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
+\[
+|\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(q_a T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
+\]
+The last inequality holds when $T$ larger than some constant.
+
+If there are at least $T_2$ pulls of arm $a$ in the first two levels, 
+\[
+|\bar{\mu}_a-\mu_a| \leq \sqrt{\frac{2\log(T)}{T_2}}. 
+\]
+
+\item For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such that $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.
+$W_4^{s_a,a,high}$,  $W_1^{s_a,a}$, $W_2^{s,a,t, q_aT_1}$ for $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and $W_2^{s,a,q_aT_1,t}$ for $t= q_aT_1,...,q_a T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
+\begin{align*}
+\bar{\mu}_a ^{1,s_a} &\geq \mu_a + \left(q_aT_1 \cdot \frac{1}{\sqrt{q_aT_1}} - \GdT \sqrt{T_1\log(T)} \cdot \sqrt{\frac{2\log(T)}{ \GdT \sqrt{T_1\log(T)}}} \right) \cdot \frac{1}{q_a T_1+ \GdT \sqrt{T_1\log(T)}} \\
+&> \mu_a + \frac{1}{4\sqrt{q_aT_1}}.
+\end{align*}
+The second last inequality holds when $T$ larger than some constant.
+Similarly, we also have
+\[
+\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
+\]
+\end{itemize}
+
+Finally we proceed to the case analysis. We give upper bounds on the expected regret conditioned on the intersection of clean events.
+
+\begin{itemize}
+\item $\mu_1 - \mu_2 \geq 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
++ \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. In this case, we want to show that agents in the second and the third levels all pull arm 1.
+
+First consider the $s$-th second-level group. We know that 
+\[
+\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{q_1T_1}} - \sqrt{\frac{4\log(T)}{q_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} 
++ \sqrt{\frac{4\log(T)}{q_2T_1}}.
+\]
+By Assumption \ref{ass:embehave}, we know agents in the $s$-th second-level group will all pull arm 1.
+
+Now consider the agents in the third level group. Recall $\bar{\mu}_a$ is the empirical mean of arm $a$ in the history they see. We have
+\[
+\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} 
++ \sqrt{\frac{4\log(T)}{q_2T_1}}.
+\]
+By Assumption \ref{ass:embehave}, we know agents in the third-level group will all pull arm 1.
+
+Therefore the expected regret is at most $S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$.
+
+\item $2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
++ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq \mu_1-\mu_2 < 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
++ \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. In this case, we want to show agents in the third level all pull arm 1. Recall $\bar{\mu}_a$ is the empirical mean of arm $a$ in the first two levels. We have
+\[
+\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} 
++ \sqrt{\frac{4\log(T)}{Sq_2T_1}}.
+\]
+By Assumption \ref{ass:embehave}, we know agents in the third-level group will all pull arm 1.
+Therefore the expected regret is at most 
+\[
+(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
++ \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
+\]
+
+\item $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 < 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
++ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.
+In this case, we just need to make sure that agents in the third level all pull arm 1.
+To do so, we need both arms to be pulled at least $T_2$ rounds in the second level.
+
+Now consider the $s_a$-th second-level group. We have
+\begin{align*}
+\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} &> \mu_a + \frac{1}{4\sqrt{q_aT_1}} -\mu_{3-a} +\frac{1}{4\sqrt{q_{3-a}T_1}} \\
+&> \frac{1}{4\sqrt{q_1T_1}}+ \frac{1}{4\sqrt{q_2T_1}} - 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
++ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \\
+&\geq \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}.
+\end{align*}
+By Assumption \ref{ass:embehave}, we know agents in the $s_a$-th second-level group will all pull arm $a$.
+Therefore in the first two levels, both arms are pulled at least $T_2$ times.
+Now consider the third-level.
+We have
+\[
+\bar{\mu}_1 - \bar{\mu}_2  \geq \mu_1 -\mu_2 - 2\sqrt{\frac{2\log(T)}{T_2}} \geq \sqrt{\frac{2\log(T)}{T_2}}.
+\]
+By Assumption \ref{ass:embehave}, we know agents in the third-level group will all pull arm 1.
+
+Therefore the expected regret is at most 
+\[
+(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
++ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
+\]
+
+\item $\mu_1 - \mu_2 \leq 3\sqrt{\frac{2\log(T)}{T_2}}$.
+This is the easy case.
+Even always pulling the sub-optimal arm (i.e.
+arm 2) gives regret at most $T \cdot (\mu_1-\mu_2) = O(T^{4/7} \log^{6/7}(T))$.
+\end{itemize}
+
+\end{proof}

### 2018-08-30 model.tex
Add some examples about posterior mean
Update about posterior mean
3-level proof

@@
 %!TEX root = main.tex
-\section{Model and Preliminaries}
+\section{Our Model}
 \label{sec:model}
@@
 The messages $m_t$ are generated according to a randomized online algorithm $\pi$ termed ``recommendation policy".
+
+\xhdr{Restrictions on the messages.} We classify recommendation policies according to what messages are allowed. 
+\begin{itemize}
+\item Full History: 
+\item Unbiased Sub-history: 
+\end{itemize}
+
+\begin{remark}
+Why not arbitrary sub-history?
+\end{remark}
+
+\xhdr{Agents behavior.} We assumes agent estimates the mean of each arm as $\hat{\mu}_a$'s and pick the arm with the best $\hat{\mu}_a$'s.
+For each agent, we also define $\bar{\mu}_a$ as the empirical average of arm $a$ given the history and we make the following assumption:
+\begin{assumption}
+\label{ass:embehave}
+Let constant $c_m = 0.00001$. For each agent $t$ and arm $a$, if arm $a$ has been pulled $t_a$ times in the history, then
+\[
+|\hat{\mu}^t_a - \bar{\mu}^t_a | < \frac{c}{\sqrt{t_a}}.
+\]
+\end{assumption}

### 2018-08-30 prelim.tex
3-level proof

%!TEX root = main.tex
\section{Preliminaries}
\label{sec:prelim}

\begin{theorem}[Chernoff Bound]
Let $X_1,...,X_n$  be independent random variables such that $X_i \in [0,1]$ for all $i$. Let $\bar{X} = \frac{1}{n}\sum_{i=1}^n X_i$ denote their empirical mean. Then
\[
\Pr[ |\bar{X} - \E[\bar{X}]| > \varepsilon] \leq 2\exp(-2n\varepsilon^2).
\]
\end{theorem}

\begin{theorem}[Berry-Essen Theorem]
Let $X_1,...,X_n$ be i.i.d. variables with $\E[ (X_1 - \E[X_1])^2] = \sigma^2 >0$ and $\E[ |X_1 - \E[X_1]|^3] =\rho <\infty$. Let $\bar{X} = \frac{1}{n} \sum_{i=1}^n X_i$. Let $F_n$ be the cumulative distribution function of $\frac{(\bar{X} - \E[\bar{X}]) \sqrt{n}}{\sigma}$ and $\Phi$ be the cumulative distribution function of the standard normal distribution. For all $x$ and $n$,
\[
|F_n(x) - \Phi(x) | \leq \frac{\rho}{2\sigma^3\sqrt{n}}.
\]
\end{theorem}

### 2018-09-04 llevel.tex
Start >3 level proof

%!TEX root = main.tex

\section{$L$-level Recommendation Policy}
In this section, we design an $L$-level recommendation policy for $L > 3$. By having more than 3 levels, we get even smaller regret.

Our recommendation policy has $L$ levels and each level has $S^2$ groups for $S = \log(T)$. Label the groups in the $l$-th level as $G_{l,a,b}$ for $a,b \in [S]$.

We set the group size as following. For $l < L$,
\[
T_l = T^{\frac{2^{L-1} + 2^{L-2} + \cdots + 2^{L-l}}{2^{L-1}+ 2^{L-2} + \cdots + 1}}.
\]
and 
\[
T_L = T/S^2 - T_1 \cdot \GdT - T_2 - \cdots - T_{l-1}. 
\]
Each first-level group ($G_{1,a,b}$ for $a,b\in [S]$) has $T_1$ \ALGG runs in parallel. For $l \geq 2$, there are $T_l$ agents in group $G_{l,a,b}$. $T_L$ is a little bit different because we want total number of agents to be $T$.

Finally we define the information flow. Agents in the first level only observe the history defined in the \ALGG. For agents in group $G_{l,a,b}$ with $l\geq 2$, they observe all the history in the first $l-2$ levels and history in group $G_{l-1,b,c}$ for all $c \in [S]$. For agents which are not in the first level, if they are in the same group, they observe the same history.

\begin{theorem}
The $L$-level recommendation policy gets expected regret $O\left(T^{\frac{2^{L-1}}{2^L-1}} \log^2(T) L \right)$. In particular, if we pick $L = \log\log(T)$, then we get regret $O(T^{1/2} \log^2(T) \log\log(T))$.  
\end{theorem}

\begin{proof}

\end{proof}

### 2018-09-11 3level.tex
Finish L-level proof

@@
 For 3-level recommendation policy, set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 = T^{6/7}\log^{-5/7}(T)$.
-The first level has $S = 2^10\log(T)$ groups of agents.
+The first level has $S = 2^{10}\log(T)$ groups of agents.
 Each group runs $T_1$ \ALGG of $T_G$ rounds in parallel.
@@
 \begin{theorem}
+\label{thm:3level}
 The 3-level recommendation policy gets expected regret $O(T^{4/7} \log^{6/7}(T))$. 
@@
 \item For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
-By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$ group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$.
+By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$.
 By Chernoff bound,
@@
 \]
-The last inequality follows when $T$ is large than some constant.
+The last inequality follows when $T$ is larger than some constant.
 Similarly we also have 
@@
 \item For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such that $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.
-$W_4^{s_a,a,high}$,  $W_1^{s_a,a}$, $W_2^{s,a,t, q_aT_1}$ for $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and $W_2^{s,a,q_aT_1,t}$ for $t= q_aT_1,...,q_a T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
+$W_4^{s_a,a,high}$,  $W_1^{s_a,a}$, $W_2^{s_a,a,t, q_aT_1}$ for $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and $W_2^{s_a,a,q_aT_1,t}$ for $t= q_aT_1,...,q_a T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
 \begin{align*}
@@
 \[
-\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{q_1T_1}} - \sqrt{\frac{4\log(T)}{q_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{q_2T_1}}.
+\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{q_1T_1}} - \sqrt{\frac{4\log(T)}{q_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}.
 \]
-By Assumption \ref{ass:embehave}, we know agents in the $s$-th second-level group will all pull arm 1.
+For any agent $t$ in the $s$-th second-level group, by Assumption \ref{ass:embehave}, we have
+\begin{align*}
+\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
+&\geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
+ &> 0.
+\end{align*}
+Therefore, we know agents in the $s$-th second-level group will all pull arm 1.
 
@@
 \]
-By Assumption \ref{ass:embehave}, we know agents in the third-level group will all pull arm 1.
-
+Similarly as above, by Assumption \ref{ass:embehave}, we know $\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third level.
+So we know agents in the third-level group will all pull arm 1.
 Therefore the expected regret is at most $S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$.
@@
 \]
-By Assumption \ref{ass:embehave}, we know agents in the third-level group will all pull arm 1.
-Therefore the expected regret is at most 
+For any agent $t$ in the third level, by Assumption \ref{ass:embehave}, we have
+\begin{align*}
+\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
+&\geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} + \sqrt{\frac{4\log(T)}{Sq_2T_1}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
+ &> 0.
+\end{align*}
+So we know agents in the third-level group will all pull arm 1. Therefore the expected regret is at most 
 \[
@@
 \end{align*}
-By Assumption \ref{ass:embehave}, we know agents in the $s_a$-th second-level group will all pull arm $a$.
-Therefore in the first two levels, both arms are pulled at least $T_2$ times.
-Now consider the third-level.
-We have
+For any agent $t$ in the $s_a$-th second-level group, by Assumption \ref{ass:embehave}, we have
+\begin{align*}
+\hat{\mu}_a^t - \hat{\mu}_a^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_a^{1,s_a} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
+&\geq   \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
+ &> 0.
+\end{align*}
+So we know agents in the $s_a$-th second-level group will all pull arm $a$. Therefore in the first two levels, both arms are pulled at least $T_2$ times. Now consider the third-level. We have
 \[
@@
 \]
-By Assumption \ref{ass:embehave}, we know agents in the third-level group will all pull arm 1.
+Similarly as above, by Assumption \ref{ass:embehave}, we know $\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third level. So we know agents in the third-level group will all pull arm 1.
 

### 2018-09-11 llevel.tex
Finish L-level proof

@@
 \section{$L$-level Recommendation Policy}
-In this section, we design an $L$-level recommendation policy for $L > 3$. By having more than 3 levels, we get even smaller regret.
+In this section, we design an $L$-level recommendation policy for $L > 3$ and 2 arms. By having more than 3 levels, we get even smaller regret.
 
-Our recommendation policy has $L$ levels and each level has $S^2$ groups for $S = \log(T)$. Label the groups in the $l$-th level as $G_{l,a,b}$ for $a,b \in [S]$.
+Our recommendation policy has $L$ levels and two types of groups: $G$-groups and $\Gamma$-groups.
+Each level has $S^2$ $G$-groups for $S = 2^{10}\log(T)$.
+Label the $G$-groups in the $l$-th level as $G_{l,u,v}$ for $u,v \in [S]$.
+Level $2$ to level $L$ also have $S^2$ $\Gamma$-groups.
+Label the $\Gamma$-groups in the $l$-th level as $\Gamma_{l,u,v}$ for $u,v \in [S]$.
 
@@
 \[
-T_l = T^{\frac{2^{L-1} + 2^{L-2} + \cdots + 2^{L-l}}{2^{L-1}+ 2^{L-2} + \cdots + 1}}.
+T_l = T^{\frac{2^{L-1} + 2^{L-2} + \cdots + 2^{L-l}}{2^{L-1}+ 2^{L-2} + \cdots + 1}}/S^3.
 \]
@@
 \[
-T_L = T/S^2 - T_1 \cdot \GdT - T_2 - \cdots - T_{l-1}. 
+T_L = (T - T_1 \cdot \GdT\cdot S^2 - (T_2 + \cdots + T_{l-1}) S^3) /S^3
 \]
-Each first-level group ($G_{1,a,b}$ for $a,b\in [S]$) has $T_1$ \ALGG runs in parallel.
-For $l \geq 2$, there are $T_l$ agents in group $G_{l,a,b}$.
+We restrict $L$ to be at most $\log(\ln(T)/\log(10S^3))$ so that $T_l / T_{l-1} \geq T^{1/2^L} \geq 10S^3$ for $l = 2,...,L-1$.
 $T_L$ is a little bit different because we want total number of agents to be $T$.
 
+Each first-level group ($G_{1,u,v}$ for $u,v\in [S]$) has $T_1$ \ALGG runs in parallel.
+For $l \geq 2$, there are $T_l$ agents in group $G_{l,u,v}$ and there are $T_l (S-1)$ agents in group $\Gamma_{l,u,v}$.
+
 Finally we define the information flow.
-Agents in the first level only observe the history defined in the \ALGG.
-For agents in group $G_{l,a,b}$ with $l\geq 2$, they observe all the history in the first $l-2$ levels and history in group $G_{l-1,b,c}$ for all $c \in [S]$.
-For agents which are not in the first level, if they are in the same group, they observe the same history.
+Agents in the first level only observe the history defined in the \ALGG run.
+For agents in group $G_{l,u,v}$ with $l\geq 2$, they observe all the history in the first $l-2$ levels (both $G$-groups and $\Gamma$-groups) and history in group $G_{l-1,v,w}$ for all $w \in [S]$.
+Agents in group $\Gamma_{l,u,v}$ observe the same history as agents in group $G_{l,u,v}$.
 
 \begin{theorem}
-The $L$-level recommendation policy gets expected regret $O\left(T^{\frac{2^{L-1}}{2^L-1}} \log^2(T) L \right)$.
-In particular, if we pick $L = \log\log(T)$, then we get regret $O(T^{1/2} \log^2(T) \log\log(T))$.
+The $L$-level recommendation policy gets expected regret $O\left(T^{\frac{2^{L-1}}{2^L-1}} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(10S^3))$.
+In particular, if we pick $L = \log(\ln(T)/\log(10S^3))$, the expected regret is at most $O(T^{1/2} \log^5(T))$.
 \end{theorem}
@@
 \begin{proof}
+Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. Similarly as the proof of Theorem \ref{thm:3level}, we start with some clean events.
 
+\begin{itemize}
+\item For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
+By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ For group $G_{1,u,v}$, define $W_1^{a,u,v}$ to be the event that the number of arm $a$ pulls in this group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$.
+By Chernoff bound,
+\[
+\Pr[W_1^{a,u,v}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
+\]
+Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,u,v}W_1^{a,u,v}$). By union bound, we have
+\[
+\Pr[W_1] \geq 1- \frac{4S^2}{T^2}.
+\]
+
+\item For each agent $t$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in agent $t$'s observed history pull arm $a$.
+Define $W_2^{t,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{3\log(T)}{t_2-t_1+1}}$ away from $\mu_a$.
+By Chernoff bound,
+\[
+\Pr[W_2^{t,a,t_1,t_2}] \geq 1 - 2\exp(-6\log(T)) \geq 1- 2/T^6.
+\]
+
+Define $W_2$ to be the intersection of all these events (i.e. $W_2 = \bigcap_{t,a,t_1,t_2} W_2^{t,a,t_1,t_2}$). By union bound, we have
+\[
+\Pr[W_2] \geq 1- \frac{4}{T^3}.
+\]
+
+\item For $2\leq l \leq L-1$, $u\in [S]$ and each arm $a$, define $n^{l,u,a}$ to be the number of arm $a$ pulls in groups $G_{l,u,1},...,G_{l,u,S}$.
+Define $W_3^{l,u,a,high}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at least $\mu_a + 1/\sqrt{n^{l,u,a}}$.
+Define $W_3^{l,u,a,low}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at most $\mu_a - 1/\sqrt{n^{l,u,a}}$.
+
+Define $H_l$ to be random variable the history of all agents in the first $l-1$ levels and which agents are chosen in the $l$-th level.
+Let $h_l$ be some realization of $H_l$.
+Notice that once we fix $H_l$, $n^{l,u,a}$ is also fixed.
+
+Now consider $h_l$ to be any possible realized value of $H_l$.
+If fixing $H_l= h_l$ makes $n^{l,u,a}<T_l$, then $\Pr[W_3^{l,u,a,high} |H_l = h_l]=1$  If fixing $H_l = h_l$ makes $n^{l,u,a} \geq T_l$, by Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
+\[
+\Pr[W_3^{l,u,a,high}|H_l = h_l] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{T_l}} > 1/4.
+\]
+Similarly we also have
+\[
+\Pr[W_3^{l,u,a,low}|H_l = h_l]  > 1/4
+\]
+Since $W_3^{l,u,a,high}$ is independent with $W_3^{l,u,3-a,low}$ when fixing $H_l$, we have
+\[
+\Pr[ W_3^{l,u,a,high} \cap W_3^{l,u,3-a,low}|H_l = h_l]  > (1/4)^2 = 1/16.
+\]
+Now define $W_3^{l,a} = \bigcup_u (W_3^{l,u,a,high} \cap W_3^{l,u,3-a,low})$. Since  $(W_3^{l,u,a,high} \cap W_3^{l,u,3-a,low})$ are independent across different $u$'s when fixing $H_l=h_l$, we have
+\[
+\Pr[W_3^{l,a}|H_l= h_l] \geq 1- (1-1/16)^S \geq 1 - 1/T^2.
+\]
+Since this holds for all $h_l$'s, we have $\Pr[W_3^{l,a}] \geq 1-1/T^2$. Finally define $W_3 = \bigcap_{l,a} W_3^{l,a}$. By union bound, we have
+\[
+W_3 \geq 1 - 2L/T^2.
+\]
+
+\item For first-level groups $G_{1,u,1},...,G_{1,u,S}$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in these groups pull arm $a$.
+Define $W_4^{u,a,high}$  to be the event that first $q_a T_1 S$ pulls of arm $a$ in the tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1 S}$ and define $W_4^{u,a,low}$  to be the event that first $q_a T_1S$ pulls of arm $a$ in the tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1S }$.
+By Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
+\[
+\Pr[W_4^{u,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1S}} > 1/4.
+\]
+The last inequality follows when $T$ is larger than some constant.
+Similarly we also have 
+\[
+\Pr[W_4^{u,a,low}] > 1/4.
+\]
+Since $W_4^{u,a,high}$ is independent with $W_4^{u,3-a,low}$, we have
+\[
+\Pr[W_4^{u,a,high} \cap W_4^{u,3-a,low}] =\Pr[W_4^{u,a,high}] \cdot  \Pr[W_4^{u,3-a,low}]>(1/4)^2 = 1/16.
+\]
+Now define $W^{a}_4$ as $\bigcup_u (W_4^{u,a,high} \cap W_4^{u,3-a,low})$. Notice that $(W_4^{u,a,high} \cap W_4^{u,3-a,low})$ are independent across different $u$'s. So we have
+\[
+\Pr[W^{a}_4] \geq 1- (1-1/16)^S \geq 1 -1/T^2.
+\]
+Finally we define $W_4$ as $\bigcap_{a} W^{a}_4$. By union bound,
+\[
+\Pr[W_4] \geq 1- 2/T^2.
+\]
+\end{itemize}
+
+By union bound, the intersection of these clean events (i.e.
+$\bigcap_{i=1}^4 W_i$) happens with probability $1-O(1/T)$.
+When this intersection does not happen, since the probability is $O(1/T)$, it cost expected regret $O(1/T) \cdot T = O(1)$.
+
+Now we assume the intersection of clean events happens and prove upper bound on the expected regret.
+
+By event $W_1$, we know that in each first-level group, there are at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$ pulls of arm $a$.
+We prove in the next claim that there are enough pulls of both arms in higher levels if $\mu_1-\mu_2$ is small enough.
+For notation convenience, we set $\varepsilon_0 = 1$, $\varepsilon_1 = \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}$ and $\varepsilon_l = 1/(4\sqrt{T_lS})$ for $l \geq 2$.
+
+\begin{claim}
+\label{clm:l2_explore}
+For any arm $a$ and $2\leq l \leq L$, if $\mu_1 - \mu_2 \leq \varepsilon_{l-1}$, then for any $u \in [S]$, there are at least $T_l$ pulls of arm $a$ in groups $G_{l,u,1},G_{l,u,2}, ...
+,G_{l,u,S}$ and there are at least $T_lS(S-1)$ pulls of arm $a$ in the $l$-th level $\Gamma$-groups.
+\end{claim}
+
+\begin{proof}
+We are going to show that for each $l$ and $a$ there exists $u_a$ such that agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$.
+This suffices to prove the claim.
+
+We prove the above via induction on $l$.
+%For notation convenience, define $\bar{\mu}^{l,u}_a$  to be the empirical mean of arm $a$ pulls in the history observed by agents in groups $G_{l,1,u},...,G_{l,S,u}$ and $\Gamma_{l,1,u},...,\Gamma_{l,S,u}$ (they observe the same history).
+We start by the base case when $l=2$.
+For each arm $a$, $W_4$ implies there exists $u_a$ such that $W^{u_a,a,high}_4$ and $W^{u_a,3-a,low}_4$ happen.
+For an agent $t$  in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$.
+$W_4^{u_a,a,high}$,  $W_1^{a,u_a,v}$ and $W_2$ together imply that 
+\begin{align*}
+\bar{\mu}_a ^t &\geq \mu_a + \left(q_aT_1S \cdot \frac{1}{\sqrt{q_aT_1S}} - \GdT \sqrt{T_1\log(T)} S\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}S}} \right) \cdot \frac{1}{(q_a T_1+ \GdT \sqrt{T_1\log(T)})S} \\
+&> \mu_a + \frac{1}{4\sqrt{q_aT_1S}}.
+\end{align*}
+The second last inequality holds when $T$ larger than some constant.
+Similarly, we also have
+\[
+\bar{\mu}_{3-a}^t< \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1S}}.
+\]
+Then we have
+\begin{align*}
+\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a} + \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}\\
+&\geq -\varepsilon_1+ \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}\\
+&\geq \frac{1}{8\sqrt{q_aT_1S}} + \frac{1}{8\sqrt{q_{3-a} T_1S}}.
+\end{align*}
+By Assumption \ref{ass:embehave}, we have
+\begin{align*}
+\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{c_m}{\sqrt{q_aT_1S/2}} - \frac{c_m}{\sqrt{q_{3-a} T_1S/2}}\\
+&> \frac{1}{8\sqrt{q_aT_1S}} + \frac{1}{8\sqrt{q_{3-a} T_1S}} -   \frac{c_m}{\sqrt{q_aT_1S/2}} - \frac{c_m}{\sqrt{q_{3-a} T_1S/2}}\\
+&>0.
+\end{align*}
+The last inequality holds since $c_m$ is a small enough constant defined in Assumption \ref{ass:embehave}.
+Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{l,1,u},...,\Gamma_{l,S,u}$ all pull arm $a$.
+
+Now we consider the case when $l > 2$ and assume the claim is true for smaller $l$'s.
+For each arm $a$, $W_3$ implies that there exists $u_a$ such that $W^{l-1,u_a,a,high}_3$ and $W^{l-1,u_a,3-a,low}_3$ happen.
+Recall $n^{l-1,u_a,a}$ is the number of arm $a$ pulls in groups $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$.
+The induction hypothesis implies that $n^{l-1,u_a,a} \geq T_{l-1}$.
+$W^{l-1,u_a,a,high}_3$ together with $n^{l-1,u_a,a} \geq T_{l-1}$ implies that the empirical mean of arm $a$ pulls in group $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$ is at least $\mu_a + 1/\sqrt{n^{l-1,u_a,a}}$.
+For any agent $t$ in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$, it observes history of groups $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$ and all groups in levels below level $l-1$.
+Notice that the groups in the first $l-2$ levels have $(T_1 \GdT + T_2 + \cdots +T_{l-2})S^3 \leq T_{l-1}/(12\log(T)) \leq n^{l-1,u_a,a}/(12\log(T))$ agents.
+By $W_2$, we have
+\begin{align*}
+\bar{\mu}_a ^t &\geq \mu_a + \left(n^{l-1,u_a,a}  \cdot \frac{1}{\sqrt{n^{l-1,u_a,a} }}- (T_1 \GdT + T_2 + \cdots +T_{l-2})S^2\cdot \sqrt{\frac{3\log(T)}{ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^2}} \right) \\
+&~~~\cdot \frac{1}{n^{l-1,u_a,a}+ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^2} \\
+&> \mu_a + \frac{1}{4\sqrt{n^{l-1,u_a,a}  }}.
+\end{align*}
+The third last inequality holds when $T$ larger than some constant.
+Similarly, we also have
+\[
+\bar{\mu}_{3-a}^t < \mu_{3-a}   -\frac{1}{4\sqrt{n^{l-1,u_a,3-a}  }}.
+\]
+Then we have
+\begin{align*}
+\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a}+ \frac{1}{4\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{4\sqrt{n^{l-1,u_a,3-a}  }}\\
+&\geq -\varepsilon_{l-1}+ \frac{1}{4\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{4\sqrt{n^{l-1,u_a,3-a}  }}\\
+&\geq \frac{1}{8\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{8\sqrt{n^{l-1,u_a,3-a}  }}.
+\end{align*}
+The last inequality holds because $n^{l-1,u_a,a}$ and $n^{l-1,u_a,3-a}$ are at most $T_{l-1} S$. By Assumption \ref{ass:embehave}, we have
+\begin{align*}
+\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{c_m}{\sqrt{n^{l-1,u_a,a} }} - \frac{c_m}{\sqrt{n^{l-1,u_a,3-a}}}\\
+&> \frac{1}{8\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{8\sqrt{n^{l-1,u_a,3-a}  }} -  \frac{c_m}{\sqrt{n^{l-1,u_a,a} }} - \frac{c_m}{\sqrt{n^{l-1,u_a,3-a}}}\\
+&>0.
+\end{align*}
+The last inequality holds since $c_m$ is a small enough constant defined in Assumption \ref{ass:embehave}.
+Therefore agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$.
 \end{proof}
+
+\begin{claim}
+\label{clm:l2_exploit}
+For any $2 \leq l \leq L$, if $\varepsilon_{l-1} S < \mu_1 - \mu_2 < \varepsilon_{l-2} S$, there are no pulls of arm 2 in groups with level $l,...,L$. 
+\end{claim}
+
+\begin{proof}
+We argue in 2 cases $\varepsilon_{l-1} \sqrt{S} \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l \geq 2$ and $\varepsilon_{l-2}  \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2} \sqrt{S}$ for $l > 2$.
+Since our recommendation policy's first level is slightly different from other levels, we need to argue case $\varepsilon_{l-1} \sqrt{S} \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l=2$ and case $\varepsilon_{l-2}  \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2} \sqrt{S}$ for $l =3$ separately.
+
+\begin{itemize}
+\item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l > 2$(i.e.
+$\varepsilon_1S\leq \mu_1 - \mu_2 \leq \varepsilon_0$): We know agents in level at least 2 will observe at least $q_aT_1/2$ pulls of arm $a$ for $a \in \{1,2\}$.
+By $W_2$, for any agent in level at least 2, we have
+\[
+|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{Sq_aT_1/2}}.
+\]
+By Assumption \ref{ass:embehave}, we have
+\begin{align*}
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{c_m}{\sqrt{Sq_1T_1/2}} -  \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
+&\geq \mu_1 -\mu_2-\sqrt{\frac{3\log(T)}{Sq_1T_1/2}} - \sqrt{\frac{3\log(T)}{Sq_2T_1/2}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} -  \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
+&\geq\frac{\sqrt{S}}{4\sqrt{q_1T_1}} +  \frac{\sqrt{S}}{4\sqrt{q_2T_1}}-\sqrt{\frac{3\log(T)}{Sq_1T_1/2}} - \sqrt{\frac{3\log(T)}{Sq_2T_1/2}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} -  \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
+&>0.
+\end{align*}
+Therefore agents in level at least 2 will all pull arm 1.
+
+\item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l > 2$: By claim \ref{clm:l2_explore}, for any agent $t$ in level at least $l$, that agent will observe at least $T_{l-1}$ arm $a$ pulls.
+By $W_2$, we have
+\[
+|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{T_{l-1}}}.
+\]
+By Assumption \ref{ass:embehave}, we have
+\begin{align*}
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2c_m}{\sqrt{T_{l-1}}} \\
+&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2c_m}{\sqrt{T_{l-1}}} \\
+&\geq\sqrt{\frac{S}{16T_{l-1}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2c_m}{\sqrt{T_{l-1}}} \\
+&>0.
+\end{align*}
+Therefore agents in level at least $l$ will all pull arm 1.
+
+\item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}S$ for $l =3$ (i.e.
+$\varepsilon_1 < \mu_1 - \mu_2 < \varepsilon_1S$): By Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $3$, that agent will observe at least $T_1q_aS^2/2$ arm $a$ pulls (just from the first level).
+By $W_2$, we have
+\[
+|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S^2q_aT_1/2}}.
+\]
+By Assumption \ref{ass:embehave}, we have
+\begin{align*}
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{c_m}{\sqrt{S^2q_1T_1/2}}-\frac{c_m}{\sqrt{S^2q_2T_1/2}}  \\
+&\geq \mu_1 -\mu_2 -  \sqrt{\frac{3\log(T)}{S^2q_1T_1/2}}- \sqrt{\frac{3\log(T)}{S^2q_2T_1/2}}- \frac{c_m}{\sqrt{S^2q_1T_1/2}}-\frac{c_m}{\sqrt{S^2q_2T_1/2}}  \\
+&\geq\frac{1}{4\sqrt{Sq_1T_1}} + \frac{1}{4\sqrt{Sq_2T_1}}  -  \sqrt{\frac{3\log(T)}{S^2q_1T_1/2}}- \sqrt{\frac{3\log(T)}{S^2q_2T_1/2}}- \frac{c_m}{\sqrt{S^2q_1T_1/2}}-\frac{c_m}{\sqrt{S^2q_2T_1/2}}  \\
+&>0.
+\end{align*}
+Therefore agents in level at least 3 will all pull arm 1.
+
+\item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}S$ for $l >3$: Since $\mu_1-\mu_2 < \varepsilon_{l-2}S < \varepsilon_{l-3}$, by Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $l$, that agent will observe at least $T_{l-2}S^2$ arm $a$ pulls (just from level $l-2$).
+By $W_2$, we have
+\[
+|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S^2T_{l-2}}}.
+\]
+By Assumption \ref{ass:embehave}, we have
+\begin{align*}
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2c_m}{\sqrt{S^2T_{l-2}}} \\
+&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{S^2T_{l-2}}}- \frac{2c_m}{\sqrt{S^2T_{l-2}}} \\
+&\geq\frac{1}{4\sqrt{ST_{l-2}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2c_m}{\sqrt{T_{l-1}}} \\
+&>0.
+\end{align*}
+Therefore agents in level at least $l$ will all pull arm 1. 
+\end{itemize}
+\end{proof}
+
+By Claim \ref{clm:l2_exploit}, we know that the expected regret conditioned the intersection of clean events is at most 
+\begin{align*}
+&\max\left( T_1T_GS^2 , \max_{l \geq 2} \varepsilon_{l-1}S(T_1T_GS^2 + T_2 S^3 + \cdots + T_lS^3)\right) \\
+\leq & \max\left( T_1T_GS^2 , \max_{l \geq 2} 2 \varepsilon_{l-1} T_l S^4 \right)\\
+= &O(T^{\frac{2^{L-1}}{2^L-1}} \log^2(T)).
+\end{align*}
+\end{proof}

### 2018-10-01 algg.tex
update model and greedy

%!TEX root = main.tex
\section{\ALGG}
We first consider \ALGG which simply shows agents the full history. We discuss in this section the exploration of \ALGG under Assumption \ref{ass:embehave}.

\begin{lemma}
\label{lem:greedy}
There exist two constants $\GdT = O_K(1)$ and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least once. 
\end{lemma}

\begin{proof}
Set $\GdT = (K-1) \cdot c_T + 1$ and $\GdP = (1/3)^{\GdT}$. We fix the behavior of agents in $\GdT$ rounds and consider the case that all realized rewards in $\GdT$ rounds are 0.

In this case, we want to show that arm $a$ is pulled at least once. We prove by contradiction. Suppose arm $a$ is not pulled. By averaging argument, we know that there is some other arm $a'$ which is pulled at least $c_T + 1$ rounds. Suppose in round $t$, arm $a'$ is pulled exactly $c_T + 1$ times. By Assumption \ref{ass:embehave}, we know 
\[
\hat{\mu}_{a'}^t \leq 0 + c_m / \sqrt{c_T} < 1/3. 
\]
On the other hand, we have $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with the fact that in round $t$, arm $a'$ is pulled.

On the other hand, we know that this case happens with probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is at most $2/3$. To sum up, we know that with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once. 
\end{proof}

### 2018-10-01 model.tex
Finish L-level proof
update model and greedy

--- 2018-08-02 model.tex
@@
 The messages $m_t$ are generated according to a randomized online algorithm $\pi$ termed ``recommendation policy".
+
+\xhdr{Restrictions on the messages.} We classify recommendation policies according to what messages are allowed. 
+\begin{itemize}
+\item Full History: 
+\item Unbiased Sub-history: 
+\end{itemize}
+
+\begin{remark}
+Why not arbitrary sub-history?
+\end{remark}
+
+\xhdr{Agents behavior.} We assume agent $t$ estimates the mean of each arm as $\hat{\mu}_a^t$'s and pick the arm with the highest $\hat{\mu}_a^t$'s.
+We also define $\bar{\mu}_a^t$ as the empirical average of arm $a$ given the history.
+We assume each agent's estimate $\hat{\mu}_a^t$ is close to the empirical average $\bar{\mu}_a^t$, more specifically as the following assumption:
+\begin{assumption}
+\label{ass:embehave}
+Let constant $c_m = 1/16$.
+There exists a constant $c_T$ such that the following is true.
+For each agent $t$ and arm $a$, let $t_a$ be the number of times arm $a$ has been pulled in the history observed by agent $t$.
+\begin{itemize}
+\item \textbf{Close to the empirical average:} If $t_a \geq c_T$, 
+\[
+|\hat{\mu}^t_a - \bar{\mu}^t_a | < \frac{c_m}{\sqrt{t_a}}.
+\]
+\item \textbf{Initial value:} If $t_a = 0$, $\hat{\mu}^t_a$ is at least $1/3$. 
+\end{itemize}
+\end{assumption}
+
+We allow different agents to have different behavior models as long as they satisfy Assumption \ref{ass:embehave}.
+More specifically, we assume each agent's behavior model is sampled from an unknown distribution independently.

### 2018-10-02 2level.tex
Update 2-level proof

--- 2018-08-13 2level.tex
@@
 %!TEX root = main.tex
-\section{Two-level Recommendation Policy}
-Run $T_2$ \ALGG in parallel and then show the later agents the history of first $T_2$ rounds.
+\section{Warm-up: Two-level Recommendation Policy}
+In this section, we are going to show a two-level recommendation policy that gets sublinear regret.
+In this first level, we run $T_1$ \ALGG ``in parallel''.
+More specifically, we divide the first $T_1 \cdot \GdT$ agents into $T_1$ groups and agents only observe the history of all previous agents in the same group.
+In the second level, we show the rest $T-T_1\cdot \GdT$ agents the history of first $T_1 \cdot \GdT$ rounds. We will pick $T_1$ in Theorem \ref{thm:2level}. 
+See also Figure \ref{fig:2level} for a graphical view of the information flow.
 
-\begin{lemma}
-For each arm $i$, any $t > 0$ and $\varepsilon \leq 1/2$, let $p$ be the probability that there exists $t \leq \tau \leq T$ such that the empirical mean of the first $\tau$ pulls of arm $i$ is $\varepsilon$ away from $\mu_i$.
-Then we have
-\[
-p \leq \frac{2}{\varepsilon^2} \exp(-2\varepsilon^2 t).
-\]
-\end{lemma}
-
-\begin{proof}
-For each $\tau \in \{t,...,T\}$, let $p_{\tau}$ be the probability that the empirical mean of the first $\tau$ pulls of arm $i$ is $\varepsilon$ away from $\mu_i$. By Chernoff bound, we have
-\[
-p_{\tau} \leq 2 \exp(-2\varepsilon^2 \tau).
-\]
-
-By union bound,
-\[
-p \leq \sum_{\tau = t}^T p_{\tau} \leq 2 \exp(-2\varepsilon^2 t)  \cdot \frac{1}{1-\exp(-2\varepsilon^2)}.
-\]
-
-We know that for any $ x \in [0,1]$, $e^{-x} \leq 1-x/2$. There we have
-\[
-p \leq  2 \exp(-2\varepsilon^2 t)  \cdot \frac{1}{1-(1-\varepsilon^2)} =  \frac{2}{\varepsilon^2} \exp(-2\varepsilon^2 t).
-\]
-\end{proof}
+\begin{figure}[H]
+\centering
+\begin{tikzpicture}  
+ \filldraw[fill=blue!20!white]
+ (0,2)--(10,2)--(10,3)--(0,3)--cycle;
+  \filldraw[fill=red!20!white]
+  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
+  \draw[dashed] (0.5,1)--(5,2);
+  \filldraw[fill=red!20!white]
+  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
+  \draw[dashed] (1.5,1)--(5,2);
+  \filldraw[fill=red!20!white]
+  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
+  \draw[dashed] (2.5,1)--(5,2);
+  \filldraw[fill=red!20!white]
+  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
+  \draw[dashed] (3.5,1)--(5,2);
+  \filldraw[fill=red!20!white]
+  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
+  \draw[dashed] (9.5,1)--(5,2);
+  \node at(5,0.5){$\cdots$};
+  \node at(6,0.5){$\cdots$};
+  \node at(7,0.5){$\cdots$};
+  \node at(8,0.5){$\cdots$};
+  \node at(5,2.5){$T -T_1 \cdot \GdT$};
+  \node at(0.5,0.5){$\GdT$};
+  \node at(1.5,0.5){$\GdT$};
+  \node at(2.5,0.5){$\GdT$};
+  \node at(3.5,0.5){$\GdT$};
+  \node at(9.5,0.5){$\GdT$};
+  \node at(-2,0.5){\textbf{First Level}};
+  \node at(-2,2.5){\textbf{Second Level}};
+\end{tikzpicture}
+\caption{2-level Recommendation Policy.}
+\label{fig:2level}
+\end{figure}
 
 \begin{theorem}
-\2LEVEL gets expected regret $O(T^{2/3} \log(T)^{1/3})$. If $\delta$, the expected regret is $O(\log(T) \cdot \delta^{-2})$. 
+\label{thm:2level}
+With proper setting of $T_1$, our two-level recommendation policy gets expected regret $O(T^{2/3} \log(T)^{1/3})$.
+If we know the gap between the means of the best arm and second best arm is larger than $\Delta$, we can make the expected regret is $O(\log(T) \cdot \Delta^{-2})$.
 \end{theorem}
@@
 \begin{proof}
-We will analyze the case when agents after \ALGG only uses empirical mean.
+We will set $T_1$ later in the proof. For now, we just need to make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$.
+
+The first $T_1 \cdot \GdT$ rounds will get total regret at most $T_1 \cdot \GdT$.
+We focus on the regret of the rest $T - T_1 \cdot \GdT$ rounds.
+We first consider the following two clean events and we show that they together imply upper bounds on $|\hat{\mu}^t_a - \mu_a|$'s for $t > T_1 \cdot \GdT$.
+
+\begin{itemize}
+\item For each arm $a$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
+By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ Define $W_1^a$ to be the event that the number of arm $a$ pulls in the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$.
+By Chernoff bound,
+\[
+\Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
+\]
+Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
+\[
+\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
+\]
+\item For each arm $a$, imagine there is a tape of $T$ arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agent pull arm $a$.
+Define $W^{a,t}_2$ to be the event that the empirical mean of the first $t$ pulls of arm $a$ is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.
+Define $W_2$ to be the intersection of these events (i.e.
+$\bigcap_{a,t} W^{a,t}_2$).
+By Chernoff bound,
+\[
+\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
+\]
+By union bound, 
+\[
+\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
+\]
+\end{itemize}
+
+By union bound, we know $\Pr[W_1 \cap W_2] \geq 1 - 3/T$. Now we consider the case when $W_1 \cap W_2$ happens.
+
+For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
+\[
+|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}.
+\]
+By $W_1$ and Assumption \ref{ass:embehave}, we have
+\[
+|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{q_aT_1/2}}.
+\]
+Therefore,
+\[
+|\bar{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}+\frac{c_m}{\sqrt{q_aT_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}
+\]
+So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most 
+\[
+T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
+\]
+By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.
+
+Notice that if we know the gap between the means of the best arm and second best arm is larger than $\Delta$, we can set 
+\[
+T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
+\]
+In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
+\[
+T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
+\]
 \end{proof}

### 2018-10-02 llevel.tex
Update 2-level proof

@@
 For any agent $t$ in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$, it observes history of groups $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$ and all groups in levels below level $l-1$.
-Notice that the groups in the first $l-2$ levels have $(T_1 \GdT + T_2 + \cdots +T_{l-2})S^3 \leq T_{l-1}/(12\log(T)) \leq n^{l-1,u_a,a}/(12\log(T))$ agents.
+Notice that the groups in the first $l-2$ levels have $(T_1 \GdT + T_2 + \cdots +T_{l-2})S^2 \leq T_{l-1}/(12\log(T)) \leq n^{l-1,u_a,a}/(12\log(T))$ agents.
 By $W_2$, we have

### 2018-10-02 model.tex
Update 2-level proof

@@
 
-\emph{Bayesian Exploration} is a game between a principal and $T$ agents who arrive one by one.
-Each round $t$ proceeds as follows: a new agent $t$ arrives, receives a message $m_t$ from the principal, chooses an action $a_t$ from a fixed action space $\A = \{1,...,K\}$, and collects a reward $r_t\in \{0,1\}$ that is immediately observed by the principal.
+\emph{Incentivizing Exploration} is a game between a principal and $T$ agents who arrive one by one.
+Each round $t$ proceeds as follows: a new agent $t$ arrives, receives a message $m_t$ from the principal, chooses an arm $a_t$ from a fixed arm space $\A = \{1,...,K\}$, and collects a reward $r_t\in \{0,1\}$ that is immediately observed by the principal.
+We mostly focus on the case when $K=2$. We also discuss how to generalize our results to the case when $K$ is a constant greater than 2.
 
-Each action $a \in \A$ has a state $\mu_a$ drawn from $\D_a$ before the game starts. For agent in round $t$ who takes action $a_t$, the reward $r_t$ is distributed as $\Ber(\mu_{a_t})$.
+Each arm $a \in \A$ has a state $\mu_a$ drawn from $\D_a$ before the game starts. For the agent in round $t$ who picks arm $a_t$, the reward $r_t$ is distributed as $\Ber(\mu_{a_t})$.
 
@@
 \begin{itemize}
-\item Full History: 
-\item Unbiased Sub-history: 
+\item \textbf{Full history:} We show each agent the history of all previous agents' pulls. We call this policy \ALGG. 
+\item \textbf{Unbiased sub-history:} We show each agent only a subset of history. The subsets are pre-determined before any arms are pulled.  
 \end{itemize}
@@
 
-\xhdr{Agents behavior.} We assume agent $t$ estimates the mean of each arm as $\hat{\mu}_a^t$'s and pick the arm with the highest $\hat{\mu}_a^t$'s.
-We also define $\bar{\mu}_a^t$ as the empirical average of arm $a$ given the history.
+\xhdr{Agents' behavior.} We assume agent $t$ estimates the mean of each arm as $\hat{\mu}_a^t$'s and picks the arm with the highest $\hat{\mu}_a^t$.
+We define $\bar{\mu}_a^t$ as the empirical average of arm $a$ given the history.
 We assume each agent's estimate $\hat{\mu}_a^t$ is close to the empirical average $\bar{\mu}_a^t$, more specifically as the following assumption:
@@
 \label{ass:embehave}
-Let constant $c_m = 1/16$.
+Set constant $c_m = 1/16$.
 There exists a constant $c_T$ such that the following is true.
@@
 More specifically, we assume each agent's behavior model is sampled from an unknown distribution independently.
+\begin{remark}
+how this relates to Bayesian exploration with conjugate priors
+\end{remark}

### 2018-10-08 2level.tex
update some figures

@@
 %!TEX root = main.tex
-\section{Warm-up: Two-level Recommendation Policy}
-In this section, we are going to show a two-level recommendation policy that gets sublinear regret.
-In this first level, we run $T_1$ \ALGG ``in parallel''.
-More specifically, we divide the first $T_1 \cdot \GdT$ agents into $T_1$ groups and agents only observe the history of all previous agents in the same group.
+\section{Warm-up: 2-level Recommendation Policy}
+In this section, we are going to show a 2-level recommendation policy that gets sublinear regret.
+
+The 2-level recommendation policy is constructed as following.
+In the first level, we run $T_1$ \ALGG of $\GdT$ rounds ``in parallel''.
+More specifically, we divide the first $T_1 \cdot \GdT$ agents into $T_1$ groups of equal size and agents only observe the history of all previous agents in the same group.
 In the second level, we show the rest $T-T_1\cdot \GdT$ agents the history of first $T_1 \cdot \GdT$ rounds. We will pick $T_1$ in Theorem \ref{thm:2level}. 
 See also Figure \ref{fig:2level} for a graphical view of the information flow.
+
+The idea of this 2-level recommendation policy is simple.
+We first try to explore all arms enough amount of times in the first level using multiple runs of \ALGG under the guarantee of Lemma \ref{lem:greedy}.
+After that, by concentration argument, we can show that while observing the history of the first level, agents in the second level pick an arm with mean close to the best arm's mean.
 
@@
   \node at(9.5,0.5){$\GdT$};
-  \node at(-2,0.5){\textbf{First Level}};
-  \node at(-2,2.5){\textbf{Second Level}};
+  \node at(-1,0.5){\textbf{Level 1}};
+  \node at(-1,2.5){\textbf{Level 2}};
+  \draw[->] (11,0)--(11,3);
+  \node at(11.5,1.5)[ rotate=90]{Time};
 \end{tikzpicture}
@@
 \label{thm:2level}
-With proper setting of $T_1$, our two-level recommendation policy gets expected regret $O(T^{2/3} \log(T)^{1/3})$.
-If we know the gap between the means of the best arm and second best arm is larger than $\Delta$, we can make the expected regret is $O(\log(T) \cdot \Delta^{-2})$.
+With proper setting of $T_1$, the 2-level recommendation policy gets expected regret $O(T^{2/3} \log(T)^{1/3})$.
+If we know the gap between the means of the best arm and second best arm is larger than $\Delta$, we can make the expected regret $O(\log(T) \cdot \Delta^{-2})$.
 \end{theorem}
@@
 \begin{proof}
-We will set $T_1$ later in the proof. For now, we just need to make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$.
+We will set $T_1$ later in the proof.
+For now, we just need to know we will make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$.
+Since this recommendation policy is symmetric over arms, we wlog assume that arm 1 has the highest mean in the proof.
 
 The first $T_1 \cdot \GdT$ rounds will get total regret at most $T_1 \cdot \GdT$.
-We focus on the regret of the rest $T - T_1 \cdot \GdT$ rounds.
-We first consider the following two clean events and we show that they together imply upper bounds on $|\hat{\mu}^t_a - \mu_a|$'s for $t > T_1 \cdot \GdT$.
+We focus on bounding the regret of the rest $T - T_1 \cdot \GdT$ rounds.
+We consider the following two clean events.
+We will first bound the probability that both of them happen and then we will show that they together imply upper bounds on $|\hat{\mu}^t_a - \mu_a|$'s for any agent $t$ in the second level.
+Recall $\hat{\mu}^t_a$ is the estimated mean of arm $a$ by agent $t$ and agent $t$ picks the arm with the highest $\hat{\mu}^t_a$.
 
@@
 \item For each arm $a$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
-By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ Define $W_1^a$ to be the event that the number of arm $a$ pulls in the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$.
+By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.
+Define $W_1^a$ to be the event that the number of arm $a$ pulls in the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$.
 By Chernoff bound,
@@
 \[
-|\bar{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}+\frac{c_m}{\sqrt{q_aT_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}
+|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}+\frac{c_m}{\sqrt{q_aT_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
 \]

### 2018-10-08 3level.tex
A figure for 3-level
update some figures

@@
 
-\section{Three-level Recommendation Policy}
+\section{3-level Recommendation Policy}
 In this section, we show how to get $o(T^{2/3})$ regret with a 3-level recommendation policy. For simplicity, we assume there are only 2 arms.
 
-For 3-level recommendation policy, set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 = T^{6/7}\log^{-5/7}(T)$.
+The 3-level recommendation policy is constructed as followings.
+Set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 = T^{6/7}\log^{-5/7}(T)$.
 The first level has $S = 2^{10}\log(T)$ groups of agents.
@@
 All the rest agents are in the third level and they observe the entire history of the first two levels.
+See also Figure \ref{fig:3level} for a graphical view of the information flow.
 
-Needs to draw a figure here.
+\begin{figure}[H]
+\centering
+\begin{tikzpicture}  
+ \filldraw[fill=green!20!white]
+ (0,4)--(10,4)--(10,5)--(0,5)--cycle;
+ \foreach \x in {0,3,8}
+ {
+ \filldraw[fill=blue!20!white]
+ (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
+ \draw[dashed] (\x+1,3)--(5,4);
+ \filldraw[fill=red!20!white]
+ (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
+ \draw[dashed] (\x+1,1)--(\x+1,2);
+ \draw[dashed] (\x+0.2,1)--(\x+1,2);
+ \draw[dashed] (\x+0.6,1)--(\x+1,2);
+ \draw[dashed] (\x+1.4,1)--(\x+1,2);
+ \draw[dashed] (\x+1.8,1)--(\x+1,2);
+ \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
+ \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
+ \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
+ \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
+ \node at(\x+1,2.5){$T_2$};
+ \node at(\x+1,0.5){$T_1 \cdot \GdT$};
+ }
+  \node at(5,4.5){$T -S(T_1 \cdot \GdT + T_2)$};
+  \node at (6,1.5){$\cdots$};
+  \node at (7,1.5){$\cdots$};
+  \node at(-1,0.5){\textbf{Level 1}};
+  \node at(-1,2.5){\textbf{Level 2}};
+  \node at(-1,4.5){\textbf{Levle 3}};
+  \draw[->] (11,0)--(11,5);
+  \node at(11.5,2.5)[ rotate=90]{Time};
+\end{tikzpicture}
+\caption{3-level Recommendation Policy.}
+\label{fig:3level}
+\end{figure}
 
@@
 \begin{proof}
-Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We do a case analysis based on $\mu_1-\mu_2$. (some intuition and explanation of these cases?)
+Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We do a case analysis based on $\mu_1-\mu_2$.
 
@@
 Define $W_3^{a,t}$ to be the event that the mean of the first $t$ pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.
-
 By Chernoff bound,
@@
 \]
-Now define $W_4$ as $\bigcap_a \bigcup_s (W_4^{s,a,high} \cap W_4^{s,3-a,low})$. Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent across different $s$'s. So by union bound, we have
+Now define $W_4$ as $\bigcap_a \bigcup_s (W_4^{s,a,high} \cap W_4^{s,3-a,low})$. Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent across different $s$'s. By union bound, we have
 \[
@@
 $\bigcap_{i=1}^4 W_i$) happens with probability $1-O(1/T)$.
-When this intersection does not happen, since the probability is $O(1/T)$, it cost expected regret $O(1/T) \cdot T = O(1)$.
+When this intersection does not happen, since the probability is $O(1/T)$, it contributes $O(1/T) \cdot T = O(1)$ to the expected regret.
 

### 2018-10-08 llevel.tex
update some figures

@@
 \end{proof}
+
+\begin{corollary}
+With the proper setting of $L$ and $T_1,...,T_L$ discribed above, the $L$-level recommendation policy gets expected regret $O(polylog(T) /\Delta)$.
+Here $\Delta = \mu_1 -\mu_2$ and the $L$-level recommendation policy does not need to know $\Delta$ ahead of the time.
+Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$.
+\end{corollary}
+
+\begin{proof}
+\end{proof}

### 2018-10-08 3level.tex
add some intuition for 3level

@@
 
-The 3-level recommendation policy is constructed as followings.
+The 3-level recommendation policy is constructed as following.
 Set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 = T^{6/7}\log^{-5/7}(T)$.
@@
 See also Figure \ref{fig:3level} for a graphical view of the information flow.
+
+Here we give some intuition about how the 3-level recommendation policy works.
+The main idea is to do the exploration more adaptively.
+In the first level, agents explore both arms.
+In the second level, agents will pull the best arm when $\mu_1 - \mu_2$ is large ($\tilde{\Omega}(1/\sqrt{T_1})$).
+Otherwise agents will explore both arms more.
+In the third level, agents will pull the best arm unless $\mu_1-\mu_2$ is much smaller ($\tilde{O}(1/\sqrt{T_2})$).
+In the proof, we need not only the concentration argument as the 2-level recommendation policy, but also the anti-concentration argument to show that agents explore more in the second round if $\mu_1-\mu_2$ is not too big.
 

### 2018-10-09 llevel.tex
add l-level figure
fix some typos

@@
 \]
-We restrict $L$ to be at most $\log(\ln(T)/\log(10S^3))$ so that $T_l / T_{l-1} \geq T^{1/2^L} \geq 10S^3$ for $l = 2,...,L-1$.
+We restrict $L$ to be at most $\log(\ln(T)/\log(S^4))$ so that $T_l / T_{l-1} \geq T^{1/2^L} \geq S^4$ for $l = 2,...,L-1$.
 $T_L$ is a little bit different because we want total number of agents to be $T$.
 
-Each first-level group ($G_{1,u,v}$ for $u,v\in [S]$) has $T_1$ \ALGG runs in parallel.
+Each first-level group ($G_{1,u,v}$ for $u,v\in [S]$) has $T_1$ \ALGG of $\GdT$ rounds in parallel.
 For $l \geq 2$, there are $T_l$ agents in group $G_{l,u,v}$ and there are $T_l (S-1)$ agents in group $\Gamma_{l,u,v}$.
@@
 Agents in group $\Gamma_{l,u,v}$ observe the same history as agents in group $G_{l,u,v}$.
+
+\begin{figure}[H]
+\centering
+\begin{tikzpicture}  
+ \foreach \x in {0,3,6,9}
+ {
+ \filldraw[fill=orange!20!white]
+ (\x+0,10)--(\x+0.8,10)--(\x+0.8,11)--(\x+0,11)--cycle;
+ \filldraw[fill=orange!30!white]
+ (\x+0.8,10)--(\x+2.8,10)--(\x+2.8,11)--(\x+0.8,11)--cycle;
+ \filldraw[fill=purple!20!white]
+ (\x+0,7.5)--(\x+0.8,7.5)--(\x+0.8,8.5)--(\x+0,8.5)--cycle;
+ \filldraw[fill=purple!30!white]
+ (\x+0.8,7.5)--(\x+2.8,7.5)--(\x+2.8,8.5)--(\x+0.8,8.5)--cycle;
+ \filldraw[fill=green!20!white]
+ (\x+0,5)--(\x+0.8,5)--(\x+0.8,6)--(\x+0,6)--cycle;
+ \filldraw[fill=green!30!white]
+ (\x+0.8,5)--(\x+2.8,5)--(\x+2.8,6)--(\x+0.8,6)--cycle;
+ \filldraw[fill=blue!20!white]
+ (\x+0,2.5)--(\x+0.8,2.5)--(\x+0.8,3.5)--(\x+0,3.5)--cycle;
+ \filldraw[fill=blue!30!white]
+ (\x+0.8,2.5)--(\x+2.8,2.5)--(\x+2.8,3.5)--(\x+0.8,3.5)--cycle;
+ \filldraw[fill=red!20!white]
+ (\x+0,0)--(\x+2.8,0)--(\x+2.8,1)--(\x+0,1)--cycle;
+ \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
+ \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
+ \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
+ \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
+ \draw[dashed] (\x+2,0)--(\x+2,1);  
+ \draw[dashed] (\x+2.4,0)--(\x+2.4,1);  
+ \node at(\x+0.4,3){$T_{l-2}$};
+ \node at(\x+1.8,3){$T_{l-2} (S-1)$};
+ \node at(\x+0.4,5.5){$T_{l-1}$};
+ \node at(\x+1.8,5.5){$T_{l-1} (S-1)$};
+ \node at(\x+0.4,8){$T_l$};
+ \node at(\x+1.8,8){$T_l (S-1)$};
+ \node at(\x+0.4,10.5){$T_L$};
+ \node at(\x+1.8,10.5){$T_L (S-1)$};
+ \node at(\x+1.4,0.5){$T_1 \cdot \GdT$};
+ }
+\foreach \y in {0,2.5,5,7.5,10}
+{
+  \node at (12.5,\y+0.5){$\cdots$};
+} 
+\foreach \u in {1,2}
+{
+	\foreach \v in {1,2}
+	{
+	\pgfmathsetmacro{\x}{((\u-1)*2+(\v-1))*3};
+	\pgfmathsetmacro{\xa}{((\u-1))*3};
+	\pgfmathsetmacro{\xb}{(2+(\u-1))*3};
+   \node at(\x+0.6,7){$G_{l,\u,\v}$};
+   \node at(\x+0.6,4.5){$G_{l-1,\u,\v}$};
+   \node at(\x+0.6,2){$G_{l-2,\u,\v}$};
+   \node at(\x+2,7){$\Gamma_{l,\u,\v}$};
+   \node at(\x+2,4.5){$\Gamma_{l-1,\u,\v}$};
+   \node at(\x+2,2){$\Gamma_{l-2,\u,\v}$};
+   %\draw[dashed] (\x+0.4,3.5)--(\xa+0.4,5);  
+   %\draw[dashed] (\x+0.4,3.5)--(\xb+0.4,5);  
+   %\draw[dashed] (\x+0.4,3.5)--(\xa+1.8,5);  
+   %\draw[dashed] (\x+0.4,3.5)--(\xb+1.8,5);
+
+   %\draw[dashed] (\x+0.4,6)--(\xa+0.4,7.5);  
+   %\draw[dashed] (\x+0.4,6)--(\xb+0.4,7.5);  
+   %\draw[dashed] (\x+0.4,6)--(\xa+1.8,7.5);  
+   %\draw[dashed] (\x+0.4,6)--(\xb+1.8,7.5);  
+	}
+}
+
+   \draw[dashed] (0+1.8,3.5)--(6.4,7.5);  	
+   \draw[dashed] (3+1.8,3.5)--(6.4,7.5);  	
+   \draw[dashed] (6+1.8,3.5)--(6.4,7.5);  	
+   \draw[dashed] (9+1.8,3.5)--(6.4,7.5);
+
+   %\draw[dashed] (0+0.4,3.5)--(6.4,7.5);  	
+   %\draw[dashed] (3+0.4,3.5)--(6.4,7.5);  	
+   %\draw[dashed] (6+0.4,3.5)--(6.4,7.5);  	
+   %\draw[dashed] (9+0.4,3.5)--(6.4,7.5);
+
+   \draw[dashed] (0+0.4,6)--(6.4,7.5);  	
+   \draw[dashed] (3+0.4,6)--(6.4,7.5);  	
+  \node at (6,1.5)[rotate = 90]{$\cdots$};
+  \node at (-1,1.5)[rotate = 90]{$\cdots$};
+  \node at (6,9.5)[rotate = 90]{$\cdots$};
+  \node at (-1,9.5)[rotate = 90]{$\cdots$};
+  \node at(-1.2,0.5){\textbf{Level 1}};
+  \node at(-1.2,3){\textbf{Level $l-2$}};
+  \node at(-1.2,5.5){\textbf{Level $l-1$}};
+  \node at(-1.2,8){\textbf{Level $l$}};
+  \node at(-1.2,10.5){\textbf{Level $L$}};
+  \draw[->] (13.3,0)--(13.3,12);
+  \node at(13.7,6)[ rotate=90]{Time};
+  \draw [rounded corners=5mm, line width=1mm, red](-0.2,1.75)--(12,1.75)--(12,9)--(-0.2,9)--cycle;\draw [rounded corners=2.5mm, line width=0.5mm, brown](5.9,6.5)--(8.9,6.5)--(8.9,8.8)--(5.9,8.8)--cycle;
+\end{tikzpicture}
+\caption{$l$-level Recommendation Policy.}
+\label{fig:llevel}
+\end{figure}
 
@@
 The last inequality holds since $c_m$ is a small enough constant defined in Assumption \ref{ass:embehave}.
-Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{l,1,u},...,\Gamma_{l,S,u}$ all pull arm $a$.
+Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$ all pull arm $a$.
 
@@
 For any agent $t$ in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$, it observes history of groups $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$ and all groups in levels below level $l-1$.
-Notice that the groups in the first $l-2$ levels have $(T_1 \GdT + T_2 + \cdots +T_{l-2})S^2 \leq T_{l-1}/(12\log(T)) \leq n^{l-1,u_a,a}/(12\log(T))$ agents.
+Notice that the groups in the first $l-2$ levels have at most $(T_1 \GdT + T_2 + \cdots +T_{l-2})S^3 \leq T_{l-1}/(12\log(T)) \leq n^{l-1,u_a,a}/(12\log(T))$ agents.
 By $W_2$, we have
 \begin{align*}
-\bar{\mu}_a ^t &\geq \mu_a + \left(n^{l-1,u_a,a}  \cdot \frac{1}{\sqrt{n^{l-1,u_a,a} }}- (T_1 \GdT + T_2 + \cdots +T_{l-2})S^2\cdot \sqrt{\frac{3\log(T)}{ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^2}} \right) \\
-&~~~\cdot \frac{1}{n^{l-1,u_a,a}+ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^2} \\
+\bar{\mu}_a ^t &\geq \mu_a + \left(n^{l-1,u_a,a}  \cdot \frac{1}{\sqrt{n^{l-1,u_a,a} }}- (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3\cdot \sqrt{\frac{3\log(T)}{ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3}} \right) \\
+&~~~\cdot \frac{1}{n^{l-1,u_a,a}+ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3} \\
 &> \mu_a + \frac{1}{4\sqrt{n^{l-1,u_a,a}  }}.
@@
 \begin{itemize}
-\item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l > 2$(i.e.
+\item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l = 2$(i.e.
 $\varepsilon_1S\leq \mu_1 - \mu_2 \leq \varepsilon_0$): We know agents in level at least 2 will observe at least $q_aT_1/2$ pulls of arm $a$ for $a \in \{1,2\}$.
@@
 
+Now we are going to change the parameters of the $L$-level recommendation policy a little bit and prove the below corollary.
+We will keep $S$ the same (i.e.
+$S = 2^{10}\log(T)$).
+We are going to change $L$ and $T_1,...,T_L$.
+We set $L = \log(T)/\log(10S^3)$, $T_l = (10S^3)^l$ for $l=1,...,L-1$ and $T_L = (T - T_1 \GdT S^2 - S^3\sum_{l=2}^{L-1} T_l)/S^3$.
 \begin{corollary}
@@
 \end{proof}
+
+\begin{claim}
+Extended to constant number of arms.
+\end{claim}

### 2018-10-09 2level.tex
small changes

@@
 \begin{itemize}
-\item For each arm $a$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
+\item \textbf{Concentration of the number of arm $a$ pulls in the first level:}
+
+For each arm $a$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
 By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.
@@
 \]
-\item For each arm $a$, imagine there is a tape of $T$ arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agent pull arm $a$.
+\item  \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
+
+For each arm $a$, imagine there is a tape of $T$ arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agent pull arm $a$.
 Define $W^{a,t}_2$ to be the event that the empirical mean of the first $t$ pulls of arm $a$ is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.

### 2018-10-09 3level.tex
fix some typos
small changes

@@
 \begin{itemize}
-\item For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
-By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$.
+\item \textbf{Concentration of the number of arm $a$ pulls in the first level:}
+
+For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
+By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.
+For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$.
 By Chernoff bound,
@@
 \]
-\item For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$.
+\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
+
+For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$.
 For the $s$-th first-level group and arm $a$, define $W_2^{s,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away from $\mu_a$.
@@
 
-\item For all the groups in the first two levels and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in the first two levels pull arm $a$.
+\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first two levels:}
+
+For all the groups in the first two levels and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in the first two levels pull arm $a$.
 Define $W_3^{a,t}$ to be the event that the mean of the first $t$ pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.
@@
 
-\item Consider the tapes defined in the second bullet again.
+\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the first level:}
+
+Consider the tapes defined in the second bullet again.
 For the $s$-th first-level group and arm $a$, define $W_4^{s,a,high}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1}$ and define  $W_4^{s,a,low}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1}$.
@@
 \]
-The last inequality holds when $T$ larger than some constant.
+The last inequality holds when $T$ is larger than some constant.
 
@@
 \end{align*}
-The second last inequality holds when $T$ larger than some constant.
+The second last inequality holds when $T$ is larger than some constant.
 Similarly, we also have
@@
 \begin{align*}
-\hat{\mu}_a^t - \hat{\mu}_a^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_a^{1,s_a} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
+\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
 &\geq   \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\

### 2018-10-09 model.tex
reading model
comments

@@
 
-Each arm $a \in \A$ has a state $\mu_a$ drawn from $\D_a$ before the game starts. For the agent in round $t$ who picks arm $a_t$, the reward $r_t$ is distributed as $\Ber(\mu_{a_t})$.
+Each arm $a \in \A$ has a state $\mu_a$ drawn from $\D_a$ before the game starts.
+For the agent in round $t$ who picks arm $a_t$, the reward $r_t$ is distributed as $\Ber(\mu_{a_t})$.\swcomment{do we plan to generalize to real-valued?}
 
@@
 \xhdr{Agents' behavior.} We assume agent $t$ estimates the mean of each arm as $\hat{\mu}_a^t$'s and picks the arm with the highest $\hat{\mu}_a^t$.
-We define $\bar{\mu}_a^t$ as the empirical average of arm $a$ given the history.
+We define $\bar{\mu}_a^t$ as the empirical average of arm $a$ given the history\swcomment{sub-history he receives?}.
 We assume each agent's estimate $\hat{\mu}_a^t$ is close to the empirical average $\bar{\mu}_a^t$, more specifically as the following assumption:

### 2018-10-09 model.tex
add info graph

--- 2018-10-02 model.tex
@@
 \item \textbf{Unbiased sub-history:} We show each agent only a subset of history. The subsets are pre-determined before any arms are pulled.  
+\item \textbf{Info graph:} All the recommendation policies in this paper can be described by an undirected transitive graph with $T$ nodes.
+We call it the info graph.
+The $T$ nodes in the graph represent the $T$ agents.
+If there is an edge between node $u$ and $v$ for $u < v$, it means the history of agent $u$ is shown to agent $v$.
 \end{itemize}

### 2018-10-09 model.tex
stuff
comment

@@
 \label{ass:embehave}
-Set constant $c_m = 1/16$.
-There exists a constant $c_T$ such that the following is true.
+Set constant $c_m = 1/16$.\swcomment{subscript $m$ meant anything?} There exists a constant $c_T$ such that the following is true.
 For each agent $t$ and arm $a$, let $t_a$ be the number of times arm $a$ has been pulled in the history observed by agent $t$.
@@
 \item \textbf{Initial value:} If $t_a = 0$, $\hat{\mu}^t_a$ is at least $1/3$.
+\swcomment{should probably mention this is just for the convenience of the analysis; mention that our analysis works as long as this is bounded away from 0?}
 \end{itemize}

### 2018-10-09 algg.tex
update some figures
Hello

@@
 There exist two constants $\GdT = O_K(1)$ and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least once.
+\swcomment{maybe explain what $O_k$ means}
 \end{lemma}
@@
 
-On the other hand, we know that this case happens with probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is at most $2/3$.
-To sum up, we know that with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.
+In addition, we know that this case happens with probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is at most $2/3$.\swcomment{where did we assume that?} To sum up, we know that with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.
 \end{proof}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2018-10-09 2level.tex
comments

@@
 
-For each arm $a$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
-By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.
-Define $W_1^a$ to be the event that the number of arm $a$ pulls in the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$.
-By Chernoff bound,
+  For each arm $a$, define $q_a$ to be the expected number of arm $a$
+  pulls in one run of \ALGG used in the first level.\swcomment{$q_a$
+    probability or number?? the issue propagates downwards} By Lemma
+  \ref{lem:greedy}, we know $\GdP \leq q_a \leq
+  \GdT$.\swcomment{$p_G T$?} Define $W_1^a$ to be the event that the
+  number of arm $a$ pulls in the first level is at least
+  $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$.\swcomment{what
+    is the condition on $T_1$ and $T_G$ for this to hold?} By Chernoff
+  bound,
 \[
@@
 \end{proof}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2018-10-09 llevel.tex
add a proof for Cor 6.4

@@
 Label the $\Gamma$-groups in the $l$-th level as $\Gamma_{l,u,v}$ for $u,v \in [S]$.
-
-We set the group size as following. For $l < L$,
-\[
-T_l = T^{\frac{2^{L-1} + 2^{L-2} + \cdots + 2^{L-l}}{2^{L-1}+ 2^{L-2} + \cdots + 1}}/S^3.
-\]
-and 
-\[
-T_L = (T - T_1 \cdot \GdT\cdot S^2 - (T_2 + \cdots + T_{l-1}) S^3) /S^3
-\]
-We restrict $L$ to be at most $\log(\ln(T)/\log(S^4))$ so that $T_l / T_{l-1} \geq T^{1/2^L} \geq S^4$ for $l = 2,...,L-1$.
-$T_L$ is a little bit different because we want total number of agents to be $T$.
-
 Each first-level group ($G_{1,u,v}$ for $u,v\in [S]$) has $T_1$ \ALGG of $\GdT$ rounds in parallel.
 For $l \geq 2$, there are $T_l$ agents in group $G_{l,u,v}$ and there are $T_l (S-1)$ agents in group $\Gamma_{l,u,v}$.
+We will pick $T_1,...,T_L$ in the proof of Theorem \ref{thm:llevel}.
 
@@
 \begin{theorem}
-The $L$-level recommendation policy gets expected regret $O\left(T^{\frac{2^{L-1}}{2^L-1}} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(10S^3))$.
-In particular, if we pick $L = \log(\ln(T)/\log(10S^3))$, the expected regret is at most $O(T^{1/2} \log^5(T))$.
+\label{thm:llevel}
+The $L$-level recommendation policy gets expected regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(S^4))$.
+In particular, if we pick $L = \log(\ln(T)/\log(S^4))$, the expected regret is $O(T^{1/2} polylog(T))$.
 \end{theorem}
@@
 \begin{proof}
-Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. Similarly as the proof of Theorem \ref{thm:3level}, we start with some clean events.
+Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms.
+We will set $T_l$'s later in the proof.
+Before that, we are only going to assume $T_l / T_{l-1} \geq S^4$ for $l=2,...,L-1$ and $T_1 \geq S^4$.
+
+Similarly as the proof of Theorem \ref{thm:3level}, we start with some clean events.
 
 \begin{itemize}
-\item For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
+\item  \textbf{Concentration of the number of arm $a$ pulls in the first level:}
+
+For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
 By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ For group $G_{1,u,v}$, define $W_1^{a,u,v}$ to be the event that the number of arm $a$ pulls in this group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$.
@@
 
-\item For each agent $t$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in agent $t$'s observed history pull arm $a$.
+\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the history observed by agent $t$:}
+
+ For each agent $t$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in agent $t$'s observed history pull arm $a$.
 Define $W_2^{t,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{3\log(T)}{t_2-t_1+1}}$ away from $\mu_a$.
@@
 
-\item For $2\leq l \leq L-1$, $u\in [S]$ and each arm $a$, define $n^{l,u,a}$ to be the number of arm $a$ pulls in groups $G_{l,u,1},...,G_{l,u,S}$.
+\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the $l$-th level  for $l \geq 2$:}
+
+For $2\leq l \leq L-1$, $u\in [S]$ and each arm $a$, define $n^{l,u,a}$ to be the number of arm $a$ pulls in groups $G_{l,u,1},...,G_{l,u,S}$.
 Define $W_3^{l,u,a,high}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at least $\mu_a + 1/\sqrt{n^{l,u,a}}$.
@@
 
-\item For first-level groups $G_{1,u,1},...,G_{1,u,S}$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in these groups pull arm $a$.
+\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the first level:}
+
+For first-level groups $G_{1,u,1},...,G_{1,u,S}$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in these groups pull arm $a$.
 Define $W_4^{u,a,high}$  to be the event that first $q_a T_1 S$ pulls of arm $a$ in the tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1 S}$ and define $W_4^{u,a,low}$  to be the event that first $q_a T_1S$ pulls of arm $a$ in the tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1S }$.
@@
 \label{clm:l2_exploit}
-For any $2 \leq l \leq L$, if $\varepsilon_{l-1} S < \mu_1 - \mu_2 < \varepsilon_{l-2} S$, there are no pulls of arm 2 in groups with level $l,...,L$. 
+For any $2 \leq l \leq L$, if $\varepsilon_{l-1} S\leq \mu_1 - \mu_2 < \varepsilon_{l-2} S$, there are no pulls of arm 2 in groups with level $l,...,L$. 
 \end{claim}
@@
 
+Now we set the group sizes $T_l$'s as following. For $l < L$,
+\[
+T_l = T^{\frac{2^{L-1} + 2^{L-2} + \cdots + 2^{L-l}}{2^{L-1}+ 2^{L-2} + \cdots + 1}}/S^3.
+\]
+and 
+\[
+T_L = (T - T_1 \cdot \GdT\cdot S^2 - (T_2 + \cdots + T_{l-1}) S^3) /S^3
+\]
+We restrict $L$ to be at most $\log(\ln(T)/\log(S^4))$ so that $T_l / T_{l-1} \geq T^{1/2^L} \geq S^4$ for $l = 2,...,L-1$.
+$T_L$ is a little bit different because we want total number of agents to be $T$.
+
 By Claim \ref{clm:l2_exploit}, we know that the expected regret conditioned the intersection of clean events is at most 
@@
 \leq & \max\left( T_1T_GS^2 , \max_{l \geq 2} 2 \varepsilon_{l-1} T_l S^4 \right)\\
-= &O(T^{\frac{2^{L-1}}{2^L-1}} \log^2(T)).
+= &O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right).
 \end{align*}
@@
 We are going to change $L$ and $T_1,...,T_L$.
-We set $L = \log(T)/\log(10S^3)$, $T_l = (10S^3)^l$ for $l=1,...,L-1$ and $T_L = (T - T_1 \GdT S^2 - S^3\sum_{l=2}^{L-1} T_l)/S^3$.
+We set $L = \log(T)/\log(S^4)$, $T_l = (S^4)^l$ for $l=1,...,L-1$ and $T_L = (T - T_1 \GdT S^2 - S^3\sum_{l=2}^{L-1} T_l)/S^3$.
 \begin{corollary}
-With the proper setting of $L$ and $T_1,...,T_L$ discribed above, the $L$-level recommendation policy gets expected regret $O(polylog(T) /\Delta)$.
-Here $\Delta = \mu_1 -\mu_2$ and the $L$-level recommendation policy does not need to know $\Delta$ ahead of the time.
+With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets expected regret $O(\min(polylog(T) /\Delta,  T\Delta))$.
+Here $\Delta = \mu_1 -\mu_2$ and the $L$-level recommendation policy does not need to know $\Delta$.
 Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$.
@@
 \begin{proof}
+Notice that in the proof of Theorem \ref{thm:llevel}, by the end of Claim \ref{clm:l2_exploit}, the only constraint we need about $T_l$'s is that $T_l / T_{l-1} \geq S^4$ for $l=2,...,L-1$ and $T_1 \geq S^4$.
+And our new settings of $T_l$'s still satisfy this constraint.
+So we can reuse the proof of Theorem \ref{thm:llevel} till the end of Claim \ref{clm:l2_exploit}.
+
+First of all, notice that even always picking the sub-optimal arm gives expected regret $T(\mu_1-\mu_2) = T\Delta$.
+In the rest of the proof, we just need to show the expected regret is $O(polylog(T)/\Delta)$.
+Now consider two cases:
+\begin{itemize}
+\item $\Delta < \varepsilon_{L-1} S$. In this case, we know $T\Delta = O(polylog(T)/\Delta)$. So the expected regret is $O(T\Delta) = O(polylog(T) /\Delta)$.
+\item $\Delta \geq \varepsilon_{L-1} S$.
+In this case, we can find $l \in \{2,...,L\}$ such that $\varepsilon_{l-1} S\leq \Delta < \varepsilon_{l-2} S$.
+By Claim \ref{clm:l2_exploit}, we can bound the expected regret by
+\begin{align*}
+&\Delta \cdot (T_1 \GdT S^2  +T_2 S^3+ \cdots T_{l-1} S^3)\\
+=& O(\Delta T_{l-1}S^3) \\
+=&O(\Delta T_{l-2}S^7) \\
+=&O(\Delta\cdot  \frac{1}{\varepsilon^2_{l-2}}\cdot S^6)\\
+=&O(\Delta \cdot \frac{1}{\Delta^2}\cdot S^8)\\
+=&O(polylog(T)/\Delta).
+\end{align*}
+\end{itemize}
 \end{proof}

### 2018-10-12 llevel.tex
update cor 6.4

@@
 \begin{corollary}
-With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets expected regret $O(\min(polylog(T) /\Delta,  T\Delta))$.
+With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$.
 Here $\Delta = \mu_1 -\mu_2$ and the $L$-level recommendation policy does not need to know $\Delta$.
@@
 
-First of all, notice that even always picking the sub-optimal arm gives expected regret $T(\mu_1-\mu_2) = T\Delta$.
-In the rest of the proof, we just need to show the expected regret is $O(polylog(T)/\Delta)$.
-Now consider two cases:
+Recall in the proof of Theorem \ref{thm:llevel}, $\varepsilon_l =\Theta(1/\sqrt{T_l S})$. Consider two cases:
 \begin{itemize}
-\item $\Delta < \varepsilon_{L-1} S$. In this case, we know $T\Delta = O(polylog(T)/\Delta)$. So the expected regret is $O(T\Delta) = O(polylog(T) /\Delta)$.
+\item $\Delta < \varepsilon_{L-1} S$.
+In this case, notice that even always picking the sub-optimal arm gives expected regret at most $T(\mu_1-\mu_2) = T\Delta = O(T^{1/2} polylog(T))$.
+On the other hand, $T^{1/2} = O(polylog(T)/\Delta)$.
+Therefore, the expected regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
 \item $\Delta \geq \varepsilon_{L-1} S$.
@@
 \end{align*}
+We also have $1/\Delta \leq 1/(\varepsilon_{L-1}S)= O(T^{1/2})$. Therefore, the expected regret is \\$O(\min(1/\Delta, T^{1/2})polylog(T))$.
 \end{itemize}

### 2018-10-16 model.tex
comments
edits

--- 2018-10-09 model.tex
@@
 
-\emph{Incentivizing Exploration} is a game between a principal and $T$ agents who arrive one by one.
-Each round $t$ proceeds as follows: a new agent $t$ arrives, receives a message $m_t$ from the principal, chooses an arm $a_t$ from a fixed arm space $\A = \{1,...,K\}$, and collects a reward $r_t\in \{0,1\}$ that is immediately observed by the principal.
-We mostly focus on the case when $K=2$. We also discuss how to generalize our results to the case when $K$ is a constant greater than 2.
+We study the mult-armed bandit problem in a social learning context,
+in which a principal faces a sequence of $T$ myopic agents. There is a
+set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
+distributed according to the Bernoulli distribution with an unknown
+mean $\mu_a$.\swcomment{do we plan to generalize to real-valued?}  At
+each round $t\in [T]$, a new agent $t$ arrives, receives a message
+$m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a
+reward $r_t\in \{0,1\}$ that is immediately observed by the
+principal.
 
-Each arm $a \in \A$ has a state $\mu_a$ drawn from $\D_a$ before the game starts. For the agent in round $t$ who picks arm $a_t$, the reward $r_t$ is distributed as $\Ber(\mu_{a_t})$.
+% We mostly focus on the case when $K=2$. We also discuss how to
+% generalize our results to the case when $K$ is a constant greater
+% than 2. The messages $m_t$ are generated according to a randomized
+% online algorithm $\pi$ termed ``recommendation policy".
 
-The messages $m_t$ are generated according to a randomized online algorithm $\pi$ termed ``recommendation policy".
+\xhdr{Unbiased sub-history policy.} The principal computes the
+sequence of messages $m_t$ according to a disclosure policy. We will
+focus on \emph{unbiased sub-history policies} that at each round $t$
+reveal the \emph{sub-history} in a subset of previous rounds
+$S_t\subseteq [t-1]$: $\{(s, a_s, r_s)\mid s \in S_t\}$, where the
+subset $S_t$ is fixed ahead of time. A simple example is the policy
+that reveals the \emph{full history}, that is $S_t = [t-1]$.  All of
+the policies we develop are \emph{transitive}: for any two agents $t$
+and $t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains
+that of $S_{t'}$.
 
-\xhdr{Restrictions on the messages.} We classify recommendation policies according to what messages are allowed. 
+\xhdr{Information flow graph.} We will describe our transitive
+policies using a \emph{information flow graph} (and henceforth
+\emph{info graph})---a directed graph over the $T$ agents such that if
+there is an edge from $u$ to $v$, it means $u\in S_v$. By the property
+of transitivity, $S_t$ is the set of nodes that can reach node $t$ in
+the info graph.
+
+\iffalse
 \begin{itemize}
@@
 \end{itemize}
+\fi
 
 \begin{remark}
-Why not arbitrary sub-history?
+  Why not arbitrary sub-history? \swcomment{important point to make;
+    but should be in the introduction}
 \end{remark}
 
-\xhdr{Agents' behavior.} We assume agent $t$ estimates the mean of each arm as $\hat{\mu}_a^t$'s and picks the arm with the highest $\hat{\mu}_a^t$.
-We define $\bar{\mu}_a^t$ as the empirical average of arm $a$ given the history.
-We assume each agent's estimate $\hat{\mu}_a^t$ is close to the empirical average $\bar{\mu}_a^t$, more specifically as the following assumption:
+\xhdr{Agents' behavior.} Based on the history over rounds $S_t$, each
+agent $t$ first computes an estimate $\hat{\mu}_a^t$ for the mean
+reward of each arm $a$, and then selects the arm with the highest
+$\hat{\mu}_a^t$. Let $t_a$ be the number of times arm $a$ is pulled in
+the observed history $S_t$. For any $a$ with $t_a > 0$, we write
+$\bar{\mu}_a^t$ as the empirical average of arm $a$ given the history.
+
+% We assume that for sufficiently high $t_a$, the estimate
+% $\hat{\mu}_a^t$ is close to the empirical average $\bar{\mu}_a^t$.
+
+We will make the following assumptions on the set of mean rewards
+$\{\mu_a\}$, and the relationship between the estimates $\hat \mu_a^t$
+.and empirical mean rewards $\bar\mu_a^t$.
+
 \begin{assumption}
 \label{ass:embehave}
-Set constant $c_m = 1/16$.
-There exists a constant $c_T$ such that the following is true.
-For each agent $t$ and arm $a$, let $t_a$ be the number of times arm $a$ has been pulled in the history observed by agent $t$.
+Let $c_m = 1/16$.\swcomment{subscript $m$ meant anything?}. 
 \begin{itemize}
-\item \textbf{Close to the empirical average:} If $t_a \geq c_T$, 
+\item The mean reward $\mu_a$ for each arm $a\in \A$ lies in the range
+  of $[1/3, 2/3]$.
+
+\item There exists a constant $c_T$ such that for any agent $t$ and
+  arm $a$, as long as $t_a \geq c_T$,
 \[
-|\hat{\mu}^t_a - \bar{\mu}^t_a | < \frac{c_m}{\sqrt{t_a}}.
+  \left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
+  \frac{c_m}{\sqrt{t_a}}.
 \]
-\item \textbf{Initial value:} If $t_a = 0$, $\hat{\mu}^t_a$ is at least $1/3$. 
+\item In the case of $t_a = 0$, the initial estimate $\hat{\mu}^t_a$
+  is at least $1/3$.
 \end{itemize}
@@
 
-We allow different agents to have different behavior models as long as they satisfy Assumption \ref{ass:embehave}.
-More specifically, we assume each agent's behavior model is sampled from an unknown distribution independently.
+The first assumption ensures that the reward distributions have
+sufficient entropy to induce natural exploration. We choose the
+bounded range $[1/3, 2/3]$ for the simplicity of our analysis, and it
+can further relaxed to $[1/C, (C-1)/C]$ for any constant $C$.
+
+We allow different agents to have different behavior models as long as
+they satisfy Assumption \ref{ass:embehave}. More specifically, we
+assume each agent's behavior model is sampled from an unknown
+distribution independently.\swcomment{why independently? can be be
+  adversarial?}
 \begin{remark}
@@
 \end{remark}
+
+\swcomment{todo: define regret. define gap $\Delta$}
+
+Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by the agents, the \emph{regret} is defined as
+\[
+  \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a - \sum_{t=1}^T
+  \mu_{a_t}.
+\]
+
+The principal's goal is then to design a policy to minimize the regret
+from the induced sequence arms chosen by agents.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2018-10-16 llevel.tex
adding Thm 6.5 (constant arms), not finished yet

@@
 We set $L = \log(T)/\log(S^4)$, $T_l = (S^4)^l$ for $l=1,...,L-1$ and $T_L = (T - T_1 \GdT S^2 - S^3\sum_{l=2}^{L-1} T_l)/S^3$.
+
 \begin{corollary}
+\label{cor:llevel}
 With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$.
-Here $\Delta = \mu_1 -\mu_2$ and the $L$-level recommendation policy does not need to know $\Delta$.
+Here $\Delta = |\mu_1 -\mu_2|$ and the $L$-level recommendation policy does not need to know $\Delta$.
 Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$.
@@
 
-Recall in the proof of Theorem \ref{thm:llevel}, $\varepsilon_l =\Theta(1/\sqrt{T_l S})$. Consider two cases:
+Recall in the proof of Theorem \ref{thm:llevel}, $\varepsilon_l =\Theta(1/\sqrt{T_l S})$ for $l \in [L-1]$ and $\varepsilon_0 = 1$. Consider two cases:
 \begin{itemize}
@@
 In this case, we can find $l \in \{2,...,L\}$ such that $\varepsilon_{l-1} S\leq \Delta < \varepsilon_{l-2} S$.
-By Claim \ref{clm:l2_exploit}, we can bound the expected regret by
+By Claim \ref{clm:l2_exploit}, we can upper bound the expected regret by
 \begin{align*}
@@
 
-\begin{claim}
-Extended to constant number of arms.
-\end{claim}
+Here we discuss about how to extend Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel} to the case when $K$ is a constant larger than 2.
+As the proof is very similar to the proofs of Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel}, we only provide a proof sketch of what changes to make.
+
+\begin{theorem}
+Let the number of arms $K$ to be a constant larger than 2.
+Let $\Delta$ to be the difference between means of best and second best arms.
+We have an $L$-level recommendation policy with expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$.
+This $L$-level recommendation policy does not need to know $\Delta$.
+Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$.
+\end{theorem}
+
+\xhdr{Proof Sketch.}
+We first extend the clean events (i.e.
+$W_1,W_2,W_3,W_4$) in Theorem \ref{thm:llevel} to the case when $K$ is larger than 2.
+$W_1$ and $W_2$ extend naturally: we still set $W_1 = \bigcap_{a,s}W_1^{a,s}$ and $W_2 = \bigcap_{t,a,t_1,t_2} W_2^{t,a,t_1,t_2}$.
+The difference is that now $a$ is taken over $K$ arms instead of 2 arms.
+For $W_3$, we change the definition $W_3^{l,a} = \bigcup_u \left(W_3^{l,u,a,high}  \cap \left(\bigcap_{a' \neq a} W_3^{l,u,a',low}\right) \right)$ and $W_3 = \bigcap_{l,a} W_3^{l,a}$.
+We extend $W_4$ in a similar way: define $W^{a}_4$ as $\bigcup_u \left(W_4^{u,a,high} \cap \left(\bigcap_{a' \neq a} W_4^{u,a',low}\right) \right)$ and $W_4 = \bigcap_a W^a_4$.
+Since $K$ is a constant, it's easy to check that the same proof technique shows that the intersection of these clean events happen with probability  $1-O(1/T)$.
+
+\qed

### 2018-10-16 model.tex
ok.

@@
 reward $r_t\in \{0,1\}$ that is immediately observed by the
-principal.
+principal. Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by
+the agents, the \emph{regret} is defined as
+\[
+  \reg(T)= \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a -
+  \sum_{t=1}^T \mu_{a_t}.
+\]
 
@@
 
-\xhdr{Unbiased sub-history policy.} The principal computes the
-sequence of messages $m_t$ according to a disclosure policy. We will
-focus on \emph{unbiased sub-history policies} that at each round $t$
-reveal the \emph{sub-history} in a subset of previous rounds
+\xhdr{Unbiased sub-history policy.} The principal's goal is to reveals
+a sequence of messages accroding to a disclosure policy so that the
+regret of the induced sequence of actions is minimized. We will focus
+on \emph{unbiased sub-history policies} that at each round $t$ reveal
+the \emph{sub-history} in a subset of previous rounds
 $S_t\subseteq [t-1]$: $\{(s, a_s, r_s)\mid s \in S_t\}$, where the
@@
 bounded range $[1/3, 2/3]$ for the simplicity of our analysis, and it
-can further relaxed to $[1/C, (C-1)/C]$ for any constant $C$.
+can further relaxed to $[1/C, (C-1)/C]$ for any constant $C$. The
+second assumption says that the estimates computed by the agents are
+well-behaved, and are close to the empirical estimates given by the
+sub-history, provided that the number of observations is sufficiently
+large.
 
@@
 \begin{remark}
-how this relates to Bayesian exploration with conjugate priors
+  how this relates to Bayesian exploration with conjugate
+  priors\swcomment{seems to be something nasty}
 \end{remark}
 
-\swcomment{todo: define regret. define gap $\Delta$}
-
-Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by the agents, the \emph{regret} is defined as
-\[
-  \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a - \sum_{t=1}^T
-  \mu_{a_t}.
-\]
-
-The principal's goal is then to design a policy to minimize the regret
-from the induced sequence arms chosen by agents.
+Given any bandit instance, we can also define the \emph{gap parameter}
+$\Delta$ as the difference between the largest and second largest mean
+rewards. In general, the gap parameter is unknown to the principal (or
+the algorithm), but we also show how we can obtain different forms of
+regret bounds if $\Delta$ is known.
 

### 2018-10-16 algg.tex
rewriting

--- 2018-10-01 algg.tex
@@
 %!TEX root = main.tex
-\section{\ALGG}
-We first consider \ALGG which simply shows agents the full history. We discuss in this section the exploration of \ALGG under Assumption \ref{ass:embehave}.
+\section{\ALGG: Revealing Full History}
+
+\swedit{Before we describe our algorithms, we will first analyze a
+  simple policy \ALGG that fully discloses the history over all
+  previous rounds, and lets the agents make the ``greedy'' choices
+  across all rounds. Even though the algorithm does not guarantee low
+  regret, it will be used as a subroutine in our main algorithms.  In
+  particular, we show that because of the randomness in the rewards,
+  with constant probability, $\ALGG$ will incentivize the agents to
+  play each arm at least once.}
 
@@
 \label{lem:greedy}
-There exist two constants $\GdT = O_K(1)$ and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least once. 
+Under \Cref{ass:embehave}, there exist two constants $\GdT = O_K(1)$
+and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability
+at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least
+once.\footnote{The notations $O_k$ and $\Omega_K$ hide the dependence
+  on the number of arms $K$.}
 \end{lemma}
@@
 \begin{proof}
-Set $\GdT = (K-1) \cdot c_T + 1$ and $\GdP = (1/3)^{\GdT}$. We fix the behavior of agents in $\GdT$ rounds and consider the case that all realized rewards in $\GdT$ rounds are 0.
+  Set $\GdT = (K-1) \cdot c_T + 1$ and $\GdP = (1/3)^{\GdT}$. We fix
+  the behavior of agents in $\GdT$ rounds and consider the case that
+  all realized rewards in $\GdT$ rounds are 0.
 
@@
 
-On the other hand, we know that this case happens with probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is at most $2/3$.
-To sum up, we know that with probability at least $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.
+In addition, we know that this case happens with probability at least
+$(1/3)^{\GdT} = \GdP$ as each arm's mean is at most $2/3$. To sum up,
+we know that with probability at least $\GdP$, \ALGG of $\GdT$ rounds
+pulls arm $a$ at least once.
 \end{proof}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2018-10-16 algg.tex
stuff

@@
   particular, we show that because of the randomness in the rewards,
-  with constant probability, $\ALGG$ will incentivize the agents to
+  with constant probability, \ALGG will incentivize the agents to
   play each arm at least once.}
@@
 \label{lem:greedy}
-Under \Cref{ass:embehave}, there exist two constants $\GdT = O_K(1)$
+Under Assumption \ref{ass:embehave}, there exist two constants $\GdT = O_K(1)$
 and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability
@@
 \begin{proof}
-  Set $\GdT = (K-1) \cdot c_T + 1$ and $\GdP = (1/3)^{\GdT}$. We fix
-  the behavior of agents in $\GdT$ rounds and consider the case that
-  all realized rewards in $\GdT$ rounds are 0.
-
-In this case, we want to show that arm $a$ is pulled at least once.
-We prove by contradiction.
-Suppose arm $a$ is not pulled.
-By averaging argument, we know that there is some other arm $a'$ which is pulled at least $c_T + 1$ rounds.
-Suppose in round $t$, arm $a'$ is pulled exactly $c_T + 1$ times.
-By Assumption \ref{ass:embehave}, we know
+  Fix any arm $a$. Let $\GdT = (K-1) \cdot c_T + 1$ and
+  $\GdP = (1/3)^{\GdT}$. \swedit{We will condition on the event that
+    all realized rewards in $\GdT$ rounds are 0, which occurs with
+    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.}
+  In this case, we want to show that arm $a$ is pulled at least
+  once. We prove by contradiction. Suppose arm $a$ is not pulled. By
+  the pigeonhole principle, we know that there is some other arm $a'$
+  that is pulled at least $c_T + 1$ rounds. Let $t$ be the round in
+  which arm $a'$ is pulled exactly $c_T + 1$ times. By Assumption
+  \ref{ass:embehave}, we know
   \[
@@
   \]
-On the other hand, we have $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with the fact that in round $t$, arm $a'$ is pulled.
-
-In addition, we know that this case happens with probability at least
-$(1/3)^{\GdT} = \GdP$ as each arm's mean is at most $2/3$. To sum up,
-we know that with probability at least $\GdP$, \ALGG of $\GdT$ rounds
-pulls arm $a$ at least once.
+  On the other hand, we have
+  $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
+  the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
+  \swdelete{ In addition, we know that this case happens with
+    probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is
+    at most $2/3$. To sum up, we know that with probability at least
+    $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.}
 \end{proof}

### 2018-10-17 llevel.tex
update thm 6.5

@@
 \begin{proof}
-We are going to show that for each $l$ and $a$ there exists $u_a$ such that agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$.
+We are going to show that for each $l$ and arm $a$ there exists $u_a$ such that agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$.
 This suffices to prove the claim.
@@
 \end{itemize}
+
+Finally we discuss about the subhistory sizes.
+We know that agents in level $l$ observes the history of all agents below level $l-2$ (including level $l-2$).
+It is easy to check that the ratio between the number of agents below level $l$ and the number of agents below level $l-2$ is bounded by $O(polylog(T))$.
+Therefore our statement about the subhistory sizes holds.
 \end{proof}
@@
 \begin{theorem}
-Let the number of arms $K$ to be a constant larger than 2.
-Let $\Delta$ to be the difference between means of best and second best arms.
-We have an $L$-level recommendation policy with expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$.
-This $L$-level recommendation policy does not need to know $\Delta$.
-Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$.
+Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel} can be extended to the case when $K$ is constant larger than 2.
+In the extension of Corollary \ref{cor:llevel}, $\Delta$ is defined as the difference between means of the best and the second best arm.
 \end{theorem}
@@
 \xhdr{Proof Sketch.}
+We still wlog assume arm 1 has the highest mean (i.e.
+$\mu_1 \geq \mu_a, \forall a \in \A$.
 We first extend the clean events (i.e.
@@
 Since $K$ is a constant, it's easy to check that the same proof technique shows that the intersection of these clean events happen with probability  $1-O(1/T)$.
+So the case when some clean event does not happen contributes $O(1)$ to the expected regret.
 
+Now we proceed to extend Claim \ref{clm:l2_explore} and Claim \ref{clm:l2_exploit}.
+The statement of Claim \ref{clm:l2_explore} should be changed to ``For any arm $a$ and $2\leq l \leq L$, if $\mu_1 - \mu_a \leq \varepsilon_{l-1}$, then for any $u \in [S]$, there are at least $T_l$ pulls of arm $a$ in groups $G_{l,u,1},G_{l,u,2}, ...
+,G_{l,u,S}$ and there are at least $T_lS(S-1)$ pulls of arm $a$ in the $l$-th level $\Gamma$-groups''.
+The statement of Claim \ref{clm:l2_exploit} should be changed to ``For any $2 \leq l \leq L$, if $\varepsilon_{l-1} S\leq \mu_1 - \mu_a < \varepsilon_{l-2} S$, there are no pulls of arm $a$ in groups with level $l,...,L$.''
+
+The proof of Claim \ref{clm:l2_exploit} can be easily changed to prove the new version by changing ``arm 2'' to ``arm $a$''.
+The proof of Claim \ref{clm:l2_explore} needs some additional argument.
+In the proof of Claim \ref{clm:l2_explore}, we show that $\hat{\mu}_a^t - \hat{\mu}_{3-a} > 0 $ for agent $t$ in the chosen groups.
+When extending to more than 2 arms, we need to show $\hat{\mu}_a^t - \hat{\mu}_{a'}^t > 0$ for all arm $a' \neq a$.
+The proof of Claim \ref{clm:l2_explore} goes through if $\mu_1- \mu_{a'} \leq \varepsilon_{l-2}$ since then there will be enough arm $a'$ pulls in level $l-1$.
+We need some additional argument for the case when $\mu_1 - \mu_{a'} > \varepsilon_{l-2}$.
+Since $\mu_1- \mu_{a'} > \varepsilon_{l-2} > \varepsilon_{l-1}S$, we can use the same proof of Claim \ref{clm:l2_exploit} (which rely on Claim \ref{clm:l2_explore} but for smaller $l$'s) to show that there are no arm $a'$ pulls in level $l$ and therefore $\hat{\mu}_a^t - \hat{\mu}_{a'}^t > 0$.
+
+Finally we proceed to bound the expected regret conditioned on the intersection of clean events happens.
+The proofs of Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel} bound it by consider the regret from pulling the suboptimal arm (i.e.
+arm 2).
+When extending to more than 2 arms, we can do the exactly same argument for all arms except arm 1.
+This will blow up the expected regret by a factor of $(K-1)$ which is a constant.
 \qed

### 2018-10-17 2level.tex
Respond to Steven's comments

@@
   pulls in one run of \ALGG used in the first level.\swcomment{$q_a$
-    probability or number?? the issue propagates downwards} By Lemma
+    probability or number?? the issue propagates downwards} 
+    \jmcomment{$q_a$ is the expected number.}
+    By Lemma
   \ref{lem:greedy}, we know $\GdP \leq q_a \leq
-  \GdT$.\swcomment{$p_G T$?} Define $W_1^a$ to be the event that the
+  \GdT$.\swcomment{$p_G T$?}
+  \jmcomment{$q_a$ is only for one run of greedy. Not $T_1$ runs of greedy.}
+   Define $W_1^a$ to be the event that the
   number of arm $a$ pulls in the first level is at least
   $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$.\swcomment{what
-    is the condition on $T_1$ and $T_G$ for this to hold?} By Chernoff
+    is the condition on $T_1$ and $T_G$ for this to hold?} 
+    \jmcomment{$\GdT$ is a constant. This holds if $T_1 = \omega(\log(T))$ and $T$ is a larger than some constant.}
+    By Chernoff
   bound,

### 2018-10-17 model.tex
Respond to Steven's comments

@@
 distributed according to the Bernoulli distribution with an unknown
-mean $\mu_a$.\swcomment{do we plan to generalize to real-valued?}  At
-each round $t\in [T]$, a new agent $t$ arrives, receives a message
+mean $\mu_a$.\swcomment{do we plan to generalize to real-valued?}  
+\jmcomment{Probably not.
+We probably need some weird assumptions to make it work and we may need to change many parts of our proofs.
+The assumptions will be like: enough variance for anti-concentration and even more stuff for the greedy to has a small chance to work.
+Probably binary sound more natural and practical.
+And we should state something like binary should be interpreted as the feedback from the user, i.e.
+``like'' or ``dislike''.}
+At each round $t\in [T]$, a new agent $t$ arrives, receives a message
 $m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a
@@
 \label{ass:embehave}
-Let $c_m = 1/16$.\swcomment{subscript $m$ meant anything?}. 
+Let $c_m = 1/16$.\swcomment{subscript $m$ meant anything?} \jmcomment{It means a constant for some assumptions about means but nothing else.
+Just want to make it different from other constants.
+Maybe there are better notations.}.
 \begin{itemize}
@@
 distribution independently.\swcomment{why independently? can be be
-  adversarial?}
+  adversarial?} \jmcomment{Actually current proofs don't work when it's adversarial.
+It's fairly annoying for the anti-concentration argument.
+In the proof, we need to use independent to show that the amount of agents pulling arm $a$ in the first level is concentrated to $T_1 q_a$.}
 \begin{remark}

### 2018-10-19 model.tex
stuff

--- 2018-10-16 model.tex
@@
 distributed according to the Bernoulli distribution with an unknown
-mean $\mu_a$.\swcomment{do we plan to generalize to real-valued?}  At
-each round $t\in [T]$, a new agent $t$ arrives, receives a message
+mean $\mu_a$.% \swcomment{do we plan to generalize to real-valued?}  
+% \jmcomment{Probably not.
+We probably need some weird assumptions to make it work and we may need to change many parts of our proofs.
+The assumptions will be like: enough variance for anti-concentration and even more stuff for the greedy to has a small chance to work.
+Probably binary sound more natural and practical.
+And we should state something like binary should be interpreted as the feedback from the user, i.e.
+``like'' or ``dislike''.}
+At each round $t\in [T]$, a new agent $t$ arrives, receives a message
 $m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a
@@
 on \emph{unbiased sub-history policies} that at each round $t$ reveal
-the \emph{sub-history} in a subset of previous rounds
-$S_t\subseteq [t-1]$: $\{(s, a_s, r_s)\mid s \in S_t\}$, where the
-subset $S_t$ is fixed ahead of time. A simple example is the policy
-that reveals the \emph{full history}, that is $S_t = [t-1]$.  All of
-the policies we develop are \emph{transitive}: for any two agents $t$
-and $t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains
+the \emph{sub-history} $H_t = \{(s, a_s, r_s)\mid s \in S_t\}$, such
+that each $S_t\subseteq [t-1]$ is a subset of previous rounds
+\emph{fixed ahead of time}. A simple example is the policy that
+reveals the \emph{full history} with $S_t = [t-1]$.  All of the
+policies we develop are \emph{transitive}: for any two agents $t$ and
+$t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains
 that of $S_{t'}$.
@@
 
-\xhdr{Agents' behavior.} Based on the history over rounds $S_t$, each
-agent $t$ first computes an estimate $\hat{\mu}_a^t$ for the mean
-reward of each arm $a$, and then selects the arm with the highest
-$\hat{\mu}_a^t$. Let $t_a$ be the number of times arm $a$ is pulled in
-the observed history $S_t$. For any $a$ with $t_a > 0$, we write
-$\bar{\mu}_a^t$ as the empirical average of arm $a$ given the history.
+\xhdr{Agents' behavior.} We model agents with heterogeneity in their
+arm selections. In particular, each agent $t$ has a private estimator
+that maps the revealed sub-history $H_t$ to a mean reward estimate
+$\hat{\mu}_a^t$ for every arm $a$, and the agent chooses the arm $a_t$
+with the highest estimate. The agents' private estimators are drawn
+i.i.d.~from some distribution. For any $t\in[T]$ and $a\in \A$, we
+write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls of
+$a$ and the empirical mean reward of arm $a$ in $H_t$ respectively. If
+an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.
 
+% \swcomment{need to assume i.i.d. types}
 % We assume that for sufficiently high $t_a$, the estimate
@@
 $\{\mu_a\}$, and the relationship between the estimates $\hat \mu_a^t$
-.and empirical mean rewards $\bar\mu_a^t$.
+and empirical mean rewards $\bar\mu_a^t$.
 
@@
 \label{ass:embehave}
-Let $c_m = 1/16$.\swcomment{subscript $m$ meant anything?}. 
+Let $c_m = 1/16$.\swcomment{maybe use a better notation} 
+% \jmcomment{It means a constant for some assumptions about means but nothing else. Just want to make it different from other constants. Maybe there are better notations.}. 
 \begin{itemize}
@@
   \left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
-  \frac{c_m}{\sqrt{t_a}}.
+  \frac{c_m}{\sqrt{N_{t,a}}}.
 \]
-\item In the case of $t_a = 0$, the initial estimate $\hat{\mu}^t_a$
-  is at least $1/3$.
+\item In the case of $N_{t,a} = 0$, the initial estimate
+  $\hat{\mu}^t_a$ is at least $1/3$.
 \end{itemize}
@@
 assume each agent's behavior model is sampled from an unknown
-distribution independently.\swcomment{why independently? can be be
-  adversarial?}
+distribution independently.
+% \swcomment{why independently? can be be
+%   adversarial?} \jmcomment{Actually current proofs don't work when it's adversarial.
+It's fairly annoying for the anti-concentration argument.
+In the proof, we need to use independent to show that the amount of agents pulling arm $a$ in the first level is concentrated to $T_1 q_a$.}
 \begin{remark}

### 2018-10-21 2level.tex
stoc

@@
 %!TEX root = main.tex
-\section{Warm-up: 2-level Recommendation Policy}
-In this section, we are going to show a 2-level recommendation policy that gets sublinear regret.
+\section{Warm-up:  Explore-then-Exploit Policy}
+\swedit{Now we provide a simple policy that can incentivize the agents
+  to perform non-adaptive exploration and achieve a sublinear regret
+  rate. The policy essentially follows the ``explore-then-exploit''
+  paradigm and consists two phases, which can be described as a
+  two-level information graph (as shown in Figure~\ref{fig:2level}).
+  In the first level, we perform exploration by simulating $T_1$
+  independent runs \ALGG of $\GdT$ rounds. This is done by randomly
+  dividing the first $T_1 \cdot \GdT$ agents into $T_1$ groups of
+  equal size and each agent only observe the history of all previous
+  agents in the same group.  In the second level, we ``exploit'' by
+  showing all the remaining agents the entire history of first phase.
 
+  The key idea behind the policy is that the first level effectively
+  boosts the exploration probability of \ALGG. Since each run of \ALGG
+  explores all arms with constant probability (Lemma
+  \ref{lem:greedy}), by simulating multiple runs of \ALGG, we can
+  ensure that with high probability, every arm is pulled with a
+  sufficient number of times. As a result, every agent in the second
+  level will pull an arm with mean rewards close to optimal.
+
+}
+
+\iffalse
 The 2-level recommendation policy is constructed as following.
@@
 After that, by concentration argument, we can show that while observing the history of the first level, agents in the second level pick an arm with mean close to the best arm's mean.
+\fi
 
@@
 \end{tikzpicture}
-\caption{2-level Recommendation Policy.}
+
+\caption{Structure of information graph for the 2-level policy. Each
+  red ``box'' is level 1 corresponds to a path connecting a set of
+  $T_G$ agents. The entire history in level 1 is then aggregated and
+  shown to each agent in level 2.}
 \label{fig:2level}
@@
 \label{thm:2level}
-With proper setting of $T_1$, the 2-level recommendation policy gets expected regret $O(T^{2/3} \log(T)^{1/3})$.
-If we know the gap between the means of the best arm and second best arm is larger than $\Delta$, we can make the expected regret $O(\log(T) \cdot \Delta^{-2})$.
+With proper setting of $T_1$, the 2-level policy gets expected regret
+$O(T^{2/3} \log(T)^{1/3})$. If we know the gap between the means of
+the best arm and second best arm is larger than $\Delta$, we can make
+the expected regret $O(\log(T) \cdot \Delta^{-2})$.
 \end{theorem}

### 2018-10-21 model.tex
oh yea
stoc

@@
 policies using a \emph{information flow graph} (and henceforth
-\emph{info graph})---a directed graph over the $T$ agents such that if
+\emph{information graph})---a directed graph over the $T$ agents such that if
 there is an edge from $u$ to $v$, it means $u\in S_v$. By the property
@@
 with the highest estimate. The agents' private estimators are drawn
-i.i.d.~from some distribution. For any $t\in[T]$ and $a\in \A$, we
-write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls of
-$a$ and the empirical mean reward of arm $a$ in $H_t$ respectively. If
-an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.
+i.i.d.~from an unknown distribution. For any $t\in[T]$ and $a\in \A$,
+we write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls
+of $a$ and the empirical mean reward of arm $a$ in $H_t$
+respectively. If an arm is not pulled in $H_t$, we will let
+$\bar{\mu}_a^t = 0$.
 

### 2018-10-22 2level.tex
2level

@@
 \swedit{Now we provide a simple policy that can incentivize the agents
-  to perform non-adaptive exploration and achieve a sublinear regret
-  rate. The policy essentially follows the ``explore-then-exploit''
-  paradigm and consists two phases, which can be described as a
-  two-level information graph (as shown in Figure~\ref{fig:2level}).
-  In the first level, we perform exploration by simulating $T_1$
-  independent runs \ALGG of $\GdT$ rounds. This is done by randomly
-  dividing the first $T_1 \cdot \GdT$ agents into $T_1$ groups of
-  equal size and each agent only observe the history of all previous
-  agents in the same group.  In the second level, we ``exploit'' by
-  showing all the remaining agents the entire history of first phase.
+  to perform non-adaptive exploration and achieve a regret rate of
+  $\tilde O(T^{2/3})$. The policy essentially follows the
+  ``explore-then-exploit'' paradigm and consists two phases, which can
+  be described as a two-level information graph (as shown in
+  Figure~\ref{fig:2level}).  In the first level, we perform
+  exploration by simulating $T_1$ independent runs \ALGG of $\GdT$
+  rounds. This is done by randomly dividing the first $T_1 \cdot \GdT$
+  agents into $T_1$ groups of equal size and each agent only observe
+  the history of all previous agents in the same group.  In the second
+  level, we ``exploit'' by showing all the remaining agents the entire
+  history of first phase.
 
   The key idea behind the policy is that the first level effectively
-  boosts the exploration probability of \ALGG. Since each run of \ALGG
-  explores all arms with constant probability (Lemma
-  \ref{lem:greedy}), by simulating multiple runs of \ALGG, we can
+  boosts the exploration probability of Greedy. Since each run of
+  \ALGG explores all arms with constant probability (Lemma
+  \ref{lem:greedy}), by simulating multiple runs of Greedy, we can
   ensure that with high probability, every arm is pulled with a
   sufficient number of times. As a result, every agent in the second
-  level will pull an arm with mean rewards close to optimal.
+  level will pull an arm with mean rewards close to the optimal.
 
@@
 
+\swcomment{I think this proof should go to appendix, so I didn't do
+  too much refactoring}
+
 \begin{proof}
-We will set $T_1$ later in the proof.
-For now, we just need to know we will make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$.
-Since this recommendation policy is symmetric over arms, we wlog assume that arm 1 has the highest mean in the proof.
+  We will set $T_1$ later in the proof, depending on whether the gap
+  parameter $\Delta$ is known. For now, we just need to know we will
+  make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$. Since this policy is
+  agnostic to the indices of the arms, we assume w.l.o.g. that arm 1
+  has the highest mean.
 
-The first $T_1 \cdot \GdT$ rounds will get total regret at most $T_1 \cdot \GdT$.
-We focus on bounding the regret of the rest $T - T_1 \cdot \GdT$ rounds.
-We consider the following two clean events.
-We will first bound the probability that both of them happen and then we will show that they together imply upper bounds on $|\hat{\mu}^t_a - \mu_a|$'s for any agent $t$ in the second level.
-Recall $\hat{\mu}^t_a$ is the estimated mean of arm $a$ by agent $t$ and agent $t$ picks the arm with the highest $\hat{\mu}^t_a$.
+  The first $T_1 \cdot \GdT$ rounds will get total regret at most
+  $T_1 \cdot \GdT$.  We focus on bounding the regret from the second
+  level of $T - T_1 \cdot \GdT$ rounds. We consider the following two
+  clean events. We will first bound the probability that both of them
+  happen and then we will show that they together imply upper bounds
+  on $|\hat{\mu}^t_a - \mu_a|$'s for any agent $t$ in the second
+  level. Recall $\hat{\mu}^t_a$ is the estimated mean of arm $a$ by
+  agent $t$ and agent $t$ picks the arm with the highest
+  $\hat{\mu}^t_a$.
 
-\begin{itemize}
-\item \textbf{Concentration of the number of arm $a$ pulls in the first level:}
-
+% \begin{itemize}
+  \paragraph{Concentration of the number of arm $a$ pulls in the first
+    level.}
   For each arm $a$, define $q_a$ to be the expected number of arm $a$
-  pulls in one run of \ALGG used in the first level.\swcomment{$q_a$
-    probability or number?? the issue propagates downwards} 
-    \jmcomment{$q_a$ is the expected number.}
-    By Lemma
-  \ref{lem:greedy}, we know $\GdP \leq q_a \leq
-  \GdT$.\swcomment{$p_G T$?}
-  \jmcomment{$q_a$ is only for one run of greedy. Not $T_1$ runs of greedy.}
-   Define $W_1^a$ to be the event that the
-  number of arm $a$ pulls in the first level is at least
-  $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$.\swcomment{what
-    is the condition on $T_1$ and $T_G$ for this to hold?} 
-    \jmcomment{$\GdT$ is a constant. This holds if $T_1 = \omega(\log(T))$ and $T$ is a larger than some constant.}
-    By Chernoff
-  bound,
+  pulls in a single run of \ALGG used in the first level.  By Lemma
+  \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. Define $W_1^a$
+  to be the event that the number of arm $a$ pulls in the first level
+  is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.  \swedit{As long as
+    we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$, this implies that
+    the number of arm $a$ pulls is then at least $q_a T_1/2$.}  By
+  Chernoff bound,
   \[
@@
 \]
-\item  \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
-
-For each arm $a$, imagine there is a tape of $T$ arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agent pull arm $a$.
-Define $W^{a,t}_2$ to be the event that the empirical mean of the first $t$ pulls of arm $a$ is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.
-Define $W_2$ to be the intersection of these events (i.e.
-$\bigcap_{a,t} W^{a,t}_2$).
-By Chernoff bound,
+\paragraph{Concentration of the empirical mean of arm $a$ pulls in the first level.}
+To facilitate our reasoning, let us imagine there is a tape of length
+$T$ for each arm $a$, with each cell containing an independent draw of
+the realized reward from the distribution Ber$(\mu_a)$. Then for each
+arm $a$ and any $N\in [T]$, we can think of the sequence of the first
+$N$ realized rewards of $a$ coming from the prefix of $N$ cells in its
+reward tape. Define $W^{a,t}_2$ to be the event that the empirical
+mean of the first $t$ \swedit{realized rewards in the tape} of arm $a$
+is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$
+to be the intersection of these events (i.e.
+$\bigcap_{a,t} W^{a,t}_2$).  By Chernoff bound,\swcomment{$t$ may be
+  confusing here}
 \[
@@
 \]
-\end{itemize}
 
-By union bound, we know $\Pr[W_1 \cap W_2] \geq 1 - 3/T$. Now we consider the case when $W_1 \cap W_2$ happens.
+By union bound, we know $\Pr[W_1 \cap W_2] \geq 1 - 3/T$. For the
+remainder of the analysis, we will condition on the event
+$W_1 \cap W_2$.
 
@@
 
-Notice that if we know the gap between the means of the best arm and second best arm is larger than $\Delta$, we can set 
+Notice that if we know the gap parameter is known to be larger than
+$\Delta$, we can set
 \[
@@
 \]
+This completes the proof.
 \end{proof}

### 2018-10-22 model.tex
2level

@@
 distributed according to the Bernoulli distribution with an unknown
-mean $\mu_a$.% \swcomment{do we plan to generalize to real-valued?}  
-% \jmcomment{Probably not.
-We probably need some weird assumptions to make it work and we may need to change many parts of our proofs.
-The assumptions will be like: enough variance for anti-concentration and even more stuff for the greedy to has a small chance to work.
-Probably binary sound more natural and practical.
-And we should state something like binary should be interpreted as the feedback from the user, i.e.
-``like'' or ``dislike''.}
-At each round $t\in [T]$, a new agent $t$ arrives, receives a message
-$m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a
-reward $r_t\in \{0,1\}$ that is immediately observed by the
-principal. Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by
-the agents, the \emph{regret} is defined as
+mean $\mu_a$. At each round $t\in [T]$, a new agent $t$ arrives,
+receives a message $m_t$ from the principal, chooses an arm
+$a_t\in \A$, and collects a reward $r_t\in \{0,1\}$ that is
+immediately observed by the principal. Given any sequence of arms
+$\{a_1, \ldots, a_T\}$ chosen by the agents, the \emph{regret} is
+defined as
 \[

### 2018-10-23 3level.tex
edits
stuff

@@
 \section{3-level Recommendation Policy}
-In this section, we show how to get $o(T^{2/3})$ regret with a 3-level recommendation policy. For simplicity, we assume there are only 2 arms.
+Now we demonstrate how to design a policy to incentivize adaptive
+exploration and improve on the $O(T^{2/3})$ regret rate. For
+simplicity, we assume there are only 2 arms.
 
@@
 \item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
-
+\swcomment{can we reuse the previous result?}
 For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
@@
 \end{proof}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2018-10-23 3level.tex
leveling

@@
 
-\section{3-level Recommendation Policy}
-Now we demonstrate how to design a policy to incentivize adaptive
-exploration and improve on the $O(T^{2/3})$ regret rate. For
-simplicity, we assume there are only 2 arms.
+\section{3-level Adaptive Policy}
+\label{sec:3level}
+Now we demonstrate how to design a e-level policy to incentivize
+adaptive exploration and improve on the $O(T^{2/3})$ regret rate. In
+\Cref{sec:llevel}, we will show how to extend this idea to achieve a
+regret rate of $\tilde O(T^{1/2})$. For simplicity, we will focus on
+the setting with 2 arms.
 

### 2018-10-23 3level.tex
refactoring

@@
 \label{sec:3level}
-Now we demonstrate how to design a e-level policy to incentivize
-adaptive exploration and improve on the $O(T^{2/3})$ regret rate. In
-\Cref{sec:llevel}, we will show how to extend this idea to achieve a
-regret rate of $\tilde O(T^{1/2})$. For simplicity, we will focus on
-the setting with 2 arms.
+Now we demonstrate how to design a 3-level policy to incentivize
+adaptive exploration and improve the $O(T^{2/3})$ regret rate to
+$\tilde O(T^{4/7})$. In \Cref{sec:llevel}, we will show how to extend
+this idea to achieve a regret rate of $\tilde O(T^{1/2})$. For
+simplicity, we will focus on the setting with 2 arms.
 
-The 3-level recommendation policy is constructed as following.
-Set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 = T^{6/7}\log^{-5/7}(T)$.
-The first level has $S = 2^{10}\log(T)$ groups of agents.
-Each group runs $T_1$ \ALGG of $T_G$ rounds in parallel.
-The second level also has $S$ groups of agents.
-Each group has $T_2$ agents and they observe the history of corresponding group in the first level.
-All the rest agents are in the third level and they observe the entire history of the first two levels.
-See also Figure \ref{fig:3level} for a graphical view of the information flow.
+The policy consists of three phases, each of which corresponds to a
+level (see Figure~\ref{fig:3level}).  In the first level, the policy
+performs the first round of exploration over the first
+$(S\cdot T_1\cdot T_G)$ agents, where $T_1 = T^{4/7}\log^{-1/7}(T)$
+and $S = 2^{10}\log(T)$. In particular, the policy randomly partitions
+the agents into $S$ groups such that each group consists of $T_1$ runs
+of \ALGG with $T_G$ rounds. In the second level, the policy performs
+further exploration on the next $(S\cdot T_2)$ agents by incorporating
+data collected in the first level, where
+$T_2 = T^{6/7}\log^{-5/7}(T)$. The agents are again partitioned into
+$S$ groups such that the agents in the $s$-th group are shown the same
+sub-history from the $s$-th group in the first level. In the third
+level, the policy exploits by showing all remaining agents the entire
+history from the first two levels.
 
-Here we give some intuition about how the 3-level recommendation policy works.
-The main idea is to do the exploration more adaptively.
-In the first level, agents explore both arms.
-In the second level, agents will pull the best arm when $\mu_1 - \mu_2$ is large ($\tilde{\Omega}(1/\sqrt{T_1})$).
-Otherwise agents will explore both arms more.
-In the third level, agents will pull the best arm unless $\mu_1-\mu_2$ is much smaller ($\tilde{O}(1/\sqrt{T_2})$).
-In the proof, we need not only the concentration argument as the 2-level recommendation policy, but also the anti-concentration argument to show that agents explore more in the second round if $\mu_1-\mu_2$ is not too big.
+They main idea for the 3-level policy is that it inserts the second
+level as an additional ``checkpoint'' to induce more adaptivity in the
+exploration. By running \ALGG in parellel, the first level ensures
+that the agents explore both arms. In the second level, agents will
+pull the best arm when $\mu_1 - \mu_2$ is large
+($\tilde{\Omega}(1/\sqrt{T_1})$). Otherwise agents will explore both
+arms more. In the third level, agents will pull the best arm unless
+$\mu_1-\mu_2$ is much smaller ($\tilde{O}(1/\sqrt{T_2})$). In the
+proof, we need not only the concentration argument as the 2-level
+recommendation policy, but also the anti-concentration argument to
+show that agents explore more in the second round if $\mu_1-\mu_2$ is
+not too big.
+
+\iffalse
+Set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 =
+T^{6/7}\log^{-5/7}(T)$. The first level has $S = 2^{10}\log(T)$ groups
+of agents. Each group runs $T_1$ \ALGG of $T_G$ rounds in
+parallel. The second level also has $S$ groups of agents. Each group
+has $T_2$ agents and they observe the history of corresponding group
+in the first level. All the rest agents are in the third level and
+they observe the entire history of the first two levels.  See also
+Figure \ref{fig:3level} for a graphical view of the information flow.
+
+Here we give some intuition about how the 3-level recommendation
+policy works. The main idea is to do the exploration more
+adaptively. In the first level, agents explore both arms. In the
+second level, agents will pull the best arm when $\mu_1 - \mu_2$ is
+large ($\tilde{\Omega}(1/\sqrt{T_1})$). Otherwise agents will explore
+both arms more. In the third level, agents will pull the best arm
+unless $\mu_1-\mu_2$ is much smaller ($\tilde{O}(1/\sqrt{T_2})$). In
+the proof, we need not only the concentration argument as the 2-level
+recommendation policy, but also the anti-concentration argument to
+show that agents explore more in the second round if $\mu_1-\mu_2$ is
+not too big.  \fi
 
@@
 \end{tikzpicture}
-\caption{3-level Recommendation Policy.}
+\caption{3-level Policy.}
 \label{fig:3level}
 \end{figure}
+\swcomment{can we index the indicate there are $S$ groups in the figure?}
 
@@
 \item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
-
+\swcomment{reusable?}
 For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$.

### 2018-10-23 3level.tex
stuff

@@
 level as an additional ``checkpoint'' to induce more adaptivity in the
-exploration. By running \ALGG in parellel, the first level ensures
-that the agents explore both arms. In the second level, agents will
-pull the best arm when $\mu_1 - \mu_2$ is large
-($\tilde{\Omega}(1/\sqrt{T_1})$). Otherwise agents will explore both
-arms more. In the third level, agents will pull the best arm unless
-$\mu_1-\mu_2$ is much smaller ($\tilde{O}(1/\sqrt{T_2})$). In the
-proof, we need not only the concentration argument as the 2-level
-recommendation policy, but also the anti-concentration argument to
-show that agents explore more in the second round if $\mu_1-\mu_2$ is
-not too big.
+exploration. While the first level ensures that the agents explore
+both arms, the second level will continue to explore both arms only if
+the rewards of the two arms are still indistinguishable (that is, when
+$|\mu_1 - \mu_2| < \tilde{O}(1/\sqrt{T_1})$). In the third level,
+agents will pull the best arm unless $|\mu_1-\mu_2|$ is much smaller
+than $\tilde{O}(1/\sqrt{T_2})$, in which case pulling either arm will
+incur small regret. The formal guarantee of the policy is the
+following.
+
+\begin{theorem}
+\label{thm:3level}
+The 3-level recommendation policy gets expected regret $O(T^{4/7} \log^{6/7}(T))$. 
+\end{theorem}
+
+In the proof, we need not only the concentration argument as the
+2-level recommendation policy, but also the anti-concentration
+argument to show that agents explore more in the second round if
+$\mu_1-\mu_2$ is not too big.
 
@@
 show that agents explore more in the second round if $\mu_1-\mu_2$ is
-not too big.  \fi
+not too big.
+\fi
 
@@
 \swcomment{can we index the indicate there are $S$ groups in the figure?}
-
-\begin{theorem}
-\label{thm:3level}
-The 3-level recommendation policy gets expected regret $O(T^{4/7} \log^{6/7}(T))$. 
-\end{theorem}
 

### 2018-10-23 3level.tex
stuff

@@
 \label{sec:3level}
+\swcomment{rewrote below}
 Now we demonstrate how to design a 3-level policy to incentivize
@@
 \end{tikzpicture}
-\caption{3-level Policy.}
+\caption{Structure of the information graph for the 3-level
+  Policy. Each red box in level 1 corresponds to $T_1$ \ALGG paths of
+  length $T_G$. The sub-history of each red box is then aggregated and
+  sent to a corresponding purple box of agents in level 2. Then the
+  entire history of levels 1 and 2 is aggregated and shown to all
+  agents in level 3.}
 \label{fig:3level}
 \end{figure}
-\swcomment{can we index the indicate there are $S$ groups in the figure?}
+\swcomment{check the figure caption above. can we index the indicate
+  there are $S$ groups in the figure?}
 

### 2018-10-24 2level.tex
leveling
stuff
refactoring

@@
 %!TEX root = main.tex
-\section{Warm-up:  Explore-then-Exploit Policy}
+\section{Warm-up:  2-Level Explore-then-Exploit Policy}
 \swedit{Now we provide a simple policy that can incentivize the agents
@@
 \caption{Structure of information graph for the 2-level policy. Each
-  red ``box'' is level 1 corresponds to a path connecting a set of
+  red ``box'' in level 1 corresponds to a path connecting a set of
   $T_G$ agents. The entire history in level 1 is then aggregated and
@@
     level.}
-  For each arm $a$, define $q_a$ to be the expected number of arm $a$
-  pulls in a single run of \ALGG used in the first level.  By Lemma
-  \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. Define $W_1^a$
-  to be the event that the number of arm $a$ pulls in the first level
-  is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.  \swedit{As long as
-    we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$, this implies that
-    the number of arm $a$ pulls is then at least $q_a T_1/2$.}  By
-  Chernoff bound,
+  By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. Define
+  $W_1^a$ to be the event that the number of arm $a$ pulls in the
+  first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
+  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
+    this implies that the number of arm $a$ pulls is then at least
+    $q_a T_1/2$.}  By Chernoff bound,
   \[

### 2018-10-24 3level.tex
refactoring

@@
 
+\begin{lemma}[``Clean'' events]
+
+\end{lemma}
+
 \begin{proof}
@@
 \item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
-\swcomment{can we reuse the previous result?}
-For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
 By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.

### 2018-10-24 2level.tex
refactor
stuff

@@
   ensure that with high probability, every arm is pulled with a
-  sufficient number of times. As a result, every agent in the second
-  level will pull an arm with mean rewards close to the optimal.
+  sufficient number of times. The following Lemma follows from
+  applying Chernoff bound and union bound.
 
 }
+
+\begin{lemma}[Concentration of arm pulls]\label{lem:t1runs}
+  Consider $T_1$ indepdent runs of \ALGG of length $T_G$. Let $N_a$ be
+  the number of arm $a$ pulls among all runs. Then with probability at
+  least $1-\delta$, for all $a\in \A$,
+  \[
+    \left| N_a - q_a T_1\right| \leq T_G \sqrt{T_1 \log(2K/\delta) / 2}
+  \]
+\end{lemma}
 
@@
 
+\swedit{As a result, every agent in the second level will pull an arm
+  with mean rewards close to the optimal, which gives us the following
+  regret guarantee.}
+
 \begin{theorem}
@@
     level.}
-  By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. Define
-  $W_1^a$ to be the event that the number of arm $a$ pulls in the
-  first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
+  \OMIT{By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
+  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
+  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
   \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
     this implies that the number of arm $a$ pulls is then at least
-    $q_a T_1/2$.}  By Chernoff bound,
+    $q_a T_1/2$.} 
+\OMIT{  By Chernoff bound,
   \[
@@
   \]
-Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
+}
+Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By \Cref{lem:t1runs}, we have
 \[

### 2018-10-24 2level.tex
update 2-level figure

--- 2018-10-22 2level.tex
@@
   \node at(11.5,1.5)[ rotate=90]{Time};
+
+  \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (10,-0.2) -- (0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ runs of \ALGG in parallel};
 \end{tikzpicture}

### 2018-10-24 3level.tex
Update 3level figure

@@
  \node at(\x+1,2.5){$T_2$};
- \node at(\x+1,0.5){$T_1 \cdot \GdT$};
+ \node at(\x+0.2, 0.5){$\GdT$};
+ \node at(\x+0.6, 0.5){$\cdot$};
+ \node at(\x+1.0, 0.5){$\cdot$};
+ \node at(\x+1.4, 0.5){$\cdot$};
+ \node at(\x+1.8, 0.5){$\GdT$};
+ %\node at(\x+1,0.5){$T_1 \cdot \GdT$}; 
+ \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (\x+2,-0.2) -- (\x+0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ runs};
  }
   \node at(5,4.5){$T -S(T_1 \cdot \GdT + T_2)$};
-  \node at (6,1.5){$\cdots$};
-  \node at (7,1.5){$\cdots$};
+  \node at (6,0.5){$\cdots$};
+  \node at (7,0.5){$\cdots$};
+  \node at (6,2.5){$\cdots$};
+  \node at (7,2.5){$\cdots$};
   \node at(-1,0.5){\textbf{Level 1}};
@@
   \node at(11.5,2.5)[ rotate=90]{Time};
+
+  \draw [decorate,decoration={brace,amplitude=10pt,aspect=0.33},xshift=0pt,yshift=0pt] (10,1.8) -- (0,1.8) node [black,pos=0.33,xshift = 0cm,yshift=-0.6cm] {$S$ groups};
+
 \end{tikzpicture}

### 2018-10-25 2level.tex
stuff

--- 2018-10-24 2level.tex
@@
 % \begin{itemize}
-  \paragraph{Concentration of the number of arm $a$ pulls in the first
+  \OMIT{\paragraph{Concentration of the number of arm $a$ pulls in the first
     level.}
-  \OMIT{By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
+By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
   Define $W_1^a$ to be the event that the number of arm $a$ pulls in
@@
 }
-Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By \Cref{lem:t1runs}, we have
+Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By Lemma~\ref{lem:t1runs}, we have
 \[
@@
 \]
-\paragraph{Concentration of the empirical mean of arm $a$ pulls in the first level.}
-To facilitate our reasoning, let us imagine there is a tape of length
-$T$ for each arm $a$, with each cell containing an independent draw of
-the realized reward from the distribution Ber$(\mu_a)$. Then for each
-arm $a$ and any $N\in [T]$, we can think of the sequence of the first
-$N$ realized rewards of $a$ coming from the prefix of $N$ cells in its
-reward tape. Define $W^{a,t}_2$ to be the event that the empirical
-mean of the first $t$ \swedit{realized rewards in the tape} of arm $a$
-is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$
-to be the intersection of these events (i.e.
-$\bigcap_{a,t} W^{a,t}_2$).  By Chernoff bound,\swcomment{$t$ may be
-  confusing here}
+\OMIT{\paragraph{Concentration of the empirical mean of arm $a$ pulls
+    in the first level.}}  Next, we show that the empirical mean of
+each arm $a$ is close to the true mean. To facilitate our reasoning,
+let us imagine there is a tape of length $T$ for each arm $a$, with
+each cell containing an independent draw of the realized reward from
+the distribution Ber$(\mu_a)$. Then for each arm $a$ and any
+$N\in [T]$, we can think of the sequence of the first $N$ realized
+rewards of $a$ coming from the prefix of $N$ cells in its reward
+tape. Define $W^{a,t}_2$ to be the event that the empirical mean of
+the first $t$ \swedit{realized rewards in the tape} of arm $a$ is at
+most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be
+the intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).
+By Chernoff bound,\swcomment{$t$ may be confusing here}
 \[

### 2018-10-25 3level.tex
stuff

@@
 \item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
-\swcomment{reusable?}
 For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$.
 For the $s$-th first-level group and arm $a$, define $W_2^{s,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away from $\mu_a$.
-By Chernoff bound,
+By Chernoff bound,\swcomment{a bit confused about what $t_1$ and $t_2$ mean?}
 \[

### 2018-10-25 2level.tex
stuff

@@
 \label{thm:2level}
-With proper setting of $T_1$, the 2-level policy gets expected regret
-$O(T^{2/3} \log(T)^{1/3})$. If we know the gap between the means of
-the best arm and second best arm is larger than $\Delta$, we can make
-the expected regret $O(\log(T) \cdot \Delta^{-2})$.
+By setting $T_1 = T^{2/3}\log(T)^{1/3}$, the 2-level policy gets
+expected regret $O(T^{2/3} \log(T)^{1/3})$.
 \end{theorem}
@@
 each cell containing an independent draw of the realized reward from
-the distribution Ber$(\mu_a)$. Then for each arm $a$ and any
-$N\in [T]$, we can think of the sequence of the first $N$ realized
-rewards of $a$ coming from the prefix of $N$ cells in its reward
-tape. Define $W^{a,t}_2$ to be the event that the empirical mean of
-the first $t$ \swedit{realized rewards in the tape} of arm $a$ is at
-most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be
-the intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).
-By Chernoff bound,\swcomment{$t$ may be confusing here}
+the distribution $\cD_a$. Then for each arm $a$ and any $N\in [T]$, we
+can think of the sequence of the first $N$ realized rewards of $a$
+coming from the prefix of $N$ cells in its reward tape. Define
+$W^{a,t}_2$ to be the event that the empirical mean of the first $t$
+\swedit{realized rewards in the tape} of arm $a$ is at most
+$\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the
+intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).  By
+Chernoff bound,\swcomment{$t$ may be confusing here}
 \[
@@
 By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.
-
-Notice that if we know the gap parameter is known to be larger than
+\OMIT{Notice that if we know the gap parameter is known to be larger than
 $\Delta$, we can set
@@
 \]
-This completes the proof.
+This completes the proof.}
 \end{proof}
+
+\begin{remark}
+  If the gap parameter $\Delta$ is known to the principal, we can set
+  $T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2
+      \cdot p_G} \log(T) \right)$, and achieves an expected regret of
+  $O(\log(T) \cdot \Delta^{-2})$.
+\end{remark}
+
 %%% Local Variables:

### 2018-10-25 3level.tex
stuff

@@
 
+\iffalse
 In the proof, we need not only the concentration argument as the
@@
 
-\iffalse
 Set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 =
@@
 \end{figure}
-\swcomment{check the figure caption above. can we index the indicate
-  there are $S$ groups in the figure?}
+% \swcomment{check the figure caption above. can we index the indicate
+%   there are $S$ groups in the figure?}
 
-\begin{lemma}[``Clean'' events]
+\subsection{Clean events}
+We will first establish four \emph{clean events} that together occur
+with probability at least $1 - O(1/T)$. The first one says that every
+group of \ALGG runs in the first level ensures that each arm $a$ is
+pulled at least $\Omega(T_1)$ times, which follows from
+Lemma~\ref{lem:t1runs} and union bound.
 
+\begin{lemma}[Concentration of first-level number of pulls.]
+  Let $W_1$ be the event that for all groups $s\in [S]$ and arms
+  $a\in \{1, 2\}$, the number of arm $a$ pulls in the $s$-th
+  first-level group is in the range of
+  $$
+  \left[q_a T_1- \GdT \sqrt{T_1\log(T)}, q_a T_1 + \GdT \sqrt{T_1\log(T)}\right],
+  $$
+  where $q_a$ is the expected number of arm $a$ pulls in a $\ALGG$ run
+  of length $T_G$. Then $\Pr[W_1] \geq 1- \frac{4S}{T^2}$.
 \end{lemma}
+
+\begin{proof}
+  For the $s$-th first-level group, define $W_1^{a,s}$ to be the event
+  that the number of arm $a$ pulls in the $s$-th first-level group is
+  between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and
+  $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
+\[
+\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
+\]
+Let $W_1$  be the intersection of all these events (i.e.
+$W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
+\[
+\Pr[W_1] \geq 1- \frac{4S}{T^2}.
+\]
+\swcomment{let's put this in appendix.}
+\end{proof}
+
+The next two events are about the distribution of the mean rewards in
+the first level. To state the events, it will be useful to think of a
+hypothetical reward tape tape $\cT_{s, a}$ of length $T$ for each
+group $s$ and arm $a$, with each cell independently sampled from
+$\cD_a$.  The tape encodes rewards as follows: the $j$-th time arm $a$
+is chosen by the group $s$ in the first level, its reward is taken
+from the $j$-th cell in this arm’s tape. We now show the concentration
+behavior of the mean rewards across all consecutive pulls among all
+such tapes.
+
+\begin{lemma}[Concetration of empirical means]
+  For any $t_1, t_2\in [T]$ such that $t_1 < t_2$, $s\in [S]$, and
+  $a\in \{1,2\}$, let $W_2^{s,a,t_1,t_2}$ be the event that the mean
+  among the cells indexed by $t_1, (t_1+1), \ldots, t_2$ in the tape
+  $\cT_{a, s}$ is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away
+  from $\mu_a$.  Let $W_2$ be the intersection of all these events
+  (i.e.  $W_2 = \bigcap_{a,s,t_1,t_2} W_2^{s,a,t_1,t_2}$). Then
+  \[
+    \Pr[W_2] \geq 1- \frac{4S}{T^2}.
+  \]
+\end{lemma}
+
+\begin{proof}
+  By Chernoff bound,
+\[
+\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
+\]
+By union bound, we have
+\[
+\Pr[W_2] \geq 1- \frac{4S}{T^2}.
+\]
+\end{proof}
+
+\begin{lemma}[Anti-concentration of empirical means]
+  For any $s\in [S]$, any arm $a$, let $\tilde\mu_{a,s}$ be the
+  empirical mean of the first $q_a T_1$ cells in tape $\cT_{a, s}$.
+  Let $W_4^{s,a,high}$ be the event
+  $\tilde\mu_{a, s} \geq \mu_a + 1/\sqrt{q_a T_1}$ and let
+  $W_4^{s,a,low}$ be the event that
+  $\tilde\mu_{a, s} \leq \mu_a - 1/\sqrt{q_a T_1}$.  Let $W_4$ be
+  $\bigcap_a \bigcup_s (W_4^{s,a,high} \cap W_4^{s,3-a,low})$.
+  \[
+    \Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
+  \]
+\end{lemma}
+
+\begin{proof}
+By Berry-Essen Theorem and
+  $\mu_a \in [1/3,2/3]$, we have
+\[
+\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1}} > 1/4.
+\]
+The last inequality follows when $T$ is larger than some constant.
+Similarly we also have 
+\[
+\Pr[W_4^{s,a,low}] > 1/4.
+\]
+Since $W_4^{s,a,high}$ is independent with $W_4^{s,3-a,low}$, we have
+\[
+\Pr[W_4^{s,a,high} \cap W_4^{s,3-a,low}] =\Pr[W_4^{s,a,high}] \cdot  \Pr[W_4^{s,3-a,low}]>(1/4)^2 = 1/16.
+\]
+Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent
+across different $s$'s. By union bound, we have
+\[
+\Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
+\]
+\end{proof}
+
+\subsection{Case Analysis}
 
@@
 \begin{itemize}
+\OMIT{
 \item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
-By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.
+\OMIT{By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.
 For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$.
-By Chernoff bound,
+By Chernoff bound,}
+For the $s$-th first-level group, define $W_1^{a,s}$ to be the event
+that the number of arm $a$ pulls in the $s$-th first-level group is
+between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and
+$q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
 \[
@@
 \]
-Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
+Let $W_1$  be the intersection of all these events (i.e.
+$W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
 \[
 \Pr[W_1] \geq 1- \frac{4S}{T^2}.
-\]
-\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
+\]}
+
+\OMIT{\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
 For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$.
@@
 \]
-
+}
 \item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first two levels:}
@@
 
-\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the first level:}
+\OMIT{\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the first level:}
 
@@
 \Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
-\]
+\]}
 \end{itemize}

### 2018-10-25 model.tex
stuff

@@
 set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
-distributed according to the Bernoulli distribution with an unknown
-mean $\mu_a$. At each round $t\in [T]$, a new agent $t$ arrives,
-receives a message $m_t$ from the principal, chooses an arm
+distributed according to the Bernoulli distribution $\cD_a$ with an
+unknown mean $\mu_a$. At each round $t\in [T]$, a new agent $t$
+arrives, receives a message $m_t$ from the principal, chooses an arm
 $a_t\in \A$, and collects a reward $r_t\in \{0,1\}$ that is

### 2018-10-26 3level.tex
stuff

@@
 the first level. To state the events, it will be useful to think of a
-hypothetical reward tape tape $\cT_{s, a}$ of length $T$ for each
+hypothetical reward tape tape $\cT^1_{s, a}$ of length $T$ for each
 group $s$ and arm $a$, with each cell independently sampled from
@@
 is chosen by the group $s$ in the first level, its reward is taken
-from the $j$-th cell in this arm’s tape. We now show the concentration
-behavior of the mean rewards across all consecutive pulls among all
-such tapes.
+from the $j$-th cell in this arm’s tape. The following result
+characterizes the concentration of the mean rewards among all
+consecutive pulls among all such tapes, which follows from Chernoff
+bound and union bound.
 
-\begin{lemma}[Concetration of empirical means]
+\begin{lemma}[Concetration of empirical means in the first level]
   For any $t_1, t_2\in [T]$ such that $t_1 < t_2$, $s\in [S]$, and
@@
   among the cells indexed by $t_1, (t_1+1), \ldots, t_2$ in the tape
-  $\cT_{a, s}$ is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away
+  $\cT^1_{a, s}$ is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away
   from $\mu_a$.  Let $W_2$ be the intersection of all these events
@@
 
+\OMIT{
 \begin{proof}
@@
 \end{proof}
+}
 
-\begin{lemma}[Anti-concentration of empirical means]
-  For any $s\in [S]$, any arm $a$, let $\tilde\mu_{a,s}$ be the
-  empirical mean of the first $q_a T_1$ cells in tape $\cT_{a, s}$.
+Our policy also relies on the anti-concentration of the empirical
+means in the first round. We show that for each arm $a\in \{1, 2\}$,
+there exists a group $s_a$ such that the empirical mean of $a$ is
+slightly above $\mu_a$, while the other arm $(3 - a)$ has empirical
+mean slightly below $\mu_{(3-a)}$. This event is crucial for making
+the agents in the second level to explore both arms when the their
+mean rewards are indistinguishable after the first level.
+
+\begin{lemma}[High and low deviations for the arms]
+  For any group $s\in [S]$, any arm $a$, let $\tilde\mu_{a,s}$ be the
+  empirical mean of the first $q_a T_1$ cells in tape $\cT^1_{a, s}$.
   Let $W_4^{s,a,high}$ be the event
@@
   $W_4^{s,a,low}$ be the event that
-  $\tilde\mu_{a, s} \leq \mu_a - 1/\sqrt{q_a T_1}$.  Let $W_4$ be
-  $\bigcap_a \bigcup_s (W_4^{s,a,high} \cap W_4^{s,3-a,low})$.
+  $\tilde\mu_{a, s} \leq \mu_a - 1/\sqrt{q_a T_1}$.  Let $W_4$ be the
+  event that for every $a\in \{1, 2\}$, there exists a group
+  $s_a\in [S]$ in the first level such that both $W_4^{s_a,a,high}$
+  and $W_4^{s_a,3-a,low}$ occur. Then
   \[
-    \Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
+    \Pr[W_4]\geq 1 -2 /T.
   \]
@@
 By Berry-Essen Theorem and
-  $\mu_a \in [1/3,2/3]$, we have
+  $\mu_a \in [1/3,2/3]$, we have for any $a$,
 \[
@@
 
+Lastly, we will condition on the event that the empirical means of
+both arms to be concentrated around their true means in any prefix of
+their pulls.
+% We will again state the event using a hypothetical reward tape
+% $\cT^2_a$ for each arm $a$: the $j$-th time arm $a$ is chosen in the
+% two levels, its reward is taken from the $j$-th cell in $\cT^2_a$.
+
+\begin{lemma}
+  With probability at least $1 - \frac{4}{T^3}$, the following event
+  $W_3$ holds: for all $a\in \{1, 2\}$ and $t\in [T]$, the empirical
+  means of the first $t$ arm $a$ pulls is at most
+  $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.
+\end{lemma}
+
+\swcomment{might want to swap out $W_3$ and $W_4$}
+
+\OMIT{\begin{proof}
+By Chernoff bound,
+\[
+\Pr[W_3^{a,t}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
+\]
+By union bound, we have
+\[
+\Pr[W_3] \geq 1- \frac{4}{T^3}.
+\]
+\end{proof}}
+
 \subsection{Case Analysis}
@@
 Before we start with the case analysis, we first define several clean events and show that the intersection of them happens with high probability. 
+\OMIT{
 \begin{itemize}
-\OMIT{
+
 \item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
@@
 }
-\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first two levels:}
+\OMIT{\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first two levels:}
 
@@
 \]
-
+}
 \OMIT{\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the first level:}
@@
 \Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
-\]}
-\end{itemize}
+\]
+\end{itemize}}
 

### 2018-10-26 3level.tex
notations

@@
   With probability at least $1 - \frac{4}{T^3}$, the following event
-  $W_3$ holds: for all $a\in \{1, 2\}$ and $t\in [T]$, the empirical
-  means of the first $t$ arm $a$ pulls is at most
-  $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.
+  $W_3$ holds: for all $a\in \{1, 2\}$ and $m \in [N_{T, a}]$, the
+  empirical means of the first $t$ arm $a$ pulls is at most
+  $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$, where $N_{T, a}$ is
+  the total number of arm $a$ pulls by the end of $T$ rounds.
 \end{lemma}

### 2018-10-27 2level.tex
3level

@@
   If the gap parameter $\Delta$ is known to the principal, we can set
-  $T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2
-      \cdot p_G} \log(T) \right)$, and achieves an expected regret of
+  $$T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2
+      \cdot p_G} \log(T) \right)$$, and achieves an expected regret of
   $O(\log(T) \cdot \Delta^{-2})$.

### 2018-10-27 3level.tex
3level

--- 2018-10-26 3level.tex
@@
 
-\section{3-level Adaptive Policy}
+\section{Adaptive Policy with Three Levels}
 \label{sec:3level}
@@
 
-\begin{lemma}[Concentration of first-level number of pulls.]
+\begin{lemma}[Concentration of first-level number of pulls.]\label{3levelw1}
   Let $W_1$ be the event that for all groups $s\in [S]$ and arms
@@
 \end{lemma}
-
-\begin{proof}
-  For the $s$-th first-level group, define $W_1^{a,s}$ to be the event
-  that the number of arm $a$ pulls in the $s$-th first-level group is
-  between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and
-  $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
-\[
-\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
-\]
-Let $W_1$  be the intersection of all these events (i.e.
-$W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
-\[
-\Pr[W_1] \geq 1- \frac{4S}{T^2}.
-\]
-\swcomment{let's put this in appendix.}
-\end{proof}
 
@@
 
-\begin{lemma}[Concetration of empirical means in the first level]
+\begin{lemma}[Concentration of empirical means in the first level]\label{3levelw2}
   For any $t_1, t_2\in [T]$ such that $t_1 < t_2$, $s\in [S]$, and
@@
 
-\OMIT{
-\begin{proof}
-  By Chernoff bound,
-\[
-\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
-\]
-By union bound, we have
-\[
-\Pr[W_2] \geq 1- \frac{4S}{T^2}.
-\]
-\end{proof}
-}
-
 Our policy also relies on the anti-concentration of the empirical
@@
 
-\begin{lemma}[High and low deviations for the arms]
+\begin{lemma}[High and low deviations for the arms]\label{3levelw4}
   For any group $s\in [S]$, any arm $a$, let $\tilde\mu_{a,s}$ be the
@@
 
-\begin{proof}
-By Berry-Essen Theorem and
-  $\mu_a \in [1/3,2/3]$, we have for any $a$,
-\[
-\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1}} > 1/4.
-\]
-The last inequality follows when $T$ is larger than some constant.
-Similarly we also have 
-\[
-\Pr[W_4^{s,a,low}] > 1/4.
-\]
-Since $W_4^{s,a,high}$ is independent with $W_4^{s,3-a,low}$, we have
-\[
-\Pr[W_4^{s,a,high} \cap W_4^{s,3-a,low}] =\Pr[W_4^{s,a,high}] \cdot  \Pr[W_4^{s,3-a,low}]>(1/4)^2 = 1/16.
-\]
-Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent
-across different $s$'s. By union bound, we have
-\[
-\Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
-\]
-\end{proof}
-
 Lastly, we will condition on the event that the empirical means of
 both arms to be concentrated around their true means in any prefix of
-their pulls.
+their pulls. This guarantees that the policy obtains an accurate
+estimate of rewards for both arms after aggregating all the data in
+the first two levels.
 % We will again state the event using a hypothetical reward tape
@@
 
-\begin{lemma}
+\swcomment{might want to swap out $W_3$ and $W_4$}
+\begin{lemma}[Concentration of empirical means in the first two
+  levels]\label{3levelw3}
   With probability at least $1 - \frac{4}{T^3}$, the following event
-  $W_3$ holds: for all $a\in \{1, 2\}$ and $t\in [T]$, the empirical
-  means of the first $t$ arm $a$ pulls is at most
-  $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.
+  $W_3$ holds: for all $a\in \{1, 2\}$ and $m \in [N_{T, a}]$, the
+  empirical means of the first $t$ arm $a$ pulls is at most
+  $\sqrt{\frac{2\log(T)}{m}}$ away from $\mu_a$, where $N_{T, a}$ is
+  the total number of arm $a$ pulls by the end of $T$ rounds.
 \end{lemma}
 
-\swcomment{might want to swap out $W_3$ and $W_4$}
+Let $W = \bigcap_{i=1}^4 W_i$ be the intersection of all 4 clean
+events.  By union bound, $W$ occuers with probability $1-O(1/T)$. Note
+that expected regret conditioned on $W$ not occuring is at most
+$O(1/T) \cdot T = O(1)$, so it suffices to bound the regret under $W$.
 
-\OMIT{\begin{proof}
-By Chernoff bound,
-\[
-\Pr[W_3^{a,t}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
-\]
-By union bound, we have
-\[
-\Pr[W_3] \geq 1- \frac{4}{T^3}.
-\]
-\end{proof}}
+\subsection{Case Analysis under Clean Events}
 
-\subsection{Case Analysis}
+We now proceed to bound the regret conditioned on all four clean
+events defined above occur. Without loss of generality, we assume
+$\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both
+arms. We break down the regret analysis into 4 cases on the scale of
+the gap parameter $\Delta = (\mu_1-\mu_2)$.
+
+We will start with the simplest case where the gap is smaller than
+$\tilde O(\sqrt{1/T_2}) = \tilde O(1/T^{3/7})$, then the regret is
+trivially bounded by $\tilde O(T^{4/7})$.
+
+\begin{claim}[Small gap case]
+  Suppose $\Delta \leq 3\sqrt{\frac{2\log(T)}{T_2}}$,
+  $\reg(T)\leq O(T^{4/7} \log^{6/7}(T))$.
+\end{claim}
+
+Another simple case is when $\Delta$ is sufficiently large, so that
+the data collected in the first level can distinguish the two
+arms. The proof essentially follows from the clean event $W_1$ that
+both arms are explored sufficient many times in level 1, and the
+empirical rewards in the first two levels concentrate around their
+true means.
+
+\begin{lemma}[Large gap case]\label{3levelbigcase}
+  Suppose
+  $\Delta \geq 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
+    \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$, then all agents in the
+  second and third levels pull arm 1.
+\end{lemma}
+
+The analysis becomes more challenging when the gap is neither too
+small to have negligible effect on regret nor too big to make the arms
+distinguishable after the first level.
 
 \begin{proof}
-Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We do a case analysis based on $\mu_1-\mu_2$.
+\OMIT{Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We do a case analysis based on $\mu_1-\mu_2$.
 
 Before we start with the case analysis, we first define several clean events and show that the intersection of them happens with high probability.
-\OMIT{
+
 \begin{itemize}
@@
 \]
-\end{itemize}}
+\end{itemize}
 
@@
 
-Now we assume the intersection of clean events happens and we summarize what these clean events imply.
+Now we assume the intersection of clean events happens and we summarize what these clean events imply.}
 
@@
 \begin{itemize}
+\OMIT{
 \item $\mu_1 - \mu_2 \geq 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
@@
 Therefore the expected regret is at most $S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$.
+}
 
@@
 
+\OMIT{
 \item $\mu_1 - \mu_2 \leq 3\sqrt{\frac{2\log(T)}{T_2}}$.
@@
 arm 2) gives regret at most $T \cdot (\mu_1-\mu_2) = O(T^{4/7} \log^{6/7}(T))$.
+}
 \end{itemize}

### 2018-10-27 3levelproofs.tex
appendix

--- 2018-10-26 3level.tex
@@
-%!TEX root = main.tex
+\section{Missing proofs from Section~\ref{sec:3level}}
 
-\section{3-level Adaptive Policy}
-\label{sec:3level}
-\swcomment{rewrote below}
-Now we demonstrate how to design a 3-level policy to incentivize
-adaptive exploration and improve the $O(T^{2/3})$ regret rate to
-$\tilde O(T^{4/7})$. In \Cref{sec:llevel}, we will show how to extend
-this idea to achieve a regret rate of $\tilde O(T^{1/2})$. For
-simplicity, we will focus on the setting with 2 arms.
+\subsection{Clean Events}
 
-The policy consists of three phases, each of which corresponds to a
-level (see Figure~\ref{fig:3level}).  In the first level, the policy
-performs the first round of exploration over the first
-$(S\cdot T_1\cdot T_G)$ agents, where $T_1 = T^{4/7}\log^{-1/7}(T)$
-and $S = 2^{10}\log(T)$. In particular, the policy randomly partitions
-the agents into $S$ groups such that each group consists of $T_1$ runs
-of \ALGG with $T_G$ rounds. In the second level, the policy performs
-further exploration on the next $(S\cdot T_2)$ agents by incorporating
-data collected in the first level, where
-$T_2 = T^{6/7}\log^{-5/7}(T)$. The agents are again partitioned into
-$S$ groups such that the agents in the $s$-th group are shown the same
-sub-history from the $s$-th group in the first level. In the third
-level, the policy exploits by showing all remaining agents the entire
-history from the first two levels.
-
-They main idea for the 3-level policy is that it inserts the second
-level as an additional ``checkpoint'' to induce more adaptivity in the
-exploration. While the first level ensures that the agents explore
-both arms, the second level will continue to explore both arms only if
-the rewards of the two arms are still indistinguishable (that is, when
-$|\mu_1 - \mu_2| < \tilde{O}(1/\sqrt{T_1})$). In the third level,
-agents will pull the best arm unless $|\mu_1-\mu_2|$ is much smaller
-than $\tilde{O}(1/\sqrt{T_2})$, in which case pulling either arm will
-incur small regret. The formal guarantee of the policy is the
-following.
-
-\begin{theorem}
-\label{thm:3level}
-The 3-level recommendation policy gets expected regret $O(T^{4/7} \log^{6/7}(T))$. 
-\end{theorem}
-
-\iffalse
-In the proof, we need not only the concentration argument as the
-2-level recommendation policy, but also the anti-concentration
-argument to show that agents explore more in the second round if
-$\mu_1-\mu_2$ is not too big.
-
-Set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 =
-T^{6/7}\log^{-5/7}(T)$. The first level has $S = 2^{10}\log(T)$ groups
-of agents. Each group runs $T_1$ \ALGG of $T_G$ rounds in
-parallel. The second level also has $S$ groups of agents. Each group
-has $T_2$ agents and they observe the history of corresponding group
-in the first level. All the rest agents are in the third level and
-they observe the entire history of the first two levels.  See also
-Figure \ref{fig:3level} for a graphical view of the information flow.
-
-Here we give some intuition about how the 3-level recommendation
-policy works. The main idea is to do the exploration more
-adaptively. In the first level, agents explore both arms. In the
-second level, agents will pull the best arm when $\mu_1 - \mu_2$ is
-large ($\tilde{\Omega}(1/\sqrt{T_1})$). Otherwise agents will explore
-both arms more. In the third level, agents will pull the best arm
-unless $\mu_1-\mu_2$ is much smaller ($\tilde{O}(1/\sqrt{T_2})$). In
-the proof, we need not only the concentration argument as the 2-level
-recommendation policy, but also the anti-concentration argument to
-show that agents explore more in the second round if $\mu_1-\mu_2$ is
-not too big.
-\fi
-
-\begin{figure}[H]
-\centering
-\begin{tikzpicture}  
- \filldraw[fill=green!20!white]
- (0,4)--(10,4)--(10,5)--(0,5)--cycle;
- \foreach \x in {0,3,8}
- {
- \filldraw[fill=blue!20!white]
- (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
- \draw[dashed] (\x+1,3)--(5,4);
- \filldraw[fill=red!20!white]
- (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
- \draw[dashed] (\x+1,1)--(\x+1,2);
- \draw[dashed] (\x+0.2,1)--(\x+1,2);
- \draw[dashed] (\x+0.6,1)--(\x+1,2);
- \draw[dashed] (\x+1.4,1)--(\x+1,2);
- \draw[dashed] (\x+1.8,1)--(\x+1,2);
- \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
- \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
- \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
- \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
- \node at(\x+1,2.5){$T_2$};
- \node at(\x+0.2, 0.5){$\GdT$};
- \node at(\x+0.6, 0.5){$\cdot$};
- \node at(\x+1.0, 0.5){$\cdot$};
- \node at(\x+1.4, 0.5){$\cdot$};
- \node at(\x+1.8, 0.5){$\GdT$};
- %\node at(\x+1,0.5){$T_1 \cdot \GdT$}; 
- \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (\x+2,-0.2) -- (\x+0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ runs};
- }
-  \node at(5,4.5){$T -S(T_1 \cdot \GdT + T_2)$};
-  \node at (6,0.5){$\cdots$};
-  \node at (7,0.5){$\cdots$};
-  \node at (6,2.5){$\cdots$};
-  \node at (7,2.5){$\cdots$};
-  \node at(-1,0.5){\textbf{Level 1}};
-  \node at(-1,2.5){\textbf{Level 2}};
-  \node at(-1,4.5){\textbf{Levle 3}};
-  \draw[->] (11,0)--(11,5);
-  \node at(11.5,2.5)[ rotate=90]{Time};
-
-  \draw [decorate,decoration={brace,amplitude=10pt,aspect=0.33},xshift=0pt,yshift=0pt] (10,1.8) -- (0,1.8) node [black,pos=0.33,xshift = 0cm,yshift=-0.6cm] {$S$ groups};
-
-\end{tikzpicture}
-\caption{Structure of the information graph for the 3-level
-  Policy. Each red box in level 1 corresponds to $T_1$ \ALGG paths of
-  length $T_G$. The sub-history of each red box is then aggregated and
-  sent to a corresponding purple box of agents in level 2. Then the
-  entire history of levels 1 and 2 is aggregated and shown to all
-  agents in level 3.}
-\label{fig:3level}
-\end{figure}
-% \swcomment{check the figure caption above. can we index the indicate
-%   there are $S$ groups in the figure?}
-
-\subsection{Clean events}
-We will first establish four \emph{clean events} that together occur
-with probability at least $1 - O(1/T)$. The first one says that every
-group of \ALGG runs in the first level ensures that each arm $a$ is
-pulled at least $\Omega(T_1)$ times, which follows from
-Lemma~\ref{lem:t1runs} and union bound.
-
-\begin{lemma}[Concentration of first-level number of pulls.]
-  Let $W_1$ be the event that for all groups $s\in [S]$ and arms
-  $a\in \{1, 2\}$, the number of arm $a$ pulls in the $s$-th
-  first-level group is in the range of
-  $$
-  \left[q_a T_1- \GdT \sqrt{T_1\log(T)}, q_a T_1 + \GdT \sqrt{T_1\log(T)}\right],
-  $$
-  where $q_a$ is the expected number of arm $a$ pulls in a $\ALGG$ run
-  of length $T_G$. Then $\Pr[W_1] \geq 1- \frac{4S}{T^2}$.
-\end{lemma}
-
-\begin{proof}
+\begin{proof}[Proof of Lemma~\ref{3levelw1}]
   For the $s$-th first-level group, define $W_1^{a,s}$ to be the event
@@
 
-The next two events are about the distribution of the mean rewards in
-the first level. To state the events, it will be useful to think of a
-hypothetical reward tape tape $\cT^1_{s, a}$ of length $T$ for each
-group $s$ and arm $a$, with each cell independently sampled from
-$\cD_a$.  The tape encodes rewards as follows: the $j$-th time arm $a$
-is chosen by the group $s$ in the first level, its reward is taken
-from the $j$-th cell in this arm’s tape. The following result
-characterizes the concentration of the mean rewards among all
-consecutive pulls among all such tapes, which follows from Chernoff
-bound and union bound.
-
-\begin{lemma}[Concetration of empirical means in the first level]
-  For any $t_1, t_2\in [T]$ such that $t_1 < t_2$, $s\in [S]$, and
-  $a\in \{1,2\}$, let $W_2^{s,a,t_1,t_2}$ be the event that the mean
-  among the cells indexed by $t_1, (t_1+1), \ldots, t_2$ in the tape
-  $\cT^1_{a, s}$ is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away
-  from $\mu_a$.  Let $W_2$ be the intersection of all these events
-  (i.e.  $W_2 = \bigcap_{a,s,t_1,t_2} W_2^{s,a,t_1,t_2}$). Then
-  \[
-    \Pr[W_2] \geq 1- \frac{4S}{T^2}.
-  \]
-\end{lemma}
-
-\OMIT{
-\begin{proof}
+\begin{proof}[Proof of Lemma~\ref{3levelw2}]
   By Chernoff bound,
@@
 \end{proof}
-}
 
-Our policy also relies on the anti-concentration of the empirical
-means in the first round. We show that for each arm $a\in \{1, 2\}$,
-there exists a group $s_a$ such that the empirical mean of $a$ is
-slightly above $\mu_a$, while the other arm $(3 - a)$ has empirical
-mean slightly below $\mu_{(3-a)}$. This event is crucial for making
-the agents in the second level to explore both arms when the their
-mean rewards are indistinguishable after the first level.
-
-\begin{lemma}[High and low deviations for the arms]
-  For any group $s\in [S]$, any arm $a$, let $\tilde\mu_{a,s}$ be the
-  empirical mean of the first $q_a T_1$ cells in tape $\cT^1_{a, s}$.
-  Let $W_4^{s,a,high}$ be the event
-  $\tilde\mu_{a, s} \geq \mu_a + 1/\sqrt{q_a T_1}$ and let
-  $W_4^{s,a,low}$ be the event that
-  $\tilde\mu_{a, s} \leq \mu_a - 1/\sqrt{q_a T_1}$.  Let $W_4$ be the
-  event that for every $a\in \{1, 2\}$, there exists a group
-  $s_a\in [S]$ in the first level such that both $W_4^{s_a,a,high}$
-  and $W_4^{s_a,3-a,low}$ occur. Then
-  \[
-    \Pr[W_4]\geq 1 -2 /T.
-  \]
-\end{lemma}
-
-\begin{proof}
+\begin{proof}[Proof of Lemma~\ref{3levelw4}]
 By Berry-Essen Theorem and
@@
 
-Lastly, we will condition on the event that the empirical means of
-both arms to be concentrated around their true means in any prefix of
-their pulls.
-% We will again state the event using a hypothetical reward tape
-% $\cT^2_a$ for each arm $a$: the $j$-th time arm $a$ is chosen in the
-% two levels, its reward is taken from the $j$-th cell in $\cT^2_a$.
-
-\begin{lemma}
-  With probability at least $1 - \frac{4}{T^3}$, the following event
-  $W_3$ holds: for all $a\in \{1, 2\}$ and $t\in [T]$, the empirical
-  means of the first $t$ arm $a$ pulls is at most
-  $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.
-\end{lemma}
-
-\swcomment{might want to swap out $W_3$ and $W_4$}
-
-\OMIT{\begin{proof}
+\begin{proof}[Proof of Lemma~\ref{3levelw3}]
 By Chernoff bound,
@@
 \]
-\end{proof}}
+\end{proof}
 
-\subsection{Case Analysis}
+\subsection{Case Analysis under Clean Events}
 
-\begin{proof}
-Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We do a case analysis based on $\mu_1-\mu_2$.
-
-Before we start with the case analysis, we first define several clean events and show that the intersection of them happens with high probability. 
-\OMIT{
-\begin{itemize}
-
-\item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
-\OMIT{By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.
-For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$.
-By Chernoff bound,}
-For the $s$-th first-level group, define $W_1^{a,s}$ to be the event
-that the number of arm $a$ pulls in the $s$-th first-level group is
-between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and
-$q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
-\[
-\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
-\]
-Let $W_1$  be the intersection of all these events (i.e.
-$W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
-\[
-\Pr[W_1] \geq 1- \frac{4S}{T^2}.
-\]}
-
-\OMIT{\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
-For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$.
-For the $s$-th first-level group and arm $a$, define $W_2^{s,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away from $\mu_a$.
-By Chernoff bound,\swcomment{a bit confused about what $t_1$ and $t_2$ mean?}
-\[
-\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
-\]
-
-Define $W_2$ to be the intersection of all these events (i.e. $W_2 = \bigcap_{a,s,t_1,t_2} W_2^{s,a,t_1,t_2}$). By union bound, we have
-\[
-\Pr[W_2] \geq 1- \frac{4S}{T^2}.
-\]
-}
-\OMIT{\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first two levels:}
-
-For all the groups in the first two levels and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in the first two levels pull arm $a$.
-Define $W_3^{a,t}$ to be the event that the mean of the first $t$ pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$.
-By Chernoff bound,
-\[
-\Pr[W_3^{a,t}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
-\]
-Define $W_3$ to be the intersection of all these events (i.e. $W_3 = \bigcap_{a,t} W_3^{a,t}$). By union bound, we have
-\[
-\Pr[W_3] \geq 1- \frac{4}{T^3}.
-\]
-}
-\OMIT{\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the first level:}
-
-Consider the tapes defined in the second bullet again.
-For the $s$-th first-level group and arm $a$, define $W_4^{s,a,high}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1}$ and define  $W_4^{s,a,low}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1}$.
-By Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
-\[
-\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1}} > 1/4.
-\]
-The last inequality follows when $T$ is larger than some constant.
-Similarly we also have 
-\[
-\Pr[W_4^{s,a,low}] > 1/4.
-\]
-Since $W_4^{s,a,high}$ is independent with $W_4^{s,3-a,low}$, we have
-\[
-\Pr[W_4^{s,a,high} \cap W_4^{s,3-a,low}] =\Pr[W_4^{s,a,high}] \cdot  \Pr[W_4^{s,3-a,low}]>(1/4)^2 = 1/16.
-\]
-Now define $W_4$ as $\bigcap_a \bigcup_s (W_4^{s,a,high} \cap W_4^{s,3-a,low})$. Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent across different $s$'s. By union bound, we have
-\[
-\Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
-\]
-\end{itemize}}
-
-By union bound, the intersection of these clean events (i.e.
-$\bigcap_{i=1}^4 W_i$) happens with probability $1-O(1/T)$.
-When this intersection does not happen, since the probability is $O(1/T)$, it contributes $O(1/T) \cdot T = O(1)$ to the expected regret.
-
-Now we assume the intersection of clean events happens and we summarize what these clean events imply.
-
-\begin{itemize}
-\item For the $s$-th first-level group and arm $a$, define $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in this group.
-$W_1^{a,s}$, $W_2^{a,s,1,t}$ for $ = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1- \GdT \sqrt{T_1\log(T)}$ together imply that
+\begin{proof}[Proof of Lemma~\ref{3levelbigcase}]
+  For each $s$-th first-level group and arm $a$, define
+  $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in
+  this group. $W_1^{a,s}$, $W_2^{a,s,1,t}$ for
+  $ = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1- \GdT
+  \sqrt{T_1\log(T)}$ together imply that
 \[
@@
 \]
-The last inequality holds when $T$ is larger than some constant.
-\item For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of arm $a$ pulls in the first two levels.
-$W_1^{a,s}$ for $s=1,...,S$ and $W_3^{a,t}$ for $t \geq  (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
+The last inequality holds as long as $T$ is larger than some
+constant. This implies that
+\[
+\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{q_1T_1}} - \sqrt{\frac{4\log(T)}{q_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}.
+\]
+
+For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of arm
+$a$ pulls in the first two levels. $W_1^{a,s}$ for $s=1,...,S$ and
+$W_3^{a,t}$ for $t \geq (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together
+imply that
 \[
@@
 
-If there are at least $T_2$ pulls of arm $a$ in the first two levels, 
-\[
-|\bar{\mu}_a-\mu_a| \leq \sqrt{\frac{2\log(T)}{T_2}}. 
-\]
-
-\item For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such that $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.
-$W_4^{s_a,a,high}$,  $W_1^{s_a,a}$, $W_2^{s_a,a,t, q_aT_1}$ for $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and $W_2^{s_a,a,q_aT_1,t}$ for $t= q_aT_1,...,q_a T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
-\begin{align*}
-\bar{\mu}_a ^{1,s_a} &\geq \mu_a + \left(q_aT_1 \cdot \frac{1}{\sqrt{q_aT_1}} - \GdT \sqrt{T_1\log(T)} \cdot \sqrt{\frac{2\log(T)}{ \GdT \sqrt{T_1\log(T)}}} \right) \cdot \frac{1}{q_a T_1+ \GdT \sqrt{T_1\log(T)}} \\
-&> \mu_a + \frac{1}{4\sqrt{q_aT_1}}.
-\end{align*}
-The second last inequality holds when $T$ is larger than some constant.
-Similarly, we also have
-\[
-\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
-\]
-\end{itemize}
-
-Finally we proceed to the case analysis. We give upper bounds on the expected regret conditioned on the intersection of clean events.
-
-\begin{itemize}
-\item $\mu_1 - \mu_2 \geq 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. In this case, we want to show that agents in the second and the third levels all pull arm 1.
-
-First consider the $s$-th second-level group. We know that 
-\[
-\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{q_1T_1}} - \sqrt{\frac{4\log(T)}{q_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}.
-\]
 For any agent $t$ in the $s$-th second-level group, by Assumption \ref{ass:embehave}, we have
@@
 \hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
-&\geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
- &> 0.
+&\geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}} > 0
 \end{align*}
@@
 
-Now consider the agents in the third level group. Recall $\bar{\mu}_a$ is the empirical mean of arm $a$ in the history they see. We have
+Now consider the agents in the third level group. Recall $\bar{\mu}_a$
+is the empirical mean of arm $a$ in the history they see. We have
 \[
@@
 \]
-Similarly as above, by Assumption \ref{ass:embehave}, we know $\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third level.
-So we know agents in the third-level group will all pull arm 1.
-Therefore the expected regret is at most $S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$.
-
-\item $2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq \mu_1-\mu_2 < 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. In this case, we want to show agents in the third level all pull arm 1. Recall $\bar{\mu}_a$ is the empirical mean of arm $a$ in the first two levels. We have
-\[
-\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}.
-\]
-For any agent $t$ in the third level, by Assumption \ref{ass:embehave}, we have
-\begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
-&\geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} + \sqrt{\frac{4\log(T)}{Sq_2T_1}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
- &> 0.
-\end{align*}
-So we know agents in the third-level group will all pull arm 1. Therefore the expected regret is at most 
-\[
-(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
-\]
-
-\item $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 < 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.
-In this case, we just need to make sure that agents in the third level all pull arm 1.
-To do so, we need both arms to be pulled at least $T_2$ rounds in the second level.
-
-Now consider the $s_a$-th second-level group. We have
-\begin{align*}
-\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} &> \mu_a + \frac{1}{4\sqrt{q_aT_1}} -\mu_{3-a} +\frac{1}{4\sqrt{q_{3-a}T_1}} \\
-&> \frac{1}{4\sqrt{q_1T_1}}+ \frac{1}{4\sqrt{q_2T_1}} - 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \\
-&\geq \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}.
-\end{align*}
-For any agent $t$ in the $s_a$-th second-level group, by Assumption \ref{ass:embehave}, we have
-\begin{align*}
-\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
-&\geq   \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
- &> 0.
-\end{align*}
-So we know agents in the $s_a$-th second-level group will all pull arm $a$. Therefore in the first two levels, both arms are pulled at least $T_2$ times. Now consider the third-level. We have
-\[
-\bar{\mu}_1 - \bar{\mu}_2  \geq \mu_1 -\mu_2 - 2\sqrt{\frac{2\log(T)}{T_2}} \geq \sqrt{\frac{2\log(T)}{T_2}}.
-\]
-Similarly as above, by Assumption \ref{ass:embehave}, we know $\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third level. So we know agents in the third-level group will all pull arm 1.
-
-Therefore the expected regret is at most 
-\[
-(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
-\]
-
-\item $\mu_1 - \mu_2 \leq 3\sqrt{\frac{2\log(T)}{T_2}}$.
-This is the easy case.
-Even always pulling the sub-optimal arm (i.e.
-arm 2) gives regret at most $T \cdot (\mu_1-\mu_2) = O(T^{4/7} \log^{6/7}(T))$.
-\end{itemize}
-
+Similarly as above, by Assumption \ref{ass:embehave}, we know
+$\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third
+level. Therefore, the agents in the third-level group will all pull
+arm 1.  \OMIT{Therefore the expected regret is at most
+  $S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$.}
 \end{proof}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "main"
-%%% End:

### 2018-10-27 3level.tex
what's up

@@
 $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both
-arms. We break down the regret analysis into 4 cases on the scale of
-the gap parameter $\Delta = (\mu_1-\mu_2)$.
+arms. We break down the regret analysis into three cases on the scale
+of the gap parameter $\Delta = (\mu_1-\mu_2)$.
 
@@
 
-The analysis becomes more challenging when the gap is neither too
+The intermediate case more challenging since the gap is neither too
 small to have negligible effect on regret nor too big to make the arms
 distinguishable after the first level.
+
+\begin{lemma}[Intermediate gap case]\label{3levelmidcase}
+  All agents pull arm 1 in the third level, when $\Delta$ satisfies
+  \[
+    \Delta\in \left( 3\sqrt{\frac{2\log(T)}{T_2}},
+      2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
+        \sqrt{\frac{4\log(T)}{q_2T_1}}\right) \right)
+  \]
+\end{lemma}
 
@@
 
-Now we assume the intersection of clean events happens and we summarize what these clean events imply.}
+Now we assume the intersection of clean events happens and we summarize what these clean events imply.
 
@@
 \end{itemize}
-
+}
 Finally we proceed to the case analysis. We give upper bounds on the expected regret conditioned on the intersection of clean events.
 
+\OMIT{
 \begin{itemize}
-\OMIT{
+
 \item $\mu_1 - \mu_2 \geq 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
@@
 Therefore the expected regret is at most $S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$.
-}
 
@@
 
-\OMIT{
 \item $\mu_1 - \mu_2 \leq 3\sqrt{\frac{2\log(T)}{T_2}}$.
@@
 arm 2) gives regret at most $T \cdot (\mu_1-\mu_2) = O(T^{4/7} \log^{6/7}(T))$.
+
+\end{itemize}
 }
-\end{itemize}
-
 \end{proof}

### 2018-10-27 3levelproofs.tex
what's up

@@
 \]
-\swcomment{let's put this in appendix.}
 \end{proof}
@@
 \subsection{Case Analysis under Clean Events}
+Now we assume the intersection of clean events happens and we
+summarize what these clean events imply.
+
+\begin{itemize}
+\item For the $s$-th first-level group and arm $a$, define $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in this group.
+$W_1^{a,s}$, $W_2^{a,s,1,t}$ for $ = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1- \GdT \sqrt{T_1\log(T)}$ together imply that
+\[
+|\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_a T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
+\]
+The last inequality holds when $T$ is larger than some constant.
+\item For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of arm $a$ pulls in the first two levels.
+$W_1^{a,s}$ for $s=1,...,S$ and $W_3^{a,t}$ for $t \geq  (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
+\[
+|\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(q_a T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
+\]
+The last inequality holds when $T$ is larger than some constant.
+
+If there are at least $T_2$ pulls of arm $a$ in the first two levels, 
+\[
+|\bar{\mu}_a-\mu_a| \leq \sqrt{\frac{2\log(T)}{T_2}}. 
+\]
+
+\item For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such that $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.
+$W_4^{s_a,a,high}$,  $W_1^{s_a,a}$, $W_2^{s_a,a,t, q_aT_1}$ for $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and $W_2^{s_a,a,q_aT_1,t}$ for $t= q_aT_1,...,q_a T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
+\begin{align*}
+\bar{\mu}_a ^{1,s_a} &\geq \mu_a + \left(q_aT_1 \cdot \frac{1}{\sqrt{q_aT_1}} - \GdT \sqrt{T_1\log(T)} \cdot \sqrt{\frac{2\log(T)}{ \GdT \sqrt{T_1\log(T)}}} \right) \cdot \frac{1}{q_a T_1+ \GdT \sqrt{T_1\log(T)}} \\
+&> \mu_a + \frac{1}{4\sqrt{q_aT_1}}.
+\end{align*}
+The second last inequality holds when $T$ is larger than some constant.
+Similarly, we also have
+\[
+\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
+\]
+\end{itemize}
 
@@
 \end{proof}
+
+\begin{proof}[Proof of Lemma~\ref{3levelmidcase}]
+  We will further break down the intermediate case into two sub-cases.
+\begin{itemize}
+
+\item $2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
++ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq \mu_1-\mu_2 < 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
++ \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. In this case, we want to show agents in the third level all pull arm 1. Recall $\bar{\mu}_a$ is the empirical mean of arm $a$ in the first two levels. We have
+\[
+\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} 
++ \sqrt{\frac{4\log(T)}{Sq_2T_1}}.
+\]
+For any agent $t$ in the third level, by Assumption \ref{ass:embehave}, we have
+\begin{align*}
+\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
+&\geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} + \sqrt{\frac{4\log(T)}{Sq_2T_1}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
+ &> 0.
+\end{align*}
+So we know agents in the third-level group will all pull arm 1. Therefore the expected regret is at most 
+\[
+(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
++ \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
+\]
+
+\item $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 < 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
++ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.
+In this case, we just need to make sure that agents in the third level all pull arm 1.
+To do so, we need both arms to be pulled at least $T_2$ rounds in the second level.
+
+Now consider the $s_a$-th second-level group. We have
+\begin{align*}
+\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} &> \mu_a + \frac{1}{4\sqrt{q_aT_1}} -\mu_{3-a} +\frac{1}{4\sqrt{q_{3-a}T_1}} \\
+&> \frac{1}{4\sqrt{q_1T_1}}+ \frac{1}{4\sqrt{q_2T_1}} - 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
++ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \\
+&\geq \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}.
+\end{align*}
+For any agent $t$ in the $s_a$-th second-level group, by Assumption \ref{ass:embehave}, we have
+\begin{align*}
+\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
+&\geq   \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
+ &> 0.
+\end{align*}
+So we know agents in the $s_a$-th second-level group will all pull arm $a$. Therefore in the first two levels, both arms are pulled at least $T_2$ times. Now consider the third-level. We have
+\[
+\bar{\mu}_1 - \bar{\mu}_2  \geq \mu_1 -\mu_2 - 2\sqrt{\frac{2\log(T)}{T_2}} \geq \sqrt{\frac{2\log(T)}{T_2}}.
+\]
+Similarly as above, by Assumption \ref{ass:embehave}, we know $\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third level. So we know agents in the third-level group will all pull arm 1.
+
+Therefore the expected regret is at most 
+\[
+(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
++ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
+\]
+
+\end{itemize}
+
+\end{proof}

### 2018-10-27 3level.tex
stuff

@@
 We will first establish four \emph{clean events} that together occur
-with probability at least $1 - O(1/T)$. The first one says that every
-group of \ALGG runs in the first level ensures that each arm $a$ is
-pulled at least $\Omega(T_1)$ times, which follows from
-Lemma~\ref{lem:t1runs} and union bound.
+with probability at least $1 - O(1/T)$. The first event says that
+every group of \ALGG runs in the first level ensures that each arm $a$
+is pulled at least $\Omega(T_1)$ times. The following lemma can
+derived from combining Lemma~\ref{lem:t1runs} and union bound. This
+will be useful for applying concentration inequalities to the
+empirical mean rewards.
 
@@
 
-\begin{lemma}[High and low deviations for the arms]\label{3levelw4}
+\begin{lemma}[Co-occurence of high and low deviations]\label{3levelw4}
   For any group $s\in [S]$, any arm $a$, let $\tilde\mu_{a,s}$ be the

### 2018-10-27 3levelproofs.tex
stuff

@@
 \subsection{Case Analysis under Clean Events}
-Now we assume the intersection of clean events happens and we
-summarize what these clean events imply.
+Now we assume the intersection of clean events happens. We will first
+provide some helper lemmas for our case analysis.
 
-\begin{itemize}
-\item For the $s$-th first-level group and arm $a$, define $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in this group.
-$W_1^{a,s}$, $W_2^{a,s,1,t}$ for $ = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1- \GdT \sqrt{T_1\log(T)}$ together imply that
+\begin{lemma}
+  For the $s$-th first-level group and arm $a$, define
+  $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in
+  this group. If $W$ holds, then
+  \[
+    |\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
+  \]
+\end{lemma}
+
+\begin{proof}
+  The events $W_1^{a,s}$, $W_2^{a,s,1,t}$ for
+  $t = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1 + \GdT
+  \sqrt{T_1\log(T)}$ together imply that
 \[
@@
 The last inequality holds when $T$ is larger than some constant.
+\end{proof}
+
+\begin{itemize}
+
 \item For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of arm $a$ pulls in the first two levels.
@@
 
-\item For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such that $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.
-$W_4^{s_a,a,high}$,  $W_1^{s_a,a}$, $W_2^{s_a,a,t, q_aT_1}$ for $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and $W_2^{s_a,a,q_aT_1,t}$ for $t= q_aT_1,...,q_a T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
+\item % For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such that $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.
+  The events $W_4^{s_a,a,high}$, $W_1^{s_a,a}$,
+  $W_2^{s_a,a,t, q_aT_1}$ for
+  $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and
+  $W_2^{s_a,a,q_aT_1,t}$ for
+  $t= q_aT_1,...,q_a T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
 \begin{align*}
@@
 \end{align*}
-The second last inequality holds when $T$ is larger than some constant.
+The second to the last inequality holds when $T$ is larger than some constant.
 Similarly, we also have
@@
 \begin{proof}[Proof of Lemma~\ref{3levelbigcase}]
-  For each $s$-th first-level group and arm $a$, define
-  $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in
-  this group. $W_1^{a,s}$, $W_2^{a,s,1,t}$ for
-  $ = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1- \GdT
-  \sqrt{T_1\log(T)}$ together imply that
-\[
-|\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_a T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
-\]
-The last inequality holds as long as $T$ is larger than some
-constant. This implies that
+%   For each $s$-th first-level group and arm $a$, define
+%   $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in
+%   this group. $W_1^{a,s}$, $W_2^{a,s,1,t}$ for
+%   $ = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1- \GdT
+%   \sqrt{T_1\log(T)}$ together imply that
+% \[
+% |\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_a T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
+% \]
+% The last inequality holds as long as $T$ is larger than some
+% constant.
+  Observe that for any group $s$ in the first level, the empirical
+  means satisfy
 \[
@@
 
-For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of arm
-$a$ pulls in the first two levels. $W_1^{a,s}$ for $s=1,...,S$ and
-$W_3^{a,t}$ for $t \geq (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together
-imply that
-\[
-|\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(q_a T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
-\]
-The last inequality holds when $T$ is larger than some constant.
+% For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of arm
+% $a$ pulls in the first two levels. $W_1^{a,s}$ for $s=1,...,S$ and
+% $W_3^{a,t}$ for $t \geq (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together
+% imply that
+% \[
+% |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(q_a T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
+% \]
+% The last inequality holds when $T$ is larger than some constant.
 
@@
 
-\item $2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq \mu_1-\mu_2 < 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. In this case, we want to show agents in the third level all pull arm 1. Recall $\bar{\mu}_a$ is the empirical mean of arm $a$ in the first two levels. We have
+\item Sub-case (1):
+  $2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
+    \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq \mu_1-\mu_2 <
+  2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
+    \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. Recall $\bar{\mu}_a$ is
+  the empirical mean of arm $a$ in the first two levels. We have
 \[
@@
 
-\item $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 < 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.
-In this case, we just need to make sure that agents in the third level all pull arm 1.
-To do so, we need both arms to be pulled at least $T_2$ rounds in the second level.
+\item Sub-case (2):
+  $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 <
+  2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
+    \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.  To do so, we need both
+  arms to be pulled at least $T_2$ rounds in the second level.
 

### 2018-10-27 3levelproofs.tex
3

@@
 \subsection{Case Analysis under Clean Events}
-Now we assume the intersection of clean events happens. We will first
-provide some helper lemmas for our case analysis.
+Now we assume the intersection of clean events $W$ happens. We will
+first provide some helper lemmas for our case analysis.
 
@@
 \begin{proof}
-  The events $W_1^{a,s}$, $W_2^{a,s,1,t}$ for
+  The events $W_1$ and $W_2^{a,s,1,t}$ for
   $t = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1 + \GdT
@@
 
-\begin{itemize}
+\begin{lemma}
+  For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of
+  arm $a$ pulls in the first two levels. If $W$ holds, then
+  \[
+    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
+  \]
+Furthermore, if there are at least $T_2$ pulls of arm $a$ in the first
+two levels,
+\[
+|\bar{\mu}_a-\mu_a| \leq \sqrt{\frac{2\log(T)}{T_2}}. 
+\]
+\end{lemma}
 
-\item For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of arm $a$ pulls in the first two levels.
-$W_1^{a,s}$ for $s=1,...,S$ and $W_3^{a,t}$ for $t \geq  (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
+\begin{proof}
+The events $W_1^{a,s}$ for $s=1,...,S$ and $W_3^{a,t}$ for $t \geq  (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
   \[
@@
 The last inequality holds when $T$ is larger than some constant.
+\end{proof}
 
-If there are at least $T_2$ pulls of arm $a$ in the first two levels, 
-\[
-|\bar{\mu}_a-\mu_a| \leq \sqrt{\frac{2\log(T)}{T_2}}. 
+\begin{lemma}
+  For each $a \in \{1,2\}$, there exists a first-level group $s_a$
+  such that
+\[\bar{\mu}_a ^{1,s_a} > \mu_a + \frac{1}{4\sqrt{q_aT_1}} \quad \mbox{and, } \quad
+\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
 \]
+\end{lemma}
 
-\item % For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such that $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.
-  The events $W_4^{s_a,a,high}$, $W_1^{s_a,a}$,
-  $W_2^{s_a,a,t, q_aT_1}$ for
-  $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and
+\begin{proof}
+  For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such
+  that both $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.  The
+  events $W_4^{s_a,a,high}$, $W_1^{s_a,a}$, $W_2^{s_a,a,t, q_aT_1}$
+  for $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and
   $W_2^{s_a,a,q_aT_1,t}$ for
@@
 \]
-\end{itemize}
+\end{proof}
 
 \begin{proof}[Proof of Lemma~\ref{3levelbigcase}]
-%   For each $s$-th first-level group and arm $a$, define
-%   $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in
-%   this group. $W_1^{a,s}$, $W_2^{a,s,1,t}$ for
-%   $ = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1- \GdT
-%   \sqrt{T_1\log(T)}$ together imply that
-% \[
-% |\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_a T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
-% \]
-% The last inequality holds as long as $T$ is larger than some
-% constant.
   Observe that for any group $s$ in the first level, the empirical
@@
 \]
-
-% For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of arm
-% $a$ pulls in the first two levels. $W_1^{a,s}$ for $s=1,...,S$ and
-% $W_3^{a,t}$ for $t \geq (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together
-% imply that
-% \[
-% |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(q_a T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
-% \]
-% The last inequality holds when $T$ is larger than some constant.
 

### 2018-10-27 model.tex
commit early and often!

@@
 %!TEX root = main.tex
-\section{Our Model}
+\section{Model}
 \label{sec:model}
@@
 
-\xhdr{Unbiased sub-history policy.} The principal's goal is to reveals
+\xhdr{Unbiased sub-history policy.} The principal's goal is to reveal
 a sequence of messages accroding to a disclosure policy so that the
@@
 
-\xhdr{Agents' behavior.} We model agents with heterogeneity in their
-arm selections. In particular, each agent $t$ has a private estimator
-that maps the revealed sub-history $H_t$ to a mean reward estimate
-$\hat{\mu}_a^t$ for every arm $a$, and the agent chooses the arm $a_t$
-with the highest estimate. The agents' private estimators are drawn
-i.i.d.~from an unknown distribution. For any $t\in[T]$ and $a\in \A$,
-we write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls
-of $a$ and the empirical mean reward of arm $a$ in $H_t$
-respectively. If an arm is not pulled in $H_t$, we will let
-$\bar{\mu}_a^t = 0$.
+\xhdr{Agents' behavior.} We model agents with heterogeneity in their arm selections.
+In particular, each agent $t$ has a private estimator that maps the revealed sub-history $H_t$ to a mean reward estimate $\hat{\mu}_a^t$ for every arm $a$, and the agent chooses the arm $a_t$ with the highest estimate.
+The agents' private estimators are drawn i.i.d.~from an unknown distribution.
+For any $t\in[T]$ and $a\in \A$, we write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls of $a$ and the empirical mean reward of arm $a$ in sub-history $H_t$ respectively.
+If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.
+We require the following assumptions.
 
@@
 
-We will make the following assumptions on the set of mean rewards
-$\{\mu_a\}$, and the relationship between the estimates $\hat \mu_a^t$
-and empirical mean rewards $\bar\mu_a^t$.
-
 \begin{assumption}
 \label{ass:embehave}
-Let $c_m = 1/16$.\swcomment{maybe use a better notation} 
-% \jmcomment{It means a constant for some assumptions about means but nothing else. Just want to make it different from other constants. Maybe there are better notations.}. 
+The set of mean rewards $\{\mu_a\}$, the estimates $\hat \mu_a^t$, and the empirical mean rewards $\bar\mu_a^t$  satisfy:
+
 \begin{itemize}
@@
 
-\item There exists a constant $c_T$ such that for any agent $t$ and
-  arm $a$, as long as $t_a \geq c_T$,
+\item Let $c_m = 1/16$.\swcomment{maybe use a better notation} \nicomment{yeah, why the subscript $m$?
+and $T$ below?
+how about just $\alpha,\beta$ for the constants in this assumption?
+or $\alpha$ and $N_0$?
+or use $n_{t,a}$ for number of pulls and $N$ for a constant that you want the $n_{t,a}$ to exceed?}
+% \jmcomment{It means a constant for some assumptions about means but nothing else. Just want to make it different from other constants. Maybe there are better notations.}. 
+There exists a constant $c_T$ such that for any agent $t$ and
+  arm $a$, as long as \niedit{$N_{t,a} \geq c_T$}, 
 \[
@@
 \]
-\item In the case of $N_{t,a} = 0$, the initial estimate
+\item If $N_{t,a} = 0$, the initial estimate
   $\hat{\mu}^t_a$ is at least $1/3$.
@@
   how this relates to Bayesian exploration with conjugate
-  priors\swcomment{seems to be something nasty}
+  priors\swcomment{seems to be something nasty} \nicomment{need to at least say if we rule out rational agents with these assumptions (which I don't think is a disaster).}
 \end{remark}
 
-Given any bandit instance, we can also define the \emph{gap parameter}
-$\Delta$ as the difference between the largest and second largest mean
-rewards. In general, the gap parameter is unknown to the principal (or
-the algorithm), but we also show how we can obtain different forms of
-regret bounds if $\Delta$ is known.
+Given any bandit instance, we define the \emph{gap parameter} $\Delta$ as the difference between the largest and second largest mean rewards.
+In general, the gap parameter is unknown to the principal (or the algorithm), but we show how to obtain different forms of regret bounds if $\Delta$ is known.
 

### 2018-10-27 prelim.tex
Update 2-level proof
commit early and often!
added a descriptive paragraph

@@
 \label{sec:prelim}
+
+We use the following  concentration and anti-concentration inequalities.
+\niedit{The concentration bound is the standard Chernoff bound which shows that sums of independent random variables converge to their expectation quickly.
+The anti-concentration bound is the Berry-Esseen theorem which shows that the CDF of an appropriately scaled average of i.i.d.\ random variables converges to the CDF of the standard normal distribution pointwise.}
 
@@
 
-\begin{theorem}[Berry-Essen Theorem]
+\begin{theorem}[Berry-Esseen Theorem]
 Let $X_1,...,X_n$ be i.i.d.

### 2018-10-27 2level.tex
finished edits

@@
   $\tilde O(T^{2/3})$. The policy essentially follows the
-  ``explore-then-exploit'' paradigm and consists two phases, which can
+  ``explore-then-exploit'' paradigm and consists of two phases, which can
   be described as a two-level information graph (as shown in
   Figure~\ref{fig:2level}).  In the first level, we perform
-  exploration by simulating $T_1$ independent runs \ALGG of $\GdT$
+  exploration by simulating $T_1$ independent runs of \ALGG of $\GdT$
   rounds. This is done by randomly dividing the first $T_1 \cdot \GdT$
-  agents into $T_1$ groups of equal size and each agent only observe
+  agents into $T_1$ groups of equal size and allowing each agent to only observe
   the history of all previous agents in the same group.  In the second
@@
   The key idea behind the policy is that the first level effectively
-  boosts the exploration probability of Greedy. Since each run of
+  boosts the exploration probability of \ALGG. Since each run of
   \ALGG explores all arms with constant probability (Lemma
-  \ref{lem:greedy}), by simulating multiple runs of Greedy, we can
-  ensure that with high probability, every arm is pulled with a
-  sufficient number of times. The following Lemma follows from
-  applying Chernoff bound and union bound.
+  \ref{lem:greedy}), by simulating multiple runs of \ALGG, we can
+  ensure that with high probability, every arm is pulled a
+  sufficient number of times. The below lemma follows from
+  concentration bounds.
 
-}
+} \nicomment{there was a proof of this once; i remember checking it. if it still exists, let's throw it in an appendix.}
 
 \begin{lemma}[Concentration of arm pulls]\label{lem:t1runs}
-  Consider $T_1$ indepdent runs of \ALGG of length $T_G$. Let $N_a$ be
+  Consider $T_1$ indepdent runs of \ALGG of $T_G$ rounds. Let $N_a$ be
   the number of arm $a$ pulls among all runs. Then with probability at
@@
 \swedit{As a result, every agent in the second level will pull an arm
-  with mean rewards close to the optimal, which gives us the following
+  with mean reward close to the optimal, which gives us the following
   regret guarantee.}
@@
 \swcomment{I think this proof should go to appendix, so I didn't do
-  too much refactoring}
+  too much refactoring} \nicomment{I read this last week and talked to jieming about it; seemed right but a bit messy, but since it's going in an appendix i won't re-read/edit it now.}
 
@@
   level of $T - T_1 \cdot \GdT$ rounds. We consider the following two
-  clean events. We will first bound the probability that both of them
+   events. We will first bound the probability that both of them
   happen and then we will show that they together imply upper bounds
@@
   $$T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2
-      \cdot p_G} \log(T) \right)$$, and achieves an expected regret of
+      \cdot p_G} \log(T) \right),$$ and achieve an expected regret of
   $O(\log(T) \cdot \Delta^{-2})$.

### 2018-10-27 model.tex
finished edits

@@
 
-We study the mult-armed bandit problem in a social learning context,
-in which a principal faces a sequence of $T$ myopic agents. There is a
-set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
-distributed according to the Bernoulli distribution $\cD_a$ with an
-unknown mean $\mu_a$. At each round $t\in [T]$, a new agent $t$
-arrives, receives a message $m_t$ from the principal, chooses an arm
-$a_t\in \A$, and collects a reward $r_t\in \{0,1\}$ that is
-immediately observed by the principal. Given any sequence of arms
-$\{a_1, \ldots, a_T\}$ chosen by the agents, the \emph{regret} is
-defined as
+We study the mult-armed bandit problem in a social learning context, in which a principal faces a sequence of $T$ myopic agents.
+There is a set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is distributed according to the Bernoulli distribution $\cD_a$ with an unknown mean $\mu_a$.
+At each round $t\in [T]$, a new agent $t$ arrives, receives a message $m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a reward $r_t\in \{0,1\}$ that is immediately observed by the principal.
+Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by the agents, the \emph{regret} is defined as
 \[
@@
 
-% We mostly focus on the case when $K=2$. We also discuss how to
-% generalize our results to the case when $K$ is a constant greater
-% than 2. The messages $m_t$ are generated according to a randomized
-% online algorithm $\pi$ termed ``recommendation policy".
+\xhdr{Unbiased sub-history policy.} The principal's goal is to reveal a sequence of messages according to a disclosure policy so that the regret of the induced sequence of actions is minimized.
+We will focus on \emph{unbiased sub-history policies} that at each round $t$ reveal the \emph{sub-history} $H_t = \{(s, a_s, r_s)\mid s \in S_t\}$, such that each $S_t\subseteq [t-1]$ is a subset of previous rounds \emph{fixed ahead of time}.
+A simple example is the policy that reveals the \emph{full history} with $S_t = [t-1]$.
+All of the policies we develop are \emph{transitive}: for any two agents $t$ and $t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains that of $S_{t'}$.
 
-\xhdr{Unbiased sub-history policy.} The principal's goal is to reveal
-a sequence of messages accroding to a disclosure policy so that the
-regret of the induced sequence of actions is minimized. We will focus
-on \emph{unbiased sub-history policies} that at each round $t$ reveal
-the \emph{sub-history} $H_t = \{(s, a_s, r_s)\mid s \in S_t\}$, such
-that each $S_t\subseteq [t-1]$ is a subset of previous rounds
-\emph{fixed ahead of time}. A simple example is the policy that
-reveals the \emph{full history} with $S_t = [t-1]$.  All of the
-policies we develop are \emph{transitive}: for any two agents $t$ and
-$t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains
-that of $S_{t'}$.
-
-\xhdr{Information flow graph.} We will describe our transitive
-policies using a \emph{information flow graph} (and henceforth
-\emph{information graph})---a directed graph over the $T$ agents such that if
-there is an edge from $u$ to $v$, it means $u\in S_v$. By the property
-of transitivity, $S_t$ is the set of nodes that can reach node $t$ in
-the info graph.
+\xhdr{Information flow graph.} We will describe our transitive policies using a \emph{information flow graph} (and henceforth \emph{information graph})---a directed graph over the $T$ agents such that if there is an edge from $u$ to $v$, it means $u\in S_v$.
+By the property of transitivity, $S_t$ is the set of nodes that can reach node $t$ in the info graph.
+\niedit{For example, an information graph for the policy that reveals the full history is the directed line graph containing edges $(t,t+1)$ for all $t\in[T-1]$.}
 
@@
 
-\xhdr{Agents' behavior.} We model agents with heterogeneity in their arm selections.
-In particular, each agent $t$ has a private estimator that maps the revealed sub-history $H_t$ to a mean reward estimate $\hat{\mu}_a^t$ for every arm $a$, and the agent chooses the arm $a_t$ with the highest estimate.
-The agents' private estimators are drawn i.i.d.~from an unknown distribution.
+\xhdr{Agents' behavior.} \nicomment{re-ordered this.} An {\em agent estimator} is a function that maps the revealed sub-history $H_t$ to a mean reward estimate $\hat{\mu}_a^t$ for every arm $a$.
 For any $t\in[T]$ and $a\in \A$, we write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls of $a$ and the empirical mean reward of arm $a$ in sub-history $H_t$ respectively.
@@
 We require the following assumptions.
-
-% \swcomment{need to assume i.i.d. types}
-% We assume that for sufficiently high $t_a$, the estimate
-% $\hat{\mu}_a^t$ is close to the empirical average $\bar{\mu}_a^t$.
 
@@
 
-The first assumption ensures that the reward distributions have
-sufficient entropy to induce natural exploration. We choose the
-bounded range $[1/3, 2/3]$ for the simplicity of our analysis, and it
-can further relaxed to $[1/C, (C-1)/C]$ for any constant $C$. The
-second assumption says that the estimates computed by the agents are
-well-behaved, and are close to the empirical estimates given by the
-sub-history, provided that the number of observations is sufficiently
-large.
+The first assumption ensures that the reward distributions have sufficient entropy to induce natural exploration.
+We choose the bounded range $[1/3, 2/3]$ for the simplicity of our analysis, and it can further relaxed to $[1/C, (C-1)/C]$ for any constant $C$.
+The second assumption says that the estimates computed by the agents are well-behaved, and are close to the empirical estimates given by the sub-history, provided that the number of observations is sufficiently large.
 
-We allow different agents to have different behavior models as long as
-they satisfy Assumption \ref{ass:embehave}. More specifically, we
-assume each agent's behavior model is sampled from an unknown
-distribution independently.
+We model agents with heterogeneity in their arm selections.
+In particular, there is an unknown distribution over the set of agent estimators satisfying Assumption~\ref{ass:embehave}.
+Each agent $t$ indepedently draws an estimator from this distribution, uses it to calculate the mean reward estimates $\hat{\mu}_a^t$ for every arm $a$, and then chooses the arm $a_t$ with the highest estimate.
 % \swcomment{why independently? can be be
@@
 In the proof, we need to use independent to show that the amount of agents pulling arm $a$ in the first level is concentrated to $T_1 q_a$.}
+
 \begin{remark}
-  how this relates to Bayesian exploration with conjugate
-  priors\swcomment{seems to be something nasty} \nicomment{need to at least say if we rule out rational agents with these assumptions (which I don't think is a disaster).}
+We emphasize that the agents we consider in this paper are {\em frequentists}.
+Thus their estimators, which determine their behavior, take samples as inputs and not priors.
+The estimators satisfying Assumption~\ref{ass:embehave} include that of the natural greedy frequentist, who always pulls the arm with the highest empirical mean.
 \end{remark}

### 2018-10-28 llevel-overview.tex
start the overview of l-level

--- 2018-10-12 llevel.tex
@@
 \section{$L$-level Recommendation Policy}
-In this section, we design an $L$-level recommendation policy for $L > 3$ and 2 arms. By having more than 3 levels, we get even smaller regret.
-
-Our recommendation policy has $L$ levels and two types of groups: $G$-groups and $\Gamma$-groups.
-Each level has $S^2$ $G$-groups for $S = 2^{10}\log(T)$.
-Label the $G$-groups in the $l$-th level as $G_{l,u,v}$ for $u,v \in [S]$.
-Level $2$ to level $L$ also have $S^2$ $\Gamma$-groups.
-Label the $\Gamma$-groups in the $l$-th level as $\Gamma_{l,u,v}$ for $u,v \in [S]$.
-Each first-level group ($G_{1,u,v}$ for $u,v\in [S]$) has $T_1$ \ALGG of $\GdT$ rounds in parallel.
-For $l \geq 2$, there are $T_l$ agents in group $G_{l,u,v}$ and there are $T_l (S-1)$ agents in group $\Gamma_{l,u,v}$.
-We will pick $T_1,...,T_L$ in the proof of Theorem \ref{thm:llevel}.
-
-Finally we define the information flow.
-Agents in the first level only observe the history defined in the \ALGG run.
-For agents in group $G_{l,u,v}$ with $l\geq 2$, they observe all the history in the first $l-2$ levels (both $G$-groups and $\Gamma$-groups) and history in group $G_{l-1,v,w}$ for all $w \in [S]$.
-Agents in group $\Gamma_{l,u,v}$ observe the same history as agents in group $G_{l,u,v}$.
-
-\begin{figure}[H]
-\centering
-\begin{tikzpicture}  
- \foreach \x in {0,3,6,9}
- {
- \filldraw[fill=orange!20!white]
- (\x+0,10)--(\x+0.8,10)--(\x+0.8,11)--(\x+0,11)--cycle;
- \filldraw[fill=orange!30!white]
- (\x+0.8,10)--(\x+2.8,10)--(\x+2.8,11)--(\x+0.8,11)--cycle;
- \filldraw[fill=purple!20!white]
- (\x+0,7.5)--(\x+0.8,7.5)--(\x+0.8,8.5)--(\x+0,8.5)--cycle;
- \filldraw[fill=purple!30!white]
- (\x+0.8,7.5)--(\x+2.8,7.5)--(\x+2.8,8.5)--(\x+0.8,8.5)--cycle;
- \filldraw[fill=green!20!white]
- (\x+0,5)--(\x+0.8,5)--(\x+0.8,6)--(\x+0,6)--cycle;
- \filldraw[fill=green!30!white]
- (\x+0.8,5)--(\x+2.8,5)--(\x+2.8,6)--(\x+0.8,6)--cycle;
- \filldraw[fill=blue!20!white]
- (\x+0,2.5)--(\x+0.8,2.5)--(\x+0.8,3.5)--(\x+0,3.5)--cycle;
- \filldraw[fill=blue!30!white]
- (\x+0.8,2.5)--(\x+2.8,2.5)--(\x+2.8,3.5)--(\x+0.8,3.5)--cycle;
- \filldraw[fill=red!20!white]
- (\x+0,0)--(\x+2.8,0)--(\x+2.8,1)--(\x+0,1)--cycle;
- \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
- \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
- \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
- \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
- \draw[dashed] (\x+2,0)--(\x+2,1);  
- \draw[dashed] (\x+2.4,0)--(\x+2.4,1);  
- \node at(\x+0.4,3){$T_{l-2}$};
- \node at(\x+1.8,3){$T_{l-2} (S-1)$};
- \node at(\x+0.4,5.5){$T_{l-1}$};
- \node at(\x+1.8,5.5){$T_{l-1} (S-1)$};
- \node at(\x+0.4,8){$T_l$};
- \node at(\x+1.8,8){$T_l (S-1)$};
- \node at(\x+0.4,10.5){$T_L$};
- \node at(\x+1.8,10.5){$T_L (S-1)$};
- \node at(\x+1.4,0.5){$T_1 \cdot \GdT$};
- }
-\foreach \y in {0,2.5,5,7.5,10}
-{
-  \node at (12.5,\y+0.5){$\cdots$};
-} 
-\foreach \u in {1,2}
-{
-	\foreach \v in {1,2}
-	{
-	\pgfmathsetmacro{\x}{((\u-1)*2+(\v-1))*3};
-	\pgfmathsetmacro{\xa}{((\u-1))*3};
-	\pgfmathsetmacro{\xb}{(2+(\u-1))*3};
-   \node at(\x+0.6,7){$G_{l,\u,\v}$};
-   \node at(\x+0.6,4.5){$G_{l-1,\u,\v}$};
-   \node at(\x+0.6,2){$G_{l-2,\u,\v}$};
-   \node at(\x+2,7){$\Gamma_{l,\u,\v}$};
-   \node at(\x+2,4.5){$\Gamma_{l-1,\u,\v}$};
-   \node at(\x+2,2){$\Gamma_{l-2,\u,\v}$};
-   %\draw[dashed] (\x+0.4,3.5)--(\xa+0.4,5);  
-   %\draw[dashed] (\x+0.4,3.5)--(\xb+0.4,5);  
-   %\draw[dashed] (\x+0.4,3.5)--(\xa+1.8,5);  
-   %\draw[dashed] (\x+0.4,3.5)--(\xb+1.8,5);
-
-   %\draw[dashed] (\x+0.4,6)--(\xa+0.4,7.5);  
-   %\draw[dashed] (\x+0.4,6)--(\xb+0.4,7.5);  
-   %\draw[dashed] (\x+0.4,6)--(\xa+1.8,7.5);  
-   %\draw[dashed] (\x+0.4,6)--(\xb+1.8,7.5);  
-	}
-}
-
-   \draw[dashed] (0+1.8,3.5)--(6.4,7.5);  	
-   \draw[dashed] (3+1.8,3.5)--(6.4,7.5);  	
-   \draw[dashed] (6+1.8,3.5)--(6.4,7.5);  	
-   \draw[dashed] (9+1.8,3.5)--(6.4,7.5);
-
-   %\draw[dashed] (0+0.4,3.5)--(6.4,7.5);  	
-   %\draw[dashed] (3+0.4,3.5)--(6.4,7.5);  	
-   %\draw[dashed] (6+0.4,3.5)--(6.4,7.5);  	
-   %\draw[dashed] (9+0.4,3.5)--(6.4,7.5);
-
-   \draw[dashed] (0+0.4,6)--(6.4,7.5);  	
-   \draw[dashed] (3+0.4,6)--(6.4,7.5);  	
-  \node at (6,1.5)[rotate = 90]{$\cdots$};
-  \node at (-1,1.5)[rotate = 90]{$\cdots$};
-  \node at (6,9.5)[rotate = 90]{$\cdots$};
-  \node at (-1,9.5)[rotate = 90]{$\cdots$};
-  \node at(-1.2,0.5){\textbf{Level 1}};
-  \node at(-1.2,3){\textbf{Level $l-2$}};
-  \node at(-1.2,5.5){\textbf{Level $l-1$}};
-  \node at(-1.2,8){\textbf{Level $l$}};
-  \node at(-1.2,10.5){\textbf{Level $L$}};
-  \draw[->] (13.3,0)--(13.3,12);
-  \node at(13.7,6)[ rotate=90]{Time};
-  \draw [rounded corners=5mm, line width=1mm, red](-0.2,1.75)--(12,1.75)--(12,9)--(-0.2,9)--cycle;\draw [rounded corners=2.5mm, line width=0.5mm, brown](5.9,6.5)--(8.9,6.5)--(8.9,8.8)--(5.9,8.8)--cycle;
-\end{tikzpicture}
-\caption{$l$-level Recommendation Policy.}
-\label{fig:llevel}
-\end{figure}
+\label{sec:llevel}
+In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ to achieve better regret.
+Detailed proofs and discussions can be found in Section \ref{sec:llevel-details}.
 
@@
 
-\begin{proof}
-Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms.
-We will set $T_l$'s later in the proof.
-Before that, we are only going to assume $T_l / T_{l-1} \geq S^4$ for $l=2,...,L-1$ and $T_1 \geq S^4$.
-
-Similarly as the proof of Theorem \ref{thm:3level}, we start with some clean events.
-
-\begin{itemize}
-\item  \textbf{Concentration of the number of arm $a$ pulls in the first level:}
-
-For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
-By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ For group $G_{1,u,v}$, define $W_1^{a,u,v}$ to be the event that the number of arm $a$ pulls in this group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$.
-By Chernoff bound,
-\[
-\Pr[W_1^{a,u,v}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
-\]
-Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,u,v}W_1^{a,u,v}$). By union bound, we have
-\[
-\Pr[W_1] \geq 1- \frac{4S^2}{T^2}.
-\]
-
-\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the history observed by agent $t$:}
-
- For each agent $t$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in agent $t$'s observed history pull arm $a$.
-Define $W_2^{t,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{3\log(T)}{t_2-t_1+1}}$ away from $\mu_a$.
-By Chernoff bound,
-\[
-\Pr[W_2^{t,a,t_1,t_2}] \geq 1 - 2\exp(-6\log(T)) \geq 1- 2/T^6.
-\]
-
-Define $W_2$ to be the intersection of all these events (i.e. $W_2 = \bigcap_{t,a,t_1,t_2} W_2^{t,a,t_1,t_2}$). By union bound, we have
-\[
-\Pr[W_2] \geq 1- \frac{4}{T^3}.
-\]
-
-\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the $l$-th level  for $l \geq 2$:}
-
-For $2\leq l \leq L-1$, $u\in [S]$ and each arm $a$, define $n^{l,u,a}$ to be the number of arm $a$ pulls in groups $G_{l,u,1},...,G_{l,u,S}$.
-Define $W_3^{l,u,a,high}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at least $\mu_a + 1/\sqrt{n^{l,u,a}}$.
-Define $W_3^{l,u,a,low}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at most $\mu_a - 1/\sqrt{n^{l,u,a}}$.
-
-Define $H_l$ to be random variable the history of all agents in the first $l-1$ levels and which agents are chosen in the $l$-th level.
-Let $h_l$ be some realization of $H_l$.
-Notice that once we fix $H_l$, $n^{l,u,a}$ is also fixed.
-
-Now consider $h_l$ to be any possible realized value of $H_l$.
-If fixing $H_l= h_l$ makes $n^{l,u,a}<T_l$, then $\Pr[W_3^{l,u,a,high} |H_l = h_l]=1$  If fixing $H_l = h_l$ makes $n^{l,u,a} \geq T_l$, by Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
-\[
-\Pr[W_3^{l,u,a,high}|H_l = h_l] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{T_l}} > 1/4.
-\]
-Similarly we also have
-\[
-\Pr[W_3^{l,u,a,low}|H_l = h_l]  > 1/4
-\]
-Since $W_3^{l,u,a,high}$ is independent with $W_3^{l,u,3-a,low}$ when fixing $H_l$, we have
-\[
-\Pr[ W_3^{l,u,a,high} \cap W_3^{l,u,3-a,low}|H_l = h_l]  > (1/4)^2 = 1/16.
-\]
-Now define $W_3^{l,a} = \bigcup_u (W_3^{l,u,a,high} \cap W_3^{l,u,3-a,low})$. Since  $(W_3^{l,u,a,high} \cap W_3^{l,u,3-a,low})$ are independent across different $u$'s when fixing $H_l=h_l$, we have
-\[
-\Pr[W_3^{l,a}|H_l= h_l] \geq 1- (1-1/16)^S \geq 1 - 1/T^2.
-\]
-Since this holds for all $h_l$'s, we have $\Pr[W_3^{l,a}] \geq 1-1/T^2$. Finally define $W_3 = \bigcap_{l,a} W_3^{l,a}$. By union bound, we have
-\[
-W_3 \geq 1 - 2L/T^2.
-\]
-
-\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the first level:}
-
-For first-level groups $G_{1,u,1},...,G_{1,u,S}$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in these groups pull arm $a$.
-Define $W_4^{u,a,high}$  to be the event that first $q_a T_1 S$ pulls of arm $a$ in the tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1 S}$ and define $W_4^{u,a,low}$  to be the event that first $q_a T_1S$ pulls of arm $a$ in the tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1S }$.
-By Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
-\[
-\Pr[W_4^{u,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1S}} > 1/4.
-\]
-The last inequality follows when $T$ is larger than some constant.
-Similarly we also have 
-\[
-\Pr[W_4^{u,a,low}] > 1/4.
-\]
-Since $W_4^{u,a,high}$ is independent with $W_4^{u,3-a,low}$, we have
-\[
-\Pr[W_4^{u,a,high} \cap W_4^{u,3-a,low}] =\Pr[W_4^{u,a,high}] \cdot  \Pr[W_4^{u,3-a,low}]>(1/4)^2 = 1/16.
-\]
-Now define $W^{a}_4$ as $\bigcup_u (W_4^{u,a,high} \cap W_4^{u,3-a,low})$. Notice that $(W_4^{u,a,high} \cap W_4^{u,3-a,low})$ are independent across different $u$'s. So we have
-\[
-\Pr[W^{a}_4] \geq 1- (1-1/16)^S \geq 1 -1/T^2.
-\]
-Finally we define $W_4$ as $\bigcap_{a} W^{a}_4$. By union bound,
-\[
-\Pr[W_4] \geq 1- 2/T^2.
-\]
-\end{itemize}
-
-By union bound, the intersection of these clean events (i.e.
-$\bigcap_{i=1}^4 W_i$) happens with probability $1-O(1/T)$.
-When this intersection does not happen, since the probability is $O(1/T)$, it cost expected regret $O(1/T) \cdot T = O(1)$.
-
-Now we assume the intersection of clean events happens and prove upper bound on the expected regret.
-
-By event $W_1$, we know that in each first-level group, there are at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$ pulls of arm $a$.
-We prove in the next claim that there are enough pulls of both arms in higher levels if $\mu_1-\mu_2$ is small enough.
-For notation convenience, we set $\varepsilon_0 = 1$, $\varepsilon_1 = \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}$ and $\varepsilon_l = 1/(4\sqrt{T_lS})$ for $l \geq 2$.
-
-\begin{claim}
-\label{clm:l2_explore}
-For any arm $a$ and $2\leq l \leq L$, if $\mu_1 - \mu_2 \leq \varepsilon_{l-1}$, then for any $u \in [S]$, there are at least $T_l$ pulls of arm $a$ in groups $G_{l,u,1},G_{l,u,2}, ...
-,G_{l,u,S}$ and there are at least $T_lS(S-1)$ pulls of arm $a$ in the $l$-th level $\Gamma$-groups.
-\end{claim}
-
-\begin{proof}
-We are going to show that for each $l$ and $a$ there exists $u_a$ such that agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$.
-This suffices to prove the claim.
-
-We prove the above via induction on $l$.
-%For notation convenience, define $\bar{\mu}^{l,u}_a$  to be the empirical mean of arm $a$ pulls in the history observed by agents in groups $G_{l,1,u},...,G_{l,S,u}$ and $\Gamma_{l,1,u},...,\Gamma_{l,S,u}$ (they observe the same history).
-We start by the base case when $l=2$.
-For each arm $a$, $W_4$ implies there exists $u_a$ such that $W^{u_a,a,high}_4$ and $W^{u_a,3-a,low}_4$ happen.
-For an agent $t$  in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$.
-$W_4^{u_a,a,high}$,  $W_1^{a,u_a,v}$ and $W_2$ together imply that 
-\begin{align*}
-\bar{\mu}_a ^t &\geq \mu_a + \left(q_aT_1S \cdot \frac{1}{\sqrt{q_aT_1S}} - \GdT \sqrt{T_1\log(T)} S\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}S}} \right) \cdot \frac{1}{(q_a T_1+ \GdT \sqrt{T_1\log(T)})S} \\
-&> \mu_a + \frac{1}{4\sqrt{q_aT_1S}}.
-\end{align*}
-The second last inequality holds when $T$ is larger than some constant.
-Similarly, we also have
-\[
-\bar{\mu}_{3-a}^t< \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1S}}.
-\]
-Then we have
-\begin{align*}
-\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a} + \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}\\
-&\geq -\varepsilon_1+ \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}\\
-&\geq \frac{1}{8\sqrt{q_aT_1S}} + \frac{1}{8\sqrt{q_{3-a} T_1S}}.
-\end{align*}
-By Assumption \ref{ass:embehave}, we have
-\begin{align*}
-\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{c_m}{\sqrt{q_aT_1S/2}} - \frac{c_m}{\sqrt{q_{3-a} T_1S/2}}\\
-&> \frac{1}{8\sqrt{q_aT_1S}} + \frac{1}{8\sqrt{q_{3-a} T_1S}} -   \frac{c_m}{\sqrt{q_aT_1S/2}} - \frac{c_m}{\sqrt{q_{3-a} T_1S/2}}\\
-&>0.
-\end{align*}
-The last inequality holds since $c_m$ is a small enough constant defined in Assumption \ref{ass:embehave}.
-Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$ all pull arm $a$.
-
-Now we consider the case when $l > 2$ and assume the claim is true for smaller $l$'s.
-For each arm $a$, $W_3$ implies that there exists $u_a$ such that $W^{l-1,u_a,a,high}_3$ and $W^{l-1,u_a,3-a,low}_3$ happen.
-Recall $n^{l-1,u_a,a}$ is the number of arm $a$ pulls in groups $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$.
-The induction hypothesis implies that $n^{l-1,u_a,a} \geq T_{l-1}$.
-$W^{l-1,u_a,a,high}_3$ together with $n^{l-1,u_a,a} \geq T_{l-1}$ implies that the empirical mean of arm $a$ pulls in group $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$ is at least $\mu_a + 1/\sqrt{n^{l-1,u_a,a}}$.
-For any agent $t$ in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$, it observes history of groups $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$ and all groups in levels below level $l-1$.
-Notice that the groups in the first $l-2$ levels have at most $(T_1 \GdT + T_2 + \cdots +T_{l-2})S^3 \leq T_{l-1}/(12\log(T)) \leq n^{l-1,u_a,a}/(12\log(T))$ agents.
-By $W_2$, we have
-\begin{align*}
-\bar{\mu}_a ^t &\geq \mu_a + \left(n^{l-1,u_a,a}  \cdot \frac{1}{\sqrt{n^{l-1,u_a,a} }}- (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3\cdot \sqrt{\frac{3\log(T)}{ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3}} \right) \\
-&~~~\cdot \frac{1}{n^{l-1,u_a,a}+ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3} \\
-&> \mu_a + \frac{1}{4\sqrt{n^{l-1,u_a,a}  }}.
-\end{align*}
-The third last inequality holds when $T$ larger than some constant.
-Similarly, we also have
-\[
-\bar{\mu}_{3-a}^t < \mu_{3-a}   -\frac{1}{4\sqrt{n^{l-1,u_a,3-a}  }}.
-\]
-Then we have
-\begin{align*}
-\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a}+ \frac{1}{4\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{4\sqrt{n^{l-1,u_a,3-a}  }}\\
-&\geq -\varepsilon_{l-1}+ \frac{1}{4\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{4\sqrt{n^{l-1,u_a,3-a}  }}\\
-&\geq \frac{1}{8\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{8\sqrt{n^{l-1,u_a,3-a}  }}.
-\end{align*}
-The last inequality holds because $n^{l-1,u_a,a}$ and $n^{l-1,u_a,3-a}$ are at most $T_{l-1} S$. By Assumption \ref{ass:embehave}, we have
-\begin{align*}
-\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{c_m}{\sqrt{n^{l-1,u_a,a} }} - \frac{c_m}{\sqrt{n^{l-1,u_a,3-a}}}\\
-&> \frac{1}{8\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{8\sqrt{n^{l-1,u_a,3-a}  }} -  \frac{c_m}{\sqrt{n^{l-1,u_a,a} }} - \frac{c_m}{\sqrt{n^{l-1,u_a,3-a}}}\\
-&>0.
-\end{align*}
-The last inequality holds since $c_m$ is a small enough constant defined in Assumption \ref{ass:embehave}.
-Therefore agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$.
-\end{proof}
-
-\begin{claim}
-\label{clm:l2_exploit}
-For any $2 \leq l \leq L$, if $\varepsilon_{l-1} S\leq \mu_1 - \mu_2 < \varepsilon_{l-2} S$, there are no pulls of arm 2 in groups with level $l,...,L$. 
-\end{claim}
-
-\begin{proof}
-We argue in 2 cases $\varepsilon_{l-1} \sqrt{S} \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l \geq 2$ and $\varepsilon_{l-2}  \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2} \sqrt{S}$ for $l > 2$.
-Since our recommendation policy's first level is slightly different from other levels, we need to argue case $\varepsilon_{l-1} \sqrt{S} \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l=2$ and case $\varepsilon_{l-2}  \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2} \sqrt{S}$ for $l =3$ separately.
-
-\begin{itemize}
-\item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l = 2$(i.e.
-$\varepsilon_1S\leq \mu_1 - \mu_2 \leq \varepsilon_0$): We know agents in level at least 2 will observe at least $q_aT_1/2$ pulls of arm $a$ for $a \in \{1,2\}$.
-By $W_2$, for any agent in level at least 2, we have
-\[
-|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{Sq_aT_1/2}}.
-\]
-By Assumption \ref{ass:embehave}, we have
-\begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{c_m}{\sqrt{Sq_1T_1/2}} -  \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
-&\geq \mu_1 -\mu_2-\sqrt{\frac{3\log(T)}{Sq_1T_1/2}} - \sqrt{\frac{3\log(T)}{Sq_2T_1/2}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} -  \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
-&\geq\frac{\sqrt{S}}{4\sqrt{q_1T_1}} +  \frac{\sqrt{S}}{4\sqrt{q_2T_1}}-\sqrt{\frac{3\log(T)}{Sq_1T_1/2}} - \sqrt{\frac{3\log(T)}{Sq_2T_1/2}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} -  \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
-&>0.
-\end{align*}
-Therefore agents in level at least 2 will all pull arm 1.
-
-\item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l > 2$: By claim \ref{clm:l2_explore}, for any agent $t$ in level at least $l$, that agent will observe at least $T_{l-1}$ arm $a$ pulls.
-By $W_2$, we have
-\[
-|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{T_{l-1}}}.
-\]
-By Assumption \ref{ass:embehave}, we have
-\begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2c_m}{\sqrt{T_{l-1}}} \\
-&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2c_m}{\sqrt{T_{l-1}}} \\
-&\geq\sqrt{\frac{S}{16T_{l-1}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2c_m}{\sqrt{T_{l-1}}} \\
-&>0.
-\end{align*}
-Therefore agents in level at least $l$ will all pull arm 1.
-
-\item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}S$ for $l =3$ (i.e.
-$\varepsilon_1 < \mu_1 - \mu_2 < \varepsilon_1S$): By Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $3$, that agent will observe at least $T_1q_aS^2/2$ arm $a$ pulls (just from the first level).
-By $W_2$, we have
-\[
-|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S^2q_aT_1/2}}.
-\]
-By Assumption \ref{ass:embehave}, we have
-\begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{c_m}{\sqrt{S^2q_1T_1/2}}-\frac{c_m}{\sqrt{S^2q_2T_1/2}}  \\
-&\geq \mu_1 -\mu_2 -  \sqrt{\frac{3\log(T)}{S^2q_1T_1/2}}- \sqrt{\frac{3\log(T)}{S^2q_2T_1/2}}- \frac{c_m}{\sqrt{S^2q_1T_1/2}}-\frac{c_m}{\sqrt{S^2q_2T_1/2}}  \\
-&\geq\frac{1}{4\sqrt{Sq_1T_1}} + \frac{1}{4\sqrt{Sq_2T_1}}  -  \sqrt{\frac{3\log(T)}{S^2q_1T_1/2}}- \sqrt{\frac{3\log(T)}{S^2q_2T_1/2}}- \frac{c_m}{\sqrt{S^2q_1T_1/2}}-\frac{c_m}{\sqrt{S^2q_2T_1/2}}  \\
-&>0.
-\end{align*}
-Therefore agents in level at least 3 will all pull arm 1.
-
-\item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}S$ for $l >3$: Since $\mu_1-\mu_2 < \varepsilon_{l-2}S < \varepsilon_{l-3}$, by Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $l$, that agent will observe at least $T_{l-2}S^2$ arm $a$ pulls (just from level $l-2$).
-By $W_2$, we have
-\[
-|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S^2T_{l-2}}}.
-\]
-By Assumption \ref{ass:embehave}, we have
-\begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2c_m}{\sqrt{S^2T_{l-2}}} \\
-&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{S^2T_{l-2}}}- \frac{2c_m}{\sqrt{S^2T_{l-2}}} \\
-&\geq\frac{1}{4\sqrt{ST_{l-2}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2c_m}{\sqrt{T_{l-1}}} \\
-&>0.
-\end{align*}
-Therefore agents in level at least $l$ will all pull arm 1. 
-\end{itemize}
-\end{proof}
-
-Now we set the group sizes $T_l$'s as following. For $l < L$,
-\[
-T_l = T^{\frac{2^{L-1} + 2^{L-2} + \cdots + 2^{L-l}}{2^{L-1}+ 2^{L-2} + \cdots + 1}}/S^3.
-\]
-and 
-\[
-T_L = (T - T_1 \cdot \GdT\cdot S^2 - (T_2 + \cdots + T_{l-1}) S^3) /S^3
-\]
-We restrict $L$ to be at most $\log(\ln(T)/\log(S^4))$ so that $T_l / T_{l-1} \geq T^{1/2^L} \geq S^4$ for $l = 2,...,L-1$.
-$T_L$ is a little bit different because we want total number of agents to be $T$.
-
-By Claim \ref{clm:l2_exploit}, we know that the expected regret conditioned the intersection of clean events is at most 
-\begin{align*}
-&\max\left( T_1T_GS^2 , \max_{l \geq 2} \varepsilon_{l-1}S(T_1T_GS^2 + T_2 S^3 + \cdots + T_lS^3)\right) \\
-\leq & \max\left( T_1T_GS^2 , \max_{l \geq 2} 2 \varepsilon_{l-1} T_l S^4 \right)\\
-= &O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right).
-\end{align*}
-\end{proof}
-
-Now we are going to change the parameters of the $L$-level recommendation policy a little bit and prove the below corollary.
-We will keep $S$ the same (i.e.
-$S = 2^{10}\log(T)$).
-We are going to change $L$ and $T_1,...,T_L$.
-We set $L = \log(T)/\log(S^4)$, $T_l = (S^4)^l$ for $l=1,...,L-1$ and $T_L = (T - T_1 \GdT S^2 - S^3\sum_{l=2}^{L-1} T_l)/S^3$.
 \begin{corollary}
+\label{cor:llevel}
 With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$.
-Here $\Delta = \mu_1 -\mu_2$ and the $L$-level recommendation policy does not need to know $\Delta$.
+Here $\Delta = |\mu_1 -\mu_2|$ and the $L$-level recommendation policy does not need to know $\Delta$.
 Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$.
 \end{corollary}
-
-\begin{proof}
-Notice that in the proof of Theorem \ref{thm:llevel}, by the end of Claim \ref{clm:l2_exploit}, the only constraint we need about $T_l$'s is that $T_l / T_{l-1} \geq S^4$ for $l=2,...,L-1$ and $T_1 \geq S^4$.
-And our new settings of $T_l$'s still satisfy this constraint.
-So we can reuse the proof of Theorem \ref{thm:llevel} till the end of Claim \ref{clm:l2_exploit}.
-
-Recall in the proof of Theorem \ref{thm:llevel}, $\varepsilon_l =\Theta(1/\sqrt{T_l S})$. Consider two cases:
-\begin{itemize}
-\item $\Delta < \varepsilon_{L-1} S$.
-In this case, notice that even always picking the sub-optimal arm gives expected regret at most $T(\mu_1-\mu_2) = T\Delta = O(T^{1/2} polylog(T))$.
-On the other hand, $T^{1/2} = O(polylog(T)/\Delta)$.
-Therefore, the expected regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
-\item $\Delta \geq \varepsilon_{L-1} S$.
-In this case, we can find $l \in \{2,...,L\}$ such that $\varepsilon_{l-1} S\leq \Delta < \varepsilon_{l-2} S$.
-By Claim \ref{clm:l2_exploit}, we can bound the expected regret by
-\begin{align*}
-&\Delta \cdot (T_1 \GdT S^2  +T_2 S^3+ \cdots T_{l-1} S^3)\\
-=& O(\Delta T_{l-1}S^3) \\
-=&O(\Delta T_{l-2}S^7) \\
-=&O(\Delta\cdot  \frac{1}{\varepsilon^2_{l-2}}\cdot S^6)\\
-=&O(\Delta \cdot \frac{1}{\Delta^2}\cdot S^8)\\
-=&O(polylog(T)/\Delta).
-\end{align*}
-We also have $1/\Delta \leq 1/(\varepsilon_{L-1}S)= O(T^{1/2})$. Therefore, the expected regret is \\$O(\min(1/\Delta, T^{1/2})polylog(T))$.
-\end{itemize}
-\end{proof}
-
-\begin{claim}
-Extended to constant number of arms.
-\end{claim}

### 2018-10-28 llevel-overview.tex
minor change

@@
 \label{sec:llevel}
-In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ to achieve better regret.
+In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ which achieves better regret.
 Detailed proofs and discussions can be found in Section \ref{sec:llevel-details}.
 
+\jmcomment{Will change these statements a bit.}
 \begin{theorem}
@@
 With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$.
-Here $\Delta = |\mu_1 -\mu_2|$ and the $L$-level recommendation policy does not need to know $\Delta$.
+Here $\Delta$ is the difference between the largest mean and second largest mean of arms and the $L$-level recommendation policy does not need to know $\Delta$.
 Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$.
 \end{corollary}
+
+Now we give some overview of the additional techniques we use for our $L$-level policy.
+
+\xhdr{New connecting structures between levels.}
+
+\xhdr{Additional groups for boundary cases.}

### 2018-10-28 3level.tex
d

@@
 is pulled at least $\Omega(T_1)$ times. The following lemma can
-derived from combining Lemma~\ref{lem:t1runs} and union bound. This
-will be useful for applying concentration inequalities to the
-empirical mean rewards.
+derived from combining Lemma~\ref{lem:t1runs} and union bound.
 
@@
 
-The intermediate case more challenging since the gap is neither too
-small to have negligible effect on regret nor too big to make the arms
-distinguishable after the first level.
+The intermediate case is more challenging since the gap is neither
+small enough to have negligible effect on regret nor large enough to
+make the arms distinguishable after the first level. In this case, we
+need to ensure that both arms will continued to be pulled in the
+second level. To achieve this, we will take advantage of the clean
+events of $W_1$ and $W_4$.
+
+\begin{lemma}\label{lem:luck}
+  For the $s$-th first-level group and arm $a$, define
+  $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in
+  this group. For each $a \in \{1,2\}$, there exists a group $s_a$
+  such that
+\[
+\bar{\mu}_a ^{1,s_a} > \mu_a + \frac{1}{4\sqrt{q_aT_1}} \quad \mbox{and, } \quad
+\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
+\]
+\end{lemma}
 
@@
 
+\OMIT{
 \begin{proof}
-\OMIT{Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We do a case analysis based on $\mu_1-\mu_2$.
+Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We do a case analysis based on $\mu_1-\mu_2$.
 
@@
 \end{itemize}
-}
+
 Finally we proceed to the case analysis. We give upper bounds on the expected regret conditioned on the intersection of clean events.
 
-\OMIT{
 \begin{itemize}
@@
 arm 2) gives regret at most $T \cdot (\mu_1-\mu_2) = O(T^{4/7} \log^{6/7}(T))$.
-
 \end{itemize}
-}
-\end{proof}
+\end{proof}}
 

### 2018-10-28 3levelproofs.tex
d

@@
 \begin{proof}[Proof of Lemma~\ref{3levelw3}]
-By Chernoff bound,
+  For any arm $a$, let's imagine a hypothetical tape of length $T$,
+  with each cell independently sampled from $\cD_a$. The tape encodes
+  rewards of the first two levels as follows: the $j$-th time arm $a$
+  is chosen in the first two levels, its reward is taken from the
+  $j$-th cell in the tape. Define $W_3^{a,t}$ to be the event that the
+  mean of the first $t$ pulls in the tape is at most
+  $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. By Chernoff bound,
 \[
@@
 \]
-By union bound, we have
+By union bound, the intersection of all these events has probability
+at least:
 \[
@@
 \begin{proof}
-The events $W_1^{a,s}$ for $s=1,...,S$ and $W_3^{a,t}$ for $t \geq  (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
+The events $W_1$ and $W_3^{a,t}$ for $t \geq  (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
   \[
@@
 
-\begin{lemma}
-  For each $a \in \{1,2\}$, there exists a first-level group $s_a$
-  such that
-\[\bar{\mu}_a ^{1,s_a} > \mu_a + \frac{1}{4\sqrt{q_aT_1}} \quad \mbox{and, } \quad
-\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
-\]
-\end{lemma}
-
-\begin{proof}
+\begin{proof}[Proof of Lemma~\ref{lem:luck}]
   For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such
   that both $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.  The
-  events $W_4^{s_a,a,high}$, $W_1^{s_a,a}$, $W_2^{s_a,a,t, q_aT_1}$
+  events $W_4^{s_a,a,high}$, $W_1$, $W_2^{s_a,a,t, q_aT_1}$
   for $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and
@@
 \end{align*}
-So we know agents in the third-level group will all pull arm 1. Therefore the expected regret is at most 
+So we know agents in the third-level group will all pull arm 1. \OMIT{Therefore the expected regret is at most 
 \[
@@
 \]
-
+}
 \item Sub-case (2):
@@
   2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
-    \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.  To do so, we need both
-  arms to be pulled at least $T_2$ rounds in the second level.
-
-Now consider the $s_a$-th second-level group. We have
+    \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.  In this sub-case, we
+  need both arms to be pulled at least $T_2$ rounds in the second
+  level. For every arm $a$, consider the $s_a$-th second-level group,
+  with $s_a$ given by Lemma~\ref{lem:luck}. We have
 \begin{align*}
@@
 \]
-Similarly as above, by Assumption \ref{ass:embehave}, we know $\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third level. So we know agents in the third-level group will all pull arm 1.
-
+Similarly as above, by Assumption \ref{ass:embehave}, we know $\hat{\mu}_1^t - \hat{\mu}_2^t > 0$ for any agent $t$ in the third level.
+So we know agents in the third-level group will all pull arm 1.\OMIT{
 Therefore the expected regret is at most 
@@
 \]
-
+}
 \end{itemize}
-
+Together the two sub-cases complete the proof.
 \end{proof}

### 2018-10-28 llevel.tex
leveling
fix a typo

@@
 \section{$L$-level Recommendation Policy}
+\label{sec:llevel-details}
 In this section, we design an $L$-level recommendation policy for $L > 3$ and 2 arms. By having more than 3 levels, we get even smaller regret.
@@
 Now consider $h_l$ to be any possible realized value of $H_l$.
-If fixing $H_l= h_l$ makes $n^{l,u,a}<T_l$, then $\Pr[W_3^{l,u,a,high} |H_l = h_l]=1$  If fixing $H_l = h_l$ makes $n^{l,u,a} \geq T_l$, by Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
+If fixing $H_l= h_l$ makes $n^{l,u,a}<T_l$, then $\Pr[W_3^{l,u,a,high} |H_l = h_l]=1$  If fixing $H_l = h_l$ makes $n^{l,u,a} \geq T_l$, by Berry-Esseen Theorem and $\mu_a \in [1/3,2/3]$, we have
 \[
@@
 Define $W_4^{u,a,high}$  to be the event that first $q_a T_1 S$ pulls of arm $a$ in the tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1 S}$ and define $W_4^{u,a,low}$  to be the event that first $q_a T_1S$ pulls of arm $a$ in the tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1S }$.
-By Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
+By Berry-Esseen Theorem and $\mu_a \in [1/3,2/3]$, we have
 \[

### 2018-10-28 3level.tex
hello

--- 2018-10-27 3level.tex
@@
 $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both
-arms. We break down the regret analysis into three cases on the scale
+arms. We break down the regret analysis into four cases on the scale
 of the gap parameter $\Delta = (\mu_1-\mu_2)$.
@@
 
-\begin{claim}[Small gap case]
+\begin{claim}[Negligible gap case]
   Suppose $\Delta \leq 3\sqrt{\frac{2\log(T)}{T_2}}$,
@@
 Another simple case is when $\Delta$ is sufficiently large, so that
-the data collected in the first level can distinguish the two
-arms. The proof essentially follows from the clean event $W_1$ that
-both arms are explored sufficient many times in level 1, and the
+the data collected in any sing first-level group can distinguish the
+two arms. The proof essentially follows from the clean event $W_1$
+that both arms are explored sufficient many times in level 1, and the
 empirical rewards in the first two levels concentrate around their
@@
 
-The intermediate case more challenging since the gap is neither too
-small to have negligible effect on regret nor too big to make the arms
-distinguishable after the first level.
+There are two more intermediate cases. In the \emph{medium gap} case,
+the gap is smaller than $\tilde O(\sqrt{1/T_1})$, but bigger than
+$\tilde \Omega(\sqrt{1/(S\, T_1)})$. Then the data collected in any
+single group from the first level no longer suffices to distinguish
+the two arms. However, we show that as the policy aggregates the
+history from all $S$ groups at the end of the second level, the data
+will enable all third-level agents to correctly identify the arm 1 as
+the better arm (even though one of the arms may not be pulled at all
+in the second level).
 
-\begin{lemma}[Intermediate gap case]\label{3levelmidcase}
+\begin{lemma}[Medium gap case]\label{3levelmedium}
+  All agents pull arm 1 in the third level, when $\Delta$ satisfies
+  \[
+  \Delta\in \left[
+   2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
+    \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right),
+ 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
+        \sqrt{\frac{4\log(T)}{q_2T_1}}\right), 
+    \right)
+  \]
+\end{lemma}
+
+Finally, consider the \emph{small gap} case where $\Delta$ is between
+$\tilde\Omega(\sqrt{1/T_2})$ and $\tilde O(\sqrt{1/(S T_1))})$. This
+is more challenging since even aggregating the data from all $S$
+groups in the first level is not sufficient for correctly
+distinguishing the two arms. Thus, we need to ensure that both arms
+will continue to be pulled in the second level. To achieve this, we
+will nicely leverage the event of $W_4$, which has the implication
+that every arm $a$ has its ``lucky'' group $s_a$ in the first level,
+for which the empirical mean is slightly higher than $\mu_a$, while
+the other arm is slightly lower than $\mu_{(3-a)}$. Since the
+deviations are in the order of $\Omega(\sqrt{1/T_1})$, the sub-history
+from this ``lucky'' group will induce a pair of estimates such that
+$\hat \mu_a^t > \hat \mu_{(3-a)}^t$, and so any second-level agent in
+group $s_a$ will pull arm $a$.  As a result, we guarantee both arms
+will be pulled at least $T_2$ times in the second level, which in turn
+gives the following guarantee.
+
+\begin{lemma}[Small gap case]\label{3levelsmallcase}
   All agents pull arm 1 in the third level, when $\Delta$ satisfies
@@
     \Delta\in \left( 3\sqrt{\frac{2\log(T)}{T_2}},
-      2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
-        \sqrt{\frac{4\log(T)}{q_2T_1}}\right) \right)
+      2\left(\sqrt{\frac{4\log(T)}{S q_1T_1}} +
+        \sqrt{\frac{4\log(T)}{S q_2T_1}}\right) \right)
   \]
@@
 
+\paragraph{Wrapping up: proof of \Cref{thm:3level}. } In negligible
+gap case, the stated regret bound holds regardless of the sequence of
+chosen arms. In the large gap case, the regret only comes from the
+first level, which is bounded
+by$S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$. In the intermediate cases of
+both medium and small gap, it suffices to bound the regret from the
+first and second levels, so
+\[
+\reg(T) \leq (S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
++ \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T)).
+\]
+Therefore, we obtain the stated regret bound in all cases.
+
+\OMIT{
 \begin{proof}
-\OMIT{Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We do a case analysis based on $\mu_1-\mu_2$.
+Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We do a case analysis based on $\mu_1-\mu_2$.
 

### 2018-10-28 3levelproofs.tex
fix a typo
hello

@@
 \begin{proof}[Proof of Lemma~\ref{3levelw4}]
-By Berry-Essen Theorem and
+By Berry-Esseen Theorem and
   $\mu_a \in [1/3,2/3]$, we have for any $a$,
@@
 
-\begin{proof}[Proof of Lemma~\ref{lem:luck}]
+\begin{lemma}\label{lem:luck}
+  For the $s$-th first-level group and arm $a$, define
+  $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in
+  this group. For each $a \in \{1,2\}$, there exists a group $s_a$
+  such that
+\[
+\bar{\mu}_a ^{1,s_a} > \mu_a + \frac{1}{4\sqrt{q_aT_1}} \quad \mbox{and, } \quad
+\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
+\]
+\end{lemma}
+
+\begin{proof}% [Proof of Lemma~\ref{lem:luck}]
   For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such
@@
 
-\begin{proof}[Proof of Lemma~\ref{3levelbigcase}]
+Now we proceed to the case analysis.
+
+\begin{proof}[Proof of Lemma~\ref{3levelbigcase} (Large gap case)]
   Observe that for any group $s$ in the first level, the empirical
@@
 
-\begin{proof}[Proof of Lemma~\ref{3levelmidcase}]
-  We will further break down the intermediate case into two sub-cases.
-\begin{itemize}
-
-\item Sub-case (1):
-  $2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
-    \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq \mu_1-\mu_2 <
-  2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
-    \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. Recall $\bar{\mu}_a$ is
+\begin{proof}[Proof of Lemma~\ref{3levelmedium} (Medium gap case)]
+  % $2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
+  %   \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq \mu_1-\mu_2 <
+  % 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
+  %   \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. 
+  Recall $\bar{\mu}_a$ is
   the empirical mean of arm $a$ in the first two levels. We have
@@
 }
-\item Sub-case (2):
-  $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 <
-  2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
-    \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.  In this sub-case, we
-  need both arms to be pulled at least $T_2$ rounds in the second
-  level. For every arm $a$, consider the $s_a$-th second-level group,
-  with $s_a$ given by Lemma~\ref{lem:luck}. We have
+\end{proof}
+
+\begin{proof}[Proof of Lemma~\ref{3levelsmallcase} (Small gap case)]
+  % $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 <
+  % 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
+  %   \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.  
+  In this case, we need both arms to be pulled at least $T_2$ rounds
+  in the second level. For every arm $a$, consider the $s_a$-th
+  second-level group, with $s_a$ given by Lemma~\ref{lem:luck}. We
+  have
 \begin{align*}
@@
 }
-\end{itemize}
-Together the two sub-cases complete the proof.
 \end{proof}

### 2018-10-28 3level.tex
check in often!

@@
 this idea to achieve a regret rate of $\tilde O(T^{1/2})$. For
-simplicity, we will focus on the setting with 2 arms.
+simplicity, we will focus on the setting with 2 arms\niedit{, although our results can be extended to a constant number of arms $K$}.
+\nicomment{I think that's true, but if not, then we're not focusing on 2 arms for ``simplicity''.}
 
@@
 history from the first two levels.
+\nicomment{This comment applies to the 2level too; why not allow the guys within the last level see each other?
+Seems like this would still work but be more of a headache to prove -- would have to argue the empirical means can't move around too much in the sub-terminal levels, but it makes a big qualitative difference because now everyone sees a vanishingly small fraction of the history whereas with this modification a fraction approaching 1 of the people see a fraction approaching 1 of the history.}
 
@@
 than $\tilde{O}(1/\sqrt{T_2})$, in which case pulling either arm will
-incur small regret. The formal guarantee of the policy is the
+incur small regret.
+\nicomment{Need to add intuition about why it's necessary to have a middle level to get this to happen, as opposed to making the bottom level bigger.
+Is it because the bottom level will start to herd on some arm and we want to refresh that process?
+Also should talk about need for anti-concentration bound.} The formal guarantee of the policy is the
 following.
@@
 
-\subsection{Clean events}
-We will first establish four \emph{clean events} that together occur
+\subsection{Events}
+We will first establish four \nidelete{\emph{clean events}} \niedit{events} \nicomment{this is a dumb name, what's clean or dirty about an event?
+i advocate deleting this adjective from our paper, as i did for the 2level section} that together occur
 with probability at least $1 - O(1/T)$. The first event says that
@@
 the first level. To state the events, it will be useful to think of a
-hypothetical reward tape tape $\cT^1_{s, a}$ of length $T$ for each
+hypothetical reward tape $\cT^1_{s, a}$ of length $T$ for each
 group $s$ and arm $a$, with each cell independently sampled from
@@
 is chosen by the group $s$ in the first level, its reward is taken
-from the $j$-th cell in this arm’s tape. The following result
+from the $j$-th cell in this arm's tape. The following result
 characterizes the concentration of the mean rewards among all
@@
 slightly above $\mu_a$, while the other arm $(3 - a)$ has empirical
-mean slightly below $\mu_{(3-a)}$. This event is crucial for making
-the agents in the second level to explore both arms when the their
+mean slightly below $\mu_{(3-a)}$. This event is crucial for inducing
+agents in the second level to explore both arms when the their
 mean rewards are indistinguishable after the first level.
@@
   empirical mean of the first $q_a T_1$ cells in tape $\cT^1_{a, s}$.
-  Let $W_4^{s,a,high}$ be the event
+  Let $W_4^{s,a,\text{high}}$ be the event
   $\tilde\mu_{a, s} \geq \mu_a + 1/\sqrt{q_a T_1}$ and let
-  $W_4^{s,a,low}$ be the event that
+  $W_4^{s,a,\text{low}}$ be the event that
   $\tilde\mu_{a, s} \leq \mu_a - 1/\sqrt{q_a T_1}$.  Let $W_4$ be the
   event that for every $a\in \{1, 2\}$, there exists a group
-  $s_a\in [S]$ in the first level such that both $W_4^{s_a,a,high}$
-  and $W_4^{s_a,3-a,low}$ occur. Then
+  $s_a\in [S]$ in the first level such that both $W_4^{s_a,a,\text{high}}$
+  and $W_4^{s_a,3-a,\text{low}}$ occur. Then
   \[
@@
 Lastly, we will condition on the event that the empirical means of
-both arms to be concentrated around their true means in any prefix of
+both arms are concentrated around their true means in any prefix of
 their pulls. This guarantees that the policy obtains an accurate
@@
 
-\swcomment{might want to swap out $W_3$ and $W_4$}
+\swcomment{might want to swap out $W_3$ and $W_4$} \nicomment{yes please!}
+
 \begin{lemma}[Concentration of empirical means in the first two
@@
   $W_3$ holds: for all $a\in \{1, 2\}$ and $m \in [N_{T, a}]$, the
-  empirical means of the first $t$ arm $a$ pulls is at most
+  empirical means of the first $t$ \nicomment{what is $t$ here; you mean $m$? in which case please replace $m$ with $t$ in the conditioning and bound} arm $a$ pulls is at most
   $\sqrt{\frac{2\log(T)}{m}}$ away from $\mu_a$, where $N_{T, a}$ is
@@
 
-Let $W = \bigcap_{i=1}^4 W_i$ be the intersection of all 4 clean
-events.  By union bound, $W$ occuers with probability $1-O(1/T)$. Note
+Let $W = \bigcap_{i=1}^4 W_i$ be the intersection of all 4 
+events.  By union bound, $W$ occurs with probability $1-O(1/T)$. Note
 that expected regret conditioned on $W$ not occuring is at most
-$O(1/T) \cdot T = O(1)$, so it suffices to bound the regret under $W$.
+$O(1/T) \cdot T = O(1)$, so it suffices to bound the regret conditioned on $W$.
 
-\subsection{Case Analysis under Clean Events}
+\subsection{Case Analysis}
 
-We now proceed to bound the regret conditioned on all four clean
-events defined above occur. Without loss of generality, we assume
+We now proceed to bound the regret conditioned on the four 
+events defined above. Without loss of generality, we assume
 $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both
@@
 Another simple case is when $\Delta$ is sufficiently large, so that
-the data collected in any sing first-level group can distinguish the
-two arms. The proof essentially follows from the clean event $W_1$
+the data collected in any single first-level group can distinguish the
+two arms. The proof essentially follows from the event $W_1$
 that both arms are explored sufficient many times in level 1, and the
@@
 will nicely leverage the event of $W_4$, which has the implication
-that every arm $a$ has its ``lucky'' group $s_a$ in the first level,
-for which the empirical mean is slightly higher than $\mu_a$, while
+that each arm $a$ has a ``lucky'' group $s_a$ in the first level,
+for which its empirical mean is slightly higher than $\mu_a$, while
 the other arm is slightly lower than $\mu_{(3-a)}$. Since the
@@
 first level, which is bounded
-by$S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$. In the intermediate cases of
-both medium and small gap, it suffices to bound the regret from the
+by $S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$. In the intermediate cases of
+both medium and small gaps, it suffices to bound the regret from the
 first and second levels, so

### 2018-10-28 3level.tex
some appendix edits

@@
 
-They main idea for the 3-level policy is that it inserts the second
-level as an additional ``checkpoint'' to induce more adaptivity in the
-exploration. While the first level ensures that the agents explore
-both arms, the second level will continue to explore both arms only if
-the rewards of the two arms are still indistinguishable (that is, when
-$|\mu_1 - \mu_2| < \tilde{O}(1/\sqrt{T_1})$). In the third level,
-agents will pull the best arm unless $|\mu_1-\mu_2|$ is much smaller
-than $\tilde{O}(1/\sqrt{T_2})$, in which case pulling either arm will
+They main idea for the 3-level policy is that it inserts the second level as an additional ``checkpoint'' to induce more adaptivity in the exploration.
+While the first level ensures that the agents explore both arms, the second level will continue to explore both arms only if the rewards of the two arms are still indistinguishable (that is, when $|\mu_1 - \mu_2| < \tilde{O}(1/\sqrt{T_1})$).
+In the third level, agents will pull the best arm unless $|\mu_1-\mu_2|$ is much smaller than $\tilde{O}(1/\sqrt{T_2})$, in which case pulling either arm will
 incur small regret.
@@
 \subsection{Events}
-We will first establish four \nidelete{\emph{clean events}} \niedit{events} \nicomment{this is a dumb name, what's clean or dirty about an event?
-i advocate deleting this adjective from our paper, as i did for the 2level section} that together occur
+We will first establish four events that together occur
 with probability at least $1 - O(1/T)$. The first event says that
@@
 the other arm is slightly lower than $\mu_{(3-a)}$. Since the
-deviations are in the order of $\Omega(\sqrt{1/T_1})$, the sub-history
-from this ``lucky'' group will induce a pair of estimates such that
+deviations are in the order of $\Omega(\sqrt{1/T_1})$, and Assumption~\ref{ass:embehave} guarantees the estimates are also within $\Omega(\sqrt{1/T_1})$ of the empirical means, the sub-history
+from this ``lucky'' group will yield estimates such that
 $\hat \mu_a^t > \hat \mu_{(3-a)}^t$, and so any second-level agent in

### 2018-10-28 3level.tex
added intuition in 3level

@@
 They main idea for the 3-level policy is that it inserts the second level as an additional ``checkpoint'' to induce more adaptivity in the exploration.
-While the first level ensures that the agents explore both arms, the second level will continue to explore both arms only if the rewards of the two arms are still indistinguishable (that is, when $|\mu_1 - \mu_2| < \tilde{O}(1/\sqrt{T_1})$).
-In the third level, agents will pull the best arm unless $|\mu_1-\mu_2|$ is much smaller than $\tilde{O}(1/\sqrt{T_2})$, in which case pulling either arm will
-incur small regret.
-\nicomment{Need to add intuition about why it's necessary to have a middle level to get this to happen, as opposed to making the bottom level bigger.
-Is it because the bottom level will start to herd on some arm and we want to refresh that process?
-Also should talk about need for anti-concentration bound.} The formal guarantee of the policy is the
-following.
+\niedit{While the first level ensures that the agents explore both arms, the better arm can only be discovered if the gap in their rewards $|\mu_1-\mu_2|$ is sufficiently high.
+When this gap is small (that is, when $|\mu_1 - \mu_2| < \tilde{O}(1/\sqrt{T_1})$), we argue that the second level will continue to explore both arms.
+Here we use the anti-concentration bound to show each arm is ``lucky'' in at least one first level group (that is, for some first level group, its empirical mean is significantly larger than its mean whereas the other arm's empirical mean is significantly smaller than its mean).
+Therefore, the corresponding second level group will explore the lucky arm, giving the third level refined estimates of each arm's mean.}  In the third level, agents will pull the best arm unless $|\mu_1-\mu_2|$ is much smaller than $\tilde{O}(1/\sqrt{T_2})$, in which case pulling either arm will
+incur small regret. The formal guarantee of the policy is the
+following. \nicomment{I'm a little confused why this works while simply growing the first level doesn't work; wouldn't the first level where the arm is ``lucky'' explore it more if it had more time?}
 

### 2018-10-28 llevel-overview.tex
llevel theorems

--- 2018-10-28 llevel-overview.tex
@@
 In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ to achieve better regret.
-Detailed proofs and discussions can be found in Section \ref{sec:llevel-details}.
+Detailed proofs and discussions can be found in Appendix \ref{sec:llevel-details}.
+
+%\jmcomment{Will change these statements a bit.}
+\begin{theorem}
+\label{thm:llevel-1}
+For any $L > 3$, we have an $L$-level recommendation policy with expected regret \\$O\left(T^{2^{L-1}/(2^L-1)} polylog(T) \right)$.
+In particular, we have an $O(\log\log(T))$-level recommendation policy with expected regret $O(T^{1/2} polylog(T))$.
+\end{theorem}
 
 \begin{theorem}
-\label{thm:llevel}
-The $L$-level recommendation policy gets expected regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(S^4))$.
-In particular, if we pick $L = \log(\ln(T)/\log(S^4))$, the expected regret is $O(T^{1/2} polylog(T))$.
+\label{thm:llevel-2}
+ We have an $O(\log(T)/\log\log(T))$-level recommendation policy with expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$.
+Here $\Delta$ is the difference between the largest mean and second largest mean of arms and the recommendation policy does not depend on $\Delta$.
+Moreover, agent in round $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$.
 \end{theorem}
 
-\begin{corollary}
-\label{cor:llevel}
-With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$.
-Here $\Delta = |\mu_1 -\mu_2|$ and the $L$-level recommendation policy does not need to know $\Delta$.
-Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$.
-\end{corollary}
+Now we give some overview of the additional techniques we use to get our $L$-level results.
+
+\xhdr{New connecting structures between levels.}
+
+\xhdr{Additional groups for boundary cases.}

### 2018-10-28 llevel-overview.tex
llevel

@@
 \label{sec:llevel}
-In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ to achieve better regret.
-Detailed proofs and discussions can be found in Appendix \ref{sec:llevel-details}.
-
-%\jmcomment{Will change these statements a bit.}
+In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ in order to achieve better regret.
+In Theorem \ref{thm:llevel-1}, we show our $L$-level policy.
+We can achieve nearly optimal regret $O(T^{1/2} polylog(T))$ with $O(\log\log(T))$ levels.
 \begin{theorem}
@@
 
+In Theorem \ref{thm:llevel-2}, we show a recommendation policy with instance-dependent regret guarantee.
+This policy has the same structure as the one in Theorem \ref{thm:llevel-1} but different parameters.
+Its expected regret depends on $\Delta$ which is the difference between the largest mean and second largest mean of arms.
+Its regret bound outperforms the one in Theorem \ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$.
+The only downside is that this policy requires more levels, i.e.
+$O(\log(T)/\log\log(T))$ levels.
+It also has the property that each agent observes a good fraction of history before its round.
+
 \begin{theorem}
@@
  We have an $O(\log(T)/\log\log(T))$-level recommendation policy with expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$.
-Here $\Delta$ is the difference between the largest mean and second largest mean of arms and the recommendation policy does not depend on $\Delta$.
+Here $\Delta$ is the difference between the largest mean and second largest mean of arms.
+The recommendation policy does not depend on $\Delta$.
 Moreover, agent in round $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$.
 \end{theorem}
+
+Detailed proofs and discussions of Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2} can be found in Appendix \ref{sec:llevel-details}.
+Similarly as Section \ref{sec:3level}, we first prove them in the case of 2 arms (Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel}).
+We then extend them to the case of constant number of arms (Theorem \ref{thm:constarm}).
 

### 2018-10-28 3level.tex
comments for 3level

--- 2018-10-28 3level.tex
@@
 simplicity, we will focus on the setting with 2 arms\niedit{, although our results can be extended to a constant number of arms $K$}.
-\nicomment{I think that's true, but if not, then we're not focusing on 2 arms for ``simplicity''.}
+\nicomment{I think that's true, but if not, then we're not focusing on 2 arms for ``simplicity''.} \jmcomment{It is true.
+We only show this extension for $l$-level tho.}
 
@@
 \nicomment{This comment applies to the 2level too; why not allow the guys within the last level see each other?
-Seems like this would still work but be more of a headache to prove -- would have to argue the empirical means can't move around too much in the sub-terminal levels, but it makes a big qualitative difference because now everyone sees a vanishingly small fraction of the history whereas with this modification a fraction approaching 1 of the people see a fraction approaching 1 of the history.}
+Seems like this would still work but be more of a headache to prove -- would have to argue the empirical means can't move around too much in the sub-terminal levels, but it makes a big qualitative difference because now everyone sees a vanishingly small fraction of the history whereas with this modification a fraction approaching 1 of the people see a fraction approaching 1 of the history.} \jmcomment{To do it for the last level is actually easy.
+It would be headache to do it for the second level as we want to prove anti-concentration in the second level.
+On the other hand, we have the property that agents see $1/polylog$ fraction of history in our final result for $l$-level.
+A different point of view is that, seeing each other requires more interaction, our policy has the nice property that the interaction is very minimal except the initial greedy runs.}
 

### 2018-10-28 llevel-overview.tex
comments for 3level

@@
 This policy has the same structure as the one in Theorem \ref{thm:llevel-1} but different parameters.
-Its expected regret depends on $\Delta$ which is the difference between the largest mean and second largest mean of arms.
+Its expected regret depends on $\Delta$ which is the difference between the largest mean and second largest mean of arms and its construction does not depend on $\Delta$.
 Its regret bound outperforms the one in Theorem \ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$.
@@
 $O(\log(T)/\log\log(T))$ levels.
-It also has the property that each agent observes a good fraction of history before its round.
+It also has the property that each agent observes a good fraction of history till its round.
 

### 2018-10-28 llevel-overview.tex

@@
 
-Now we give some overview of the additional techniques we use to get our $L$-level results.
+The main idea of extending from 3-level to $L$-level is that instead of using the second level as one ``check-point'', we use more levels to have multiple ``check points''.
+Some new challenges appear in this process.
+Here give an overview of the additional techniques we use to get our $L$-level results.
 
-\xhdr{New connecting structures between levels.}
+\xhdr{Connecting structures between levels.} In our 3-level policy, the second level has $S = \Theta(\log(T))$ groups.
+We do so to ensure that in the small gap case, with high probability, both arms are pulled enough times in the second level.
+The argument relies on the fact that agents in different second-level groups observe disjoint histories of the first level and the independent randomness in first level groups guarantee each arm $a$ to have a ``lucky'' second-level group such that agents in that group all pull arm $a$ with high probability.
+
+Simply generalizing this idea to an $L$-level policy would give us a $S$-ary tree like structure in the info graph.
+It incurs an extra $S^L$ factor in the expected regret.
+If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor would be $\Omega\left(\log(T)^{\log\log(T)}\right)$ which is super poly-logarithmic.
+If we use $\log(T)/\log\log(T)$ levels as in Theorem \ref{thm:llevel-2}, this factor goes up to polynomial in $T$.
+
+In order to avoid this undesirable factor, we design a slightly different connecting structure in our $L$-level policy.
+The key observation is that, for any level $l \in \{3,...,L-1\}$, we do want agents in different $l$-th level groups to see disjoint histories of the $(l-1)$-th level to ensure that there is some ``lucky'' group for each arm $a$ when arm $a$'s mean is close enough to the best arm.
+However, it does not matter much if these agents see the same history of levels below $l-1$ because group sizes in lower levels are much smaller than group sizes in higher levels and the independent randomness in level $l-1$ is sufficient.
 

### 2018-10-28 llevel.tex
llevel theorems

@@
 
-\section{$L$-level Recommendation Policy}
+\section{Missing Proofs of Section \ref{sec:llevel}}
 \label{sec:llevel-details}
@@
 \begin{theorem}
+\label{thm:constarm}
 Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel} can be extended to the case when $K$ is constant larger than 2.

### 2018-10-29 llevel.tex
llevel

@@
 \label{sec:llevel-details}
-In this section, we design an $L$-level recommendation policy for $L > 3$ and 2 arms. By having more than 3 levels, we get even smaller regret.
+In this section, we design our $L$-level recommendation policy for $L > 3$.
+Similarly as Section \ref{sec:3level}, we first prove them in the case of 2 arms (Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel}).
+We then extend them to the case of constant number of arms (Theorem \ref{thm:constarm}).
 
+Now we start with the case of 2 arms.
 Our recommendation policy has $L$ levels and two types of groups: $G$-groups and $\Gamma$-groups.
@@
 
+ \begin{comment}
 \begin{figure}[H]
@@
 \end{figure}
+\end{comment}
 

### 2018-10-29 llevel-overview.tex
update figures
llevel in intro

@@
 Some new challenges appear in this process.
-Here give an overview of the additional techniques we use to get our $L$-level results.
+Here we give an overview of the additional techniques we use to get our $L$-level results.
 
@@
 
-In order to avoid this undesirable factor, we design a slightly different connecting structure in our $L$-level policy.
+In order to avoid this undesirable factor, we design a slightly different connecting structure between levels in our $L$-level policy.
 The key observation is that, for any level $l \in \{3,...,L-1\}$, we do want agents in different $l$-th level groups to see disjoint histories of the $(l-1)$-th level to ensure that there is some ``lucky'' group for each arm $a$ when arm $a$'s mean is close enough to the best arm.
@@
 
+For each level, we will have $S^2$ groups for some $S = \Theta(\log(T))$.
+The groups in the $l$-th level is labeled as $G_{l,u,v}$ for $u,v\in[S]$.
+For any $l \in \{2,...,L\}$ and $u,v,w\in [S]$, agents in group $G_{l,u,v}$ sees the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$).
+See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level).
+This connecting structure has three nice properties: \\
+(i) The number of groups does not grow with the level and stays as $S^2 = \Theta(\log^2(T))$.  Having these groups only adds a $\Theta(\log^2(T))$ multiplicative factor to the expected regret.\\
+(ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,S,v}$ (e.g.
+$G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l$ and $v$.
+The agents in a set of groups see the same history.
+They get ``lucky'' for some arm at the same time.\\
+(iii) For each set of groups in level $l-1$, agents in the level $l$ see the history of agents in one of these groups.
+Therefore, we just need one set of groups in level $l-1$ to get ``lucky'' and then all agents in level $l$ will see enough pulls of arm $a$.
+
+\begin{figure}[H]
+\centering
+\begin{tikzpicture}  
+ \foreach \x in {0,3,6,9}
+ {
+ \filldraw[fill=purple!20!white]
+ (\x+0,7.5)--(\x+2,7.5)--(\x+2,8.5)--(\x+0,8.5)--cycle;
+ \filldraw[fill=green!20!white]
+ (\x+0,5)--(\x+2,5)--(\x+2,6)--(\x+0,6)--cycle;
+ \filldraw[fill=blue!20!white]
+ (\x+0,2.5)--(\x+2,2.5)--(\x+2,3.5)--(\x+0,3.5)--cycle;
+ }
+\foreach \y in {2.5,5,7.5}
+{
+  \node at (12.5,\y+0.5){$\cdots$};
+}
+
+\foreach \y in {3.5,6}
+{
+  \draw (1,\y) -- (1,\y+1.5);
+  \draw (1,\y) -- (7,\y+1.5);
+
+  \draw (4,\y) -- (1,\y+1.5);
+  \draw (4,\y) -- (7,\y+1.5);
+
+  \draw (7,\y) -- (4,\y+1.5);
+  \draw (7,\y) -- (10,\y+1.5);
+
+  \draw (10,\y) -- (4,\y+1.5);
+  \draw (10,\y) -- (10,\y+1.5);
+}
+
+\foreach \u in {1,2}
+{
+	\foreach \v in {1,2}
+	{
+	\pgfmathsetmacro{\x}{((\u-1)*2+(\v-1))*3};
+	\pgfmathsetmacro{\xa}{((\u-1))*3};
+	\pgfmathsetmacro{\xb}{(2+(\u-1))*3};
+   \node at(\x+1,8){$G_{l,\u,\v}$};
+   \node at(\x+1,5.5){$G_{l-1,\u,\v}$};
+   \node at(\x+1,3){$G_{l-2,\u,\v}$};
+	}
+}
+
+  \node at(-1.2,3){\textbf{Level $l-2$}};
+  \node at(-1.2,5.5){\textbf{Level $l-1$}};
+  \node at(-1.2,8){\textbf{Level $l$}};
+  \draw[->] (13.3,2)--(13.3,8.5);
+  \node at(13.7,5)[ rotate=90]{Time};
+
+ \draw [rounded corners=3mm, line width=1mm, red](-0.2,4.8)--(2.2,4.8)--(2.2,6.2)--(-0.2,6.2)--cycle;
+  \draw [rounded corners=3mm, line width=1mm, red](5.8,4.8)--(8.2,4.8)--(8.2,6.2)--(5.8,6.2)--cycle;
+\end{tikzpicture}
+\caption{Connectiing structures between levels for the $L$-level policy.}
+\label{fig:llevel-connecting}
+\end{figure}
 \xhdr{Additional groups for boundary cases.}

### 2018-10-29 llevel-overview.tex
llevel intro update

@@
 \xhdr{Connecting structures between levels.} In our 3-level policy, the second level has $S = \Theta(\log(T))$ groups.
-We do so to ensure that in the small gap case, with high probability, both arms are pulled enough times in the second level.
+We do so to ensure that in the small gap case (Lemma \ref{3levelsmallcase}), with high probability, both arms are pulled enough times in the second level.
 The argument relies on the fact that agents in different second-level groups observe disjoint histories of the first level and the independent randomness in first level groups guarantee each arm $a$ to have a ``lucky'' second-level group such that agents in that group all pull arm $a$ with high probability.
 
-Simply generalizing this idea to an $L$-level policy would give us a $S$-ary tree like structure in the info graph.
-It incurs an extra $S^L$ factor in the expected regret.
-If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor would be $\Omega\left(\log(T)^{\log\log(T)}\right)$ which is super poly-logarithmic.
+Simply generalizing this idea to an $L$-level policy would give us a $S$-ary tree like structure and the first level will have $S^{L-1}$ groups.
+It incurs an extra $S^{\Omega(L)}$ factor in the expected regret.
+If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor super poly-logarithmic.
 If we use $\log(T)/\log\log(T)$ levels as in Theorem \ref{thm:llevel-2}, this factor goes up to polynomial in $T$.
@@
 (ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,S,v}$ (e.g.
-$G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l$ and $v$.
+$G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l-1$ and $v$.
 The agents in a set of groups see the same history.
@@
 \end{figure}
-\xhdr{Additional groups for boundary cases.}
+\xhdr{Additional groups for boundary cases.} In our 3-level policy, recall the medium gap case (Lemma \ref{3levelmedium}) is the boundary case when the gap $|\mu_1-\mu_2|$ is $\Omega\left(\sqrt{\frac{1}{T_1}}\right)$ and $O\left(\sqrt{\frac{\log(T)}{T_1}}\right)$.
+In this case, the gap is not large enough to conclude that with high probability agents in both the second level and the third level all pull the best arm.
+The gap is also not small enough to conclude that with high probability both arms are explored enough times in the second level.
+
+In our $L$-level policy, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups and we call the original groups $G$-groups.

### 2018-10-29 llevel-overview.tex
llevel in intro

@@
 \end{figure}
-\xhdr{Additional groups for boundary cases.} In our 3-level policy, recall the medium gap case (Lemma \ref{3levelmedium}) is the boundary case when the gap $|\mu_1-\mu_2|$ is $\Omega\left(\sqrt{\frac{1}{T_1}}\right)$ and $O\left(\sqrt{\frac{\log(T)}{T_1}}\right)$.
+\xhdr{Additional groups for boundary cases.} Recall in our 3-level policy, the medium gap case (Lemma \ref{3levelmedium}) is the boundary case when the gap $|\mu_1-\mu_2|$ is $\Omega\left(\sqrt{\frac{1}{T_1}}\right)$ and $O\left(\sqrt{\frac{\log(T)}{T_1}}\right)$.
 In this case, the gap is not large enough to conclude that with high probability agents in both the second level and the third level all pull the best arm.
 The gap is also not small enough to conclude that with high probability both arms are explored enough times in the second level.
+We need to worry about the situation in which the sub-optimal arm does not get pulled enough times in the first two levels and some agents in the third level may pull the sub-optimal arm.
+Such situation is naturally ruled out in our 3-level policy for the following reason.
+Agents in the third level observe the history of the entire first level while agents in the second level only observes the history of a single first-level group.
+For each arm, even if it is not pulled at all in the second level, its empirical mean concentrates closer to its actual mean in the history observed by a third-level agent than the one observed by a second-level agent.
+Therefore, although the gap in the medium gap case is just not large enough for agents in the second level to all pull the best arm, it is large enough for agents in the third level to all pull the best arm.
 
-In our $L$-level policy, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups and we call the original groups $G$-groups.
+When we extend the 3-level policy to an $L$-level policy, we have such boundary case for each intermediate level.
+Moreover, the worry mentioned above does not get naturally resolved as in some of these boundary cases, the ratios between the upper and lower bounds of the gap rise from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$.
+The reason for such rise is that, except the first level, we don't have good enough guarantee of the number of pulls of each arm.
+For example, in Figure \ref{fig:llevel-connecting}, when we talk about having enough arm $a$ pulls in the history observed by agents in $G_{l,1,1}$, it could be that just only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it could also be that most agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,S}$ are pulling arm $a$.
+Therefore we only get a $S=\Theta(\log(T))$ multiplicative factor estimate of the number of arm $a$ pulls and this finally makes the boundary cases harder to deal with.
+
+In our $L$-level policy, after understanding the boundary cases well, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups.
+For each $l \in [L], u,v \in [S]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$.
+Agents in $\Gamma_{l,u,v}$ observe the same history as agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$.
+The history of $\Gamma$ groups in level $l$ is not sent to agents in level $l+1$ but higher levels.
+Consider the boundary case in which we can not say anything about the $l+1$ level agents' pulls.
+The new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm in this boundary case.

### 2018-10-30 llevel-overview.tex
Update llevel-overview.tex

@@
 We do so to ensure that in the small gap case (Lemma \ref{3levelsmallcase}), with high probability, both arms are pulled enough times in the second level.
-The argument relies on the fact that agents in different second-level groups observe disjoint histories of the first level and the independent randomness in first level groups guarantee each arm $a$ to have a ``lucky'' second-level group such that agents in that group all pull arm $a$ with high probability.
+The argument relies on the fact that agents in different second-level groups observe disjoint histories of the first level and the independent randomness in first level groups guarantees each arm $a$ to have a ``lucky'' second-level group such that agents in that group all pull arm $a$ with high probability.
 
@@
 In order to avoid this undesirable factor, we design a slightly different connecting structure between levels in our $L$-level policy.
-The key observation is that, for any level $l \in \{3,...,L-1\}$, we do want agents in different $l$-th level groups to see disjoint histories of the $(l-1)$-th level to ensure that there is some ``lucky'' group for each arm $a$ when arm $a$'s mean is close enough to the best arm.
-However, it does not matter much if these agents see the same history of levels below $l-1$ because group sizes in lower levels are much smaller than group sizes in higher levels and the independent randomness in level $l-1$ is sufficient.
+The key observation is that, for any level $l \in \{3,...,L-1\}$, we do want agents in different $l$-th level groups to see disjoint histories of the $(l-1)$-th level to ensure that there is some ``lucky'' group for each arm whose mean is close enough to the best arm.
+However, it does not matter much if pulls in levels below $l-1$ get observed by agents in different $l$-th level groups because group sizes in lower levels are much smaller than group sizes of level $l-1$ and the independent randomness in level $l-1$ is sufficient.
 
-For each level, we will have $S^2$ groups for some $S = \Theta(\log(T))$.
-The groups in the $l$-th level is labeled as $G_{l,u,v}$ for $u,v\in[S]$.
-For any $l \in \{2,...,L\}$ and $u,v,w\in [S]$, agents in group $G_{l,u,v}$ sees the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$).
+For each level, our $L$-level policy has $S^2$ groups for some $S = \Theta(\log(T))$.
+The groups in the $l$-th level are labeled as $G_{l,u,v}$ for $u,v\in[S]$.
+For any $l \in \{2,...,L\}$ and $u,v,w\in [S]$, agents in group $G_{l,u,v}$ see the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$).
 See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level).
 This connecting structure has three nice properties: \\
-(i) The number of groups does not grow with the level and stays as $S^2 = \Theta(\log^2(T))$.  Having these groups only adds a $\Theta(\log^2(T))$ multiplicative factor to the expected regret.\\
+(i) The number of groups does not grow with $L$ and stays as $S^2 = \Theta(\log^2(T))$ in each level.
+Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the expected regret.\\
 (ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,S,v}$ (e.g.
@@
 They get ``lucky'' for some arm at the same time.\\
-(iii) For each set of groups in level $l-1$, agents in the level $l$ see the history of agents in one of these groups.
-Therefore, we just need one set of groups in level $l-1$ to get ``lucky'' and then all agents in level $l$ will see enough pulls of arm $a$.
+(iii) For each set of groups in level $l-1$, agents in level $l$ see the history of agents in one of these groups.
+Therefore, for each arm $a$, we just need one set of groups in level $l-1$ to get ``lucky'' and then all agents in level $l$ will see enough pulls of arm $a$.
 
@@
 Agents in the third level observe the history of the entire first level while agents in the second level only observes the history of a single first-level group.
-For each arm, even if it is not pulled at all in the second level, its empirical mean concentrates closer to its actual mean in the history observed by a third-level agent than the one observed by a second-level agent.
+For each arm, even if it is not explored enough times in the second level, its empirical mean concentrates closer to its actual mean in the history observed by a third-level agent than the one observed by a second-level agent.
 Therefore, although the gap in the medium gap case is just not large enough for agents in the second level to all pull the best arm, it is large enough for agents in the third level to all pull the best arm.
@@
 The reason for such rise is that, except the first level, we don't have good enough guarantee of the number of pulls of each arm.
-For example, in Figure \ref{fig:llevel-connecting}, when we talk about having enough arm $a$ pulls in the history observed by agents in $G_{l,1,1}$, it could be that just only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it could also be that most agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,S}$ are pulling arm $a$.
-Therefore we only get a $S=\Theta(\log(T))$ multiplicative factor estimate of the number of arm $a$ pulls and this finally makes the boundary cases harder to deal with.
+For example, in Figure \ref{fig:llevel-connecting}, when we talk about having enough arm $a$ pulls in the history observed by agents in $G_{l,1,1}$, it could be that  only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,S}$ are pulling arm $a$.
+Therefore our estimate of the number of arm $a$ pulls can be off by an $S=\Theta(\log(T))$ multiplicative factor.
+This finally makes the boundary cases harder to deal with.
 
@@
 For each $l \in [L], u,v \in [S]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$.
-Agents in $\Gamma_{l,u,v}$ observe the same history as agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$.
-The history of $\Gamma$ groups in level $l$ is not sent to agents in level $l+1$ but higher levels.
-Consider the boundary case in which we can not say anything about the $l+1$ level agents' pulls.
-The new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm in this boundary case.
+Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$.
+The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$ groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels.
+When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm.

### 2018-10-31 model.tex
Rewrote the model section.

@@
 %!TEX root = main.tex
-\section{Model}
+\section{Model and Preliminaries}
 \label{sec:model}
 
-We study the mult-armed bandit problem in a social learning context, in which a principal faces a sequence of $T$ myopic agents.
-There is a set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is distributed according to the Bernoulli distribution $\cD_a$ with an unknown mean $\mu_a$.
+\newcommand{\SubH}[1]{H_{#1}} % subhistory
+\newcommand{\AnonSubH}[1]{H^{\texttt{anon}}_{#1}} % subhistory
+
+We study the multi-armed bandit problem in a social learning context, in which a principal faces a sequence of $T$ myopic agents.
+There is a set $\A$ of $K$ possible actions, a.k.a.
+\emph{arms}.
 At each round $t\in [T]$, a new agent $t$ arrives, receives a message $m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a reward $r_t\in \{0,1\}$ that is immediately observed by the principal.
-Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by the agents, the \emph{regret} is defined as
+The reward from pulling an arm $a\in \A$ is drawn independently from Bernoulli distribution $\cD_a$ with an unknown mean $\mu_a$.
+An agent does not observe anything from the previous rounds, other than the message $m_t$.
+The problem instance is defined by (known) parameters $K,T$ and the (unknown) tuple of mean rewards, $(\mu_a:\,a\in\A)$.
+We are interested in \emph{regret}, defined as
+\[\textstyle 
+  \reg(T)
+  %= \reg(a_1, \ldots , a_T) 
+  = T \max_{a\in \A} \mu_a -
+  \sum_{t\in [T]} \E[\mu_{a_t}].
+\]
+The principal chooses messages $m_t$ according to an online algorithm called \emph{disclosure policy}, with a goal to minimize regret.
+We assume that mean rewards are bounded away from $0$ and $1$, to ensure sufficient entropy in rewards.
+For concreteness, we posit that
+    $\mu_a\in [\tfrac13,\tfrac23]$.
+
+\xhdr{Unbiased subhistories.}  
+The \emph{subhistory} for a subset of rounds $S\subset [T]$, and the corresponding \emph{anonymized subhistory} are defined, respectively, as
+\[ \SubH{S} = \{\; (s,a_s,r_s):\;s\in S \;\}
+\quad\text{and}\quad
+   \AnonSubH{S} = \{\; (a_s,r_s):\;s\in S \}.
+\]
+Accordingly, $\SubH{[t-1]}$ is called the \emph{full history} at time $t$.
+
+We focus on disclosure policies of a particular form, where the message in each round $t$ is $m_t = \SubH{S_t}$ for some subset $S_t\subset [t-1]$.
+We assume that the subset $S_t$ is chosen ahead of time, before round $1$ (and therefore does not depend on the observations $\SubH{t-1}$).
+Such message is called \emph{unbiased subhistory}, and the resulting disclosure policy is called an \emph{unbiased-history policy}.
+
+Further, we assume that disclosure policies are \emph{transitive}, in the following sense:
+\[ t'\in S_t \Rightarrow S_{t'}\subset S_t
+    \qquad \text{for all rounds $t,t'\in [T]$}. \]
+In words, if agent observes the subhistory for some previous agent, then she observes the entire message for that agent.
+
+A transitive unbiased-history policy $\pi$ can be represented as an undirected graph $G_\pi$, where nodes correspond to rounds, and any two rounds $t'<t$ are connected if and only if $t'\in S_t$ and there is no intermediate round $t''$ with
+    $t'\in S_{t''}$ and $t''\in S_t$.
+This graph is henceforth called the \emph{information flow graph} of policy $\pi$, or \emph{info-graph} for short.
+
+\xhdr{Agents' behavior.} Let us define agents' behavior in response to an unbiased-history policy.
+We posit that each agent $t$ uses its observed subhistory $m_t$ to form a reward estimate $\hat{\mu}_{t,a} \in [0,1]$ for each arm $a\in \A$, and chooses an arm with a maximal estimator.
+(Ties are broken according to an arbitrary rule that is the same for all agents.)
+We make some mild assumptions:
+
+%If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.
+
+\begin{assumption}\label{ass:embehave}
+Reward estimates satisfy the following assumptions:
+\begin{itemize}
+\item[(a)] Reward estimates are close to empirical averages.
+Let $N_{t,a}$ and $\bar{\mu}_{t,a}$ denote the number of pulls and the empirical mean reward of arm $a$ in subhistory $m_t$.
+Then for some absolute constant $N_0\in \N$ and $C_0=\tfrac{1}{16}$ it holds that
 \[
-  \reg(T)= \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a -
-  \sum_{t=1}^T \mu_{a_t}.
+\forall t\in[T],\, a\in\A \qquad
+N_{t,a} \geq N_0 \quad\Rightarrow\quad
+    \left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
+		\frac{C_0}{\sqrt{N_{t,a}}},
+\]
+\item[(b)] Reward estimates have a warm-start property:
+\[
+\forall t\in[T],\, a\in\A \qquad
+N_{t,a} =0 \quad\Rightarrow\quad
+    \hat{\mu}^t_a \geq \tfrac13.
 \]
 
-\xhdr{Unbiased sub-history policy.} The principal's goal is to reveal a sequence of messages according to a disclosure policy so that the regret of the induced sequence of actions is minimized.
-We will focus on \emph{unbiased sub-history policies} that at each round $t$ reveal the \emph{sub-history} $H_t = \{(s, a_s, r_s)\mid s \in S_t\}$, such that each $S_t\subseteq [t-1]$ is a subset of previous rounds \emph{fixed ahead of time}.
-A simple example is the policy that reveals the \emph{full history} with $S_t = [t-1]$.
-All of the policies we develop are \emph{transitive}: for any two agents $t$ and $t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains that of $S_{t'}$.
+\item[(c)] Reward estimates $\hat{\mu}_a^t$ depend only on the anonymized subhistory $\AnonSubH{S_t}$.
+That is, reward estimates depend only on the observations, not on the rounds in which these observations are collected.
 
-\xhdr{Information flow graph.} We will describe our transitive policies using a \emph{information flow graph} (and henceforth \emph{information graph})---a directed graph over the $T$ agents such that if there is an edge from $u$ to $v$, it means $u\in S_v$.
-By the property of transitivity, $S_t$ is the set of nodes that can reach node $t$ in the info graph.
-\niedit{For example, an information graph for the policy that reveals the full history is the directed line graph containing edges $(t,t+1)$ for all $t\in[T-1]$.}
-
-\iffalse
-\begin{itemize}
-\item \textbf{Full history:} We show each agent the history of all previous agents' pulls. We call this policy \ALGG. 
-\item \textbf{Unbiased sub-history:} We show each agent only a subset of history. The subsets are pre-determined before any arms are pulled.  
-\item \textbf{Info graph:} All the recommendation policies in this paper can be described by an undirected transitive graph with $T$ nodes.
-We call it the info graph.
-The $T$ nodes in the graph represent the $T$ agents.
-If there is an edge between node $u$ and $v$ for $u < v$, it means the history of agent $u$ is shown to agent $v$.
-\end{itemize}
-\fi
-
-\begin{remark}
-  Why not arbitrary sub-history? \swcomment{important point to make;
-    but should be in the introduction}
-\end{remark}
-
-\xhdr{Agents' behavior.} \nicomment{re-ordered this.} An {\em agent estimator} is a function that maps the revealed sub-history $H_t$ to a mean reward estimate $\hat{\mu}_a^t$ for every arm $a$.
-For any $t\in[T]$ and $a\in \A$, we write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls of $a$ and the empirical mean reward of arm $a$ in sub-history $H_t$ respectively.
-If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.
-We require the following assumptions.
-
-\begin{assumption}
-	\label{ass:embehave}
-	The set of mean rewards $\{\mu_a\}$, the estimates $\hat \mu_a^t$, and the empirical mean rewards $\bar\mu_a^t$  satisfy:
-
-	\begin{itemize}
-		\item The mean reward $\mu_a$ for each arm $a\in \A$ lies in the range
-		of $[1/3, 2/3]$.
-
-		\item Let $c_m = 1/16$.\swcomment{maybe use a better notation} \nicomment{yeah, why the subscript $m$?
-and $T$ below?
-how about just $\alpha,\beta$ for the constants in this assumption?
-or $\alpha$ and $N_0$?
-or use $n_{t,a}$ for number of pulls and $N$ for a constant that you want the $n_{t,a}$ to exceed?}
-		% \jmcomment{It means a constant for some assumptions about means but nothing else. Just want to make it different from other constants. Maybe there are better notations.}. 
-		There exists a constant $c_T$ such that for any agent $t$ and
-		arm $a$, as long as \niedit{$N_{t,a} \geq c_T$}, 
-		\[
-		\left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
-		\frac{c_m}{\sqrt{N_{t,a}}}.
-		\]
-		\item If $N_{t,a} = 0$, the initial estimate
-		$\hat{\mu}^t_a$ is at least $1/3$.
+\item[(c)] Reward estimates are consistent over time, but allow some agent heterogeneity.
+Formally, each agent $t$ forms its estimates according to a \emph{reward estimate function}: a function $f_t$ from anonymous subhistories to $[0,1]^K$, so that the estimate vector
+        $(\hat{\mu}_{t,a}:\, a\in\A)$
+    equals $f_t(\AnonSubH{S_t})$. And this function is drawn independently from some fixed distribution over reward estimate functions.
 \end{itemize}
@@
 
+\OMIT{ %%%%%%%%%%
 The first assumption ensures that the reward distributions have sufficient entropy to induce natural exploration.
@@
 \end{remark}
+} %%%%%%%
 
-Given any bandit instance, we define the \emph{gap parameter} $\Delta$ as the difference between the largest and second largest mean rewards.
-In general, the gap parameter is unknown to the principal (or the algorithm), but we show how to obtain different forms of regret bounds if $\Delta$ is known.
+\xhdr{Connection to multi-armed bandits.}
+The special case when each message $m_t$ is an arm, and the $t$-th agent always chooses this arm, corresponds to a standard multi-armed bandit problem with IID rewards.
+Following the literature on bandits, we define the \emph{gap parameter} $\Delta$ as the difference between the largest and second largest mean rewards.%
+\footnote{Formally, the second-largest mean reward is 
+    $\max_{a\in\A:\mu(a)<\mu^*} \mu(a)$,
+where $\mu^* = \max_{a\in\A} \mu(a)$.
+}
+The gap parameter is not known to the principal (in our problem), or to the algorithm (in the bandit problem). However, it is essential for regret bounds.
+
+\ascomment{We'll need to state/discuss optimal regret bounds somewhere, probably here.}
 

### 2018-10-31 2level.tex
update figures
remove "randomness" in the policy description, our info graph is deterministic and public knowledge

@@
   exploration by simulating $T_1$ independent runs of \ALGG of $\GdT$
-  rounds. This is done by randomly dividing the first $T_1 \cdot \GdT$
+  rounds. This is done by dividing the first $T_1 \cdot \GdT$
   agents into $T_1$ groups of equal size and allowing each agent to only observe
@@
   (0,0)--(1,0)--(1,1)--(0,1)--cycle;
-  \draw[dashed] (0.5,1)--(5,2);
+  \draw (0.5,1)--(5,2);
   \filldraw[fill=red!20!white]
   (1,0)--(2,0)--(2,1)--(1,1)--cycle;
-  \draw[dashed] (1.5,1)--(5,2);
+  \draw (1.5,1)--(5,2);
   \filldraw[fill=red!20!white]
   (2,0)--(3,0)--(3,1)--(2,1)--cycle;
-  \draw[dashed] (2.5,1)--(5,2);
+  \draw(2.5,1)--(5,2);
   \filldraw[fill=red!20!white]
   (3,0)--(4,0)--(4,1)--(3,1)--cycle;
-  \draw[dashed] (3.5,1)--(5,2);
+  \draw(3.5,1)--(5,2);
   \filldraw[fill=red!20!white]
   (9,0)--(10,0)--(10,1)--(9,1)--cycle;
-  \draw[dashed] (9.5,1)--(5,2);
+  \draw(9.5,1)--(5,2);
   \node at(5,0.5){$\cdots$};

### 2018-10-31 model.tex
Another revision of prelims.

@@
 We are interested in \emph{regret}, defined as
-\[\textstyle 
+\begin{align}
+\textstyle
   \reg(T)
@@
   \sum_{t\in [T]} \E[\mu_{a_t}].
-\]
+\end{align}
 The principal chooses messages $m_t$ according to an online algorithm called \emph{disclosure policy}, with a goal to minimize regret.
@@
 \xhdr{Unbiased subhistories.}
-The \emph{subhistory} for a subset of rounds $S\subset [T]$, and the corresponding \emph{anonymized subhistory} are defined, respectively, as
-\[ \SubH{S} = \{\; (s,a_s,r_s):\;s\in S \;\}
-\quad\text{and}\quad
-   \AnonSubH{S} = \{\; (a_s,r_s):\;s\in S \}.
-\]
+The \emph{subhistory} for a subset of rounds $S\subset [T]$ is defined as 
+\begin{align} \label{eq:model-subhistory}
+    \SubH{S} = \left\{\; (s,a_s,r_s):\;s\in S \;\right\}.
+\end{align}
 Accordingly, $\SubH{[t-1]}$ is called the \emph{full history} at time $t$. 
+The \emph{outcome} for agent $t$ is the tuple $(t,a_t,r_t)$.
 
@@
 
-Further, we assume that disclosure policies are \emph{transitive}, in the following sense:
+Further, we focus on disclosure policies that are \emph{transitive}, in the following sense:
 \[ t'\in S_t \Rightarrow S_{t'}\subset S_t
     \qquad \text{for all rounds $t,t'\in [T]$}. \]
-In words, if agent observes the subhistory for some previous agent, then she observes the entire message for that agent.
+In words, if an agent observes the outcome for some previous agent, then she observes the entire message revealed to that agent.
 
-A transitive unbiased-history policy $\pi$ can be represented as an undirected graph $G_\pi$, where nodes correspond to rounds, and any two rounds $t'<t$ are connected if and only if $t'\in S_t$ and there is no intermediate round $t''$ with
+A transitive unbiased-history policy can be represented as an undirected graph, where nodes correspond to rounds, and any two rounds $t'<t$ are connected if and only if $t'\in S_t$ and there is no intermediate round $t''$ with
     $t'\in S_{t''}$ and $t''\in S_t$.
-This graph is henceforth called the \emph{information flow graph} of policy $\pi$, or \emph{info-graph} for short.
+This graph is henceforth called the \emph{information flow graph} of policy $\pi$, or \emph{info-graph} for short. We assume that it is common knowledge.
 
@@
 We posit that each agent $t$ uses its observed subhistory $m_t$ to form a reward estimate $\hat{\mu}_{t,a} \in [0,1]$ for each arm $a\in \A$, and chooses an arm with a maximal estimator.
-(Ties are broken according to an arbitrary rule that is the same for all agents.)
-We make some mild assumptions:
+(Ties are broken according to an arbitrary rule that is the same for all agents.) The basic model is that $\hat{\mu}_{t,a}$ is the sample average for arm $a$ over the subhistory $m_t$, as long as it includes at least one sample for $a$; else, $\hat{\mu}_{t,a}\geq \tfrac13$.
+
+We allow a much more permissive model, characterized by the following assumption:
 
@@
 \begin{assumption}\label{ass:embehave}
-Reward estimates satisfy the following assumptions:
-\begin{itemize}
-\item[(a)] Reward estimates are close to empirical averages.
+Reward estimates are close to empirical averages.
 Let $N_{t,a}$ and $\bar{\mu}_{t,a}$ denote the number of pulls and the empirical mean reward of arm $a$ in subhistory $m_t$.
-Then for some absolute constant $N_0\in \N$ and $C_0=\tfrac{1}{16}$ it holds that
+Then for some absolute constant $N_0\in \N$ and $C_0=\tfrac{1}{16}$, and for all agents $t\in [T]$ and arms $a\in\A$ it holds that
 \[
-\forall t\in[T],\, a\in\A \qquad
-N_{t,a} \geq N_0 \quad\Rightarrow\quad
+\text{if}\; N_{t,a} \geq N_0 
+\quad\text{then}\quad
     \left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
-		\frac{C_0}{\sqrt{N_{t,a}}},
+		\frac{C_0}{\sqrt{N_{t,a}}}.
 \]
-\item[(b)] Reward estimates have a warm-start property:
-\[
-\forall t\in[T],\, a\in\A \qquad
-N_{t,a} =0 \quad\Rightarrow\quad
-    \hat{\mu}^t_a \geq \tfrac13.
-\]
+Also, 
+    $\hat{\mu}^t_a\geq\tfrac13$ if $N_{t,a}=0$.
+(NB: we make no assumption if $1\leq N_{t,a}<N_0$.)
+\end{assumption}
 
-\item[(c)] Reward estimates $\hat{\mu}_a^t$ depend only on the anonymized subhistory $\AnonSubH{S_t}$.
-That is, reward estimates depend only on the observations, not on the rounds in which these observations are collected.
-
-\item[(c)] Reward estimates are consistent over time, but allow some agent heterogeneity.
-Formally, each agent $t$ forms its estimates according to a \emph{reward estimate function}: a function $f_t$ from anonymous subhistories to $[0,1]^K$, so that the estimate vector
+\OMIT{ %%%%%%%%
+\begin{assumption}
+Reward estimates are consistent over time, but allow some agent heterogeneity.
+Formally, each agent $t$ forms its estimates according to a \emph{reward estimate function}: a function $f_t$ from subhistories to $[0,1]^K$, so that the estimate vector
         $(\hat{\mu}_{t,a}:\, a\in\A)$
-    equals $f_t(\AnonSubH{S_t})$. And this function is drawn independently from some fixed distribution over reward estimate functions.
-\end{itemize}
+    equals $f_t(m_t)$. This function is drawn independently from some fixed distribution over reward estimate functions.
 \end{assumption}
+} %%%%%%%
 
@@
 The special case when each message $m_t$ is an arm, and the $t$-th agent always chooses this arm, corresponds to a standard multi-armed bandit problem with IID rewards.
+Thus, regret in our problem can be directly compared to regret in the bandit problem with the same mean rewards $(\mu_a:\,a\in\A)$.
 Following the literature on bandits, we define the \emph{gap parameter} $\Delta$ as the difference between the largest and second largest mean rewards.%
@@
 }
-The gap parameter is not known to the principal (in our problem), or to the algorithm (in the bandit problem). However, it is essential for regret bounds.
+The gap parameter is not known to the principal (in our problem), or to the algorithm (in the bandit problem).
+Optimal regret rates for bandits with IID rewards are as follows \cite{bandits-ucb1,bandits-exp3,Lai-Robbins-85}:
+\begin{align}\label{eq:model-OptRegret}
+\reg(T) \leq O\left(\min\left( 
+    \sqrt{KT\log T)},\; \tfrac{1}{\Delta} \log T
+    \right)\right).
+\end{align}
+This regret bound can only be achieved using \emph{adaptive exploration}: \ie when exploration schedule is adapted to the observations.
+A simple example of \emph{non}-adaptive exploration is the \emph{explore-then-exploit} algorithm which samples arms uniformly at random for the first $N$ rounds, for some pre-set number $N$, then chooses one arm and sticks with it till the end.
+More generally,
+\emph{exploration-separating} algorithms have a property that in each round $t$, either the choice of an arm does not depend on the observations so far, or the reward collected in this round is not used in the subsequent rounds.
+Any such algorithm suffers from $\Omega(T^{2/3})$ regret in the worst case.%
+\footnote{The first explicit reference we are aware of is \cite{MechMAB-ec09,DevanurK09}, but this fact has been known in the community for much longer.}
 
-\ascomment{We'll need to state/discuss optimal regret bounds somewhere, probably here.}
+\xhdr{Preliminaries.}
+Throughout the paper, we will use the standard concentration and anti-concentration inequalities: respectively, Chernoff Bounds and Berry-Esseen Theorem.
+The former states that that a sum of independent random variables converges to its expectation quickly.
+The latter states that the CDF of an appropriately scaled average of IID random variables converges to the CDF of the standard normal distribution pointwise.
+In particular, the average strays far enough from its expectation with some guaranteed probability.
+The theorem statements are moved to Appendix~\ref{sec:prelim}.
 

### 2018-10-31 prelim.tex
Moved concentration and anti-concentration theorem statements to appendix.

--- 2018-08-30 prelim.tex
@@
 %!TEX root = main.tex
-\section{Preliminaries}
+\section{Tools from Probability: concentration and anti-concentration}
 \label{sec:prelim}
 
-\begin{theorem}[Chernoff Bound]
+We use standard tools for concentration and anti-concentration, stated below.
+
+\begin{theorem}[Chernoff Bounds]\label{thm:prelims-chernoff}
 Let $X_1,...,X_n$  be independent random variables such that $X_i \in [0,1]$ for all $i$. Let $\bar{X} = \frac{1}{n}\sum_{i=1}^n X_i$ denote their empirical mean. Then
@@
 
-\begin{theorem}[Berry-Essen Theorem]
+\begin{theorem}[Berry-Esseen Theorem]\label{thm:prelims-Berry}
 Let $X_1,...,X_n$ be i.i.d.

### 2018-10-31 2level.tex
Moved Greedy into Warmup, and started revising.

@@
 %!TEX root = main.tex
-\section{Warm-up:  2-Level Explore-then-Exploit Policy}
+\section{Warm-up: Explore-then-Exploit Policy}
+
+We first consider the simplest disclosure policy which reveals the full history in each round $t$, \ie $m_t=\SubH{t-1}$; we call it the \emph{full-disclosure policy}.
+The info-path for this policy is a simple path.
+We use this policy as a ``gadget" in our constructions.
+Hence, we formulate it slightly more generally:
+
+\begin{definition}
+A subset of rounds $S\subset [T]$ is called a \emph{full-disclosure path} in info-graph $G$ if the induced subgraph $G_S$ is a simple path, and it connects to the rest of the graph only through the terminal node $\max(S)$, if at all.
+\end{definition}
+
+We prove that with constant probability, a full-disclosure path of constant length samples each arm at least once (and we will build on this fact throughout).
+
+\ascomment{stopped here.}
+
+\begin{lemma}
+\label{lem:greedy}
+Under Assumption \ref{ass:embehave}, there exist two constants $\GdT = O_K(1)$
+and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability
+at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least
+once.\footnote{The notations $O_k$ and $\Omega_K$ hide the dependence
+  on the number of arms $K$.} \nicomment{If we change the name of the policy, we might also want to change the subscripts of these constants.}
+\end{lemma}
+
+\begin{proof}
+  Fix any arm $a$. Let $\GdT = (K-1) \cdot c_T + 1$ and
+  $\GdP = (1/3)^{\GdT}$. \swedit{We will condition on the event that
+    all the realized rewards in $\GdT$ rounds are 0, which occurs with
+    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.}
+  In this case, we want to show that arm $a$ is pulled at least
+  once. We prove this by contradiction. Suppose arm $a$ is not pulled. By
+  the pigeonhole principle, we know that there is some other arm $a'$
+  that is pulled at least $c_T + 1$ rounds. Let $t$ be the round in
+  which arm $a'$ is pulled exactly $c_T + 1$ times. By Assumption
+  \ref{ass:embehave}, we know
+  \[
+    \hat{\mu}_{a'}^t \leq 0 + c_m / \sqrt{c_T} < 1/3.
+  \]
+  \nicomment{Wait, where did we set $c_T$?} On the other hand, we have
+  $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
+  the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
+  \swdelete{ In addition, we know that this case happens with
+    probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is
+    at most $2/3$. To sum up, we know that with probability at least
+    $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.}
+   \jmcomment{Agree with these changes.}
+\end{proof}
+
+\swedit{In our policies presented in the next sections, we will use
+  \ALGG of $T_G$ rounds as a subroutine for initial exploration. For
+  any $a$, let $q_a$ \nicomment{$q$ sounds like a fraction; maybe $n^G_a$ or $N^G_a$} be the expected number of arm $a$ pulls in one
+  run of \ALGG of $T_G$ rounds.} \nicomment{\ALGG of $T_G$ rounds is a mouthful; what about using notation like \ALGG($T_G$)?
+or if we will always use $T_G$ rounds, then just define the policy to be that from now on?}
+
 \swedit{Now we provide a simple policy that can incentivize the agents

### 2018-11-01 model.tex
Moved Greedy into Warmup, and started revising.
Moved a macro to the main file.

@@
 \label{sec:model}
-
-\newcommand{\SubH}[1]{H_{#1}} % subhistory
-\newcommand{\AnonSubH}[1]{H^{\texttt{anon}}_{#1}} % subhistory
 
@@
 
-We allow a much more permissive model, characterized by the following assumption:
+We allow a much more permissive model, characterized by the following assumption:%
+\footnote{In what follows, we make this assumption without further notice.}
 
@@
 
+We use $O_K(\cdot)$ notation to hide the dependence on parameter $K$, and $\tilde O(\cdot)$ notation to hide polylogarithmic factors. We denote $[T]= \{1,2 \LDOTS T\}$.
+
 %%% Local Variables:

### 2018-11-01 2level.tex
Rewrote the 2level/warmup section.

--- 2018-10-31 2level.tex
@@
 %!TEX root = main.tex
-\section{Warm-up:  2-Level Explore-then-Exploit Policy}
-\swedit{Now we provide a simple policy that can incentivize the agents
-  to perform non-adaptive exploration and achieve a regret rate of
-  $\tilde O(T^{2/3})$. The policy essentially follows the
-  ``explore-then-exploit'' paradigm and consists of two phases, which can
-  be described as a two-level information graph (as shown in
-  Figure~\ref{fig:2level}).  In the first level, we perform
-  exploration by simulating $T_1$ independent runs of \ALGG of $\GdT$
-  rounds. This is done by dividing the first $T_1 \cdot \GdT$
-  agents into $T_1$ groups of equal size and allowing each agent to only observe
-  the history of all previous agents in the same group.  In the second
-  level, we ``exploit'' by showing all the remaining agents the entire
-  history of first phase.
+\section{Warm-up: full-disclosure paths}
 
-  The key idea behind the policy is that the first level effectively
-  boosts the exploration probability of \ALGG. Since each run of
-  \ALGG explores all arms with constant probability (Lemma
-  \ref{lem:greedy}), by simulating multiple runs of \ALGG, we can
-  ensure that with high probability, every arm is pulled a
-  sufficient number of times. The below lemma follows from
-  concentration bounds.
+We first consider a disclosure policy that reveals the full history in each round $t$, \ie $m_t=\SubH{t-1}$; we call it the \emph{full-disclosure policy}.
+The info-path for this policy is a simple path.
+We use this policy as a ``gadget" in our constructions.
+Hence, we formulate it slightly more generally:
 
-} \nicomment{there was a proof of this once; i remember checking it. if it still exists, let's throw it in an appendix.}
+\begin{definition}
+A subset of rounds $S\subset [T]$ is called a \emph{full-disclosure path} in the  info-graph $G$ if the induced subgraph $G_S$ is a simple path, and it connects to the rest of the graph only through the terminal node $\max(S)$, if at all.
+\end{definition}
 
-\begin{lemma}[Concentration of arm pulls]\label{lem:t1runs}
-  Consider $T_1$ indepdent runs of \ALGG of $T_G$ rounds. Let $N_a$ be
-  the number of arm $a$ pulls among all runs. Then with probability at
-  least $1-\delta$, for all $a\in \A$,
-  \[
-    \left| N_a - q_a T_1\right| \leq T_G \sqrt{T_1 \log(2K/\delta) / 2}
-  \]
+We prove that for a constant number of arms, with constant probability, a full-disclosure path of constant length suffices to sample each arm at least once. We will build on this fact throughout.
+
+\begin{lemma}\label{lem:greedy}
+There exist numbers $\GdT>0$ and $\GdP>0$ that depend only on $K$, the number of arms, with the following property.
+Consider an arbitrary disclosure policy, and let $S\subset [T]$ be a full-disclosure path in its info-graph, of length $|S|\geq \GdT$.
+Under Assumption \ref{ass:embehave}, with probability at least $\GdP$, subhistory $\SubH{S}$ contains at least once sample of each arm $a$.
 \end{lemma}
 
-\iffalse
-The 2-level recommendation policy is constructed as following.
-In the first level, we run $T_1$ \ALGG of $\GdT$ rounds ``in parallel''.
-More specifically, we divide the first $T_1 \cdot \GdT$ agents into $T_1$ groups of equal size and agents only observe the history of all previous agents in the same group.
-In the second level, we show the rest $T-T_1\cdot \GdT$ agents the history of first $T_1 \cdot \GdT$ rounds. We will pick $T_1$ in Theorem \ref{thm:2level}. 
-See also Figure \ref{fig:2level} for a graphical view of the information flow.
+\begin{proof}[Proof Sketch]
+\end{proof}
 
-The idea of this 2-level recommendation policy is simple.
-We first try to explore all arms enough amount of times in the first level using multiple runs of \ALGG under the guarantee of Lemma \ref{lem:greedy}.
-After that, by concentration argument, we can show that while observing the history of the first level, agents in the second level pick an arm with mean close to the best arm's mean.
-\fi
+\ascomment{Where do we need to introduce the expected \#pulls in full-disclosure path?}
+
+We provide a simple disclosure policy based on full-disclosure paths.
+The policy follows the ``explore-then-exploit'' paradigm.
+The ``exploration phase" comprises the first $N = T_1\cdot \GdT$ rounds, and consists of $T_1$ full-disclosure paths of length $\GdT$ each.
+Here $\GdT$ is the constant from Lemma~\ref{lem:greedy}, and $T_1$ is a parameter.
+In the ``exploitation phase", each agent $t>N$ receives the full subhistory from exploration, \ie $m_t = \SubH{[N]}$.
+The info-graph for this disclosure policy is shown in Figure~\ref{fig:2level}.
 
@@
   \node at(8,0.5){$\cdots$};
-  \node at(5,2.5){$T -T_1 \cdot \GdT$};
+  \node at(5,2.5){$T -T_1 \cdot \GdT$ rounds};
   \node at(0.5,0.5){$\GdT$};
@@
 
-  \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (10,-0.2) -- (0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ runs of \ALGG in parallel};
+  \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (10,-0.2) -- (0,-0.2) node [black,midway,yshift=-0.6cm] 
+  {$T_1$ full-disclosure paths of length $\GdT$ each};
 \end{tikzpicture}
 
-\caption{Structure of information graph for the 2-level policy. Each
-  red ``box'' in level 1 corresponds to a path connecting a set of
-  $T_G$ agents. The entire history in level 1 is then aggregated and
-  shown to each agent in level 2.}
+\caption{Info-graph for the 2-level policy. }
+%Each red box in level 1 corresponds to a path connecting a set of
+%  $T_G$ agents. The entire history in level 1 is then aggregated and
+%  shown to each agent in level 2.}
 \label{fig:2level}
@@
 
-\swedit{As a result, every agent in the second level will pull an arm
-  with mean reward close to the optimal, which gives us the following
-  regret guarantee.}
+It is useful to think of the info-graph as having two levels (corresponding to exploration and exploitation).
+Accordingly, we call this policy the \emph{2-level policy}.
+We show that it incentivizes the agents to perform non-adaptive exploration, and achieves a regret rate of  $\tilde O_K(T^{2/3})$.
+The key idea is that using many full-disclosure paths ``in parallel" ensures that sufficiently many samples of each arm are collected during exploration.
 
-\begin{theorem}
-\label{thm:2level}
-By setting $T_1 = T^{2/3}\log(T)^{1/3}$, the 2-level policy gets
-expected regret $O(T^{2/3} \log(T)^{1/3})$.
+\begin{theorem}\label{thm:2level}
+The 2-level policy with parameter $T_1 = T^{2/3}\,\log(T)^{1/3}$ achieves regret
+\[ \reg(T) \leq O_K\left( T^{2/3}\, \log(T)^{1/3} \right).\]
 \end{theorem}
 
-\swcomment{I think this proof should go to appendix, so I didn't do
-  too much refactoring} \nicomment{I read this last week and talked to jieming about it; seemed right but a bit messy, but since it's going in an appendix i won't re-read/edit it now.}
+\begin{remark}
+For a constant $K$, the number of arms, we match the optimal regret rate for non-adaptive multi-armed bandit algorithms.
+If the gap parameter $\Delta$ is known to the principal, then (for an appropriate tuning of parameter $T_1$) we can achieve regret
+  $\reg(T) \leq O_K(\log(T) \cdot \Delta^{-2})$.
+\end{remark}
 
-\begin{proof}
-  We will set $T_1$ later in the proof, depending on whether the gap
-  parameter $\Delta$ is known. For now, we just need to know we will
-  make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$. Since this policy is
-  agnostic to the indices of the arms, we assume w.l.o.g. that arm 1
-  has the highest mean.
-
-  The first $T_1 \cdot \GdT$ rounds will get total regret at most
-  $T_1 \cdot \GdT$.  We focus on bounding the regret from the second
-  level of $T - T_1 \cdot \GdT$ rounds. We consider the following two
-   events. We will first bound the probability that both of them
-  happen and then we will show that they together imply upper bounds
-  on $|\hat{\mu}^t_a - \mu_a|$'s for any agent $t$ in the second
-  level. Recall $\hat{\mu}^t_a$ is the estimated mean of arm $a$ by
-  agent $t$ and agent $t$ picks the arm with the highest
-  $\hat{\mu}^t_a$.
-
-% \begin{itemize}
-  \OMIT{\paragraph{Concentration of the number of arm $a$ pulls in the first
-    level.}
-By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
-  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
-  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
-  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
-    this implies that the number of arm $a$ pulls is then at least
-    $q_a T_1/2$.} 
-\OMIT{  By Chernoff bound,
+\begin{lemma}[Concentration of arm pulls]\label{lem:t1runs}
+  Consider $T_1$ indepdent runs of \ALGG of $T_G$ rounds. Let $N_a$ be
+  the number of arm $a$ pulls among all runs. Then with probability at
+  least $1-\delta$, for all $a\in \A$,
   \[
-    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
+    \left| N_a - q_a T_1\right| \leq T_G \sqrt{T_1 \log(2K/\delta) / 2}
   \]
-}
-Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By Lemma~\ref{lem:t1runs}, we have
-\[
-\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
-\]
-\OMIT{\paragraph{Concentration of the empirical mean of arm $a$ pulls
-    in the first level.}}  Next, we show that the empirical mean of
-each arm $a$ is close to the true mean. To facilitate our reasoning,
-let us imagine there is a tape of length $T$ for each arm $a$, with
-each cell containing an independent draw of the realized reward from
-the distribution $\cD_a$. Then for each arm $a$ and any $N\in [T]$, we
-can think of the sequence of the first $N$ realized rewards of $a$
-coming from the prefix of $N$ cells in its reward tape. Define
-$W^{a,t}_2$ to be the event that the empirical mean of the first $t$
-\swedit{realized rewards in the tape} of arm $a$ is at most
-$\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the
-intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).  By
-Chernoff bound,\swcomment{$t$ may be confusing here}
-\[
-\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
-\]
-By union bound, 
-\[
-\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
-\]
-
-By union bound, we know $\Pr[W_1 \cap W_2] \geq 1 - 3/T$. For the
-remainder of the analysis, we will condition on the event
-$W_1 \cap W_2$.
-
-For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
-\[
-|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}.
-\]
-By $W_1$ and Assumption \ref{ass:embehave}, we have
-\[
-|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{q_aT_1/2}}.
-\]
-Therefore,
-\[
-|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}+\frac{c_m}{\sqrt{q_aT_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
-\]
-So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most 
-\[
-T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
-\]
-By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.
-\OMIT{Notice that if we know the gap parameter is known to be larger than
-$\Delta$, we can set
-\[
-T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
-\]
-In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
-\[
-T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
-\]
-This completes the proof.}
-\end{proof}
-
-\begin{remark}
-  If the gap parameter $\Delta$ is known to the principal, we can set
-  $$T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2
-      \cdot p_G} \log(T) \right),$$ and achieve an expected regret of
-  $O(\log(T) \cdot \Delta^{-2})$.
-\end{remark}
+\end{lemma}
 

### 2018-11-01 app-warmup.tex
copied proofs from warmpup to a separate file/appendix.

\section{Proofs from Section~\ref{sec:warmup}}
\label{app:warmup}

\begin{proof}[Proof of Lemma~\ref{lem:greedy}]
  Fix any arm $a$. Let $\GdT = (K-1) \cdot c_T + 1$ and
  $\GdP = (1/3)^{\GdT}$. \swedit{We will condition on the event that
    all the realized rewards in $\GdT$ rounds are 0, which occurs with
    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.}
  In this case, we want to show that arm $a$ is pulled at least
  once. We prove this by contradiction. Suppose arm $a$ is not pulled. By
  the pigeonhole principle, we know that there is some other arm $a'$
  that is pulled at least $c_T + 1$ rounds. Let $t$ be the round in
  which arm $a'$ is pulled exactly $c_T + 1$ times. By Assumption
  \ref{ass:embehave}, we know
  \[
    \hat{\mu}_{a'}^t \leq 0 + c_m / \sqrt{c_T} < 1/3.
  \]
  \nicomment{Wait, where did we set $c_T$?} On the other hand, we have
  $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
  the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
  \swdelete{ In addition, we know that this case happens with
    probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is
    at most $2/3$. To sum up, we know that with probability at least
    $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.}
   \jmcomment{Agree with these changes.}
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:2level}]
  We will set $T_1$ later in the proof, depending on whether the gap
  parameter $\Delta$ is known. For now, we just need to know we will
  make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$. Since this policy is
  agnostic to the indices of the arms, we assume w.l.o.g. that arm 1
  has the highest mean.

  The first $T_1 \cdot \GdT$ rounds will get total regret at most
  $T_1 \cdot \GdT$.  We focus on bounding the regret from the second
  level of $T - T_1 \cdot \GdT$ rounds. We consider the following two
   events. We will first bound the probability that both of them
  happen and then we will show that they together imply upper bounds
  on $|\hat{\mu}^t_a - \mu_a|$'s for any agent $t$ in the second
  level. Recall $\hat{\mu}^t_a$ is the estimated mean of arm $a$ by
  agent $t$ and agent $t$ picks the arm with the highest
  $\hat{\mu}^t_a$.

% \begin{itemize}
  \OMIT{\paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $q_a T_1/2$.}
\OMIT{  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
}
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By Lemma~\ref{lem:t1runs}, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\OMIT{\paragraph{Concentration of the empirical mean of arm $a$ pulls
    in the first level.}}  Next, we show that the empirical mean of
each arm $a$ is close to the true mean. To facilitate our reasoning,
let us imagine there is a tape of length $T$ for each arm $a$, with
each cell containing an independent draw of the realized reward from
the distribution $\cD_a$. Then for each arm $a$ and any $N\in [T]$, we
can think of the sequence of the first $N$ realized rewards of $a$
coming from the prefix of $N$ cells in its reward tape. Define
$W^{a,t}_2$ to be the event that the empirical mean of the first $t$
\swedit{realized rewards in the tape} of arm $a$ is at most
$\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the
intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).  By
Chernoff bound,\swcomment{$t$ may be confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound,
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

By union bound, we know $\Pr[W_1 \cap W_2] \geq 1 - 3/T$. For the
remainder of the analysis, we will condition on the event
$W_1 \cap W_2$.

For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
\[
|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}.
\]
By $W_1$ and Assumption \ref{ass:embehave}, we have
\[
|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{q_aT_1/2}}.
\]
Therefore,
\[
|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}+\frac{c_m}{\sqrt{q_aT_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.
\OMIT{Notice that if we know the gap parameter is known to be larger than
$\Delta$, we can set
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
This completes the proof.}
\end{proof}

### 2018-11-01 model.tex
Removed some omitted/obsolete statement.

@@
 
-\OMIT{ %%%%%%%%
-\begin{assumption}
-Reward estimates are consistent over time, but allow some agent heterogeneity.
-Formally, each agent $t$ forms its estimates according to a \emph{reward estimate function}: a function $f_t$ from subhistories to $[0,1]^K$, so that the estimate vector
-        $(\hat{\mu}_{t,a}:\, a\in\A)$
-    equals $f_t(m_t)$. This function is drawn independently from some fixed distribution over reward estimate functions.
-\end{assumption}
-} %%%%%%%
-
 \OMIT{ %%%%%%%%%%

### 2018-11-01 2level.tex
2level: Finished my rewrite, I think.

@@
 \begin{lemma}\label{lem:greedy}
-There exist numbers $\GdT>0$ and $\GdP>0$ that depend only on $K$, the number of arms, with the following property.
-Consider an arbitrary disclosure policy, and let $S\subset [T]$ be a full-disclosure path in its info-graph, of length $|S|\geq \GdT$.
-Under Assumption \ref{ass:embehave}, with probability at least $\GdP$, subhistory $\SubH{S}$ contains at least once sample of each arm $a$.
+There exist numbers $\fdpL>0$ and $\fdpP>0$ that depend only on $K$, the number of arms, with the following property.
+Consider an arbitrary disclosure policy, and let $S\subset [T]$ be a full-disclosure path in its info-graph, of length $|S|\geq \fdpL$.
+Under Assumption \ref{ass:embehave}, with probability at least $\fdpP$, subhistory $\SubH{S}$ contains at least once sample of each arm $a$.
 \end{lemma}
@@
 \begin{proof}[Proof Sketch]
+\ascomment{Jieming, pls add a brief proof sketch if you can.}
 \end{proof}
-
-\ascomment{Where do we need to introduce the expected \#pulls in full-disclosure path?}
 
@@
 The policy follows the ``explore-then-exploit'' paradigm.
-The ``exploration phase" comprises the first $N = T_1\cdot \GdT$ rounds, and consists of $T_1$ full-disclosure paths of length $\GdT$ each.
-Here $\GdT$ is the constant from Lemma~\ref{lem:greedy}, and $T_1$ is a parameter.
+The ``exploration phase" comprises the first $N = T_1\cdot \fdpL$ rounds, and consists of $T_1$ full-disclosure paths of length $\fdpL$ each, where $T_1$ is a parameter.
 In the ``exploitation phase", each agent $t>N$ receives the full subhistory from exploration, \ie $m_t = \SubH{[N]}$.
@@
   \node at(8,0.5){$\cdots$};
-  \node at(5,2.5){$T -T_1 \cdot \GdT$ rounds};
-  \node at(0.5,0.5){$\GdT$};
-  \node at(1.5,0.5){$\GdT$};
-  \node at(2.5,0.5){$\GdT$};
-  \node at(3.5,0.5){$\GdT$};
-  \node at(9.5,0.5){$\GdT$};
+  \node at(5,2.5){$T -T_1 \cdot \fdpL$ rounds};
+  \node at(0.5,0.5){$\fdpL$};
+  \node at(1.5,0.5){$\fdpL$};
+  \node at(2.5,0.5){$\fdpL$};
+  \node at(3.5,0.5){$\fdpL$};
+  \node at(9.5,0.5){$\fdpL$};
   \node at(-1,0.5){\textbf{Level 1}};
@@
   \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (10,-0.2) -- (0,-0.2) node [black,midway,yshift=-0.6cm] 
-  {$T_1$ full-disclosure paths of length $\GdT$ each};
+  {$T_1$ full-disclosure paths of length $\fdpL$ each};
 \end{tikzpicture}
@@
 It is useful to think of the info-graph as having two levels (corresponding to exploration and exploitation).
-Accordingly, we call this policy the \emph{2-level policy}.
+Accordingly, we call this policy the \emph{\2LEVEL}.
 We show that it incentivizes the agents to perform non-adaptive exploration, and achieves a regret rate of  $\tilde O_K(T^{2/3})$.
@@
 \begin{theorem}\label{thm:2level}
-The 2-level policy with parameter $T_1 = T^{2/3}\,\log(T)^{1/3}$ achieves regret
+The \2LEVEL with parameter $T_1 = T^{2/3}\,\log(T)^{1/3}$ achieves regret
 \[ \reg(T) \leq O_K\left( T^{2/3}\, \log(T)^{1/3} \right).\]
@@
 
-\begin{lemma}[Concentration of arm pulls]\label{lem:t1runs}
-  Consider $T_1$ indepdent runs of \ALGG of $T_G$ rounds. Let $N_a$ be
-  the number of arm $a$ pulls among all runs. Then with probability at
+To simplify presentation of the proofs, we will make the following assumption.%
+\footnote{This assumption can be removed, without any conceptual difficulty, but at the cost of a somewhat lengthier proofs.}
+
+\begin{assumption}\label{ass:simplifying}
+In each round $t$, the estimates $\hat{\mu}_{t,a}$ depend only the multiset 
+    $\left\{\; (a_s,r_s):\;s\in S_t \;\right\}$,
+called \emph{anonymized subhistory}. Each agent forms its estimates according to the same \emph{estimate function}: a function $f$ from subhistories to $[0,1]^K$, so that the estimate vector
+        $(\hat{\mu}_{t,a}:\, a\in\A)$
+equals $f(m_t)$. 
+\end{assumption}
+
+Among other things, this assumption allows us to the define the expected number of samples of a given arm $a$ collected by a full-disclosure path $S$ of length $\fdpL$ (\ie present in the subhistory $\SubH{S}$.
+Indeed, this number, denoted $\fdpN$, is the same for all such paths.
+Then,
+
+\begin{lemma}\label{lem:t1runs}
+Suppose the info-graph contains $T_1$ full-disclosure paths of $\fdpL$ rounds each. Let $N_a$ be the number of samples of arm $a$ collected by all paths. Then with probability at
   least $1-\delta$, for all $a\in \A$,
   \[
-    \left| N_a - q_a T_1\right| \leq T_G \sqrt{T_1 \log(2K/\delta) / 2}
+    \left| N_a - \fdpN T_1\right| \leq \fdpL\cdot \sqrt{T_1 \log(2K/\delta) / 2}.
   \]

### 2018-11-01 2level.tex
Fixed a typo.

@@
 \begin{assumption}\label{ass:simplifying}
-In each round $t$, the estimates $\hat{\mu}_{t,a}$ depend only the multiset 
+In each round $t$, the estimates $\hat{\mu}_{t,a}$ depend only on the multiset 
     $\left\{\; (a_s,r_s):\;s\in S_t \;\right\}$,

### 2018-11-01 3level.tex
update figures
remove "randomness" in the policy description, our info graph is deterministic and public knowledge
T_G -> alex's macro

@@
 performs the first round of exploration over the first
-$(S\cdot T_1\cdot T_G)$ agents, where $T_1 = T^{4/7}\log^{-1/7}(T)$
-and $S = 2^{10}\log(T)$. In particular, the policy randomly partitions
+$(S\cdot T_1\cdot \GdT)$ agents, where $T_1 = T^{4/7}\log^{-1/7}(T)$
+and $S = 2^{10}\log(T)$. In particular, the policy partitions
 the agents into $S$ groups such that each group consists of $T_1$ runs
-of \ALGG with $T_G$ rounds. In the second level, the policy performs
+of \ALGG with $\GdT$ rounds. In the second level, the policy performs
 further exploration on the next $(S\cdot T_2)$ agents by incorporating
@@
  (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
- \draw[dashed] (\x+1,3)--(5,4);
+ \draw (\x+1,3)--(5,4);
  \filldraw[fill=red!20!white]
  (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
- \draw[dashed] (\x+1,1)--(\x+1,2);
- \draw[dashed] (\x+0.2,1)--(\x+1,2);
- \draw[dashed] (\x+0.6,1)--(\x+1,2);
- \draw[dashed] (\x+1.4,1)--(\x+1,2);
- \draw[dashed] (\x+1.8,1)--(\x+1,2);
- \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
- \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
- \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
- \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
+ \draw (\x+1,1)--(\x+1,2);
+ \draw(\x+0.2,1)--(\x+1,2);
+ \draw(\x+0.6,1)--(\x+1,2);
+ \draw(\x+1.4,1)--(\x+1,2);
+ \draw(\x+1.8,1)--(\x+1,2);
+ \draw(\x+0.4,0)--(\x+0.4,1); 
+ \draw(\x+0.8,0)--(\x+0.8,1); 
+ \draw (\x+1.2,0)--(\x+1.2,1); 
+ \draw(\x+1.6,0)--(\x+1.6,1);  
  \node at(\x+1,2.5){$T_2$};
@@
   Policy. Each red box in level 1 corresponds to $T_1$ \ALGG paths of
-  length $T_G$. The sub-history of each red box is then aggregated and
+  length $\GdT$. The sub-history of each red box is then aggregated and
   sent to a corresponding purple box of agents in level 2. Then the
@@
   where $q_a$ is the expected number of arm $a$ pulls in a $\ALGG$ run
-  of length $T_G$. Then $\Pr[W_1] \geq 1- \frac{4S}{T^2}$.
+  of length $\GdT$. Then $\Pr[W_1] \geq 1- \frac{4S}{T^2}$.
 \end{lemma}
@@
 first level, which is bounded
-by $S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$. In the intermediate cases of
+by $S \GdT T_1 = O(T^{4/7} \log^{6/7}(T))$. In the intermediate cases of
 both medium and small gaps, it suffices to bound the regret from the
@@
 \[
-\reg(T) \leq (S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
+\reg(T) \leq (S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
 + \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T)).

### 2018-11-01 3levelproofs.tex
check in often!
some appendix edits
T_G -> alex's macro

@@
 
-\subsection{Clean Events}
+\subsection{Events}
 
@@
 
-\subsection{Case Analysis under Clean Events}
-Now we assume the intersection of clean events $W$ happens. We will
+\subsection{Case Analysis}
+Now we assume the intersection $W$ of events $W_1,\cdots,W_4$ happens. We will
 first provide some helper lemmas for our case analysis.
@@
   \]
-Furthermore, if there are at least $T_2$ pulls of arm $a$ in the first
-two levels,
+Furthermore, if there are at least $T_2$ pulls of arm $a$ in the first two levels, 
 \[
@@
 arm 1.  \OMIT{Therefore the expected regret is at most
-  $S T_G T_1 = O(T^{4/7} \log^{6/7}(T))$.}
+  $S \GdT T_1 = O(T^{4/7} \log^{6/7}(T))$.}
 \end{proof}
@@
 \[
-(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
+(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
 + \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
@@
 \[
-(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
+(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
 + \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))

### 2018-11-01 app-warmup.tex
T_G -> alex's macro

@@
   parameter $\Delta$ is known. For now, we just need to know we will
-  make $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$. Since this policy is
+  make $T_1 \geq \frac{4(\GdT)^2}{(\GdP)^2}\log(T)$. Since this policy is
   agnostic to the indices of the arms, we assume w.l.o.g. that arm 1
@@
   the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
-  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
+  \swedit{As long as we set $T_1 \geq \frac{4(\GdT)^2}{(\GdP)^2}\log(T)$,
     this implies that the number of arm $a$ pulls is then at least

### 2018-11-01 3level.tex
q_a -> \fdpN
fun fact: we now have at most 30 q's in the paper

@@
   $$
-  \left[q_a T_1- \GdT \sqrt{T_1\log(T)}, q_a T_1 + \GdT \sqrt{T_1\log(T)}\right],
+  \left[\fdpN  T_1- \GdT \sqrt{T_1\log(T)}, \fdpN  T_1 + \GdT \sqrt{T_1\log(T)}\right],
   $$
-  where $q_a$ is the expected number of arm $a$ pulls in a $\ALGG$ run
+  where $\fdpN $ is the expected number of arm $a$ pulls in a $\ALGG$ run
   of length $\GdT$. Then $\Pr[W_1] \geq 1- \frac{4S}{T^2}$.
@@
   For any group $s\in [S]$, any arm $a$, let $\tilde\mu_{a,s}$ be the
-  empirical mean of the first $q_a T_1$ cells in tape $\cT^1_{a, s}$.
+  empirical mean of the first $\fdpN  T_1$ cells in tape $\cT^1_{a, s}$.
   Let $W_4^{s,a,\text{high}}$ be the event
-  $\tilde\mu_{a, s} \geq \mu_a + 1/\sqrt{q_a T_1}$ and let
+  $\tilde\mu_{a, s} \geq \mu_a + 1/\sqrt{\fdpN  T_1}$ and let
   $W_4^{s,a,\text{low}}$ be the event that
-  $\tilde\mu_{a, s} \leq \mu_a - 1/\sqrt{q_a T_1}$.  Let $W_4$ be the
+  $\tilde\mu_{a, s} \leq \mu_a - 1/\sqrt{\fdpN  T_1}$.  Let $W_4$ be the
   event that for every $a\in \{1, 2\}$, there exists a group
@@
   Suppose
-  $\Delta \geq 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
-    \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$, then all agents in the
+  $\Delta \geq 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
+    \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right)$, then all agents in the
   second and third levels pull arm 1.
@@
   \Delta\in \left[
-   2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
-    \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right),
- 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
-        \sqrt{\frac{4\log(T)}{q_2T_1}}\right), 
+   2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} +
+    \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right),
+ 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
+        \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right), 
     \right)
@@
     \Delta\in \left( 3\sqrt{\frac{2\log(T)}{T_2}},
-      2\left(\sqrt{\frac{4\log(T)}{S q_1T_1}} +
-        \sqrt{\frac{4\log(T)}{S q_2T_1}}\right) \right)
+      2\left(\sqrt{\frac{4\log(T)}{S \fdpN[1]T_1}} +
+        \sqrt{\frac{4\log(T)}{S \fdpN[2]T_1}}\right) \right)
   \]
@@
 \[
-\reg(T) \leq (S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T)).
+\reg(T) \leq (S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right) = O(T^{4/7} \log^{6/7}(T)).
 \]
@@
 \item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
-\OMIT{By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.
-For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$.
+\OMIT{By Lemma \ref{lem:greedy}, we know $\GdP \leq \fdpN  \leq \GdT$.
+For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $\fdpN  T_1- \GdT \sqrt{T_1\log(T)}$ and $\fdpN  T_1 + \GdT \sqrt{T_1\log(T)}$.
 By Chernoff bound,}
@@
 that the number of arm $a$ pulls in the $s$-th first-level group is
-between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and
-$q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
+between $\fdpN  T_1- \GdT \sqrt{T_1\log(T)}$ and
+$\fdpN  T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
 \[
@@
 Consider the tapes defined in the second bullet again.
-For the $s$-th first-level group and arm $a$, define $W_4^{s,a,high}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1}$ and define  $W_4^{s,a,low}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1}$.
+For the $s$-th first-level group and arm $a$, define $W_4^{s,a,high}$  to be the event that first $\fdpN  T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at least $\mu_a + 1/\sqrt{\fdpN  T_1}$ and define  $W_4^{s,a,low}$  to be the event that first $\fdpN  T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at most $\mu_a - 1/\sqrt{\fdpN  T_1}$.
 By Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
 \[
-\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1}} > 1/4.
+\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{\fdpN T_1}} > 1/4.
 \]
@@
 \item For the $s$-th first-level group and arm $a$, define $\bar{\mu}_a^{1,s}$ to be the empirical mean of arm $a$ pulls in this group.
-$W_1^{a,s}$, $W_2^{a,s,1,t}$ for $ = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1- \GdT \sqrt{T_1\log(T)}$ together imply that
+$W_1^{a,s}$, $W_2^{a,s,1,t}$ for $ = \fdpN  T_1- \GdT \sqrt{T_1\log(T)},...,\fdpN  T_1- \GdT \sqrt{T_1\log(T)}$ together imply that
 \[
-|\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_a T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
+|\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{\fdpN  T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{\fdpN  T_1}}.
 \]
@@
 \item For each arm $a$, define $\bar{\mu}_a$ to be the empirical mean of arm $a$ pulls in the first two levels.
-$W_1^{a,s}$ for $s=1,...,S$ and $W_3^{a,t}$ for $t \geq  (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
+$W_1^{a,s}$ for $s=1,...,S$ and $W_3^{a,t}$ for $t \geq  (\fdpN  T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
 \[
-|\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(q_a T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
+|\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(\fdpN  T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S \fdpN  T_1}} .
 \]
@@
 \item For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such that $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.
-$W_4^{s_a,a,high}$,  $W_1^{s_a,a}$, $W_2^{s_a,a,t, q_aT_1}$ for $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and $W_2^{s_a,a,q_aT_1,t}$ for $t= q_aT_1,...,q_a T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
+$W_4^{s_a,a,high}$,  $W_1^{s_a,a}$, $W_2^{s_a,a,t, \fdpN T_1}$ for $t = \fdpN  T_1- \GdT \sqrt{T_1\log(T)}+1, ...,\fdpN T_1-1$ and $W_2^{s_a,a,\fdpN T_1,t}$ for $t= \fdpN T_1,...,\fdpN  T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
 \begin{align*}
-\bar{\mu}_a ^{1,s_a} &\geq \mu_a + \left(q_aT_1 \cdot \frac{1}{\sqrt{q_aT_1}} - \GdT \sqrt{T_1\log(T)} \cdot \sqrt{\frac{2\log(T)}{ \GdT \sqrt{T_1\log(T)}}} \right) \cdot \frac{1}{q_a T_1+ \GdT \sqrt{T_1\log(T)}} \\
-&> \mu_a + \frac{1}{4\sqrt{q_aT_1}}.
+\bar{\mu}_a ^{1,s_a} &\geq \mu_a + \left(\fdpN T_1 \cdot \frac{1}{\sqrt{\fdpN T_1}} - \GdT \sqrt{T_1\log(T)} \cdot \sqrt{\frac{2\log(T)}{ \GdT \sqrt{T_1\log(T)}}} \right) \cdot \frac{1}{\fdpN  T_1+ \GdT \sqrt{T_1\log(T)}} \\
+&> \mu_a + \frac{1}{4\sqrt{\fdpN T_1}}.
 \end{align*}
@@
 
-\item $\mu_1 - \mu_2 \geq 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. In this case, we want to show that agents in the second and the third levels all pull arm 1.
+\item $\mu_1 - \mu_2 \geq 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right)$. In this case, we want to show that agents in the second and the third levels all pull arm 1.
 
@@
 \[
-\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{q_1T_1}} - \sqrt{\frac{4\log(T)}{q_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}.
+\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} - \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}} \geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}.
 \]
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
-&\geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
+\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} - \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}}\\
+&\geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}- \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}}\\
  &> 0.
@@
 \[
-\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{q_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{q_2T_1}}.
+\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} - \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}} \geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}.
 \]
@@
 
-\item $2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq \mu_1-\mu_2 < 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. In this case, we want to show agents in the third level all pull arm 1. Recall $\bar{\mu}_a$ is the empirical mean of arm $a$ in the first two levels. We have
+\item $2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right) \leq \mu_1-\mu_2 < 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right)$.
+In this case, we want to show agents in the third level all pull arm 1.
+Recall $\bar{\mu}_a$ is the empirical mean of arm $a$ in the first two levels.
+We have
 \[
-\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}.
+\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} - \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}} \geq  \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}.
 \]
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
-&\geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} + \sqrt{\frac{4\log(T)}{Sq_2T_1}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} - \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
+\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
+&\geq  \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}- \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
  &> 0.
@@
 \[
-(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
+(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
 \]
 
-\item $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 < 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.
+\item $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 < 2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right)$.
 In this case, we just need to make sure that agents in the third level all pull arm 1.
@@
 \begin{align*}
-\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} &> \mu_a + \frac{1}{4\sqrt{q_aT_1}} -\mu_{3-a} +\frac{1}{4\sqrt{q_{3-a}T_1}} \\
-&> \frac{1}{4\sqrt{q_1T_1}}+ \frac{1}{4\sqrt{q_2T_1}} - 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \\
-&\geq \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}.
+\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} &> \mu_a + \frac{1}{4\sqrt{\fdpN T_1}} -\mu_{3-a} +\frac{1}{4\sqrt{q_{3-a}T_1}} \\
+&> \frac{1}{4\sqrt{\fdpN[1]T_1}}+ \frac{1}{4\sqrt{\fdpN[2]T_1}} - 2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right) \\
+&\geq \frac{1}{8\sqrt{\fdpN[1]T_1}}+ \frac{1}{8\sqrt{\fdpN[2]T_1}}.
 \end{align*}
@@
 \begin{align*}
-\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
-&\geq   \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
+\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}}\\
+&\geq   \frac{1}{8\sqrt{\fdpN[1]T_1}}+ \frac{1}{8\sqrt{\fdpN[2]T_1}}- \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}}\\
  &> 0.
@@
 \[
-(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
+(S T_G T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
 \]

### 2018-11-01 3levelproofs.tex
q_a -> \fdpN
fun fact: we now have at most 30 q's in the paper

@@
   that the number of arm $a$ pulls in the $s$-th first-level group is
-  between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and
-  $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
+  between $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$ and
+  $\fdpN T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
 \[
@@
 \[
-\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1}} > 1/4.
+\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{\fdpN T_1}} > 1/4.
 \]
@@
   \[
-    |\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
+    |\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{4\log(T)}{\fdpN T_1}}.
   \]
@@
   The events $W_1$ and $W_2^{a,s,1,t}$ for
-  $t = q_a T_1- \GdT \sqrt{T_1\log(T)},...,q_a T_1 + \GdT
+  $t = \fdpN T_1- \GdT \sqrt{T_1\log(T)},...,\fdpN T_1 + \GdT
   \sqrt{T_1\log(T)}$ together imply that
 \[
-|\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_a T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{q_a T_1}}.
+|\bar{\mu}_a^{1,s} - \mu_a| \leq \sqrt{\frac{2\log(T)}{\fdpN T_1- \GdT \sqrt{T_1\log(T)}}} \leq \sqrt{\frac{4\log(T)}{\fdpN T_1}}.
 \]
@@
   \[
-    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
+    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{4\log(T)}{S \fdpN T_1}} .
   \]
@@
 \begin{proof}
-The events $W_1$ and $W_3^{a,t}$ for $t \geq  (q_a T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
+The events $W_1$ and $W_3^{a,t}$ for $t \geq  (\fdpN T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
   \[
-    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(q_a T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S q_a T_1}} .
+    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(\fdpN T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S \fdpN T_1}} .
 \]
@@
 \[
-\bar{\mu}_a ^{1,s_a} > \mu_a + \frac{1}{4\sqrt{q_aT_1}} \quad \mbox{and, } \quad
-\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
+\bar{\mu}_a ^{1,s_a} > \mu_a + \frac{1}{4\sqrt{\fdpN T_1}} \quad \mbox{and, } \quad
+\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{\fdpN[3-a] T_1}}.
 \]
@@
   that both $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.  The
-  events $W_4^{s_a,a,high}$, $W_1$, $W_2^{s_a,a,t, q_aT_1}$
-  for $t = q_a T_1- \GdT \sqrt{T_1\log(T)}+1, ...,q_aT_1-1$ and
-  $W_2^{s_a,a,q_aT_1,t}$ for
-  $t= q_aT_1,...,q_a T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
+  events $W_4^{s_a,a,high}$, $W_1$, $W_2^{s_a,a,t, \fdpN T_1}$
+  for $t = \fdpN T_1- \GdT \sqrt{T_1\log(T)}+1, ...,\fdpN T_1-1$ and
+  $W_2^{s_a,a,\fdpN T_1,t}$ for
+  $t= \fdpN T_1,...,\fdpN T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
 \begin{align*}
-\bar{\mu}_a ^{1,s_a} &\geq \mu_a + \left(q_aT_1 \cdot \frac{1}{\sqrt{q_aT_1}} - \GdT \sqrt{T_1\log(T)} \cdot \sqrt{\frac{2\log(T)}{ \GdT \sqrt{T_1\log(T)}}} \right) \cdot \frac{1}{q_a T_1+ \GdT \sqrt{T_1\log(T)}} \\
-&> \mu_a + \frac{1}{4\sqrt{q_aT_1}}.
+\bar{\mu}_a ^{1,s_a} &\geq \mu_a + \left(\fdpN T_1 \cdot \frac{1}{\sqrt{\fdpN T_1}} - \GdT \sqrt{T_1\log(T)} \cdot \sqrt{\frac{2\log(T)}{ \GdT \sqrt{T_1\log(T)}}} \right) \cdot \frac{1}{\fdpN T_1+ \GdT \sqrt{T_1\log(T)}} \\
+&> \mu_a + \frac{1}{4\sqrt{\fdpN T_1}}.
 \end{align*}
@@
 \[
-\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1}}.
+\bar{\mu}_{3-a} ^{1,s_a} < \mu_{3-a}   - \frac{1}{4\sqrt{\fdpN[3-a] T_1}}.
 \]
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} - \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}}\\
-&\geq  \sqrt{\frac{4\log(T)}{q_1T_1}} + \sqrt{\frac{4\log(T)}{q_2T_1}}- \frac{c_m}{\sqrt{q_1T_1/2}} - \frac{c_m}{\sqrt{q_2T_1/2}} > 0
+\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} - \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}}\\
+&\geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}- \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}} > 0
 \end{align*}
@@
 \begin{proof}[Proof of Lemma~\ref{3levelmedium} (Medium gap case)]
-  % $2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
-  %   \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq \mu_1-\mu_2 <
-  % 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} +
-  %   \sqrt{\frac{4\log(T)}{q_2T_1}}\right)$. 
+  % $2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} +
+  %   \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right) \leq \mu_1-\mu_2 <
+  % 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
+  %   \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right)$. 
   Recall $\bar{\mu}_a$ is
@@
 \[
-\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{Sq_1T_1}} - \sqrt{\frac{4\log(T)}{Sq_2T_1}} \geq  \sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}.
+\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} - \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}} \geq  \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}.
 \]
@@
 \[
-(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{q_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{q_2T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
+(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
 \]
@@
   % $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 <
-  % 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} +
-  %   \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right)$.  
+  % 2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} +
+  %   \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right)$.  
   In this case, we need both arms to be pulled at least $T_2$ rounds
@@
 \begin{align*}
-\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} &> \mu_a + \frac{1}{4\sqrt{q_aT_1}} -\mu_{3-a} +\frac{1}{4\sqrt{q_{3-a}T_1}} \\
-&> \frac{1}{4\sqrt{q_1T_1}}+ \frac{1}{4\sqrt{q_2T_1}} - 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \\
-&\geq \frac{1}{8\sqrt{q_1T_1}}+ \frac{1}{8\sqrt{q_2T_1}}.
+\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} &> \mu_a + \frac{1}{4\sqrt{\fdpN T_1}} -\mu_{3-a} +\frac{1}{4\sqrt{\fdpN[3-a]T_1}} \\
+&> \frac{1}{4\sqrt{\fdpN[1]T_1}}+ \frac{1}{4\sqrt{\fdpN[2]T_1}} - 2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right) \\
+&\geq \frac{1}{8\sqrt{\fdpN[1]T_1}}+ \frac{1}{8\sqrt{\fdpN[2]T_1}}.
 \end{align*}
@@
 \[
-(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{Sq_1T_1}} 
-+ \sqrt{\frac{4\log(T)}{Sq_2T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
+(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} 
++ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
 \]

### 2018-11-01 app-warmup.tex
q_a -> \fdpN
fun fact: we now have at most 30 q's in the paper

@@
     level.}
-By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
+By Lemma \ref{lem:greedy}, we know $\GdP \leq \fdpN \leq \GdT$.}
   Define $W_1^a$ to be the event that the number of arm $a$ pulls in
-  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
+  the first level is at least $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$.
   \swedit{As long as we set $T_1 \geq \frac{4(\GdT)^2}{(\GdP)^2}\log(T)$,
     this implies that the number of arm $a$ pulls is then at least
-    $q_a T_1/2$.}
+    $\fdpN T_1/2$.}
 \OMIT{  By Chernoff bound,
@@
 \[
-|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}.
+|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}.
 \]
@@
 \[
-|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{q_aT_1/2}}.
+|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{\fdpN T_1/2}}.
 \]
@@
 \[
-|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}+\frac{c_m}{\sqrt{q_aT_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
+|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}+\frac{c_m}{\sqrt{\fdpN T_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
 \]

### 2018-11-01 llevel.tex
T_G -> alex's macro
q_a -> \fdpN
fun fact: we now have at most 30 q's in the paper

@@
 
-For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
-By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ For group $G_{1,u,v}$, define $W_1^{a,u,v}$ to be the event that the number of arm $a$ pulls in this group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$.
+For $a \in \{1,2\}$, define $\fdpN$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level.
+By Lemma \ref{lem:greedy}, we know $\GdP \leq \fdpN \leq \GdT$ For group $G_{1,u,v}$, define $W_1^{a,u,v}$ to be the event that the number of arm $a$ pulls in this group is between $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$ and $\fdpN T_1 + \GdT \sqrt{T_1\log(T)}$.
 By Chernoff bound,
@@
 For first-level groups $G_{1,u,1},...,G_{1,u,S}$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in these groups pull arm $a$.
-Define $W_4^{u,a,high}$  to be the event that first $q_a T_1 S$ pulls of arm $a$ in the tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1 S}$ and define $W_4^{u,a,low}$  to be the event that first $q_a T_1S$ pulls of arm $a$ in the tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1S }$.
+Define $W_4^{u,a,high}$  to be the event that first $\fdpN T_1 S$ pulls of arm $a$ in the tape has empirical mean at least $\mu_a + 1/\sqrt{\fdpN T_1 S}$ and define $W_4^{u,a,low}$  to be the event that first $\fdpN T_1S$ pulls of arm $a$ in the tape has empirical mean at most $\mu_a - 1/\sqrt{\fdpN T_1S }$.
 By Berry-Esseen Theorem and $\mu_a \in [1/3,2/3]$, we have
 \[
-\Pr[W_4^{u,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1S}} > 1/4.
+\Pr[W_4^{u,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{\fdpN T_1S}} > 1/4.
 \]
@@
 
-By event $W_1$, we know that in each first-level group, there are at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$ pulls of arm $a$.
+By event $W_1$, we know that in each first-level group, there are at least $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$ pulls of arm $a$.
 We prove in the next claim that there are enough pulls of both arms in higher levels if $\mu_1-\mu_2$ is small enough.
-For notation convenience, we set $\varepsilon_0 = 1$, $\varepsilon_1 = \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}$ and $\varepsilon_l = 1/(4\sqrt{T_lS})$ for $l \geq 2$.
+For notation convenience, we set $\varepsilon_0 = 1$, $\varepsilon_1 = \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}$ and $\varepsilon_l = 1/(4\sqrt{T_lS})$ for $l \geq 2$.
 
@@
 \begin{align*}
-\bar{\mu}_a ^t &\geq \mu_a + \left(q_aT_1S \cdot \frac{1}{\sqrt{q_aT_1S}} - \GdT \sqrt{T_1\log(T)} S\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}S}} \right) \cdot \frac{1}{(q_a T_1+ \GdT \sqrt{T_1\log(T)})S} \\
-&> \mu_a + \frac{1}{4\sqrt{q_aT_1S}}.
+\bar{\mu}_a ^t &\geq \mu_a + \left(\fdpN T_1S \cdot \frac{1}{\sqrt{\fdpN T_1S}} - \GdT \sqrt{T_1\log(T)} S\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}S}} \right) \cdot \frac{1}{(\fdpN T_1+ \GdT \sqrt{T_1\log(T)})S} \\
+&> \mu_a + \frac{1}{4\sqrt{\fdpN T_1S}}.
 \end{align*}
@@
 \[
-\bar{\mu}_{3-a}^t< \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1S}}.
+\bar{\mu}_{3-a}^t< \mu_{3-a}   - \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}.
 \]
@@
 \begin{align*}
-\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a} + \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}\\
-&\geq -\varepsilon_1+ \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}\\
-&\geq \frac{1}{8\sqrt{q_aT_1S}} + \frac{1}{8\sqrt{q_{3-a} T_1S}}.
+\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a} + \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}\\
+&\geq -\varepsilon_1+ \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}\\
+&\geq \frac{1}{8\sqrt{\fdpN T_1S}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1S}}.
 \end{align*}
@@
 \begin{align*}
-\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{c_m}{\sqrt{q_aT_1S/2}} - \frac{c_m}{\sqrt{q_{3-a} T_1S/2}}\\
-&> \frac{1}{8\sqrt{q_aT_1S}} + \frac{1}{8\sqrt{q_{3-a} T_1S}} -   \frac{c_m}{\sqrt{q_aT_1S/2}} - \frac{c_m}{\sqrt{q_{3-a} T_1S/2}}\\
+\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{c_m}{\sqrt{\fdpN T_1S/2}} - \frac{c_m}{\sqrt{\fdpN[3-a] T_1S/2}}\\
+&> \frac{1}{8\sqrt{\fdpN T_1S}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1S}} -   \frac{c_m}{\sqrt{\fdpN T_1S/2}} - \frac{c_m}{\sqrt{\fdpN[3-a] T_1S/2}}\\
 &>0.
@@
 \item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l = 2$(i.e.
-$\varepsilon_1S\leq \mu_1 - \mu_2 \leq \varepsilon_0$): We know agents in level at least 2 will observe at least $q_aT_1/2$ pulls of arm $a$ for $a \in \{1,2\}$.
+$\varepsilon_1S\leq \mu_1 - \mu_2 \leq \varepsilon_0$): We know agents in level at least 2 will observe at least $\fdpN T_1/2$ pulls of arm $a$ for $a \in \{1,2\}$.
 By $W_2$, for any agent in level at least 2, we have
 \[
-|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{Sq_aT_1/2}}.
+|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S\fdpN T_1/2}}.
 \]
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{c_m}{\sqrt{Sq_1T_1/2}} -  \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
-&\geq \mu_1 -\mu_2-\sqrt{\frac{3\log(T)}{Sq_1T_1/2}} - \sqrt{\frac{3\log(T)}{Sq_2T_1/2}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} -  \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
-&\geq\frac{\sqrt{S}}{4\sqrt{q_1T_1}} +  \frac{\sqrt{S}}{4\sqrt{q_2T_1}}-\sqrt{\frac{3\log(T)}{Sq_1T_1/2}} - \sqrt{\frac{3\log(T)}{Sq_2T_1/2}}- \frac{c_m}{\sqrt{Sq_1T_1/2}} -  \frac{c_m}{\sqrt{Sq_2T_1/2}}\\
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
+&\geq \mu_1 -\mu_2-\sqrt{\frac{3\log(T)}{S\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{S\fdpN[2]T_1/2}}- \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
+&\geq\frac{\sqrt{S}}{4\sqrt{\fdpN[1]T_1}} +  \frac{\sqrt{S}}{4\sqrt{\fdpN[2]T_1}}-\sqrt{\frac{3\log(T)}{S\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{S\fdpN[2]T_1/2}}- \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
 &>0.
@@
 \item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}S$ for $l =3$ (i.e.
-$\varepsilon_1 < \mu_1 - \mu_2 < \varepsilon_1S$): By Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $3$, that agent will observe at least $T_1q_aS^2/2$ arm $a$ pulls (just from the first level).
+$\varepsilon_1 < \mu_1 - \mu_2 < \varepsilon_1S$): By Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $3$, that agent will observe at least $T_1\fdpN S^2/2$ arm $a$ pulls (just from the first level).
 By $W_2$, we have
 \[
-|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S^2q_aT_1/2}}.
+|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S^2\fdpN T_1/2}}.
 \]
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{c_m}{\sqrt{S^2q_1T_1/2}}-\frac{c_m}{\sqrt{S^2q_2T_1/2}}  \\
-&\geq \mu_1 -\mu_2 -  \sqrt{\frac{3\log(T)}{S^2q_1T_1/2}}- \sqrt{\frac{3\log(T)}{S^2q_2T_1/2}}- \frac{c_m}{\sqrt{S^2q_1T_1/2}}-\frac{c_m}{\sqrt{S^2q_2T_1/2}}  \\
-&\geq\frac{1}{4\sqrt{Sq_1T_1}} + \frac{1}{4\sqrt{Sq_2T_1}}  -  \sqrt{\frac{3\log(T)}{S^2q_1T_1/2}}- \sqrt{\frac{3\log(T)}{S^2q_2T_1/2}}- \frac{c_m}{\sqrt{S^2q_1T_1/2}}-\frac{c_m}{\sqrt{S^2q_2T_1/2}}  \\
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{c_m}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{c_m}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
+&\geq \mu_1 -\mu_2 -  \sqrt{\frac{3\log(T)}{S^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{S^2\fdpN[2]T_1/2}}- \frac{c_m}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{c_m}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
+&\geq\frac{1}{4\sqrt{S\fdpN[1]T_1}} + \frac{1}{4\sqrt{S\fdpN[2]T_1}}  -  \sqrt{\frac{3\log(T)}{S^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{S^2\fdpN[2]T_1/2}}- \frac{c_m}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{c_m}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
 &>0.
@@
 \begin{align*}
-&\max\left( T_1T_GS^2 , \max_{l \geq 2} \varepsilon_{l-1}S(T_1T_GS^2 + T_2 S^3 + \cdots + T_lS^3)\right) \\
-\leq & \max\left( T_1T_GS^2 , \max_{l \geq 2} 2 \varepsilon_{l-1} T_l S^4 \right)\\
+&\max\left( T_1\GdT S^2 , \max_{l \geq 2} \varepsilon_{l-1}S(T_1\GdT S^2 + T_2 S^3 + \cdots + T_lS^3)\right) \\
+\leq & \max\left( T_1\GdT S^2 , \max_{l \geq 2} 2 \varepsilon_{l-1} T_l S^4 \right)\\
 = &O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right).

### 2018-11-01 app-warmup.tex
ct,cm->N0,C0

@@
+%!TEX root = main.tex
 \section{Proofs from Section~\ref{sec:warmup}}
@@
 \begin{proof}[Proof of Lemma~\ref{lem:greedy}]
-  Fix any arm $a$. Let $\GdT = (K-1) \cdot c_T + 1$ and
+  Fix any arm $a$. Let $\GdT = (K-1) \cdot N_0 + 1$ and
   $\GdP = (1/3)^{\GdT}$. \swedit{We will condition on the event that
@@
   the pigeonhole principle, we know that there is some other arm $a'$
-  that is pulled at least $c_T + 1$ rounds. Let $t$ be the round in
-  which arm $a'$ is pulled exactly $c_T + 1$ times. By Assumption
+  that is pulled at least $N_0 + 1$ rounds. Let $t$ be the round in
+  which arm $a'$ is pulled exactly $N_0 + 1$ times. By Assumption
   \ref{ass:embehave}, we know
   \[
-    \hat{\mu}_{a'}^t \leq 0 + c_m / \sqrt{c_T} < 1/3.
+    \hat{\mu}_{a'}^t \leq 0 + C_0 / \sqrt{N_0} < 1/3.
   \]
-  \nicomment{Wait, where did we set $c_T$?} On the other hand, we have
+  \nicomment{Wait, where did we set $N_0$?} On the other hand, we have
   $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
@@
 \[
-|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{\fdpN T_1/2}}.
+|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{C_0}{\sqrt{\fdpN T_1/2}}.
 \]
@@
 \[
-|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}+\frac{c_m}{\sqrt{\fdpN T_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
+|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}+\frac{C_0}{\sqrt{\fdpN T_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
 \]

### 2018-11-01 llevel.tex
information graph -> info-graph
ct,cm->N0,C0

@@
 
-Finally we define the information flow.
+Finally we define the info-graph.
 Agents in the first level only observe the history defined in the \ALGG run.
@@
 \begin{align*}
-\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{c_m}{\sqrt{\fdpN T_1S/2}} - \frac{c_m}{\sqrt{\fdpN[3-a] T_1S/2}}\\
-&> \frac{1}{8\sqrt{\fdpN T_1S}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1S}} -   \frac{c_m}{\sqrt{\fdpN T_1S/2}} - \frac{c_m}{\sqrt{\fdpN[3-a] T_1S/2}}\\
+\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{C_0}{\sqrt{\fdpN T_1S/2}} - \frac{C_0}{\sqrt{\fdpN[3-a] T_1S/2}}\\
+&> \frac{1}{8\sqrt{\fdpN T_1S}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1S}} -   \frac{C_0}{\sqrt{\fdpN T_1S/2}} - \frac{C_0}{\sqrt{\fdpN[3-a] T_1S/2}}\\
 &>0.
 \end{align*}
-The last inequality holds since $c_m$ is a small enough constant defined in Assumption \ref{ass:embehave}.
+The last inequality holds since $C_0$ is a small enough constant defined in Assumption \ref{ass:embehave}.
 Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$ all pull arm $a$.
@@
 \begin{align*}
-\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{c_m}{\sqrt{n^{l-1,u_a,a} }} - \frac{c_m}{\sqrt{n^{l-1,u_a,3-a}}}\\
-&> \frac{1}{8\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{8\sqrt{n^{l-1,u_a,3-a}  }} -  \frac{c_m}{\sqrt{n^{l-1,u_a,a} }} - \frac{c_m}{\sqrt{n^{l-1,u_a,3-a}}}\\
+\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{C_0}{\sqrt{n^{l-1,u_a,a} }} - \frac{C_0}{\sqrt{n^{l-1,u_a,3-a}}}\\
+&> \frac{1}{8\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{8\sqrt{n^{l-1,u_a,3-a}  }} -  \frac{C_0}{\sqrt{n^{l-1,u_a,a} }} - \frac{C_0}{\sqrt{n^{l-1,u_a,3-a}}}\\
 &>0.
 \end{align*}
-The last inequality holds since $c_m$ is a small enough constant defined in Assumption \ref{ass:embehave}.
+The last inequality holds since $C_0$ is a small enough constant defined in Assumption \ref{ass:embehave}.
 Therefore agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$.
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
-&\geq \mu_1 -\mu_2-\sqrt{\frac{3\log(T)}{S\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{S\fdpN[2]T_1/2}}- \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
-&\geq\frac{\sqrt{S}}{4\sqrt{\fdpN[1]T_1}} +  \frac{\sqrt{S}}{4\sqrt{\fdpN[2]T_1}}-\sqrt{\frac{3\log(T)}{S\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{S\fdpN[2]T_1/2}}- \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
+&\geq \mu_1 -\mu_2-\sqrt{\frac{3\log(T)}{S\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{S\fdpN[2]T_1/2}}- \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
+&\geq\frac{\sqrt{S}}{4\sqrt{\fdpN[1]T_1}} +  \frac{\sqrt{S}}{4\sqrt{\fdpN[2]T_1}}-\sqrt{\frac{3\log(T)}{S\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{S\fdpN[2]T_1/2}}- \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
 &>0.
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2c_m}{\sqrt{T_{l-1}}} \\
-&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2c_m}{\sqrt{T_{l-1}}} \\
-&\geq\sqrt{\frac{S}{16T_{l-1}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2c_m}{\sqrt{T_{l-1}}} \\
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2C_0}{\sqrt{T_{l-1}}} \\
+&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2C_0}{\sqrt{T_{l-1}}} \\
+&\geq\sqrt{\frac{S}{16T_{l-1}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2C_0}{\sqrt{T_{l-1}}} \\
 &>0.
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{c_m}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{c_m}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
-&\geq \mu_1 -\mu_2 -  \sqrt{\frac{3\log(T)}{S^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{S^2\fdpN[2]T_1/2}}- \frac{c_m}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{c_m}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
-&\geq\frac{1}{4\sqrt{S\fdpN[1]T_1}} + \frac{1}{4\sqrt{S\fdpN[2]T_1}}  -  \sqrt{\frac{3\log(T)}{S^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{S^2\fdpN[2]T_1/2}}- \frac{c_m}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{c_m}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{C_0}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{C_0}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
+&\geq \mu_1 -\mu_2 -  \sqrt{\frac{3\log(T)}{S^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{S^2\fdpN[2]T_1/2}}- \frac{C_0}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{C_0}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
+&\geq\frac{1}{4\sqrt{S\fdpN[1]T_1}} + \frac{1}{4\sqrt{S\fdpN[2]T_1}}  -  \sqrt{\frac{3\log(T)}{S^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{S^2\fdpN[2]T_1/2}}- \frac{C_0}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{C_0}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
 &>0.
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2c_m}{\sqrt{S^2T_{l-2}}} \\
-&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{S^2T_{l-2}}}- \frac{2c_m}{\sqrt{S^2T_{l-2}}} \\
-&\geq\frac{1}{4\sqrt{ST_{l-2}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2c_m}{\sqrt{T_{l-1}}} \\
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2C_0}{\sqrt{S^2T_{l-2}}} \\
+&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{S^2T_{l-2}}}- \frac{2C_0}{\sqrt{S^2T_{l-2}}} \\
+&\geq\frac{1}{4\sqrt{ST_{l-2}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2C_0}{\sqrt{T_{l-1}}} \\
 &>0.

### 2018-11-01 model.tex
q_a -> \fdpN
fun fact: we now have at most 30 q's in the paper
typo
hm

@@
 \label{sec:model}
-
 We study the multi-armed bandit problem in a social learning context, in which a principal faces a sequence of $T$ myopic agents.
@@
   \sum_{t\in [T]} \E[\mu_{a_t}].
-\end{align}
+\end{align}\swcomment{why expectation over the second term?}
 The principal chooses messages $m_t$ according to an online algorithm called \emph{disclosure policy}, with a goal to minimize regret.
@@
 \reg(T) \leq O\left(\min\left( 
-    \sqrt{KT\log T)},\; \tfrac{1}{\Delta} \log T
+    \sqrt{KT\log T},\; \tfrac{1}{\Delta} \log T
     \right)\right).

### 2018-11-01 model.tex
s

@@
   \sum_{t\in [T]} \E[\mu_{a_t}].
-\end{align}\swcomment{why expectation over the second term?}
+\end{align}\swcomment{maybe explain the randomness in the expectation?}
 The principal chooses messages $m_t$ according to an online algorithm called \emph{disclosure policy}, with a goal to minimize regret.

### 2018-11-01 main.tex
2level
3-level proof
Start >3 level proof
update model and greedy
Update 2-level proof
edits
rewriting
GITHUB SUCKS
update 2-level figure
stuff
3level
llevel theorems
brown is the new pink
llevel in intro
Moved concentration and anti-concentration theorem statements to appendix.
Moved Greedy into Warmup, and started revising.
Moved a macro to the main file.
Revised some macro.
Changed some macro.
T_G -> alex's macro
q_a -> \fdpN
fun fact: we now have at most 30 q's in the paper
Acknowledgment for  Bobby

@@
 %\usepackage{amsmath, amsfonts, amssymb, amsthm, amsbsy, amscd, bm, bbm}
-\usepackage{amsbsy, amscd, bm, bbm}
+%\usepackage{amsbsy,amscd, bm, bbm}
+\usepackage{kpfonts}
 \usepackage{array}
@@
 \usepackage{comment}
+\usepackage{tikz}
+\usetikzlibrary{decorations.pathreplacing}
+\usepackage{cleveref}
 
@@
 \addauthor{jm}{blue}     % jm for Jieming
-\addauthor{ni}{green}     % ni for Nicole
-\addauthor{sw}{magenta}     % sw for Steven
+\addauthor{ni}{magenta}     % ni for Nicole
+\addauthor{sw}{brown}     % sw for Steven
 % e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newtheorem{theorem}{Theorem}[section]
-%\newtheorem{corollary}[theorem]{Corollary}
-%\newtheorem{conjecture}[theorem]{Conjecture}
-%\newtheorem{proposition}[theorem]{Proposition}
-%\newtheorem{definition}[theorem]{Definition}
-%\newtheorem{lemma}[theorem]{Lemma}
-%\newtheorem{remark}{Remark}[section]
-%\newtheorem{claim}{Claim}[section]
-%\newtheorem{example}{Example}[section]
+% \newtheorem{theorem}{Theorem}[section]
+% \newtheorem{corollary}[theorem]{Corollary}
+% \newtheorem{conjecture}[theorem]{Conjecture}
+% \newtheorem{proposition}[theorem]{Proposition}
+% \newtheorem{definition}[theorem]{Definition}
+% \newtheorem{lemma}[theorem]{Lemma}
+% \newtheorem{remark}{Remark}[section]
+% \newtheorem{claim}{Claim}[section]
+% \newtheorem{example}{Example}[section]
 
-\newcommand{\term}[1]{\ensuremath{\mathtt{#1}}}
+\newcommand{\term}[1]{\ensuremath{\mathtt{#1}}\xspace}
 \newcommand{\thread}{\term{thread}}
+\newcommand{\ALGG}{full-disclosure path }
+\newcommand{\ALGPG}{\term{Parallel Greedy}}
+
+% Alex's notation!
+\newcommand{\SubH}[1]{\mathcal{H}_{#1}} % subhistory
+\newcommand{\AnonSubH}[1]{H^{\texttt{anon}}_{#1}} % subhistory
+
+% new notation for FDPs (full-disclosure paths)
+\newcommand{\fdp}{\term{FDP}}
+\newcommand{\fdpL}{L^\fdp_K} % sufficient length of greedy path
+\newcommand{\fdpP}{p^\fdp_K} % success prob for greedy path
+\newcommand{\fdpN}[1][a]{N^\fdp_{K,#1}} % Exp #pulls for arm $a$ in greedy path of length L_K.
+
+% Greedy notation
+\def\GdT{L^\fdp_K} % sufficient length of greedy path
+\def\GdP{p^\fdp_K} % success prob for greedy path
+
+\def\2LEVEL{two-level policy}
 
@@
 \def\E{\mathbb{E}}
-
+\def\reg{\mathrm{Reg}}
 \def\A{\mathcal{A}}
@@
 \def\varOmega{\bold{\Omega}}
-
-\def\ALGG{Greedy }
-\def\ALGPG{Parallel Greedy }
-\def\2LEVEL{Two-level Policy}
+\def\cD{\mathcal{D}}
+\def\cT{\mathcal{T}}
 \def\Ber{\emph{Ber} }
@@
 \def\emn{\bar{\mu}}
+%\def\q_a{\fdpN}
+%\def\ell{l}
 
-\title{Bayesian Exploration with Unbiased History}
+\title{Incentivizing Exploration with Unbiased History}
 
@@
 
-\section{Social Learning}
-\begin{lemma}
-\ALGG of $T_c$ rounds pulls each arm w.p. at least $p_c$. 
-\end{lemma}
-
-\begin{corollary}
-\ALGPG of $c \cdot T_c \cdot \frac{1}{p_c} \cdot \log(1/\delta)$ rounds pulls each at least once w.p. $1-\delta$. \jmcomment{Do we actually need this?}
-\end{corollary}
+%\input{algg}
 
@@
 
+%l-level in the 10page
+\input{llevel-overview}
+
+\bibliographystyle{plain}
+\bibliography{bib-abbrv,bib-AGT,bib-bandits,bib-ML,bib-random,bib-slivkins}
+
+\section*{Acknowledgment}
+We would like to thank Robert Kleinberg for discussions in the early stage of this project.
+
 \appendix
-
+\input{prelim}
+\input{app-warmup}
+\input{3levelproofs}
+\input{llevel}
 \input{posterior}
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2018-11-01 2level.tex
.

@@
 \section{Warm-up: full-disclosure paths}
-
+\label{sec:warmup}
 We first consider a disclosure policy that reveals the full history in each round $t$, \ie $m_t=\SubH{t-1}$; we call it the \emph{full-disclosure policy}.

### 2018-11-01 model.tex
Minor edits in model.

@@
 Further, we focus on disclosure policies that are \emph{transitive}, in the following sense:
-\[ t'\in S_t \Rightarrow S_{t'}\subset S_t
+\[ t\in S_{t'} \Rightarrow S_t\subset S_{t'}
     \qquad \text{for all rounds $t,t'\in [T]$}. \]
-In words, if an agent observes the outcome for some previous agent, then she observes the entire message revealed to that agent.
+In words, if agent $t'$ observes the outcome for some previous agent $t$, then she observes the entire message revealed to that agent.
+In particular, agent $t'$ does not need to second-guess which message has caused agent $t$ to choose action $a_t$.
 
-A transitive unbiased-history policy can be represented as an undirected graph, where nodes correspond to rounds, and any two rounds $t'<t$ are connected if and only if $t'\in S_t$ and there is no intermediate round $t''$ with
-    $t'\in S_{t''}$ and $t''\in S_t$.
-This graph is henceforth called the \emph{information flow graph} of policy $\pi$, or \emph{info-graph} for short. We assume that it is common knowledge.
+A transitive unbiased-history policy can be represented as an undirected graph, where nodes correspond to rounds, and any two rounds $t<t'$ are connected if and only if $t\in S_{t'}$ and there is no intermediate round $t''$ with
+    $t\in S_{t''}$ and $t''\in S_{t'}$.
+This graph is henceforth called the \emph{information flow graph} of the policy, or \emph{info-graph} for short. We assume that this graph is common knowledge.
 

### 2018-11-01 model.tex
Another minor edit.

@@
 We are interested in \emph{regret}, defined as
-\begin{align}
+\begin{align}\label{eq:intro-regret-defn}
 \textstyle
@@
   \sum_{t\in [T]} \E[\mu_{a_t}].
-\end{align}\swcomment{maybe explain the randomness in the expectation?}
+\end{align}
+(The expectation is over the chosen arms $a_t$, which depend on randomness in rewards, and possibly in the algorithm.)
 The principal chooses messages $m_t$ according to an online algorithm called \emph{disclosure policy}, with a goal to minimize regret.
 We assume that mean rewards are bounded away from $0$ and $1$, to ensure sufficient entropy in rewards.
-For concreteness, we posit that
+For concreteness, we posit
     $\mu_a\in [\tfrac13,\tfrac23]$.

### 2018-11-01 model.tex
Added notation for constants in low-deviation assumption for agents' estimates.

@@
 Let $N_{t,a}$ and $\bar{\mu}_{t,a}$ denote the number of pulls and the empirical mean reward of arm $a$ in subhistory $m_t$.
-Then for some absolute constant $N_0\in \N$ and $C_0=\tfrac{1}{16}$, and for all agents $t\in [T]$ and arms $a\in\A$ it holds that
+Then for some absolute constant $\estN\in \N$ and $\estC=\tfrac{1}{16}$, and for all agents $t\in [T]$ and arms $a\in\A$ it holds that
 \[
-\text{if}\; N_{t,a} \geq N_0
+\text{if}\; N_{t,a} \geq \estN
 \quad\text{then}\quad
     \left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
-		\frac{C_0}{\sqrt{N_{t,a}}}.
+		\frac{\estC}{\sqrt{N_{t,a}}}.
 \]
@@
     $\hat{\mu}^t_a\geq\tfrac13$ if $N_{t,a}=0$.
-(NB: we make no assumption if $1\leq N_{t,a}<N_0$.)
+(NB: we make no assumption if $1\leq N_{t,a}<\estN$.)
 \end{assumption}

### 2018-11-01 2level.tex
sketch?
Minor edits.

@@
 \ascomment{Jieming, pls add a brief proof sketch if you can.}
+\jmcomment{The main idea of the proof is to consider the case when all pulled arms have bad realized rewards (i.e. 0). }
+\jmcomment{Actually, not clear about how to write a sketch for a proof of 8 lines.}
 \end{proof}
@@
 
-To simplify presentation of the proofs, we will make the following assumption.%
-\footnote{This assumption can be removed, without any conceptual difficulty, but at the cost of a somewhat lengthier proofs.}
+The proofs can be found in Appendix~\ref{app:warmup}. To simplify presentation, here and elsewhere we make the following assumption (which can be removed at the cost of a somewhat lengthier proofs).
 

### 2018-11-01 2level.tex
Removed proof sketch.
More minor edits.

@@
 
+\OMIT{ %%%%%%
 \begin{proof}[Proof Sketch]
@@
 \end{proof}
+} %%%%%%
 
@@
 
-It is useful to think of the info-graph as having two levels (corresponding to exploration and exploitation).
+The info-graph has two ``levels", corresponding to exploration and exploitation.
 Accordingly, we call this policy the \emph{\2LEVEL}.
 We show that it incentivizes the agents to perform non-adaptive exploration, and achieves a regret rate of  $\tilde O_K(T^{2/3})$.
-The key idea is that using many full-disclosure paths ``in parallel" ensures that sufficiently many samples of each arm are collected during exploration.
+The key idea is that since one full-disclosure path collects one sample of a given arm with constant probability, using many full-disclosure paths ``in parallel" ensures that sufficiently many samples of this arm are collected.
 

### 2018-11-01 model.tex
Minor edit in the model.

@@
 \xhdr{Preliminaries.}
-Throughout the paper, we will use the standard concentration and anti-concentration inequalities: respectively, Chernoff Bounds and Berry-Esseen Theorem.
+\asedit{We assume that $K$ is constant, and focus on the dependence on $T$. However, we explicitly state the dependence on $K$, \eg using the $O_K()$ notation.}
+
+Throughout the paper, we use the standard concentration and anti-concentration inequalities: respectively, Chernoff Bounds and Berry-Esseen Theorem.
 The former states that that a sum of independent random variables converges to its expectation quickly.

### 2018-11-01 3level.tex
information graph -> info-graph
update figure
Started revising the 3-level policy.

@@
 
-\section{Adaptive Policy with Three Levels}
+\section{Adaptive exploration with a three-level disclosure policy}
 \label{sec:3level}
-\swcomment{rewrote below}
-Now we demonstrate how to design a 3-level policy to incentivize
-adaptive exploration and improve the $O(T^{2/3})$ regret rate to
-$\tilde O(T^{4/7})$. In \Cref{sec:llevel}, we will show how to extend
-this idea to achieve a regret rate of $\tilde O(T^{1/2})$. For
-simplicity, we will focus on the setting with 2 arms\niedit{, although our results can be extended to a constant number of arms $K$}.
-\nicomment{I think that's true, but if not, then we're not focusing on 2 arms for ``simplicity''.} \jmcomment{It is true.
-We only show this extension for $l$-level tho.}
 
-The policy consists of three phases, each of which corresponds to a
-level (see Figure~\ref{fig:3level}).  In the first level, the policy
-performs the first round of exploration over the first
-$(S\cdot T_1\cdot \GdT)$ agents, where $T_1 = T^{4/7}\log^{-1/7}(T)$
-and $S = 2^{10}\log(T)$. In particular, the policy partitions
-the agents into $S$ groups such that each group consists of $T_1$ runs
-of \ALGG with $\GdT$ rounds. In the second level, the policy performs
-further exploration on the next $(S\cdot T_2)$ agents by incorporating
-data collected in the first level, where
-$T_2 = T^{6/7}\log^{-5/7}(T)$. The agents are again partitioned into
-$S$ groups such that the agents in the $s$-th group are shown the same
-sub-history from the $s$-th group in the first level. In the third
-level, the policy exploits by showing all remaining agents the entire
-history from the first two levels.
-\nicomment{This comment applies to the 2level too; why not allow the guys within the last level see each other?
-Seems like this would still work but be more of a headache to prove -- would have to argue the empirical means can't move around too much in the sub-terminal levels, but it makes a big qualitative difference because now everyone sees a vanishingly small fraction of the history whereas with this modification a fraction approaching 1 of the people see a fraction approaching 1 of the history.} \jmcomment{To do it for the last level is actually easy.
-It would be headache to do it for the second level as we want to prove anti-concentration in the second level.
-On the other hand, we have the property that agents see $1/polylog$ fraction of history in our final result for $l$-level.
-A different point of view is that, seeing each other requires more interaction, our policy has the nice property that the interaction is very minimal except the initial greedy runs.}
+The two-level policy from the previous section implements the explore-then-exploit paradigm using a basic design with parallel full-disclosure paths.
+The next challenge is to implement \emph{adaptive exploration}, and go below the $T^{2/3}$ barrier.
+We accomplish this using a construction that adds a middle level to the info-graph.
+This construction also provides intuition for the main result, the multi-level construction presented in the next section.
+For simplicity, we assume $K=2$ arms.
+
+\begin{figure}[t]
+\centering
+\begin{tikzpicture}
+ \filldraw[fill=green!20!white]
+ (0,4)--(10,4)--(10,5)--(0,5)--cycle;
+ \foreach \x in {0,3,8}
+ {
+ \filldraw[fill=blue!20!white]
+ (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
+ \draw (\x+1,3)--(5,4);
+ \filldraw[fill=red!20!white]
+ (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
+ \draw (\x+1,1)--(\x+1,2);
+ \draw(\x+0.33,1)--(\x+1,2);
+ \draw(\x+1.66,1)--(\x+1,2);
+ %\draw(\x+1.4,1)--(\x+1,2);
+ %\draw(\x+1.8,1)--(\x+1,2);
+ \draw(\x+0.66,0)--(\x+0.66,1);
+ \draw(\x+1.33,0)--(\x+1.33,1);
+% \draw (\x+1.2,0)--(\x+1.2,1);
+ %\draw(\x+1.6,0)--(\x+1.6,1);
+ \node at(\x+1,2.5){$N_2$ rounds};
+ \node at(\x+0.33, 0.5){$\GdT$};
+ %\node at(\x+0.6, 0.5){$\cdot$};
+ \node at(\x+1.0, 0.5){$\cdots$};
+ %\node at(\x+1.4, 0.5){$\cdot$};
+ \node at(\x+1.66, 0.5){$\GdT$};
+ %\node at(\x+1,0.5){$T_1 \cdot \GdT$};
+ \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (\x+2,-0.2) -- (\x+0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ paths};
+ }
+  \node at(5,4.5){all remaining rounds};
+  \node at (6,0.5){$\cdots$};
+  \node at (7,0.5){$\cdots$};
+  \node at (6,2.5){$\cdots$};
+  \node at (7,2.5){$\cdots$};
+  \node at(-1,0.5){\textbf{Level 1}};
+  \node at(-1,2.5){\textbf{Level 2}};
+  \node at(-1,4.5){\textbf{Level 3}};
+  \draw[->] (11,0)--(11,5);
+  \node at(11.5,2.5)[ rotate=90]{Time};
+
+  \draw [decorate,decoration={brace,amplitude=10pt,aspect=0.33},xshift=0pt,yshift=0pt] (10,1.8) -- (0,1.8) node [black,pos=0.33,xshift = 0cm,yshift=-0.6cm] {$T_2$ groups};
+
+\end{tikzpicture}
+\caption{Info-graph for the three-level policy. Each red box in level 1 corresponds to $T_1$ full-disclosure paths of length $\GdT$ each.}
+\label{fig:3level}
+\end{figure}
+
+The new policy, called the \emph{three-level policy}, is as follows
+ (see Figure~\ref{fig:3level}).
+
+\begin{construction}
+The info-graph consists of three levels: the first two correspond to \emph{exploration}, and the third implements \emph{exploitation}.
+Like in the two-level policy, the first level consists of multiple full-disclosure paths of length $\fdpL$ each, and each agent $t$ in the exploitation level sees full history from exploration.
+The middle layer is what ensures adaptive exploration.
+It consists of $T_2$ disjoint subsets of $N_2$ agents each, called \emph{second-level groups}.
+Each second-level group $S$ has the following property:
+\begin{align}\label{eq:group-defn}
+\text{all nodes in $S$ are connected to the same nodes outside of $S$, but not to one another.}
+\end{align}
+
+The full-disclosure paths in the first level are also split into $T_2$ disjoint subsets, called \emph{first-level groups}.
+Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot T_2\cdot \fdpL$ rounds in the first layer.
+There is a 1-1 correspondence between first-level groups $S_1$ and second-level groups $S_2$, whereby each agent $t\in S_2$ observes the full history from the corresponding group $S_1$.
+More formally, agent $t$ is connected to the last node of each full-disclosure path in $S_1$.
+In other words, this agent receives message
+    $m_t = \SubH{V(S_1)}$,
+where $V(S_1)$ is the set of all rounds in $S_1$. 
+\end{construction}
+
+\begin{theorem}
+\label{thm:3level}
+For two arms, the three-level policy
+achieves regret
+\[ \reg(T) \leq O\left( T^{4/7}\, \log T \right).\]
+This is achieved with parameters
+    $T_1 = T^{4/7}\log^{-1/7}(T)$,
+    $T_2 = 2^{10}\log(T)$, and
+    $N_2 = T^{6/7}\log^{-5/7}(T)$.
+\end{theorem}
+
+\ascomment{stopped here.}
 
@@
 following. \nicomment{I'm a little confused why this works while simply growing the first level doesn't work; wouldn't the first level where the arm is ``lucky'' explore it more if it had more time?}
-
-\begin{theorem}
-\label{thm:3level}
-The 3-level recommendation policy gets expected regret $O(T^{4/7} \log^{6/7}(T))$. 
-\end{theorem}
 
@@
 \fi
-
-\begin{figure}[H]
-\centering
-\begin{tikzpicture}  
- \filldraw[fill=green!20!white]
- (0,4)--(10,4)--(10,5)--(0,5)--cycle;
- \foreach \x in {0,3,8}
- {
- \filldraw[fill=blue!20!white]
- (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
- \draw (\x+1,3)--(5,4);
- \filldraw[fill=red!20!white]
- (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
- \draw (\x+1,1)--(\x+1,2);
- \draw(\x+0.2,1)--(\x+1,2);
- \draw(\x+0.6,1)--(\x+1,2);
- \draw(\x+1.4,1)--(\x+1,2);
- \draw(\x+1.8,1)--(\x+1,2);
- \draw(\x+0.4,0)--(\x+0.4,1); 
- \draw(\x+0.8,0)--(\x+0.8,1); 
- \draw (\x+1.2,0)--(\x+1.2,1); 
- \draw(\x+1.6,0)--(\x+1.6,1);  
- \node at(\x+1,2.5){$T_2$};
- \node at(\x+0.2, 0.5){$\GdT$};
- \node at(\x+0.6, 0.5){$\cdot$};
- \node at(\x+1.0, 0.5){$\cdot$};
- \node at(\x+1.4, 0.5){$\cdot$};
- \node at(\x+1.8, 0.5){$\GdT$};
- %\node at(\x+1,0.5){$T_1 \cdot \GdT$}; 
- \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (\x+2,-0.2) -- (\x+0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ runs};
- }
-  \node at(5,4.5){$T -S(T_1 \cdot \GdT + T_2)$};
-  \node at (6,0.5){$\cdots$};
-  \node at (7,0.5){$\cdots$};
-  \node at (6,2.5){$\cdots$};
-  \node at (7,2.5){$\cdots$};
-  \node at(-1,0.5){\textbf{Level 1}};
-  \node at(-1,2.5){\textbf{Level 2}};
-  \node at(-1,4.5){\textbf{Levle 3}};
-  \draw[->] (11,0)--(11,5);
-  \node at(11.5,2.5)[ rotate=90]{Time};
-
-  \draw [decorate,decoration={brace,amplitude=10pt,aspect=0.33},xshift=0pt,yshift=0pt] (10,1.8) -- (0,1.8) node [black,pos=0.33,xshift = 0cm,yshift=-0.6cm] {$S$ groups};
-
-\end{tikzpicture}
-\caption{Structure of the information graph for the 3-level
-  Policy. Each red box in level 1 corresponds to $T_1$ \ALGG paths of
-  length $\GdT$. The sub-history of each red box is then aggregated and
-  sent to a corresponding purple box of agents in level 2. Then the
-  entire history of levels 1 and 2 is aggregated and shown to all
-  agents in level 3.}
-\label{fig:3level}
-\end{figure}
-% \swcomment{check the figure caption above. can we index the indicate
-%   there are $S$ groups in the figure?}
 

### 2018-11-01 3level.tex
Pushed a comment.
Switched notation a bit.

@@
  %\draw(\x+1.6,0)--(\x+1.6,1);
- \node at(\x+1,2.5){$N_2$ rounds};
+ \node at(\x+1,2.5){$T_2$ rounds};
  \node at(\x+0.33, 0.5){$\GdT$};
@@
 
-  \draw [decorate,decoration={brace,amplitude=10pt,aspect=0.33},xshift=0pt,yshift=0pt] (10,1.8) -- (0,1.8) node [black,pos=0.33,xshift = 0cm,yshift=-0.6cm] {$T_2$ groups};
+  \draw [decorate,decoration={brace,amplitude=10pt,aspect=0.33},xshift=0pt,yshift=0pt] (10,1.8) -- (0,1.8) node [black,pos=0.33,xshift = 0cm,yshift=-0.6cm] {$N_2$ groups};
 
@@
 The middle layer is what ensures adaptive exploration.
-It consists of $T_2$ disjoint subsets of $N_2$ agents each, called \emph{second-level groups}.
+It consists of $N_2$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}.
 Each second-level group $S$ has the following property:
@@
 
-The full-disclosure paths in the first level are also split into $T_2$ disjoint subsets, called \emph{first-level groups}.
-Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot T_2\cdot \fdpL$ rounds in the first layer.
+The full-disclosure paths in the first level are also split into $N_2$ disjoint subsets, called \emph{first-level groups}.
+Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot N_2\cdot \fdpL$ rounds in the first layer.
 There is a 1-1 correspondence between first-level groups $S_1$ and second-level groups $S_2$, whereby each agent $t\in S_2$ observes the full history from the corresponding group $S_1$.
@@
     $T_1 = T^{4/7}\log^{-1/7}(T)$,
-    $T_2 = 2^{10}\log(T)$, and
-    $N_2 = T^{6/7}\log^{-5/7}(T)$.
+    $N_2 = 2^{10}\log(T)$, and
+    $T_2 = T^{6/7}\log^{-5/7}(T)$.
 \end{theorem}

### 2018-11-01 llevel-overview.tex
expected regret -> regret

@@
 \label{thm:llevel-1}
-For any $L > 3$, we have an $L$-level recommendation policy with expected regret \\$O\left(T^{2^{L-1}/(2^L-1)} polylog(T) \right)$.
-In particular, we have an $O(\log\log(T))$-level recommendation policy with expected regret $O(T^{1/2} polylog(T))$.
+For any $L > 3$, we have an $L$-level recommendation policy with regret \\$O\left(T^{2^{L-1}/(2^L-1)} polylog(T) \right)$.
+In particular, we have an $O(\log\log(T))$-level recommendation policy with regret $O(T^{1/2} polylog(T))$.
 \end{theorem}
@@
 This policy has the same structure as the one in Theorem \ref{thm:llevel-1} but different parameters.
-Its expected regret depends on $\Delta$ which is the difference between the largest mean and second largest mean of arms and its construction does not depend on $\Delta$.
+Its regret depends on $\Delta$ which is the difference between the largest mean and second largest mean of arms and its construction does not depend on $\Delta$.
 Its regret bound outperforms the one in Theorem \ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$.
@@
 \label{thm:llevel-2}
- We have an $O(\log(T)/\log\log(T))$-level recommendation policy with expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$.
+ We have an $O(\log(T)/\log\log(T))$-level recommendation policy with regret \\$O(\min(1/\Delta, T^{1/2})polylog(T))$.
 Here $\Delta$ is the difference between the largest mean and second largest mean of arms.
@@
 Simply generalizing this idea to an $L$-level policy would give us a $S$-ary tree like structure and the first level will have $S^{L-1}$ groups.
-It incurs an extra $S^{\Omega(L)}$ factor in the expected regret.
+It incurs an extra $S^{\Omega(L)}$ factor in the regret.
 If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor super poly-logarithmic.
@@
 This connecting structure has three nice properties: \\
-(i) The number of groups does not grow with $L$ and stays as $S^2 = \Theta(\log^2(T))$ in each level.
-Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the expected regret.\\
+(i) The number of groups does not grow with $L$ and stays as $S^2 = \Theta(\log^2(T))$ in each level. Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\
 (ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,S,v}$ (e.g.

### 2018-11-01 llevel.tex
.
expected regret -> regret

@@
 
-\section{Missing Proofs of Section \ref{sec:llevel}}
+\section{Proofs of Section \ref{sec:llevel}}
 \label{sec:llevel-details}
@@
 \label{thm:llevel}
-The $L$-level recommendation policy gets expected regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(S^4))$.
-In particular, if we pick $L = \log(\ln(T)/\log(S^4))$, the expected regret is $O(T^{1/2} polylog(T))$.
+The $L$-level recommendation policy gets regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(S^4))$.
+In particular, if we pick $L = \log(\ln(T)/\log(S^4))$, the regret is $O(T^{1/2} polylog(T))$.
 \end{theorem}
@@
 $\bigcap_{i=1}^4 W_i$) happens with probability $1-O(1/T)$.
-When this intersection does not happen, since the probability is $O(1/T)$, it cost expected regret $O(1/T) \cdot T = O(1)$.
+When this intersection does not happen, since the probability is $O(1/T)$, it contributes $O(1/T) \cdot T = O(1)$ to the regret.
 
-Now we assume the intersection of clean events happens and prove upper bound on the expected regret.
+Now we assume the intersection of clean events happens and prove upper bound on the regret.
 
@@
 
-By Claim \ref{clm:l2_exploit}, we know that the expected regret conditioned the intersection of clean events is at most 
+By Claim \ref{clm:l2_exploit}, we know that the regret conditioned the intersection of clean events is at most 
 \begin{align*}
@@
 \label{cor:llevel}
-With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$.
+With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets regret $O(\min(1/\Delta, T^{1/2})polylog(T))$.
 Here $\Delta = |\mu_1 -\mu_2|$ and the $L$-level recommendation policy does not need to know $\Delta$.
@@
 On the other hand, $T^{1/2} = O(polylog(T)/\Delta)$.
-Therefore, the expected regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
+Therefore, the regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
 \item $\Delta \geq \varepsilon_{L-1} S$.
 In this case, we can find $l \in \{2,...,L\}$ such that $\varepsilon_{l-1} S\leq \Delta < \varepsilon_{l-2} S$.
-By Claim \ref{clm:l2_exploit}, we can upper bound the expected regret by
+By Claim \ref{clm:l2_exploit}, we can upper bound the regret by
 \begin{align*}
@@
 \end{align*}
-We also have $1/\Delta \leq 1/(\varepsilon_{L-1}S)= O(T^{1/2})$. Therefore, the expected regret is \\$O(\min(1/\Delta, T^{1/2})polylog(T))$.
+We also have $1/\Delta \leq 1/(\varepsilon_{L-1}S)= O(T^{1/2})$. Therefore, the regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
 \end{itemize}
@@
 Since $K$ is a constant, it's easy to check that the same proof technique shows that the intersection of these clean events happen with probability  $1-O(1/T)$.
-So the case when some clean event does not happen contributes $O(1)$ to the expected regret.
+So the case when some clean event does not happen contributes $O(1)$ to the regret.
 
@@
 
-Finally we proceed to bound the expected regret conditioned on the intersection of clean events happens.
+Finally we proceed to bound the regret conditioned on the intersection of clean events happens.
 The proofs of Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel} bound it by consider the regret from pulling the suboptimal arm (i.e.
@@
 When extending to more than 2 arms, we can do the exactly same argument for all arms except arm 1.
-This will blow up the expected regret by a factor of $(K-1)$ which is a constant.
+This will blow up the regret by a factor of $(K-1)$ which is a constant.
 \qed

### 2018-11-01 llevel-overview.tex
O ---> O_K

@@
 In Theorem \ref{thm:llevel-1}, we show our $L$-level policy.
-We can achieve nearly optimal regret $O(T^{1/2} polylog(T))$ with $O(\log\log(T))$ levels.
+We can achieve nearly optimal regret $O_K(T^{1/2} polylog(T))$ with $O(\log\log(T))$ levels.
 \begin{theorem}
 \label{thm:llevel-1}
-For any $L > 3$, we have an $L$-level recommendation policy with regret \\$O\left(T^{2^{L-1}/(2^L-1)} polylog(T) \right)$.
-In particular, we have an $O(\log\log(T))$-level recommendation policy with regret $O(T^{1/2} polylog(T))$.
+For any $L > 3$, we have an $L$-level recommendation policy with regret \\$O_K\left(T^{2^{L-1}/(2^L-1)} polylog(T) \right)$.
+In particular, we have an $O(\log\log(T))$-level recommendation policy with regret $O_K(T^{1/2} polylog(T))$.
 \end{theorem}
@@
 \label{thm:llevel-2}
- We have an $O(\log(T)/\log\log(T))$-level recommendation policy with regret \\$O(\min(1/\Delta, T^{1/2})polylog(T))$.
+ We have an $O(\log(T)/\log\log(T))$-level recommendation policy with regret \\$O_K(\min(1/\Delta, T^{1/2})polylog(T))$.
 Here $\Delta$ is the difference between the largest mean and second largest mean of arms.

### 2018-11-02 model.tex
some comments
Minor edit.

@@
 
-We allow a much more permissive model, characterized by the following assumption:%
-\footnote{In what follows, we make this assumption without further notice.}
+We allow a much more permissive model that allows each agent to form arbitrary reward estimates as long as they lie within some ``confidence range" of the sample average.
+Formally, the model is characterized by the following assumption (which we make without further notice).
 

### 2018-11-02 model.tex
add a citation

--- 2018-11-01 model.tex
@@
 \label{sec:model}
+\cite{Perchet2015BatchedBP} gives regret guarantees for mult-armed bandit in $M$ batches. They have 2 upper bounds which are similar to our Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2}.
+
 We study the multi-armed bandit problem in a social learning context, in which a principal faces a sequence of $T$ myopic agents.
@@
 
+\jmcomment{Should we emphasize heterogeneity here?}
 %If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.

### 2018-11-02 2level.tex
Small edit.
some comments

@@
 The \2LEVEL with parameter $T_1 = T^{2/3}\,\log(T)^{1/3}$ achieves regret
-\[ \reg(T) \leq O_K\left( T^{2/3}\, \log(T)^{1/3} \right).\]
+\[ \reg(T) \leq O_K\left( T^{2/3}\, (\log T)^{1/3} \right).\]
 \end{theorem}
@@
     $\left\{\; (a_s,r_s):\;s\in S_t \;\right\}$,
-called \emph{anonymized subhistory}. Each agent forms its estimates according to the same \emph{estimate function}: a function $f$ from subhistories to $[0,1]^K$, so that the estimate vector
+called \emph{anonymized subhistory}. Each agent $t$ forms its estimates according to the same \emph{estimate function}: a function $f_t$ from subhistories to $[0,1]^K$, so that the estimate vector
         $(\hat{\mu}_{t,a}:\, a\in\A)$
-equals $f(m_t)$.
+equals $f_t(m_t)$. This function is drawn from some fixed distribution over estimate functions.
 \end{assumption}

### 2018-11-02 model.tex

@@
 
-We allow a much more permissive model, characterized by the following assumption:%
-\footnote{In what follows, we make this assumption without further notice.}
+We allow a much more permissive model that allows each agent to form arbitrary reward estimates as long as they lie within some ``confidence range" of the sample average.
+Formally, the model is characterized by the following assumption (which we make without further notice).
 
-\jmcomment{Should we emphasize heterogeneity here?}
 %If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.

### 2018-11-02 3level.tex
Moved the figure.
expected regret -> regret
Revised the "intro" of 3level section.

@@
 For simplicity, we assume $K=2$ arms.
+
+For the sake of intuition, consider the framework of bandit algorithms with limited adaptivity.
+Suppose a bandit algorithm outputs a distribution $p_t$ over arms in each round $t$, and the arm $a_t$ is then drawn independently from $p_t$.
+This distribution can change only in a small number of rounds, called \emph{adaptivity rounds}, that need to be chosen by the algorithm in advance.
+A single round of adaptivity corresponds to explore-then-exploit paradigm.
+Our goal here is to implement one extra adaptivity round, and this is what the middle level accomplishes.
+
+\begin{construction}
+The \emph{three-level policy} is defined as follows.
+The info-graph consists of three levels: the first two correspond to \emph{exploration}, and the third implements \emph{exploitation}.
+Like in the two-level policy, the first level consists of multiple full-disclosure paths of length $\fdpL$ each, and each agent $t$ in the exploitation level sees full history from exploration  (see Figure~\ref{fig:3level}).
+
+The middle level consists of $N_2$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}. Each second-level group $S$ has the following property:
+\begin{align}\label{eq:group-defn}
+\text{all nodes in $S$ are connected to the same nodes outside of $S$, but not to one another.}
+\end{align}
+
+The full-disclosure paths in the first level are also split into $N_2$ disjoint subsets, called \emph{first-level groups}.
+Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot N_2\cdot \fdpL$ rounds in the first layer.
+There is a 1-1 correspondence between first-level groups $S_1$ and second-level groups $S_2$, whereby each agent $t\in S_2$ observes the full history from the corresponding group $S_1$.
+More formally, agent $t$ is connected to the last node of each full-disclosure path in $S_1$.
+In other words, this agent receives message
+    $m_t = \SubH{V(S_1)}$,
+where $V(S_1)$ is the set of all rounds in $S_1$.
+\end{construction}
 
@@
 
-The new policy, called the \emph{three-level policy}, is as follows
- (see Figure~\ref{fig:3level}).
-
-\begin{construction}
-The info-graph consists of three levels: the first two correspond to \emph{exploration}, and the third implements \emph{exploitation}.
-Like in the two-level policy, the first level consists of multiple full-disclosure paths of length $\fdpL$ each, and each agent $t$ in the exploitation level sees full history from exploration.
-The middle layer is what ensures adaptive exploration.
-It consists of $N_2$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}.
-Each second-level group $S$ has the following property:
-\begin{align}\label{eq:group-defn}
-\text{all nodes in $S$ are connected to the same nodes outside of $S$, but not to one another.}
-\end{align}
-
-The full-disclosure paths in the first level are also split into $N_2$ disjoint subsets, called \emph{first-level groups}.
-Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot N_2\cdot \fdpL$ rounds in the first layer.
-There is a 1-1 correspondence between first-level groups $S_1$ and second-level groups $S_2$, whereby each agent $t\in S_2$ observes the full history from the corresponding group $S_1$.
-More formally, agent $t$ is connected to the last node of each full-disclosure path in $S_1$.
-In other words, this agent receives message
-    $m_t = \SubH{V(S_1)}$,
-where $V(S_1)$ is the set of all rounds in $S_1$. 
-\end{construction}
+The key idea is as follows.
+Consider the gap parameter $\Delta = |\mu_1-\mu_2|$.
+If it is is large, then each first-level group produces enough data to determine the best arm with high confidence, and so each agent in the upper levels chooses the best arm.
+If $\Delta$ is small, then due to \emph{anti-concentration} each arm can get ``lucky" within any given first-level group and appear much better to the corresponding second-level group (and therefore get explored within that group).
+To summarize, the middle level exploits if the gap parameter is large, and explores if it is small.
 
@@
 
-\ascomment{stopped here.}
-
-They main idea for the 3-level policy is that it inserts the second level as an additional ``checkpoint'' to induce more adaptivity in the exploration.
-\niedit{While the first level ensures that the agents explore both arms, the better arm can only be discovered if the gap in their rewards $|\mu_1-\mu_2|$ is sufficiently high.
-When this gap is small (that is, when $|\mu_1 - \mu_2| < \tilde{O}(1/\sqrt{T_1})$), we argue that the second level will continue to explore both arms.
-Here we use the anti-concentration bound to show each arm is ``lucky'' in at least one first level group (that is, for some first level group, its empirical mean is significantly larger than its mean whereas the other arm's empirical mean is significantly smaller than its mean).
-Therefore, the corresponding second level group will explore the lucky arm, giving the third level refined estimates of each arm's mean.}  In the third level, agents will pull the best arm unless $|\mu_1-\mu_2|$ is much smaller than $\tilde{O}(1/\sqrt{T_2})$, in which case pulling either arm will
-incur small regret. The formal guarantee of the policy is the
-following. \nicomment{I'm a little confused why this works while simply growing the first level doesn't work; wouldn't the first level where the arm is ``lucky'' explore it more if it had more time?}
+\ascomment{Stopped here.}
 
@@
 events.  By union bound, $W$ occurs with probability $1-O(1/T)$. Note
-that expected regret conditioned on $W$ not occuring is at most
+that the regret conditioned on $W$ not occurring is at most
 $O(1/T) \cdot T = O(1)$, so it suffices to bound the regret conditioned on $W$.

### 2018-11-02 model.tex
Defined reward tape in prelims.

@@
 
+\asedit{We use the notion of \emph{reward tape} to simplify the application of (anti-)concentration inequalities.
+This is a $K\times T$ random matrix with rows and columns corresponding to arms and rounds, respectively.
+For each arm $a$ and round $t$, the value in cell $(a,t)$ is drawn independently from Bernoulli distribution $\mD_a$.
+W.l.o.g., rewards in our model are defined by the rewards tape: namely, the reward for the $j$-th pull of arm $a$ is taken from the $(a,j)$-th entry of the reward matrix.}
+
 We use $O_K(\cdot)$ notation to hide the dependence on parameter $K$, and $\tilde O(\cdot)$ notation to hide polylogarithmic factors. We denote $[T]= \{1,2 \LDOTS T\}$.

### 2018-11-02 llevel-overview.tex
ll

@@
 
-\section{$L$-level Recommendation Policy}
+\section{$\tilde O(T)$ Regret with $L$-Level Policy}
 \label{sec:llevel}
@@
 In Theorem \ref{thm:llevel-1}, we show our $L$-level policy.
-We can achieve nearly optimal regret $O_K(T^{1/2} polylog(T))$ with $O(\log\log(T))$ levels.
+We can achieve nearly optimal regret $O_K(T^{1/2} \polylog(T))$ with $O(\log\log(T))$ levels.
 \begin{theorem}
 \label{thm:llevel-1}
-For any $L > 3$, we have an $L$-level recommendation policy with regret \\$O_K\left(T^{2^{L-1}/(2^L-1)} polylog(T) \right)$.
-In particular, we have an $O(\log\log(T))$-level recommendation policy with regret $O_K(T^{1/2} polylog(T))$.
+For any $L > 3$, we have an $L$-level recommendation policy with regret \\$O_K\left(T^{2^{L-1}/(2^L-1)} \polylog(T) \right)$.
+In particular, we have an $O(\log\log(T))$-level recommendation policy with regret $O_K(T^{1/2} \polylog(T))$.
 \end{theorem}
@@
 The recommendation policy does not depend on $\Delta$.
-Moreover, agent in round $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$.
+Moreover, agent in round $t$ observes a subhistory of size at least $\Omega( \lfloor t/\polylog(T)\rfloor)$.
 \end{theorem}
@@
 When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm.
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2018-11-02 3levelproofs.tex
ct,cm->N0,C0
Added a section label.
Moved stuff from the 3level section.

@@
 \section{Missing proofs from Section~\ref{sec:3level}}
+\label{sec:3level-pfs}
+
+\ascomment{I copied this from the 3-level section. This needs to be revised and made consistent, etc.}
+
+The following lemma can be derived from combining Lemma~\ref{lem:t1runs} and union bound.
+
+\begin{lemma}[Concentration of first-level number of pulls.]\label{3levelw1}
+  Let $W_1$ be the event that for all groups $s\in [S]$ and arms
+  $a\in \{1, 2\}$, the number of arm $a$ pulls in the $s$-th
+  first-level group is in the range of
+  $$
+  \left[\fdpN  T_1- \GdT \sqrt{T_1\log(T)}, \fdpN  T_1 + \GdT \sqrt{T_1\log(T)}\right],
+  $$
+  where $\fdpN $ is the expected number of arm $a$ pulls in a $\ALGG$ run
+  of length $\GdT$. Then $\Pr[W_1] \geq 1- \frac{4S}{T^2}$.
+\end{lemma}
+
+To state the events, it will be useful to think of a
+hypothetical reward tape $\cT^1_{s, a}$ of length $T$ for each
+group $s$ and arm $a$, with each cell independently sampled from
+$\cD_a$.  The tape encodes rewards as follows: the $j$-th time arm $a$
+is chosen by the group $s$ in the first level, its reward is taken
+from the $j$-th cell in this arm's tape. The following result
+characterizes the concentration of the mean rewards among all
+consecutive pulls among all such tapes, which follows from Chernoff
+bound and union bound.
+
+\begin{lemma}[Concentration of empirical means in the first level]\label{3levelw2}
+  For any $t_1, t_2\in [T]$ such that $t_1 < t_2$, $s\in [S]$, and
+  $a\in \{1,2\}$, let $W_2^{s,a,t_1,t_2}$ be the event that the mean
+  among the cells indexed by $t_1, (t_1+1), \ldots, t_2$ in the tape
+  $\cT^1_{a, s}$ is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away
+  from $\mu_a$.  Let $W_2$ be the intersection of all these events
+  (i.e.  $W_2 = \bigcap_{a,s,t_1,t_2} W_2^{s,a,t_1,t_2}$). Then
+  \[
+    \Pr[W_2] \geq 1- \frac{4S}{T^2}.
+  \]
+\end{lemma}
+
+Our policy also relies on the anti-concentration of the empirical
+means in the first round. We show that for each arm $a\in \{1, 2\}$,
+there exists a group $s_a$ such that the empirical mean of $a$ is
+slightly above $\mu_a$, while the other arm $(3 - a)$ has empirical
+mean slightly below $\mu_{(3-a)}$. This event is crucial for inducing
+agents in the second level to explore both arms when the their
+mean rewards are indistinguishable after the first level.
+
+\begin{lemma}[Co-occurence of high and low deviations]\label{3levelw4}
+  For any group $s\in [S]$, any arm $a$, let $\tilde\mu_{a,s}$ be the
+  empirical mean of the first $\fdpN  T_1$ cells in tape $\cT^1_{a, s}$.
+  Let $W_4^{s,a,\text{high}}$ be the event
+  $\tilde\mu_{a, s} \geq \mu_a + 1/\sqrt{\fdpN  T_1}$ and let
+  $W_4^{s,a,\text{low}}$ be the event that
+  $\tilde\mu_{a, s} \leq \mu_a - 1/\sqrt{\fdpN  T_1}$.  Let $W_4$ be the
+  event that for every $a\in \{1, 2\}$, there exists a group
+  $s_a\in [S]$ in the first level such that both $W_4^{s_a,a,\text{high}}$
+  and $W_4^{s_a,3-a,\text{low}}$ occur. Then
+  \[
+    \Pr[W_4]\geq 1 -2 /T.
+  \]
+\end{lemma}
+
+Lastly, we will condition on the event that the empirical means of
+both arms are concentrated around their true means in any prefix of
+their pulls. This guarantees that the policy obtains an accurate
+estimate of rewards for both arms after aggregating all the data in
+the first two levels.
+% We will again state the event using a hypothetical reward tape
+% $\cT^2_a$ for each arm $a$: the $j$-th time arm $a$ is chosen in the
+% two levels, its reward is taken from the $j$-th cell in $\cT^2_a$.
+
+\swcomment{might want to swap out $W_3$ and $W_4$} \nicomment{yes please!}
+
+\begin{lemma}[Concentration of empirical means in the first two
+  levels]\label{3levelw3}
+  With probability at least $1 - \frac{4}{T^3}$, the following event
+  $W_3$ holds: for all $a\in \{1, 2\}$ and $m \in [N_{T, a}]$, the
+  empirical means of the first $t$ \nicomment{what is $t$ here; you mean $m$? in which case please replace $m$ with $t$ in the conditioning and bound} arm $a$ pulls is at most
+  $\sqrt{\frac{2\log(T)}{m}}$ away from $\mu_a$, where $N_{T, a}$ is
+  the total number of arm $a$ pulls by the end of $T$ rounds.
+\end{lemma}
+
+Let $W = \bigcap_{i=1}^4 W_i$ be the intersection of all 4
+events.  By union bound, $W$ occurs with probability $1-O(1/T)$. Note
+that the regret conditioned on $W$ not occurring is at most
+$O(1/T) \cdot T = O(1)$, so it suffices to bound the regret conditioned on $W$.
+
+\ascomment{end of copy-and-paste}
 
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} - \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}}\\
-&\geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}- \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}} > 0
+\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} - \frac{C_0}{\sqrt{\fdpN[1]T_1/2}} - \frac{C_0}{\sqrt{\fdpN[2]T_1/2}}\\
+&\geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}- \frac{C_0}{\sqrt{\fdpN[1]T_1/2}} - \frac{C_0}{\sqrt{\fdpN[2]T_1/2}} > 0
 \end{align*}
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
-&\geq  \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}- \frac{c_m}{\sqrt{S\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{S\fdpN[2]T_1/2}}\\
+\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} - \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
+&\geq  \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}- \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} - \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
  &> 0.
@@
 \begin{align*}
-\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}}\\
-&\geq   \frac{1}{8\sqrt{\fdpN[1]T_1}}+ \frac{1}{8\sqrt{\fdpN[2]T_1}}- \frac{c_m}{\sqrt{\fdpN[1]T_1/2}} - \frac{c_m}{\sqrt{\fdpN[2]T_1/2}}\\
+\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{C_0}{\sqrt{\fdpN[1]T_1/2}} - \frac{C_0}{\sqrt{\fdpN[2]T_1/2}}\\
+&\geq   \frac{1}{8\sqrt{\fdpN[1]T_1}}+ \frac{1}{8\sqrt{\fdpN[2]T_1}}- \frac{C_0}{\sqrt{\fdpN[1]T_1/2}} - \frac{C_0}{\sqrt{\fdpN[2]T_1/2}}\\
  &> 0.

### 2018-11-02 3level.tex
Done with 3level revision.

@@
 If it is is large, then each first-level group produces enough data to determine the best arm with high confidence, and so each agent in the upper levels chooses the best arm.
-If $\Delta$ is small, then due to \emph{anti-concentration} each arm can get ``lucky" within any given first-level group and appear much better to the corresponding second-level group (and therefore get explored within that group).
-To summarize, the middle level exploits if the gap parameter is large, and explores if it is small.
+If $\Delta$ is small, then due to \emph{anti-concentration} each arm gets ``lucky" within  at least once first-level group, in the sense that it appears much better than the other arm based on the data collected in this group (and therefore this arm gets explored by the corresponding second-level group).
+To summarize, the middle level exploits if the gap parameter is large, and provides some more exploration if it is small.
 
@@
 
-\ascomment{Stopped here.}
+Let us sketch the proof of this theorem; the full proof can be found in Appendix~\ref{sec:3level-pfs}.
 
-\iffalse
-In the proof, we need not only the concentration argument as the
-2-level recommendation policy, but also the anti-concentration
-argument to show that agents explore more in the second round if
-$\mu_1-\mu_2$ is not too big.
+\xhdr{The ``good events".}
+We establish four ``good events" each of which occurs with high probability.
+\begin{description}
+\item[(\event{1})] \emph{Exploration in Level 1:} Every first-level group collects at least $\Omega(T_1)$ samples of each arm.
+\item[(\event{2})] \emph{Concentration in Level 1:} Within each first-level group, empirical mean rewards of each arm $a$ concentrate around $\mu_a$.
+\item[(\event{3})] \emph{Anti-concentration in Level 1:} For each arm, some first-level subgroup collects data which makes this arm look much better than the other.
+\item[(\event{4})] \emph{Concentration in prefix:}
+The empirical mean reward of each arm $a$ concentrates around $\mu_a$ in any prefix of its pulls. (This ensures accurate reward estimates in exploitation.)
+\end{description}
 
-Set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 =
-T^{6/7}\log^{-5/7}(T)$. The first level has $S = 2^{10}\log(T)$ groups
-of agents. Each group runs $T_1$ \ALGG of $T_G$ rounds in
-parallel. The second level also has $S$ groups of agents. Each group
-has $T_2$ agents and they observe the history of corresponding group
-in the first level. All the rest agents are in the third level and
-they observe the entire history of the first two levels.  See also
-Figure \ref{fig:3level} for a graphical view of the information flow.
+The analysis of these events applies Chernoff Bounds to a suitable version of ``reward tape" (see the definition of ``reward tape" in Section~\ref{sec:model}).
+For example, \event{2} considers a reward tape restricted to a given first-level group.
 
-Here we give some intuition about how the 3-level recommendation
-policy works. The main idea is to do the exploration more
-adaptively. In the first level, agents explore both arms. In the
-second level, agents will pull the best arm when $\mu_1 - \mu_2$ is
-large ($\tilde{\Omega}(1/\sqrt{T_1})$). Otherwise agents will explore
-both arms more. In the third level, agents will pull the best arm
-unless $\mu_1-\mu_2$ is much smaller ($\tilde{O}(1/\sqrt{T_2})$). In
-the proof, we need not only the concentration argument as the 2-level
-recommendation policy, but also the anti-concentration argument to
-show that agents explore more in the second round if $\mu_1-\mu_2$ is
-not too big.
-\fi
+\xhdr{Case analysis.}
+We now proceed to bound the regret conditioned on the four ``good events".
+W.l.o.g., assume $\mu_1 \geq \mu_2$.
+We break down the regret analysis into four cases, based on the magnitude the gap parameter $\Delta = \mu_1-\mu_2$.
+As a shorthand, denote
+    $\conf{n} = \sqrt{\log(T)/n}$.
+In words, this is a confidence term, up to constant factors, for $n$ independent random samples.
 
-\subsection{Events}
-We will first establish four events that together occur
-with probability at least $1 - O(1/T)$. The first event says that
-every group of \ALGG runs in the first level ensures that each arm $a$
-is pulled at least $\Omega(T_1)$ times. The following lemma can
-derived from combining Lemma~\ref{lem:t1runs} and union bound.
+The simplest case is very small gap, which trivially yields an upper bound on regret.
 
-\begin{lemma}[Concentration of first-level number of pulls.]\label{3levelw1}
-  Let $W_1$ be the event that for all groups $s\in [S]$ and arms
-  $a\in \{1, 2\}$, the number of arm $a$ pulls in the $s$-th
-  first-level group is in the range of
-  $$
-  \left[\fdpN  T_1- \GdT \sqrt{T_1\log(T)}, \fdpN  T_1 + \GdT \sqrt{T_1\log(T)}\right],
-  $$
-  where $\fdpN $ is the expected number of arm $a$ pulls in a $\ALGG$ run
-  of length $\GdT$. Then $\Pr[W_1] \geq 1- \frac{4S}{T^2}$.
-\end{lemma}
-
-The next two events are about the distribution of the mean rewards in
-the first level. To state the events, it will be useful to think of a
-hypothetical reward tape $\cT^1_{s, a}$ of length $T$ for each
-group $s$ and arm $a$, with each cell independently sampled from
-$\cD_a$.  The tape encodes rewards as follows: the $j$-th time arm $a$
-is chosen by the group $s$ in the first level, its reward is taken
-from the $j$-th cell in this arm's tape. The following result
-characterizes the concentration of the mean rewards among all
-consecutive pulls among all such tapes, which follows from Chernoff
-bound and union bound.
-
-\begin{lemma}[Concentration of empirical means in the first level]\label{3levelw2}
-  For any $t_1, t_2\in [T]$ such that $t_1 < t_2$, $s\in [S]$, and
-  $a\in \{1,2\}$, let $W_2^{s,a,t_1,t_2}$ be the event that the mean
-  among the cells indexed by $t_1, (t_1+1), \ldots, t_2$ in the tape
-  $\cT^1_{a, s}$ is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away
-  from $\mu_a$.  Let $W_2$ be the intersection of all these events
-  (i.e.  $W_2 = \bigcap_{a,s,t_1,t_2} W_2^{s,a,t_1,t_2}$). Then
-  \[
-    \Pr[W_2] \geq 1- \frac{4S}{T^2}.
-  \]
-\end{lemma}
-
-Our policy also relies on the anti-concentration of the empirical
-means in the first round. We show that for each arm $a\in \{1, 2\}$,
-there exists a group $s_a$ such that the empirical mean of $a$ is
-slightly above $\mu_a$, while the other arm $(3 - a)$ has empirical
-mean slightly below $\mu_{(3-a)}$. This event is crucial for inducing
-agents in the second level to explore both arms when the their
-mean rewards are indistinguishable after the first level.
-
-\begin{lemma}[Co-occurence of high and low deviations]\label{3levelw4}
-  For any group $s\in [S]$, any arm $a$, let $\tilde\mu_{a,s}$ be the
-  empirical mean of the first $\fdpN  T_1$ cells in tape $\cT^1_{a, s}$.
-  Let $W_4^{s,a,\text{high}}$ be the event
-  $\tilde\mu_{a, s} \geq \mu_a + 1/\sqrt{\fdpN  T_1}$ and let
-  $W_4^{s,a,\text{low}}$ be the event that
-  $\tilde\mu_{a, s} \leq \mu_a - 1/\sqrt{\fdpN  T_1}$.  Let $W_4$ be the
-  event that for every $a\in \{1, 2\}$, there exists a group
-  $s_a\in [S]$ in the first level such that both $W_4^{s_a,a,\text{high}}$
-  and $W_4^{s_a,3-a,\text{low}}$ occur. Then
-  \[
-    \Pr[W_4]\geq 1 -2 /T.
-  \]
-\end{lemma}
-
-Lastly, we will condition on the event that the empirical means of
-both arms are concentrated around their true means in any prefix of
-their pulls. This guarantees that the policy obtains an accurate
-estimate of rewards for both arms after aggregating all the data in
-the first two levels.
-% We will again state the event using a hypothetical reward tape
-% $\cT^2_a$ for each arm $a$: the $j$-th time arm $a$ is chosen in the
-% two levels, its reward is taken from the $j$-th cell in $\cT^2_a$.
-
-\swcomment{might want to swap out $W_3$ and $W_4$} \nicomment{yes please!}
-
-\begin{lemma}[Concentration of empirical means in the first two
-  levels]\label{3levelw3}
-  With probability at least $1 - \frac{4}{T^3}$, the following event
-  $W_3$ holds: for all $a\in \{1, 2\}$ and $m \in [N_{T, a}]$, the
-  empirical means of the first $t$ \nicomment{what is $t$ here; you mean $m$? in which case please replace $m$ with $t$ in the conditioning and bound} arm $a$ pulls is at most
-  $\sqrt{\frac{2\log(T)}{m}}$ away from $\mu_a$, where $N_{T, a}$ is
-  the total number of arm $a$ pulls by the end of $T$ rounds.
-\end{lemma}
-
-Let $W = \bigcap_{i=1}^4 W_i$ be the intersection of all 4
-events.  By union bound, $W$ occurs with probability $1-O(1/T)$. Note
-that the regret conditioned on $W$ not occurring is at most
-$O(1/T) \cdot T = O(1)$, so it suffices to bound the regret conditioned on $W$.
-
-\subsection{Case Analysis}
-
-We now proceed to bound the regret conditioned on the four
-events defined above. Without loss of generality, we assume
-$\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both
-arms. We break down the regret analysis into four cases on the scale
-of the gap parameter $\Delta = (\mu_1-\mu_2)$.
-
-We will start with the simplest case where the gap is smaller than
-$\tilde O(\sqrt{1/T_2}) = \tilde O(1/T^{3/7})$, then the regret is
-trivially bounded by $\tilde O(T^{4/7})$.
-
-\begin{claim}[Negligible gap case]
-  Suppose $\Delta \leq 3\sqrt{\frac{2\log(T)}{T_2}}$,
+\begin{claim}[Negligible gap]
+If
+%  $\Delta \leq 3\sqrt{\frac{2\log(T)}{T_2}}$,
+    $\Delta \leq 3\sqrt{2}\cdot  \conf{T_2}$
+then 
   $\reg(T)\leq O(T^{4/7} \log^{6/7}(T))$.
@@
 Another simple case is when $\Delta$ is sufficiently large, so that
-the data collected in any single first-level group can distinguish the
-two arms. The proof essentially follows from the event $W_1$
-that both arms are explored sufficient many times in level 1, and the
-empirical rewards in the first two levels concentrate around their
-true means.
+the data collected in any first-level group suffices to determine the best arm. The proof follows from \event{1} and \event{2}.
 
-\begin{lemma}[Large gap case]\label{3levelbigcase}
-  Suppose
-  $\Delta \geq 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
-    \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right)$, then all agents in the
-  second and third levels pull arm 1.
+\begin{lemma}[Large gap]\label{3levelbigcase}
+If
+% $\Delta \geq 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
+%  \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right)$, 
+  $ \Delta \geq 4 \sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}$
+then all agents in Levels 2 and 3 pull arm 1.
 \end{lemma}
 
-There are two more intermediate cases. In the \emph{medium gap} case,
-the gap is smaller than $\tilde O(\sqrt{1/T_1})$, but bigger than
-$\tilde \Omega(\sqrt{1/(S\, T_1)})$. Then the data collected in any
-single group from the first level no longer suffices to distinguish
-the two arms. However, we show that as the policy aggregates the
-history from all $S$ groups at the end of the second level, the data
-will enable all third-level agents to correctly identify the arm 1 as
-the better arm (even though one of the arms may not be pulled at all
-in the second level).
+In the \emph{medium gap} case, the data collected in a given first-level group is no longer guaranteed to determine the best arm.
+However, the data collected by the second-level groups enables all agents in the third level to correctly identify the best arm.
 
-\begin{lemma}[Medium gap case]\label{3levelmedium}
+%(even though one of the arms may not be pulled at all in the second level).
+
+\begin{lemma}[Medium gap]\label{3levelmedium}
   All agents pull arm 1 in the third level, when $\Delta$ satisfies
-  \[
-  \Delta\in \left[
-   2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} +
-    \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right),
- 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
-        \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right),
+%  \[
+%  \Delta\in \left[
+%   2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} +
+%    \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right),
+% 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
+%        \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right),
+%    \right)
+%  \]
+\[ \textstyle \Delta\in \left[
+    4\,\sum_{a\in\A}\; \conf{N_2\cdot \fdpN[a]\cdot T_1},\quad
+    4\,\sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}
+ \right] \]
+\end{lemma}
+
+Finally, the \emph{small gap} case, when  $\Delta$ is between
+$\tilde\Omega(\sqrt{1/T_2})$ and $\tilde O(\sqrt{1/(N_2\, T_1)})$ 
+is more challenging since even aggregating the data from all $N_2$
+first-level groups is not sufficient for identify the best arm. 
+We need to ensure that both arms continue to be explored in the second level. 
+To achieve this, we leverage \event[4], which implies 
+that each arm $a$ has a first-level group $s_a$ where it gets ``lucky", in the sense that its empirical mean reward is slightly higher than $\mu_a$, while the empirical mean reward of the other arm is slightly lower than its true mean.
+Since the
+deviations are in the order of $\Omega(\sqrt{1/T_1})$, and Assumption~\ref{ass:embehave} guarantees the agents' reward estimates are also within $\Omega(\sqrt{1/T_1})$ of the empirical means, the sub-history
+from this group $s_a$ ensures that all agents in the respective second-level group prefer arm $a$.
+Therefore, both arms are pulled at least $T_2$ times in the second level, which in turn gives the following guarantee:
+
+\begin{lemma}[Small gap]\label{3levelsmallcase}
+  All agents pull arm 1 in the third level, when $\Delta$ satisfies
+%  \[
+%    \Delta\in \left( 3\sqrt{\frac{2\log(T)}{T_2}},
+%      2\left(\sqrt{\frac{4\log(T)}{S \fdpN[1]T_1}} +
+%        \sqrt{\frac{4\log(T)}{S \fdpN[2]T_1}}\right) \right)
+%  \]
+\[ \textstyle 
+    \Delta\in \left( 3\sqrt{2}\cdot\conf{T_2},\quad
+      4\,\sum_{a\in\A}\; \conf{N_2\cdot \fdpN[a]\cdot T_1}
 \right)
@@
 
-Finally, consider the \emph{small gap} case where $\Delta$ is between
-$\tilde\Omega(\sqrt{1/T_2})$ and $\tilde O(\sqrt{1/(S T_1))})$. This
-is more challenging since even aggregating the data from all $S$
-groups in the first level is not sufficient for correctly
-distinguishing the two arms. Thus, we need to ensure that both arms
-will continue to be pulled in the second level. To achieve this, we
-will nicely leverage the event of $W_4$, which has the implication
-that each arm $a$ has a ``lucky'' group $s_a$ in the first level,
-for which its empirical mean is slightly higher than $\mu_a$, while
-the other arm is slightly lower than $\mu_{(3-a)}$. Since the
-deviations are in the order of $\Omega(\sqrt{1/T_1})$, and Assumption~\ref{ass:embehave} guarantees the estimates are also within $\Omega(\sqrt{1/T_1})$ of the empirical means, the sub-history
-from this ``lucky'' group will yield estimates such that
-$\hat \mu_a^t > \hat \mu_{(3-a)}^t$, and so any second-level agent in
-group $s_a$ will pull arm $a$.  As a result, we guarantee both arms
-will be pulled at least $T_2$ times in the second level, which in turn
-gives the following guarantee.
-
-\begin{lemma}[Small gap case]\label{3levelsmallcase}
-  All agents pull arm 1 in the third level, when $\Delta$ satisfies
-  \[
-    \Delta\in \left( 3\sqrt{\frac{2\log(T)}{T_2}},
-      2\left(\sqrt{\frac{4\log(T)}{S \fdpN[1]T_1}} +
-        \sqrt{\frac{4\log(T)}{S \fdpN[2]T_1}}\right) \right)
-  \]
-\end{lemma}
-
 \paragraph{Wrapping up: proof of \Cref{thm:3level}. } In negligible
-gap case, the stated regret bound holds regardless of the sequence of
-chosen arms. In the large gap case, the regret only comes from the
-first level, which is bounded
-by $S \GdT T_1 = O(T^{4/7} \log^{6/7}(T))$. In the intermediate cases of
-both medium and small gaps, it suffices to bound the regret from the
+gap case, the stated regret bound holds regardless of what the algorithm does. In the large gap case, the regret only comes from the
+first level, so it is upper-bounded by the total number of agents in this level, which is 
+    $N_2\cdot \GdT \cdot T_1 = O(T^{4/7} \log T)$. 
+In both intermediate cases, it suffices to bound the regret from the
 first and second levels, so
-\[
-\reg(T) \leq (S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}}
-+ \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right) = O(T^{4/7} \log^{6/7}(T)).
+\[ \textstyle 
+\reg(T) \leq (N_2\,T_1\cdot \GdT + N_2\, T_2) 
+\cdot 4\,\sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}
+= O(T^{4/7} \log^{6/7}(T)).
 \]

### 2018-11-02 llevel-overview.tex
ll

@@
 
-\section{$\tilde O(T)$ Regret with $L$-Level Policy}
+\section{$\tilde O(\sqrt{T})$ regret with $L$-level policy}
 \label{sec:llevel}
-In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ in order to achieve better regret.
-In Theorem \ref{thm:llevel-1}, we show our $L$-level policy.
-We can achieve nearly optimal regret $O_K(T^{1/2} \polylog(T))$ with $O(\log\log(T))$ levels.
+In this section, we give an overview of how we extend our three-level
+policy to an $L$-level policy for $L > 3$ in order to achieve a regret
+rate of $O_K(\sqrt{T} \polylog(T))$. We provide two such policies. The
+first policy achieves the root-$T$ regret rate with $O(\log \log T)$
+levels.
+
+% In Theorem \ref{thm:llevel-1}, we show our $L$-level policy. We can
+% achieve nearly optimal regret $O_K(T^{1/2} \polylog(T))$ with
+% $O(\log\log(T))$ levels.
 \begin{theorem}
 \label{thm:llevel-1}
-For any $L > 3$, we have an $L$-level recommendation policy with regret \\$O_K\left(T^{2^{L-1}/(2^L-1)} \polylog(T) \right)$.
-In particular, we have an $O(\log\log(T))$-level recommendation policy with regret $O_K(T^{1/2} \polylog(T))$.
+For any $L > 3$, there exists an $L$-level disclosure policy with
+regret $$O_K\left(T^{2^{L-1}/(2^L-1)} \polylog(T) \right).$$ In
+particular, there exists a $O(\log\log(T))$-level recommendation
+policy with regret $O_K(T^{1/2} \polylog(T))$.
 \end{theorem}
 
-In Theorem \ref{thm:llevel-2}, we show a recommendation policy with instance-dependent regret guarantee.
-This policy has the same structure as the one in Theorem \ref{thm:llevel-1} but different parameters.
-Its regret depends on $\Delta$ which is the difference between the largest mean and second largest mean of arms and its construction does not depend on $\Delta$.
-Its regret bound outperforms the one in Theorem \ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$.
-The only downside is that this policy requires more levels, i.e.
-$O(\log(T)/\log\log(T))$ levels.
-It also has the property that each agent observes a good fraction of history till its round.
+% In Theorem \ref{thm:llevel-2}, we show a policy with
+Our second policy achieves an instance-dependent regret
+guarantee. This policy has the same info-graph structure as the first
+one in Theorem \ref{thm:llevel-1}, but requires a higher number of
+levels $L = O(\log(T/\log\log(T)))$ and larger group sizes. We will
+bound its regret as a function of on the gap parameter $\Delta$ even
+though the construction of the policy does not depend on $\Delta$. In
+particular, this regret bound outperforms the one in Theorem
+\ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$.  It
+also has the desirable property that the policy does not conceal too
+much information from agents---any agent $t$ observes a good fraction
+of history in previous rounds.
 
@@
 \label{thm:llevel-2}
- We have an $O(\log(T)/\log\log(T))$-level recommendation policy with regret \\$O_K(\min(1/\Delta, T^{1/2})polylog(T))$.
-Here $\Delta$ is the difference between the largest mean and second largest mean of arms.
-The recommendation policy does not depend on $\Delta$.
-Moreover, agent in round $t$ observes a subhistory of size at least $\Omega( \lfloor t/\polylog(T)\rfloor)$.
+There exists a $O(\log(T)/\log\log(T))$-level policy such that for
+every multi-armed bandit instance with gap parameter $\Delta$, the
+policy has regret $$O_K(\min(1/\Delta, T^{1/2})\polylog(T))$$
+Moreover, under this policy, each agent $t$ observes a subhistory of
+size at least $\Omega( t/\polylog(T))$.
 \end{theorem}
+\swcomment{think the theorem statement implies independence of
+  $\Delta$}
 
@@
 
-The main idea of extending from 3-level to $L$-level is that instead of using the second level as one ``check-point'', we use more levels to have multiple ``check points''.
-Some new challenges appear in this process.
-Here we give an overview of the additional techniques we use to get our $L$-level results.
+We will now present the main idea of extending from 3-level to
+$L$-level is that instead of using the second level as one
+``check-point'', we use more levels to have multiple ``check points''.
+Some new challenges appear in this process. Here we give an overview
+of the additional techniques we use to get our $L$-level results.
 
-\xhdr{Connecting structures between levels.} In our 3-level policy, the second level has $S = \Theta(\log(T))$ groups.
-We do so to ensure that in the small gap case (Lemma \ref{3levelsmallcase}), with high probability, both arms are pulled enough times in the second level.
-The argument relies on the fact that agents in different second-level groups observe disjoint histories of the first level and the independent randomness in first level groups guarantees each arm $a$ to have a ``lucky'' second-level group such that agents in that group all pull arm $a$ with high probability.
+\xhdr{Connecting structures between levels with $S=2$.} In our 3-level
+policy, the second level has $S = \Theta(\log(T))$ groups. We do so to
+ensure that in the small gap case (Lemma \ref{3levelsmallcase}), with
+high probability, both arms are pulled enough times in the second
+level. The argument relies on the fact that agents in different
+second-level groups observe disjoint histories of the first level and
+the independent randomness in first level groups guarantees each arm
+$a$ to have a ``lucky'' second-level group such that agents in that
+group all pull arm $a$ with high probability.
 

### 2018-11-02 intro.tex
First page of the intro!

\section{Introduction}
\label{sec:intro}

Recommendation systems are ubiquitous, providing recommendations for movies (\eg  Netflix), products (\eg  Amazon), restaurants (\eg  Yelp), vacations (\eg Tripadvisor), etc.  A typical recommendation system elicits user feedback about their experiences, and aggregates this feedback in order to provide better recommendations in the future. Thus, each user she consumes information from the previous users (indirectly, \eg via recommendations), and produces new information (\eg  a review) that benefits future users. This dual role creates a three-way tension between exploration, exploitation, and users' incentives.
A social planner would balance ``exploration" of insufficiently known alternatives and ``exploitation" of the information acquired so far. Designing algorithms to trade off these two objectives is a well-researched subject in machine learning and operations research. However, a given user who decides to ``explore" typically suffers all the downside of this decision, whereas the upside (improved recommendations) is spread over many users in the future. Therefore, users' incentives are skewed in favor of exploitation. As a result, observations may be collected at a slower rate, and may suffer from selection bias (\eg  ratings of a particular movie may mostly come from people who like this type of movies). Moreover, in some natural but idealized models (\eg  \cite{Kremer-JPE14,ICexploration-ec15}), there are simple  examples when optimal recommendations are never found because the corresponding actions are never taken.

Thus, we have a problem of \emph{incentivizing exploration}. Providing monetary incentives can be financially or technologically unfeasible, and relying on voluntary exploration can lead to selection biases. A recent line of work, started by \cite{Kremer-JPE14}, relies on the inherent \emph{information asymmetry} between the recommendation system and a user. These papers posit a simple model, termed \emph{Bayesian Exploration} in \cite{ICexplorationGames-ec16}. The recommendation system is a ``principal" that interacts with self-interested ``agents" who arrive one by one. Each agent needs to make a decision: take an action from a given set of alternatives. The principal sends a \emph{message} to the agent according to some ``disclosure policy", \eg issues a recommendation. Then the agent chooses an action, and both the agent and the principal observe the outcome.  Crucially, the principal does not control the agent's decision. The problem is to design the disclosure policy for the principal that learns over time to issue messages so as to incentivize the agents to balance exploration and exploitation in a socially optimal way. 
A single round of this model is a version of a well-known ``Bayesian Persuasion game" \cite{Kamenica-aer11}.

\xhdr{Our scope.} Prior work on incentivizing exploration, with or without monetary incentives, achieves much progress (more on this in ``related work"), but relies heavily on the standard assumptions of Bayesian rationality and the ``power to commit" (\ie users trust the system to implement the mechanism that it claims to implement). However, these assumptions are quite problematic when the disclosure policy selectively withholds information, \eg recommends randomly chosen actions to some randomly selected agents (which is a major technique in the prior work).

We take a step back and re-examine these assumptions. We ask: How would users interpret messages/recommendations generated by a disclosure policy? More importantly, how to design disclosure policies that would be interpreted by users in a predictable way, while ensuring good exploration-exploitation balance? Which conceptual framework should we use to reason about the user response to a disclosure policy, in the absence of the standard assumptions?

Consider the \emph{full-disclosure policy} that always reveals all information available to the principal. We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it. However, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}.

\xhdr{Related work.}

\cite{Perchet2015BatchedBP} gives regret guarantees for mult-armed bandit in $M$ batches. They have 2 upper bounds which are similar to our Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2}.

### 2018-11-02 intro.tex
Stopping for the night, I think.

@@
 More importantly, how to design disclosure policies that would be interpreted by users in a predictable way, while ensuring good exploration-exploitation balance?
-Which conceptual framework should we use to reason about the user response to a disclosure policy, in the absence of the standard assumptions?
+Without the standard assumptions, which conceptual frameworks can be used to reason about the user response to a disclosure policy in precise terms?
 
-Consider the \emph{full-disclosure policy} that always reveals all information available to the principal.
+We build one such conceptual framework for a particular type of disclosure policies.
+Consider the \emph{full-disclosure policy} that reveals the full history of observations from the previous users.
 We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it.
-However, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}.
+Unfortunately, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}.
+However, for the sake of the argument, what if the policy reveals the history for every other agent, rather than the history for all agents?
+We posit that users would trust such policy, too.
+Given a large volume of data, we posit that users would not be too unhappy with having access to only a fraction this data.
+A crucial aspect of our intuition here is that the ``subhistory" revealed to a given user is chosen in advance, without looking at the observations.
+In particular, the disclosure policy cannot subsample the observations that make a particular action look good.
+
+\ascomment{stopped for the day ...}
 

### 2018-11-02 app-warmup.tex
expected regret -> regret
Clean Appendix B

@@
 \begin{proof}[Proof of Lemma~\ref{lem:greedy}]
-  Fix any arm $a$. Let $\GdT = (K-1) \cdot N_0 + 1$ and
-  $\GdP = (1/3)^{\GdT}$. \swedit{We will condition on the event that
+  Fix any arm $a$. Let $\GdT = (K-1) \cdot \estN + 1$ and
+  $\GdP = (1/3)^{\GdT}$. We will condition on the event that
     all the realized rewards in $\GdT$ rounds are 0, which occurs with
-    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.}
+    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.
   In this case, we want to show that arm $a$ is pulled at least
@@
   the pigeonhole principle, we know that there is some other arm $a'$
-  that is pulled at least $N_0 + 1$ rounds. Let $t$ be the round in
-  which arm $a'$ is pulled exactly $N_0 + 1$ times. By Assumption
+  that is pulled at least $\estN + 1$ rounds. Let $t$ be the round in
+  which arm $a'$ is pulled exactly $\estN + 1$ times. By Assumption
   \ref{ass:embehave}, we know
   \[
-    \hat{\mu}_{a'}^t \leq 0 + C_0 / \sqrt{N_0} < 1/3.
+    \hat{\mu}_{a'}^t \leq 0 + \estC / \sqrt{\estN}  \leq \estC < 1/3.
   \]
-  \nicomment{Wait, where did we set $N_0$?} On the other hand, we have
+  %\nicomment{Wait, where did we set $\estN$?} 
+  On the other hand, we have
   $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
   the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
-  \swdelete{ In addition, we know that this case happens with
-    probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is
-    at most $2/3$. To sum up, we know that with probability at least
-    $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.}
-   \jmcomment{Agree with these changes.}
+  %\swdelete{ In addition, we know that this case happens with
+    %probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is
+    %at most $2/3$. To sum up, we know that with probability at least
+    %$\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.}
+  % \jmcomment{Agree with these changes.}
 \end{proof}
@@
   the first level is at least $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$.
-  \swedit{As long as we set $T_1 \geq \frac{4(\GdT)^2}{(\GdP)^2}\log(T)$,
+  As long as we set $T_1 \geq \frac{4(\GdT)^2}{(\GdP)^2}\log(T)$,
     this implies that the number of arm $a$ pulls is then at least
-    $\fdpN T_1/2$.}
+    $\fdpN T_1/2$.
 \OMIT{  By Chernoff bound,
@@
 coming from the prefix of $N$ cells in its reward tape. Define
-$W^{a,t}_2$ to be the event that the empirical mean of the first $t$
-\swedit{realized rewards in the tape} of arm $a$ is at most
-$\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the
-intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).  By
-Chernoff bound,\swcomment{$t$ may be confusing here}
+$W^{a,N}_2$ to be the event that the empirical mean of the first $N$
+realized rewards in the tape of arm $a$ is at most
+$\sqrt{\frac{2\log(T)}{N}}$ away from $\mu_a$. Define $W_2$ to be the
+intersection of these events (i.e.  $\bigcap_{a,N\in[T]} W^{a,N}_2$).  By
+Chernoff bound,%\swcomment{$t$ may be confusing here}
 \[
-\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
+\Pr[W^{a,N}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
 \]
@@
 \[
-|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{C_0}{\sqrt{\fdpN T_1/2}}.
+|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{\estC}{\sqrt{\fdpN T_1/2}}.
 \]
@@
 \[
-|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}+\frac{C_0}{\sqrt{\fdpN T_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
+|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}+\frac{\estC}{\sqrt{\fdpN T_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
 \]
-So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most
+So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total regret is at most
 \[
@@
 \]
-By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.
+By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get regret $O(T^{2/3}\log(T)^{1/3})$.
 \OMIT{Notice that if we know the gap parameter is known to be larger than
@@
 \]
-In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
+In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total regret is at most
 \[

### 2018-11-02 3level.tex
About the notation for number of groups
C_0,N_0 => \estC, \estN
define macro \NG for number of groups

@@
 
-The middle level consists of $N_2$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}. Each second-level group $S$ has the following property:
+The middle level consists of $\NG$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}. Each second-level group $S$ has the following property:
 \begin{align}\label{eq:group-defn}
@@
 
-The full-disclosure paths in the first level are also split into $N_2$ disjoint subsets, called \emph{first-level groups}.
-Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot N_2\cdot \fdpL$ rounds in the first layer.
+\jmcomment{$\NG$ is also used in Lemma 3.6.
+We need to find another notation.
+And I think it should be something without subscript 2.
+It's generally a property of the whole construction.
+How about $\NG$.}
+
+The full-disclosure paths in the first level are also split into $\NG$ disjoint subsets, called \emph{first-level groups}.
+Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot \NG\cdot \fdpL$ rounds in the first layer.
 There is a 1-1 correspondence between first-level groups $S_1$ and second-level groups $S_2$, whereby each agent $t\in S_2$ observes the full history from the corresponding group $S_1$.
@@
 
-  \draw [decorate,decoration={brace,amplitude=10pt,aspect=0.33},xshift=0pt,yshift=0pt] (10,1.8) -- (0,1.8) node [black,pos=0.33,xshift = 0cm,yshift=-0.6cm] {$N_2$ groups};
+  \draw [decorate,decoration={brace,amplitude=10pt,aspect=0.33},xshift=0pt,yshift=0pt] (10,1.8) -- (0,1.8) node [black,pos=0.33,xshift = 0cm,yshift=-0.6cm] {$\NG$ groups};
 
@@
     $T_1 = T^{4/7}\log^{-1/7}(T)$,
-    $N_2 = 2^{10}\log(T)$, and
+    $\NG = 2^{10}\log(T)$, and
     $T_2 = T^{6/7}\log^{-5/7}(T)$.
@@
 \[ \textstyle \Delta\in \left[
-    4\,\sum_{a\in\A}\; \conf{N_2\cdot \fdpN[a]\cdot T_1},\quad
+    4\,\sum_{a\in\A}\; \conf{\NG\cdot \fdpN[a]\cdot T_1},\quad
     4\,\sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}
@@
 Finally, the \emph{small gap} case, when  $\Delta$ is between
-$\tilde\Omega(\sqrt{1/T_2})$ and $\tilde O(\sqrt{1/(N_2\, T_1)})$ 
-is more challenging since even aggregating the data from all $N_2$
+$\tilde\Omega(\sqrt{1/T_2})$ and $\tilde O(\sqrt{1/(\NG\, T_1)})$ 
+is more challenging since even aggregating the data from all $\NG$
 first-level groups is not sufficient for identify the best arm. 
@@
     \Delta\in \left( 3\sqrt{2}\cdot\conf{T_2},\quad
-      4\,\sum_{a\in\A}\; \conf{N_2\cdot \fdpN[a]\cdot T_1}
+      4\,\sum_{a\in\A}\; \conf{\NG\cdot \fdpN[a]\cdot T_1}
 \right)
@@
 first level, so it is upper-bounded by the total number of agents in this level, which is 
-    $N_2\cdot \GdT \cdot T_1 = O(T^{4/7} \log T)$. 
+    $\NG\cdot \GdT \cdot T_1 = O(T^{4/7} \log T)$. 
 In both intermediate cases, it suffices to bound the regret from the
@@
 \[ \textstyle 
-\reg(T) \leq (N_2\,T_1\cdot \GdT + N_2\, T_2) 
+\reg(T) \leq (\NG\,T_1\cdot \GdT + \NG\, T_2) 
 \cdot 4\,\sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}

### 2018-11-02 llevel-overview.tex
.
define macro \NG for number of groups

@@
 
-\xhdr{Connecting structures between levels with $S=2$.} In our 3-level
-policy, the second level has $S = \Theta(\log(T))$ groups. We do so to
+\xhdr{Connecting structures between levels} In our 3-level
+policy, the second level has $\NG = \Theta(\log(T))$ groups. We do so to
 ensure that in the small gap case (Lemma \ref{3levelsmallcase}), with
@@
 
-Simply generalizing this idea to an $L$-level policy would give us a $S$-ary tree like structure and the first level will have $S^{L-1}$ groups.
-It incurs an extra $S^{\Omega(L)}$ factor in the regret.
+Simply generalizing this idea to an $L$-level policy would give us a $\NG$-ary tree like structure and the first level will have $\NG^{L-1}$ groups.
+It incurs an extra $\NG^{\Omega(L)}$ factor in the regret.
 If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor super poly-logarithmic.
@@
 
-For each level, our $L$-level policy has $S^2$ groups for some $S = \Theta(\log(T))$.
-The groups in the $l$-th level are labeled as $G_{l,u,v}$ for $u,v\in[S]$.
-For any $l \in \{2,...,L\}$ and $u,v,w\in [S]$, agents in group $G_{l,u,v}$ see the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$).
+For each level, our $L$-level policy has $\NG^2$ groups for some $\NG = \Theta(\log(T))$.
+The groups in the $l$-th level are labeled as $G_{l,u,v}$ for $u,v\in[\NG]$.
+For any $l \in \{2,...,L\}$ and $u,v,w\in [\NG]$, agents in group $G_{l,u,v}$ see the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$).
 See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level).
 This connecting structure has three nice properties: \\
-(i) The number of groups does not grow with $L$ and stays as $S^2 = \Theta(\log^2(T))$ in each level. Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\
-(ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,S,v}$ (e.g.
+(i) The number of groups does not grow with $L$ and stays as $\NG^2 = \Theta(\log^2(T))$ in each level. Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\
+(ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,\NG,v}$ (e.g.
 $G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l-1$ and $v$.
@@
 The reason for such rise is that, except the first level, we don't have good enough guarantee of the number of pulls of each arm.
-For example, in Figure \ref{fig:llevel-connecting}, when we talk about having enough arm $a$ pulls in the history observed by agents in $G_{l,1,1}$, it could be that  only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,S}$ are pulling arm $a$.
-Therefore our estimate of the number of arm $a$ pulls can be off by an $S=\Theta(\log(T))$ multiplicative factor.
+For example, in Figure \ref{fig:llevel-connecting}, when we talk about having enough arm $a$ pulls in the history observed by agents in $G_{l,1,1}$, it could be that  only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm $a$.
+Therefore our estimate of the number of arm $a$ pulls can be off by an $\NG=\Theta(\log(T))$ multiplicative factor.
 This finally makes the boundary cases harder to deal with.
@@
 In our $L$-level policy, after understanding the boundary cases well, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups.
-For each $l \in [L], u,v \in [S]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$.
+For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$.
 Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$.

### 2018-11-02 llevel.tex
C_0,N_0 => \estC, \estN
switch S to \NG

@@
 
-\section{Proofs of Section \ref{sec:llevel}}
+\section{Proofs from Section \ref{sec:llevel}}
 \label{sec:llevel-details}
@@
 Our recommendation policy has $L$ levels and two types of groups: $G$-groups and $\Gamma$-groups.
-Each level has $S^2$ $G$-groups for $S = 2^{10}\log(T)$.
-Label the $G$-groups in the $l$-th level as $G_{l,u,v}$ for $u,v \in [S]$.
-Level $2$ to level $L$ also have $S^2$ $\Gamma$-groups.
-Label the $\Gamma$-groups in the $l$-th level as $\Gamma_{l,u,v}$ for $u,v \in [S]$.
-Each first-level group ($G_{1,u,v}$ for $u,v\in [S]$) has $T_1$ \ALGG of $\GdT$ rounds in parallel.
-For $l \geq 2$, there are $T_l$ agents in group $G_{l,u,v}$ and there are $T_l (S-1)$ agents in group $\Gamma_{l,u,v}$.
+Each level has $\NG^2$ $G$-groups for $\NG = 2^{10}\log(T)$.
+Label the $G$-groups in the $l$-th level as $G_{l,u,v}$ for $u,v \in [\NG]$.
+Level $2$ to level $L$ also have $\NG^2$ $\Gamma$-groups.
+Label the $\Gamma$-groups in the $l$-th level as $\Gamma_{l,u,v}$ for $u,v \in [\NG]$.
+Each first-level group ($G_{1,u,v}$ for $u,v\in [\NG]$) has $T_1$ \ALGG of $\GdT$ rounds in parallel.
+For $l \geq 2$, there are $T_l$ agents in group $G_{l,u,v}$ and there are $T_l (\NG-1)$ agents in group $\Gamma_{l,u,v}$.
 We will pick $T_1,...,T_L$ in the proof of Theorem \ref{thm:llevel}.
@@
 Agents in the first level only observe the history defined in the \ALGG run.
-For agents in group $G_{l,u,v}$ with $l\geq 2$, they observe all the history in the first $l-2$ levels (both $G$-groups and $\Gamma$-groups) and history in group $G_{l-1,v,w}$ for all $w \in [S]$.
+For agents in group $G_{l,u,v}$ with $l\geq 2$, they observe all the history in the first $l-2$ levels (both $G$-groups and $\Gamma$-groups) and history in group $G_{l-1,v,w}$ for all $w \in [\NG]$.
 Agents in group $\Gamma_{l,u,v}$ observe the same history as agents in group $G_{l,u,v}$.
@@
  \node at(\x+0.4,3){$T_{l-2}$};
- \node at(\x+1.8,3){$T_{l-2} (S-1)$};
+ \node at(\x+1.8,3){$T_{l-2} (\NG-1)$};
  \node at(\x+0.4,5.5){$T_{l-1}$};
- \node at(\x+1.8,5.5){$T_{l-1} (S-1)$};
+ \node at(\x+1.8,5.5){$T_{l-1} (\NG-1)$};
  \node at(\x+0.4,8){$T_l$};
- \node at(\x+1.8,8){$T_l (S-1)$};
+ \node at(\x+1.8,8){$T_l (\NG-1)$};
  \node at(\x+0.4,10.5){$T_L$};
- \node at(\x+1.8,10.5){$T_L (S-1)$};
+ \node at(\x+1.8,10.5){$T_L (\NG-1)$};
  \node at(\x+1.4,0.5){$T_1 \cdot \GdT$};
@@
 \label{thm:llevel}
-The $L$-level recommendation policy gets regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(S^4))$.
-In particular, if we pick $L = \log(\ln(T)/\log(S^4))$, the regret is $O(T^{1/2} polylog(T))$.
+The $L$-level recommendation policy gets regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(\NG^4))$.
+In particular, if we pick $L = \log(\ln(T)/\log(\NG^4))$, the regret is $O(T^{1/2} polylog(T))$.
 \end{theorem}
@@
 We will set $T_l$'s later in the proof.
-Before that, we are only going to assume $T_l / T_{l-1} \geq S^4$ for $l=2,...,L-1$ and $T_1 \geq S^4$.
+Before that, we are only going to assume $T_l / T_{l-1} \geq \NG^4$ for $l=2,...,L-1$ and $T_1 \geq \NG^4$.
 
@@
 \[
-\Pr[W_1] \geq 1- \frac{4S^2}{T^2}.
+\Pr[W_1] \geq 1- \frac{4\NG^2}{T^2}.
 \]
@@
 
-For $2\leq l \leq L-1$, $u\in [S]$ and each arm $a$, define $n^{l,u,a}$ to be the number of arm $a$ pulls in groups $G_{l,u,1},...,G_{l,u,S}$.
-Define $W_3^{l,u,a,high}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at least $\mu_a + 1/\sqrt{n^{l,u,a}}$.
-Define $W_3^{l,u,a,low}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at most $\mu_a - 1/\sqrt{n^{l,u,a}}$.
+For $2\leq l \leq L-1$, $u\in [\NG]$ and each arm $a$, define $n^{l,u,a}$ to be the number of arm $a$ pulls in groups $G_{l,u,1},...,G_{l,u,\NG}$.
+Define $W_3^{l,u,a,high}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,\NG}$ is at least $\mu_a + 1/\sqrt{n^{l,u,a}}$.
+Define $W_3^{l,u,a,low}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,\NG}$ is at most $\mu_a - 1/\sqrt{n^{l,u,a}}$.
 
@@
 \[
-\Pr[W_3^{l,a}|H_l= h_l] \geq 1- (1-1/16)^S \geq 1 - 1/T^2.
+\Pr[W_3^{l,a}|H_l= h_l] \geq 1- (1-1/16)^\NG \geq 1 - 1/T^2.
 \]
@@
 
-For first-level groups $G_{1,u,1},...,G_{1,u,S}$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in these groups pull arm $a$.
-Define $W_4^{u,a,high}$  to be the event that first $\fdpN T_1 S$ pulls of arm $a$ in the tape has empirical mean at least $\mu_a + 1/\sqrt{\fdpN T_1 S}$ and define $W_4^{u,a,low}$  to be the event that first $\fdpN T_1S$ pulls of arm $a$ in the tape has empirical mean at most $\mu_a - 1/\sqrt{\fdpN T_1S }$.
+For first-level groups $G_{1,u,1},...,G_{1,u,\NG}$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in these groups pull arm $a$.
+Define $W_4^{u,a,high}$  to be the event that first $\fdpN T_1 \NG$ pulls of arm $a$ in the tape has empirical mean at least $\mu_a + 1/\sqrt{\fdpN T_1 \NG}$ and define $W_4^{u,a,low}$  to be the event that first $\fdpN T_1\NG$ pulls of arm $a$ in the tape has empirical mean at most $\mu_a - 1/\sqrt{\fdpN T_1\NG }$.
 By Berry-Esseen Theorem and $\mu_a \in [1/3,2/3]$, we have
 \[
-\Pr[W_4^{u,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{\fdpN T_1S}} > 1/4.
+\Pr[W_4^{u,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{\fdpN T_1\NG}} > 1/4.
 \]
@@
 \[
-\Pr[W^{a}_4] \geq 1- (1-1/16)^S \geq 1 -1/T^2.
+\Pr[W^{a}_4] \geq 1- (1-1/16)^\NG \geq 1 -1/T^2.
 \]
@@
 We prove in the next claim that there are enough pulls of both arms in higher levels if $\mu_1-\mu_2$ is small enough.
-For notation convenience, we set $\varepsilon_0 = 1$, $\varepsilon_1 = \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}$ and $\varepsilon_l = 1/(4\sqrt{T_lS})$ for $l \geq 2$.
+For notation convenience, we set $\varepsilon_0 = 1$, $\varepsilon_1 = \frac{1}{4\sqrt{\fdpN T_1\NG}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1\NG}}$ and $\varepsilon_l = 1/(4\sqrt{T_l\NG})$ for $l \geq 2$.
 
@@
 \label{clm:l2_explore}
-For any arm $a$ and $2\leq l \leq L$, if $\mu_1 - \mu_2 \leq \varepsilon_{l-1}$, then for any $u \in [S]$, there are at least $T_l$ pulls of arm $a$ in groups $G_{l,u,1},G_{l,u,2}, ...
-,G_{l,u,S}$ and there are at least $T_lS(S-1)$ pulls of arm $a$ in the $l$-th level $\Gamma$-groups.
+For any arm $a$ and $2\leq l \leq L$, if $\mu_1 - \mu_2 \leq \varepsilon_{l-1}$, then for any $u \in [\NG]$, there are at least $T_l$ pulls of arm $a$ in groups $G_{l,u,1},G_{l,u,2}, ...
+,G_{l,u,\NG}$ and there are at least $T_l\NG(\NG-1)$ pulls of arm $a$ in the $l$-th level $\Gamma$-groups.
 \end{claim}
@@
 \begin{proof}
-We are going to show that for each $l$ and arm $a$ there exists $u_a$ such that agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$.
+We are going to show that for each $l$ and arm $a$ there exists $u_a$ such that agents in groups $G_{l,1,u_a},...,G_{l,\NG,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,\NG,u_a}$ all pull arm $a$.
 This suffices to prove the claim.
@@
 We prove the above via induction on $l$.
-%For notation convenience, define $\bar{\mu}^{l,u}_a$  to be the empirical mean of arm $a$ pulls in the history observed by agents in groups $G_{l,1,u},...,G_{l,S,u}$ and $\Gamma_{l,1,u},...,\Gamma_{l,S,u}$ (they observe the same history).
+%For notation convenience, define $\bar{\mu}^{l,u}_a$  to be the empirical mean of arm $a$ pulls in the history observed by agents in groups $G_{l,1,u},...,G_{l,\NG,u}$ and $\Gamma_{l,1,u},...,\Gamma_{l,\NG,u}$ (they observe the same history).
 We start by the base case when $l=2$.
 For each arm $a$, $W_4$ implies there exists $u_a$ such that $W^{u_a,a,high}_4$ and $W^{u_a,3-a,low}_4$ happen.
-For an agent $t$  in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$.
+For an agent $t$  in groups $G_{2,1,u_a},...,G_{2,\NG,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,\NG,u_a}$.
 $W_4^{u_a,a,high}$,  $W_1^{a,u_a,v}$ and $W_2$ together imply that 
 \begin{align*}
-\bar{\mu}_a ^t &\geq \mu_a + \left(\fdpN T_1S \cdot \frac{1}{\sqrt{\fdpN T_1S}} - \GdT \sqrt{T_1\log(T)} S\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}S}} \right) \cdot \frac{1}{(\fdpN T_1+ \GdT \sqrt{T_1\log(T)})S} \\
-&> \mu_a + \frac{1}{4\sqrt{\fdpN T_1S}}.
+\bar{\mu}_a ^t &\geq \mu_a + \left(\fdpN T_1\NG \cdot \frac{1}{\sqrt{\fdpN T_1\NG}} - \GdT \sqrt{T_1\log(T)} \NG\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}\NG}} \right) \cdot \frac{1}{(\fdpN T_1+ \GdT \sqrt{T_1\log(T)})\NG} \\
+&> \mu_a + \frac{1}{4\sqrt{\fdpN T_1\NG}}.
 \end{align*}
@@
 \[
-\bar{\mu}_{3-a}^t< \mu_{3-a}   - \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}.
+\bar{\mu}_{3-a}^t< \mu_{3-a}   - \frac{1}{4\sqrt{\fdpN[3-a] T_1\NG}}.
 \]
@@
 \begin{align*}
-\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a} + \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}\\
-&\geq -\varepsilon_1+ \frac{1}{4\sqrt{\fdpN T_1S}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1S}}\\
-&\geq \frac{1}{8\sqrt{\fdpN T_1S}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1S}}.
+\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a} + \frac{1}{4\sqrt{\fdpN T_1\NG}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1\NG}}\\
+&\geq -\varepsilon_1+ \frac{1}{4\sqrt{\fdpN T_1\NG}} + \frac{1}{4\sqrt{\fdpN[3-a] T_1\NG}}\\
+&\geq \frac{1}{8\sqrt{\fdpN T_1\NG}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1\NG}}.
 \end{align*}
@@
 \begin{align*}
-\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{C_0}{\sqrt{\fdpN T_1S/2}} - \frac{C_0}{\sqrt{\fdpN[3-a] T_1S/2}}\\
-&> \frac{1}{8\sqrt{\fdpN T_1S}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1S}} -   \frac{C_0}{\sqrt{\fdpN T_1S/2}} - \frac{C_0}{\sqrt{\fdpN[3-a] T_1S/2}}\\
+\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{\estC}{\sqrt{\fdpN T_1\NG/2}} - \frac{\estC}{\sqrt{\fdpN[3-a] T_1\NG/2}}\\
+&> \frac{1}{8\sqrt{\fdpN T_1\NG}} + \frac{1}{8\sqrt{\fdpN[3-a] T_1\NG}} -   \frac{\estC}{\sqrt{\fdpN T_1\NG/2}} - \frac{\estC}{\sqrt{\fdpN[3-a] T_1\NG/2}}\\
 &>0.
 \end{align*}
-The last inequality holds since $C_0$ is a small enough constant defined in Assumption \ref{ass:embehave}.
-Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$ all pull arm $a$.
+The last inequality holds since $\estC$ is a small enough constant defined in Assumption \ref{ass:embehave}.
+Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,\NG,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,\NG,u_a}$ all pull arm $a$.
 
@@
 For each arm $a$, $W_3$ implies that there exists $u_a$ such that $W^{l-1,u_a,a,high}_3$ and $W^{l-1,u_a,3-a,low}_3$ happen.
-Recall $n^{l-1,u_a,a}$ is the number of arm $a$ pulls in groups $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$.
+Recall $n^{l-1,u_a,a}$ is the number of arm $a$ pulls in groups $G_{l-1,u_a,1},...,G_{l-1,u_a,\NG}$.
 The induction hypothesis implies that $n^{l-1,u_a,a} \geq T_{l-1}$.
-$W^{l-1,u_a,a,high}_3$ together with $n^{l-1,u_a,a} \geq T_{l-1}$ implies that the empirical mean of arm $a$ pulls in group $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$ is at least $\mu_a + 1/\sqrt{n^{l-1,u_a,a}}$.
-For any agent $t$ in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$, it observes history of groups $G_{l-1,u_a,1},...,G_{l-1,u_a,S}$ and all groups in levels below level $l-1$.
-Notice that the groups in the first $l-2$ levels have at most $(T_1 \GdT + T_2 + \cdots +T_{l-2})S^3 \leq T_{l-1}/(12\log(T)) \leq n^{l-1,u_a,a}/(12\log(T))$ agents.
+$W^{l-1,u_a,a,high}_3$ together with $n^{l-1,u_a,a} \geq T_{l-1}$ implies that the empirical mean of arm $a$ pulls in group $G_{l-1,u_a,1},...,G_{l-1,u_a,\NG}$ is at least $\mu_a + 1/\sqrt{n^{l-1,u_a,a}}$.
+For any agent $t$ in groups $G_{l,1,u_a},...,G_{l,\NG,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,\NG,u_a}$, it observes history of groups $G_{l-1,u_a,1},...,G_{l-1,u_a,\NG}$ and all groups in levels below level $l-1$.
+Notice that the groups in the first $l-2$ levels have at most $(T_1 \GdT + T_2 + \cdots +T_{l-2})\NG^3 \leq T_{l-1}/(12\log(T)) \leq n^{l-1,u_a,a}/(12\log(T))$ agents.
 By $W_2$, we have
 \begin{align*}
-\bar{\mu}_a ^t &\geq \mu_a + \left(n^{l-1,u_a,a}  \cdot \frac{1}{\sqrt{n^{l-1,u_a,a} }}- (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3\cdot \sqrt{\frac{3\log(T)}{ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3}} \right) \\
-&~~~\cdot \frac{1}{n^{l-1,u_a,a}+ (T_1 \GdT + T_2 + \cdots +T_{l-2})S^3} \\
+\bar{\mu}_a ^t &\geq \mu_a + \left(n^{l-1,u_a,a}  \cdot \frac{1}{\sqrt{n^{l-1,u_a,a} }}- (T_1 \GdT + T_2 + \cdots +T_{l-2})\NG^3\cdot \sqrt{\frac{3\log(T)}{ (T_1 \GdT + T_2 + \cdots +T_{l-2})\NG^3}} \right) \\
+&~~~\cdot \frac{1}{n^{l-1,u_a,a}+ (T_1 \GdT + T_2 + \cdots +T_{l-2})\NG^3} \\
 &> \mu_a + \frac{1}{4\sqrt{n^{l-1,u_a,a}  }}.
@@
 \end{align*}
-The last inequality holds because $n^{l-1,u_a,a}$ and $n^{l-1,u_a,3-a}$ are at most $T_{l-1} S$. By Assumption \ref{ass:embehave}, we have
+The last inequality holds because $n^{l-1,u_a,a}$ and $n^{l-1,u_a,3-a}$ are at most $T_{l-1} \NG$. By Assumption \ref{ass:embehave}, we have
 \begin{align*}
-\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{C_0}{\sqrt{n^{l-1,u_a,a} }} - \frac{C_0}{\sqrt{n^{l-1,u_a,3-a}}}\\
-&> \frac{1}{8\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{8\sqrt{n^{l-1,u_a,3-a}  }} -  \frac{C_0}{\sqrt{n^{l-1,u_a,a} }} - \frac{C_0}{\sqrt{n^{l-1,u_a,3-a}}}\\
+\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{\estC}{\sqrt{n^{l-1,u_a,a} }} - \frac{\estC}{\sqrt{n^{l-1,u_a,3-a}}}\\
+&> \frac{1}{8\sqrt{n^{l-1,u_a,a}  }} +\frac{1}{8\sqrt{n^{l-1,u_a,3-a}  }} -  \frac{\estC}{\sqrt{n^{l-1,u_a,a} }} - \frac{\estC}{\sqrt{n^{l-1,u_a,3-a}}}\\
 &>0.
 \end{align*}
-The last inequality holds since $C_0$ is a small enough constant defined in Assumption \ref{ass:embehave}.
-Therefore agents in groups $G_{l,1,u_a},...,G_{l,S,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,S,u_a}$ all pull arm $a$.
+The last inequality holds since $\estC$ is a small enough constant defined in Assumption \ref{ass:embehave}.
+Therefore agents in groups $G_{l,1,u_a},...,G_{l,\NG,u_a}$ and $\Gamma_{l,1,u_a},...,\Gamma_{l,\NG,u_a}$ all pull arm $a$.
 \end{proof}
@@
 \label{clm:l2_exploit}
-For any $2 \leq l \leq L$, if $\varepsilon_{l-1} S\leq \mu_1 - \mu_2 < \varepsilon_{l-2} S$, there are no pulls of arm 2 in groups with level $l,...,L$. 
+For any $2 \leq l \leq L$, if $\varepsilon_{l-1} \NG\leq \mu_1 - \mu_2 < \varepsilon_{l-2} \NG$, there are no pulls of arm 2 in groups with level $l,...,L$. 
 \end{claim}
@@
 \begin{proof}
-We argue in 2 cases $\varepsilon_{l-1} \sqrt{S} \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l \geq 2$ and $\varepsilon_{l-2}  \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2} \sqrt{S}$ for $l > 2$.
-Since our recommendation policy's first level is slightly different from other levels, we need to argue case $\varepsilon_{l-1} \sqrt{S} \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l=2$ and case $\varepsilon_{l-2}  \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2} \sqrt{S}$ for $l =3$ separately.
+We argue in 2 cases $\varepsilon_{l-1} \sqrt{\NG} \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l \geq 2$ and $\varepsilon_{l-2}  \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2} \sqrt{\NG}$ for $l > 2$.
+Since our recommendation policy's first level is slightly different from other levels, we need to argue case $\varepsilon_{l-1} \sqrt{\NG} \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l=2$ and case $\varepsilon_{l-2}  \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2} \sqrt{\NG}$ for $l =3$ separately.
 
 \begin{itemize}
-\item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l = 2$(i.e.
-$\varepsilon_1S\leq \mu_1 - \mu_2 \leq \varepsilon_0$): We know agents in level at least 2 will observe at least $\fdpN T_1/2$ pulls of arm $a$ for $a \in \{1,2\}$.
+\item $\varepsilon_{l-1} \NG \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l = 2$(i.e.
+$\varepsilon_1\NG\leq \mu_1 - \mu_2 \leq \varepsilon_0$): We know agents in level at least 2 will observe at least $\fdpN T_1/2$ pulls of arm $a$ for $a \in \{1,2\}$.
 By $W_2$, for any agent in level at least 2, we have
 \[
-|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S\fdpN T_1/2}}.
+|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{\NG\fdpN T_1/2}}.
 \]
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
-&\geq \mu_1 -\mu_2-\sqrt{\frac{3\log(T)}{S\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{S\fdpN[2]T_1/2}}- \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
-&\geq\frac{\sqrt{S}}{4\sqrt{\fdpN[1]T_1}} +  \frac{\sqrt{S}}{4\sqrt{\fdpN[2]T_1}}-\sqrt{\frac{3\log(T)}{S\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{S\fdpN[2]T_1/2}}- \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} -  \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{\estC}{\sqrt{\NG\fdpN[1]T_1/2}} -  \frac{\estC}{\sqrt{\NG\fdpN[2]T_1/2}}\\
+&\geq \mu_1 -\mu_2-\sqrt{\frac{3\log(T)}{\NG\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{\NG\fdpN[2]T_1/2}}- \frac{\estC}{\sqrt{\NG\fdpN[1]T_1/2}} -  \frac{\estC}{\sqrt{\NG\fdpN[2]T_1/2}}\\
+&\geq\frac{\sqrt{\NG}}{4\sqrt{\fdpN[1]T_1}} +  \frac{\sqrt{\NG}}{4\sqrt{\fdpN[2]T_1}}-\sqrt{\frac{3\log(T)}{\NG\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{\NG\fdpN[2]T_1/2}}- \frac{\estC}{\sqrt{\NG\fdpN[1]T_1/2}} -  \frac{\estC}{\sqrt{\NG\fdpN[2]T_1/2}}\\
 &>0.
@@
 
-\item $\varepsilon_{l-1} S \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l > 2$: By claim \ref{clm:l2_explore}, for any agent $t$ in level at least $l$, that agent will observe at least $T_{l-1}$ arm $a$ pulls.
+\item $\varepsilon_{l-1} \NG \leq \mu_1 - \mu_2 \leq \varepsilon_{l-2}$ for $l > 2$: By claim \ref{clm:l2_explore}, for any agent $t$ in level at least $l$, that agent will observe at least $T_{l-1}$ arm $a$ pulls.
 By $W_2$, we have
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2C_0}{\sqrt{T_{l-1}}} \\
-&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2C_0}{\sqrt{T_{l-1}}} \\
-&\geq\sqrt{\frac{S}{16T_{l-1}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2C_0}{\sqrt{T_{l-1}}} \\
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2\estC}{\sqrt{T_{l-1}}} \\
+&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2\estC}{\sqrt{T_{l-1}}} \\
+&\geq\sqrt{\frac{\NG}{16T_{l-1}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2\estC}{\sqrt{T_{l-1}}} \\
 &>0.
@@
 
-\item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}S$ for $l =3$ (i.e.
-$\varepsilon_1 < \mu_1 - \mu_2 < \varepsilon_1S$): By Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $3$, that agent will observe at least $T_1\fdpN S^2/2$ arm $a$ pulls (just from the first level).
+\item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}\NG$ for $l =3$ (i.e.
+$\varepsilon_1 < \mu_1 - \mu_2 < \varepsilon_1\NG$): By Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $3$, that agent will observe at least $T_1\fdpN \NG^2/2$ arm $a$ pulls (just from the first level).
 By $W_2$, we have
 \[
-|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S^2\fdpN T_1/2}}.
+|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{\NG^2\fdpN T_1/2}}.
 \]
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{C_0}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{C_0}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
-&\geq \mu_1 -\mu_2 -  \sqrt{\frac{3\log(T)}{S^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{S^2\fdpN[2]T_1/2}}- \frac{C_0}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{C_0}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
-&\geq\frac{1}{4\sqrt{S\fdpN[1]T_1}} + \frac{1}{4\sqrt{S\fdpN[2]T_1}}  -  \sqrt{\frac{3\log(T)}{S^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{S^2\fdpN[2]T_1/2}}- \frac{C_0}{\sqrt{S^2\fdpN[1]T_1/2}}-\frac{C_0}{\sqrt{S^2\fdpN[2]T_1/2}}  \\
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{\estC}{\sqrt{\NG^2\fdpN[1]T_1/2}}-\frac{\estC}{\sqrt{\NG^2\fdpN[2]T_1/2}}  \\
+&\geq \mu_1 -\mu_2 -  \sqrt{\frac{3\log(T)}{\NG^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{\NG^2\fdpN[2]T_1/2}}- \frac{\estC}{\sqrt{\NG^2\fdpN[1]T_1/2}}-\frac{\estC}{\sqrt{\NG^2\fdpN[2]T_1/2}}  \\
+&\geq\frac{1}{4\sqrt{\NG\fdpN[1]T_1}} + \frac{1}{4\sqrt{\NG\fdpN[2]T_1}}  -  \sqrt{\frac{3\log(T)}{\NG^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{\NG^2\fdpN[2]T_1/2}}- \frac{\estC}{\sqrt{\NG^2\fdpN[1]T_1/2}}-\frac{\estC}{\sqrt{\NG^2\fdpN[2]T_1/2}}  \\
 &>0.
@@
 
-\item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}S$ for $l >3$: Since $\mu_1-\mu_2 < \varepsilon_{l-2}S < \varepsilon_{l-3}$, by Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $l$, that agent will observe at least $T_{l-2}S^2$ arm $a$ pulls (just from level $l-2$).
+\item $\varepsilon_{l-2} < \mu_1 - \mu_2 < \varepsilon_{l-2}\NG$ for $l >3$: Since $\mu_1-\mu_2 < \varepsilon_{l-2}\NG < \varepsilon_{l-3}$, by Claim \ref{clm:l2_explore}, for any agent $t$ in level at least $l$, that agent will observe at least $T_{l-2}\NG^2$ arm $a$ pulls (just from level $l-2$).
 By $W_2$, we have
 \[
-|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{S^2T_{l-2}}}.
+|\bar{\mu}_a^t - \mu_a| \leq \sqrt{\frac{3\log(T)}{\NG^2T_{l-2}}}.
 \]
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2C_0}{\sqrt{S^2T_{l-2}}} \\
-&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{S^2T_{l-2}}}- \frac{2C_0}{\sqrt{S^2T_{l-2}}} \\
-&\geq\frac{1}{4\sqrt{ST_{l-2}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2C_0}{\sqrt{T_{l-1}}} \\
+\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{2\estC}{\sqrt{\NG^2T_{l-2}}} \\
+&\geq \mu_1 -\mu_2 - 2 \sqrt{\frac{3\log(T)}{\NG^2T_{l-2}}}- \frac{2\estC}{\sqrt{\NG^2T_{l-2}}} \\
+&\geq\frac{1}{4\sqrt{\NG T_{l-2}}} -  2 \sqrt{\frac{3\log(T)}{T_{l-1}}}- \frac{2\estC}{\sqrt{T_{l-1}}} \\
 &>0.
@@
 \[
-T_l = T^{\frac{2^{L-1} + 2^{L-2} + \cdots + 2^{L-l}}{2^{L-1}+ 2^{L-2} + \cdots + 1}}/S^3.
+T_l = T^{\frac{2^{L-1} + 2^{L-2} + \cdots + 2^{L-l}}{2^{L-1}+ 2^{L-2} + \cdots + 1}}/\NG^3.
 \]
@@
 \[
-T_L = (T - T_1 \cdot \GdT\cdot S^2 - (T_2 + \cdots + T_{l-1}) S^3) /S^3
+T_L = (T - T_1 \cdot \GdT\cdot \NG^2 - (T_2 + \cdots + T_{l-1}) \NG^3) /\NG^3
 \]
-We restrict $L$ to be at most $\log(\ln(T)/\log(S^4))$ so that $T_l / T_{l-1} \geq T^{1/2^L} \geq S^4$ for $l = 2,...,L-1$.
+We restrict $L$ to be at most $\log(\ln(T)/\log(\NG^4))$ so that $T_l / T_{l-1} \geq T^{1/2^L} \geq \NG^4$ for $l = 2,...,L-1$.
 $T_L$ is a little bit different because we want total number of agents to be $T$.
@@
 \begin{align*}
-&\max\left( T_1\GdT S^2 , \max_{l \geq 2} \varepsilon_{l-1}S(T_1\GdT S^2 + T_2 S^3 + \cdots + T_lS^3)\right) \\
-\leq & \max\left( T_1\GdT S^2 , \max_{l \geq 2} 2 \varepsilon_{l-1} T_l S^4 \right)\\
+&\max\left( T_1\GdT \NG^2 , \max_{l \geq 2} \varepsilon_{l-1}\NG(T_1\GdT \NG^2 + T_2 \NG^3 + \cdots + T_l\NG^3)\right) \\
+\leq & \max\left( T_1\GdT \NG^2 , \max_{l \geq 2} 2 \varepsilon_{l-1} T_l \NG^4 \right)\\
 = &O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right).
@@
 Now we are going to change the parameters of the $L$-level recommendation policy a little bit and prove the below corollary.
-We will keep $S$ the same (i.e.
-$S = 2^{10}\log(T)$).
+We will keep $\NG$ the same (i.e.
+$\NG = 2^{10}\log(T)$).
 We are going to change $L$ and $T_1,...,T_L$.
-We set $L = \log(T)/\log(S^4)$, $T_l = (S^4)^l$ for $l=1,...,L-1$ and $T_L = (T - T_1 \GdT S^2 - S^3\sum_{l=2}^{L-1} T_l)/S^3$.
+We set $L = \log(T)/\log(\NG^4)$, $T_l = (\NG^4)^l$ for $l=1,...,L-1$ and $T_L = (T - T_1 \GdT \NG^2 - \NG^3\sum_{l=2}^{L-1} T_l)/\NG^3$.
 
@@
 \begin{proof}
-Notice that in the proof of Theorem \ref{thm:llevel}, by the end of Claim \ref{clm:l2_exploit}, the only constraint we need about $T_l$'s is that $T_l / T_{l-1} \geq S^4$ for $l=2,...,L-1$ and $T_1 \geq S^4$.
+Notice that in the proof of Theorem \ref{thm:llevel}, by the end of Claim \ref{clm:l2_exploit}, the only constraint we need about $T_l$'s is that $T_l / T_{l-1} \geq \NG^4$ for $l=2,...,L-1$ and $T_1 \geq \NG^4$.
 And our new settings of $T_l$'s still satisfy this constraint.
@@
 
-Recall in the proof of Theorem \ref{thm:llevel}, $\varepsilon_l =\Theta(1/\sqrt{T_l S})$ for $l \in [L-1]$ and $\varepsilon_0 = 1$. Consider two cases:
+Recall in the proof of Theorem \ref{thm:llevel}, $\varepsilon_l =\Theta(1/\sqrt{T_l \NG})$ for $l \in [L-1]$ and $\varepsilon_0 = 1$. Consider two cases:
 \begin{itemize}
-\item $\Delta < \varepsilon_{L-1} S$.
+\item $\Delta < \varepsilon_{L-1} \NG$.
 In this case, notice that even always picking the sub-optimal arm gives expected regret at most $T(\mu_1-\mu_2) = T\Delta = O(T^{1/2} polylog(T))$.
@@
 Therefore, the regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
-\item $\Delta \geq \varepsilon_{L-1} S$.
-In this case, we can find $l \in \{2,...,L\}$ such that $\varepsilon_{l-1} S\leq \Delta < \varepsilon_{l-2} S$.
+\item $\Delta \geq \varepsilon_{L-1} \NG$.
+In this case, we can find $l \in \{2,...,L\}$ such that $\varepsilon_{l-1} \NG\leq \Delta < \varepsilon_{l-2} \NG$.
 By Claim \ref{clm:l2_exploit}, we can upper bound the regret by
 \begin{align*}
-&\Delta \cdot (T_1 \GdT S^2  +T_2 S^3+ \cdots T_{l-1} S^3)\\
-=& O(\Delta T_{l-1}S^3) \\
-=&O(\Delta T_{l-2}S^7) \\
-=&O(\Delta\cdot  \frac{1}{\varepsilon^2_{l-2}}\cdot S^6)\\
-=&O(\Delta \cdot \frac{1}{\Delta^2}\cdot S^8)\\
+&\Delta \cdot (T_1 \GdT \NG^2  +T_2 \NG^3+ \cdots T_{l-1} \NG^3)\\
+=& O(\Delta T_{l-1}\NG^3) \\
+=&O(\Delta T_{l-2}\NG^7) \\
+=&O(\Delta\cdot  \frac{1}{\varepsilon^2_{l-2}}\cdot \NG^6)\\
+=&O(\Delta \cdot \frac{1}{\Delta^2}\cdot \NG^8)\\
 =&O(polylog(T)/\Delta).
 \end{align*}
-We also have $1/\Delta \leq 1/(\varepsilon_{L-1}S)= O(T^{1/2})$. Therefore, the regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
+We also have $1/\Delta \leq 1/(\varepsilon_{L-1}\NG)= O(T^{1/2})$. Therefore, the regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
 \end{itemize}
@@
 Now we proceed to extend Claim \ref{clm:l2_explore} and Claim \ref{clm:l2_exploit}.
-The statement of Claim \ref{clm:l2_explore} should be changed to ``For any arm $a$ and $2\leq l \leq L$, if $\mu_1 - \mu_a \leq \varepsilon_{l-1}$, then for any $u \in [S]$, there are at least $T_l$ pulls of arm $a$ in groups $G_{l,u,1},G_{l,u,2}, ...
-,G_{l,u,S}$ and there are at least $T_lS(S-1)$ pulls of arm $a$ in the $l$-th level $\Gamma$-groups''.
-The statement of Claim \ref{clm:l2_exploit} should be changed to ``For any $2 \leq l \leq L$, if $\varepsilon_{l-1} S\leq \mu_1 - \mu_a < \varepsilon_{l-2} S$, there are no pulls of arm $a$ in groups with level $l,...,L$.''
+The statement of Claim \ref{clm:l2_explore} should be changed to ``For any arm $a$ and $2\leq l \leq L$, if $\mu_1 - \mu_a \leq \varepsilon_{l-1}$, then for any $u \in [\NG]$, there are at least $T_l$ pulls of arm $a$ in groups $G_{l,u,1},G_{l,u,2}, ...
+,G_{l,u,\NG}$ and there are at least $T_l\NG(\NG-1)$ pulls of arm $a$ in the $l$-th level $\Gamma$-groups''.
+The statement of Claim \ref{clm:l2_exploit} should be changed to ``For any $2 \leq l \leq L$, if $\varepsilon_{l-1} \NG\leq \mu_1 - \mu_a < \varepsilon_{l-2} \NG$, there are no pulls of arm $a$ in groups with level $l,...,L$.''
 
@@
 We need some additional argument for the case when $\mu_1 - \mu_{a'} > \varepsilon_{l-2}$.
-Since $\mu_1- \mu_{a'} > \varepsilon_{l-2} > \varepsilon_{l-1}S$, we can use the same proof of Claim \ref{clm:l2_exploit} (which rely on Claim \ref{clm:l2_explore} but for smaller $l$'s) to show that there are no arm $a'$ pulls in level $l$ and therefore $\hat{\mu}_a^t - \hat{\mu}_{a'}^t > 0$.
+Since $\mu_1- \mu_{a'} > \varepsilon_{l-2} > \varepsilon_{l-1}\NG$, we can use the same proof of Claim \ref{clm:l2_exploit} (which rely on Claim \ref{clm:l2_explore} but for smaller $l$'s) to show that there are no arm $a'$ pulls in level $l$ and therefore $\hat{\mu}_a^t - \hat{\mu}_{a'}^t > 0$.
 

### 2018-11-02 3levelproofs.tex
C_0,N_0 => \estC, \estN

@@
+%!TEX root = main.tex
+
 \section{Missing proofs from Section~\ref{sec:3level}}
@@
 \begin{lemma}[Concentration of first-level number of pulls.]\label{3levelw1}
-  Let $W_1$ be the event that for all groups $s\in [S]$ and arms
+  Let $W_1$ be the event that for all groups $s\in [\NG]$ and arms
   $a\in \{1, 2\}$, the number of arm $a$ pulls in the $s$-th
@@
   where $\fdpN $ is the expected number of arm $a$ pulls in a $\ALGG$ run
-  of length $\GdT$. Then $\Pr[W_1] \geq 1- \frac{4S}{T^2}$.
+  of length $\GdT$. Then $\Pr[W_1] \geq 1- \frac{4\NG}{T^2}$.
 \end{lemma}
@@
 \begin{lemma}[Concentration of empirical means in the first level]\label{3levelw2}
-  For any $t_1, t_2\in [T]$ such that $t_1 < t_2$, $s\in [S]$, and
+  For any $t_1, t_2\in [T]$ such that $t_1 < t_2$, $s\in [\NG]$, and
   $a\in \{1,2\}$, let $W_2^{s,a,t_1,t_2}$ be the event that the mean
@@
   \[
-    \Pr[W_2] \geq 1- \frac{4S}{T^2}.
+    \Pr[W_2] \geq 1- \frac{4\NG}{T^2}.
   \]
@@
 \begin{lemma}[Co-occurence of high and low deviations]\label{3levelw4}
-  For any group $s\in [S]$, any arm $a$, let $\tilde\mu_{a,s}$ be the
+  For any group $s\in [\NG]$, any arm $a$, let $\tilde\mu_{a,s}$ be the
   empirical mean of the first $\fdpN  T_1$ cells in tape $\cT^1_{a, s}$.
@@
   event that for every $a\in \{1, 2\}$, there exists a group
-  $s_a\in [S]$ in the first level such that both $W_4^{s_a,a,\text{high}}$
+  $s_a\in [\NG]$ in the first level such that both $W_4^{s_a,a,\text{high}}$
   and $W_4^{s_a,3-a,\text{low}}$ occur. Then
@@
 \[
-\Pr[W_1] \geq 1- \frac{4S}{T^2}.
+\Pr[W_1] \geq 1- \frac{4\NG}{T^2}.
 \]
@@
 \[
-\Pr[W_2] \geq 1- \frac{4S}{T^2}.
+\Pr[W_2] \geq 1- \frac{4\NG}{T^2}.
 \]
@@
 \[
-\Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
+\Pr[W_4] \geq 1- 2(1-1/16)^\NG \geq 1 -2 /T.
 \]
@@
   \[
-    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{4\log(T)}{S \fdpN T_1}} .
+    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{4\log(T)}{\NG \fdpN T_1}} .
   \]
@@
 \begin{proof}
-The events $W_1$ and $W_3^{a,t}$ for $t \geq  (\fdpN T_1- \GdT \sqrt{T_1\log(T)})S$ together imply that
+The events $W_1$ and $W_3^{a,t}$ for $t \geq  (\fdpN T_1- \GdT \sqrt{T_1\log(T)})\NG$ together imply that
   \[
-    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{S\left(\fdpN T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{S \fdpN T_1}} .
+    |\bar{\mu}_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{\NG\left(\fdpN T_1- \GdT \sqrt{T_1\log(T)}\right)}} \leq \sqrt{\frac{4\log(T)}{\NG \fdpN T_1}} .
 \]
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} - \frac{C_0}{\sqrt{\fdpN[1]T_1/2}} - \frac{C_0}{\sqrt{\fdpN[2]T_1/2}}\\
-&\geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}- \frac{C_0}{\sqrt{\fdpN[1]T_1/2}} - \frac{C_0}{\sqrt{\fdpN[2]T_1/2}} > 0
+\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1^{1,s} - \bar{\mu}_2^{1,s} - \frac{\estC}{\sqrt{\fdpN[1]T_1/2}} - \frac{\estC}{\sqrt{\fdpN[2]T_1/2}}\\
+&\geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}- \frac{\estC}{\sqrt{\fdpN[1]T_1/2}} - \frac{\estC}{\sqrt{\fdpN[2]T_1/2}} > 0
 \end{align*}
@@
 \[
-\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} - \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}} \geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}}
+\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{\NG\fdpN[1]T_1}} - \sqrt{\frac{4\log(T)}{\NG\fdpN[2]T_1}} \geq  \sqrt{\frac{4\log(T)}{\fdpN[1]T_1}}
 + \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}.
@@
 arm 1.  \OMIT{Therefore the expected regret is at most
-  $S \GdT T_1 = O(T^{4/7} \log^{6/7}(T))$.}
+  $\NG \GdT T_1 = O(T^{4/7} \log^{6/7}(T))$.}
 \end{proof}
@@
 \begin{proof}[Proof of Lemma~\ref{3levelmedium} (Medium gap case)]
-  % $2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} +
-  %   \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right) \leq \mu_1-\mu_2 <
+  % $2\left(\sqrt{\frac{4\log(T)}{\NG\fdpN[1]T_1}} +
+  %   \sqrt{\frac{4\log(T)}{\NG\fdpN[2]T_1}}\right) \leq \mu_1-\mu_2 <
   % 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}} +
@@
 \[
-\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} - \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}} \geq  \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}}
-+ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}.
+\bar{\mu}_1 - \bar{\mu}_2 \geq \mu_1 -\mu_2 - \sqrt{\frac{4\log(T)}{\NG\fdpN[1]T_1}} - \sqrt{\frac{4\log(T)}{\NG\fdpN[2]T_1}} \geq  \sqrt{\frac{4\log(T)}{\NG\fdpN[1]T_1}}
++ \sqrt{\frac{4\log(T)}{\NG\fdpN[2]T_1}}.
 \]
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} - \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
-&\geq  \sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}- \frac{C_0}{\sqrt{S\fdpN[1]T_1/2}} - \frac{C_0}{\sqrt{S\fdpN[2]T_1/2}}\\
+\hat{\mu}_1^t - \hat{\mu}_2^t &>\bar{\mu}_1 - \bar{\mu}_2 - \frac{\estC}{\sqrt{\NG\fdpN[1]T_1/2}} - \frac{\estC}{\sqrt{\NG\fdpN[2]T_1/2}}\\
+&\geq  \sqrt{\frac{4\log(T)}{\NG\fdpN[1]T_1}} + \sqrt{\frac{4\log(T)}{\NG\fdpN[2]T_1}}- \frac{\estC}{\sqrt{\NG\fdpN[1]T_1/2}} - \frac{\estC}{\sqrt{\NG\fdpN[2]T_1/2}}\\
  &> 0.
@@
 \[
-(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}}
+(\NG \GdT T_1 + \NG T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{\fdpN[1]T_1}}
 + \sqrt{\frac{4\log(T)}{\fdpN[2]T_1}}\right) = O(T^{4/7} \log^{6/7}(T))
@@
   % $ 3\sqrt{\frac{2\log(T)}{T_2}} < \mu_1-\mu_2 <
-  % 2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}} +
-  %   \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right)$.
+  % 2\left(\sqrt{\frac{4\log(T)}{\NG\fdpN[1]T_1}} +
+  %   \sqrt{\frac{4\log(T)}{\NG\fdpN[2]T_1}}\right)$.
   In this case, we need both arms to be pulled at least $T_2$ rounds
@@
 \bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} &> \mu_a + \frac{1}{4\sqrt{\fdpN T_1}} -\mu_{3-a} +\frac{1}{4\sqrt{\fdpN[3-a]T_1}} \\
-&> \frac{1}{4\sqrt{\fdpN[1]T_1}}+ \frac{1}{4\sqrt{\fdpN[2]T_1}} - 2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}}
-+ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right) \\
+&> \frac{1}{4\sqrt{\fdpN[1]T_1}}+ \frac{1}{4\sqrt{\fdpN[2]T_1}} - 2\left(\sqrt{\frac{4\log(T)}{\NG\fdpN[1]T_1}}
++ \sqrt{\frac{4\log(T)}{\NG\fdpN[2]T_1}}\right) \\
 &\geq \frac{1}{8\sqrt{\fdpN[1]T_1}}+ \frac{1}{8\sqrt{\fdpN[2]T_1}}.
@@
 \begin{align*}
-\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{C_0}{\sqrt{\fdpN[1]T_1/2}} - \frac{C_0}{\sqrt{\fdpN[2]T_1/2}}\\
-&\geq   \frac{1}{8\sqrt{\fdpN[1]T_1}}+ \frac{1}{8\sqrt{\fdpN[2]T_1}}- \frac{C_0}{\sqrt{\fdpN[1]T_1/2}} - \frac{C_0}{\sqrt{\fdpN[2]T_1/2}}\\
+\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &>\bar{\mu}_a^{1,s_a} - \bar{\mu}_{3-a}^{1,s_a} - \frac{\estC}{\sqrt{\fdpN[1]T_1/2}} - \frac{\estC}{\sqrt{\fdpN[2]T_1/2}}\\
+&\geq   \frac{1}{8\sqrt{\fdpN[1]T_1}}+ \frac{1}{8\sqrt{\fdpN[2]T_1}}- \frac{\estC}{\sqrt{\fdpN[1]T_1/2}} - \frac{\estC}{\sqrt{\fdpN[2]T_1/2}}\\
  &> 0.
@@
 \[
-(S \GdT T_1 + S T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{S\fdpN[1]T_1}}
-+ \sqrt{\frac{4\log(T)}{S\fdpN[2]T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
+(\NG \GdT T_1 + \NG T_2) \cdot 2\left(\sqrt{\frac{4\log(T)}{\NG\fdpN[1]T_1}}
++ \sqrt{\frac{4\log(T)}{\NG\fdpN[2]T_1}}\right) \leq O(T^{4/7} \log^{6/7}(T))
 \]

### 2018-11-02 llevel-overview.tex
ll

@@
 In this section, we give an overview of how we extend our three-level
-policy to an $L$-level policy for $L > 3$ in order to achieve a regret
-rate of $O_K(\sqrt{T} \polylog(T))$. We provide two such policies. The
-first policy achieves the root-$T$ regret rate with $O(\log \log T)$
-levels.
+policy to a more adaptive $L$-level policy for $L > 3$ in order to
+achieve a regret rate of $O_K(\sqrt{T} \polylog(T))$. We provide two
+such policies. The first policy achieves the root-$T$ regret rate with
+$O(\log \log T)$ levels.
 
@@
 For any $L > 3$, there exists an $L$-level disclosure policy with
-regret $$O_K\left(T^{2^{L-1}/(2^L-1)} \polylog(T) \right).$$ In
+regret $$O_K\left(T^{2^{L-1}/(2^L-1)} \cdot \polylog(T) \right).$$ In
 particular, there exists a $O(\log\log(T))$-level recommendation
@@
 levels $L = O(\log(T/\log\log(T)))$ and larger group sizes. We will
-bound its regret as a function of on the gap parameter $\Delta$ even
+bound its regret as a function of the gap parameter $\Delta$ even
 though the construction of the policy does not depend on $\Delta$. In
@@
 every multi-armed bandit instance with gap parameter $\Delta$, the
-policy has regret $$O_K(\min(1/\Delta, T^{1/2})\polylog(T))$$
+policy has regret $$O_K(\min(1/\Delta, T^{1/2}) \cdot \polylog(T))$$
 Moreover, under this policy, each agent $t$ observes a subhistory of
@@
 
-Detailed proofs and discussions of Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2} can be found in Appendix \ref{sec:llevel-details}.
+In this section, we present the main techniques in our solution, and the 
+full proofs of Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2} will be deferred to Appendix \ref{sec:llevel-details}.
 Similarly as Section \ref{sec:3level}, we first prove them in the case of 2 arms (Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel}).
@@
 
-\xhdr{Connecting structures between levels} In our 3-level
+\xhdr{Connecting structures between levels.} In our 3-level
 policy, the second level has $\NG = \Theta(\log(T))$ groups. We do so to

### 2018-11-02 intro.tex
Working on the intro ...

@@
 
-\xhdr{Our scope.} Prior work on incentivizing exploration, with or without monetary incentives, achieves much progress (more on this in ``related work"), but relies heavily on the standard assumptions of Bayesian rationality and the ``power to commit" (\ie users trust the system to implement the mechanism that it claims to implement).
-However, these assumptions are quite problematic when the disclosure policy selectively withholds information, \eg recommends randomly chosen actions to some randomly selected agents (which is a major technique in the prior work).
+\xhdr{Our scope.} Prior work on incentivizing exploration, with or without monetary incentives, achieves much progress (more on this in ``related work"), but relies heavily on the standard assumptions of Bayesian rationality and the ``power to commit" (\ie users trust that the principal actually implements the policy that it claims to implement).
+However, these assumptions appear quite problematic in the context of recommendation systems.
+In particular, disclosure policies studied in prior work merely recommend an action to each agent, without any other supporting information, and moreover recommend exploratory actions to some randomly selected users.
+This works out extremely well in theory, but it is very unclear whether users would trust the principal to implement the stated policy and, even if they do, whether they would react to it rationally.
+Several issues are in play: to wit, whether the principal intentionally uses a different disclosure policy than the claimed one (\eg because its incentives are not quite aligned with the users'), whether the principal correctly implements the policy that it wants to implement, whether the users trust the principal to make correct inferences on their behalf, and whether they find it acceptable that they may be singled out for exploration.
+Furthermore, regardless of how the users react to such disclosure policies, they may prefer not to be subjected to them, and leave the system.
 
-We take a step back and re-examine these assumptions.
-We ask: How would users interpret messages/recommendations generated by a disclosure policy?
-More importantly, how to design disclosure policies that would be interpreted by users in a predictable way, while ensuring good exploration-exploitation balance?
-Without the standard assumptions, which conceptual frameworks can be used to reason about the user response to a disclosure policy in precise terms?
+\ascomment{stable text up to here.}
 
@@
 
-\ascomment{stopped for the day ...}
-
 \xhdr{Related work.}

### 2018-11-02 intro-intro.tex
Splitting off intro-intro for Nicole.

--- 2018-11-02 intro.tex
@@
-\section{Introduction}
-\label{sec:intro}
+\ascomment{Nicole, it is all yours ..}
 
@@
 
-\xhdr{Our scope.} Prior work on incentivizing exploration, with or without monetary incentives, achieves much progress (more on this in ``related work"), but relies heavily on the standard assumptions of Bayesian rationality and the ``power to commit" (\ie users trust the system to implement the mechanism that it claims to implement).
-However, these assumptions are quite problematic when the disclosure policy selectively withholds information, \eg recommends randomly chosen actions to some randomly selected agents (which is a major technique in the prior work).
-
-We take a step back and re-examine these assumptions.
-We ask: How would users interpret messages/recommendations generated by a disclosure policy?
-More importantly, how to design disclosure policies that would be interpreted by users in a predictable way, while ensuring good exploration-exploitation balance?
-Which conceptual framework should we use to reason about the user response to a disclosure policy, in the absence of the standard assumptions?
-
-Consider the \emph{full-disclosure policy} that always reveals all information available to the principal.
-We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it.
-However, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}.
-
-\xhdr{Related work.}
-
-\cite{Perchet2015BatchedBP} gives regret guarantees for mult-armed bandit in $M$ batches. They have 2 upper bounds which are similar to our Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2}.
+\ascomment{ ... up to here.}

### 2018-11-02 intro.tex
Splitting off intro-intro for Nicole.

@@
 
-Recommendation systems are ubiquitous, providing recommendations for movies (\eg  Netflix), products (\eg  Amazon), restaurants (\eg  Yelp), vacations (\eg Tripadvisor), etc.
-A typical recommendation system elicits user feedback about their experiences, and aggregates this feedback in order to provide better recommendations in the future.
-Thus, each user she consumes information from the previous users (indirectly, \eg via recommendations), and produces new information (\eg  a review) that benefits future users.
-This dual role creates a three-way tension between exploration, exploitation, and users' incentives.
-A social planner would balance ``exploration" of insufficiently known alternatives and ``exploitation" of the information acquired so far.
-Designing algorithms to trade off these two objectives is a well-researched subject in machine learning and operations research.
-However, a given user who decides to ``explore" typically suffers all the downside of this decision, whereas the upside (improved recommendations) is spread over many users in the future.
-Therefore, users' incentives are skewed in favor of exploitation.
-As a result, observations may be collected at a slower rate, and may suffer from selection bias (\eg  ratings of a particular movie may mostly come from people who like this type of movies).
-Moreover, in some natural but idealized models (\eg  \cite{Kremer-JPE14,ICexploration-ec15}), there are simple  examples when optimal recommendations are never found because the corresponding actions are never taken.
-
-Thus, we have a problem of \emph{incentivizing exploration}.
-Providing monetary incentives can be financially or technologically unfeasible, and relying on voluntary exploration can lead to selection biases.
-A recent line of work, started by \cite{Kremer-JPE14}, relies on the inherent \emph{information asymmetry} between the recommendation system and a user.
-These papers posit a simple model, termed \emph{Bayesian Exploration} in \cite{ICexplorationGames-ec16}.
-The recommendation system is a ``principal" that interacts with self-interested ``agents" who arrive one by one.
-Each agent needs to make a decision: take an action from a given set of alternatives.
-The principal sends a \emph{message} to the agent according to some ``disclosure policy", \eg issues a recommendation.
-Then the agent chooses an action, and both the agent and the principal observe the outcome.
-Crucially, the principal does not control the agent's decision.
-The problem is to design the disclosure policy for the principal that learns over time to issue messages so as to incentivize the agents to balance exploration and exploitation in a socially optimal way.
-A single round of this model is a version of a well-known ``Bayesian Persuasion game" \cite{Kamenica-aer11}.
+\input{intro-intro.tex}
 
@@
 \ascomment{stable text up to here.}
+
+Our goal is to design disclosure policies which mitigate these issues and (still) incentivize a good balance between exploration and exploitation.
+While some assumptions on human behavior are unavoidable, we are looking for a class of disclosure policies for which we can make plausible behavioral assumptions.
 

### 2018-11-02 intro.tex
Done with "scope", or so it seems.

@@
 
+We strive to design disclosure policies which mitigate these issues and (still) incentivize a good balance between exploration and exploitation.
+While some assumptions on human behavior are unavoidable, we are looking for a class of disclosure policies for which we can make plausible behavioral assumptions.
+Then we arrive at a concrete mathematical problem: design policies from this class so as to optimize performance, \ie  the induced explore-exploit tradeoff.
+Our goal in terms of performance is as ambitious as the one in prior work on incentivizing exploration: essentially, to approach the performance of the social planner.
+
 \ascomment{stable text up to here.}
 
-Our goal is to design disclosure policies which mitigate these issues and (still) incentivize a good balance between exploration and exploitation.
-While some assumptions on human behavior are unavoidable, we are looking for a class of disclosure policies for which we can make plausible behavioral assumptions.
-
+\xhdr{Our contributions.}
 We build one such conceptual framework for a particular type of disclosure policies.

### 2018-11-02 3levelproofs.tex
clean up proofs

@@
 
-\ascomment{I copied this from the 3-level section. This needs to be revised and made consistent, etc.}
+%\ascomment{I copied this from the 3-level section. This needs to be revised and made consistent, etc.}
 
-The following lemma can be derived from combining Lemma~\ref{lem:t1runs} and union bound.
+%\ascomment{end of copy-and-paste}
+
+\subsection{Events}
+
+The following lemmas can be derived from combining Lemma~\ref{lem:t1runs} and union bound.
 
@@
 \end{lemma}
+
+\begin{proof}[Proof of Lemma~\ref{3levelw1}]
+  For the $s$-th first-level group, define $W_1^{a,s}$ to be the event
+  that the number of arm $a$ pulls in the $s$-th first-level group is
+  between $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$ and
+  $\fdpN T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
+\[
+\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
+\]
+Let $W_1$  be the intersection of all these events (i.e.
+$W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
+\[
+\Pr[W_1] \geq 1- \frac{4\NG}{T^2}.
+\]
+\end{proof}
 
@@
 
+\begin{proof}[Proof of Lemma~\ref{3levelw2}]
+  By Chernoff bound,
+\[
+\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
+\]
+By union bound, we have
+\[
+\Pr[W_2] \geq 1- \frac{4\NG}{T^2}.
+\]
+\end{proof}
+
 Our policy also relies on the anti-concentration of the empirical
@@
 
-\begin{lemma}[Co-occurence of high and low deviations]\label{3levelw4}
+\begin{lemma}[Co-occurence of high and low deviations in this first level]\label{3levelw4}
   For any group $s\in [\NG]$, any arm $a$, let $\tilde\mu_{a,s}$ be the
@@
 \end{lemma}
-
-Lastly, we will condition on the event that the empirical means of
-both arms are concentrated around their true means in any prefix of
-their pulls. This guarantees that the policy obtains an accurate
-estimate of rewards for both arms after aggregating all the data in
-the first two levels.
-% We will again state the event using a hypothetical reward tape
-% $\cT^2_a$ for each arm $a$: the $j$-th time arm $a$ is chosen in the
-% two levels, its reward is taken from the $j$-th cell in $\cT^2_a$.
-
-\swcomment{might want to swap out $W_3$ and $W_4$} \nicomment{yes please!}
-
-\begin{lemma}[Concentration of empirical means in the first two
-  levels]\label{3levelw3}
-  With probability at least $1 - \frac{4}{T^3}$, the following event
-  $W_3$ holds: for all $a\in \{1, 2\}$ and $m \in [N_{T, a}]$, the
-  empirical means of the first $t$ \nicomment{what is $t$ here; you mean $m$? in which case please replace $m$ with $t$ in the conditioning and bound} arm $a$ pulls is at most
-  $\sqrt{\frac{2\log(T)}{m}}$ away from $\mu_a$, where $N_{T, a}$ is
-  the total number of arm $a$ pulls by the end of $T$ rounds.
-\end{lemma}
-
-Let $W = \bigcap_{i=1}^4 W_i$ be the intersection of all 4
-events.  By union bound, $W$ occurs with probability $1-O(1/T)$. Note
-that the regret conditioned on $W$ not occurring is at most
-$O(1/T) \cdot T = O(1)$, so it suffices to bound the regret conditioned on $W$.
-
-\ascomment{end of copy-and-paste}
-
-\subsection{Events}
-
-\begin{proof}[Proof of Lemma~\ref{3levelw1}]
-  For the $s$-th first-level group, define $W_1^{a,s}$ to be the event
-  that the number of arm $a$ pulls in the $s$-th first-level group is
-  between $\fdpN T_1- \GdT \sqrt{T_1\log(T)}$ and
-  $\fdpN T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
-\[
-\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
-\]
-Let $W_1$  be the intersection of all these events (i.e.
-$W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
-\[
-\Pr[W_1] \geq 1- \frac{4\NG}{T^2}.
-\]
-\end{proof}
-
-\begin{proof}[Proof of Lemma~\ref{3levelw2}]
-  By Chernoff bound,
-\[
-\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
-\]
-By union bound, we have
-\[
-\Pr[W_2] \geq 1- \frac{4\NG}{T^2}.
-\]
-\end{proof}
 
@@
 
+Lastly, we will condition on the event that the empirical means of
+both arms are concentrated around their true means in any prefix of
+their pulls. This guarantees that the policy obtains an accurate
+estimate of rewards for both arms after aggregating all the data in
+the first two levels.
+% We will again state the event using a hypothetical reward tape
+% $\cT^2_a$ for each arm $a$: the $j$-th time arm $a$ is chosen in the
+% two levels, its reward is taken from the $j$-th cell in $\cT^2_a$.
+
+%\swcomment{might want to swap out $W_3$ and $W_4$} \nicomment{yes please!}
+%\jmcomment{let's follow the order of levels}
+
+\begin{lemma}[Concentration of empirical means in the first two
+  levels]\label{3levelw3}
+  With probability at least $1 - \frac{4}{T^3}$, the following event
+  $W_3$ holds: for all $a\in \{1, 2\}$ and $m \in [N_{T, a}]$, the
+  empirical means of the first $t$ \nicomment{what is $t$ here; you mean $m$? in which case please replace $m$ with $t$ in the conditioning and bound} arm $a$ pulls is at most
+  $\sqrt{\frac{2\log(T)}{m}}$ away from $\mu_a$, where $N_{T, a}$ is
+  the total number of arm $a$ pulls by the end of $T$ rounds.
+\end{lemma}
+
 \begin{proof}[Proof of Lemma~\ref{3levelw3}]
@@
 \end{proof}
+
+Let $W = \bigcap_{i=1}^4 W_i$ be the intersection of all 4
+events.  By union bound, $W$ occurs with probability $1-O(1/T)$. Note
+that the regret conditioned on $W$ not occurring is at most
+$O(1/T) \cdot T = O(1)$, so it suffices to bound the regret conditioned on $W$.
 

### 2018-11-02 app-warmup.tex
clean up proofs

@@
 each cell containing an independent draw of the realized reward from
-the distribution $\cD_a$. Then for each arm $a$ and any $N\in [T]$, we
-can think of the sequence of the first $N$ realized rewards of $a$
-coming from the prefix of $N$ cells in its reward tape. Define
-$W^{a,N}_2$ to be the event that the empirical mean of the first $N$
+the distribution $\cD_a$. Then for each arm $a$ and any $m\in [T]$, we
+can think of the sequence of the first $m$ realized rewards of $a$
+coming from the prefix of $m$ cells in its reward tape. Define
+$W^{a,m}_2$ to be the event that the empirical mean of the first $m$
 realized rewards in the tape of arm $a$ is at most
-$\sqrt{\frac{2\log(T)}{N}}$ away from $\mu_a$. Define $W_2$ to be the
-intersection of these events (i.e.  $\bigcap_{a,N\in[T]} W^{a,N}_2$).  By
+$\sqrt{\frac{2\log(T)}{m}}$ away from $\mu_a$. Define $W_2$ to be the
+intersection of these events (i.e.  $\bigcap_{a,m\in[T]} W^{a,m}_2$).  By
 Chernoff bound,%\swcomment{$t$ may be confusing here}
 \[
-\Pr[W^{a,N}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
+\Pr[W^{a,m}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
 \]

### 2018-11-02 main.tex
Added notation for constants in low-deviation assumption for agents' estimates.
Added a file for the intro.
Added a macro.
Added some macro.
define macro \NG for number of groups
a new macro
abstract added

@@
 \newcommand{\fdpP}{p^\fdp_K} % success prob for greedy path
-\newcommand{\fdpN}[1][a]{N^\fdp_{K,#1}} % Exp #pulls for arm $a$ in greedy path of length L_K.
+\newcommand{\fdpN}[1][a]{N^\fdp_{K,#1}}
+    % Exp #pulls for arm $a$ in greedy path of length L_K.
+
+% new notation for low-deviation assumption on agents' reward estimates
+\newcommand{\estN}{N_{\term{est}}}
+\newcommand{\estC}{C_{\term{est}}}
+
+% notation for 3level section
+\newcommand{\conf}[1]{\mathtt{conf}\left(#1\right)}
+\newcommand{\event}[1]{\ensuremath{\mathtt{event}_{#1}}\xspace}
 
@@
 \newcommand{\DT}{\mD} % Alex' notation for distribution over types.
+
+%number of groups 
+\def\NG{\sigma}
 
@@
 
+%index on the tap
+\def\z{z}
 \title{Incentivizing Exploration with Unbiased History}
@@
 \begin{abstract}
-aaa
+In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world.
+A sequence of agents each choose an action with the goal of maximizing payoff given estimates of the state of the world.
+A recommendation algorithm tries to coordinate the choices of the agents by sending messages about the history of past actions.
+The goal of the algorithm is to minimize the regret of the action sequence.
+
+In this paper, we study a particular class of recommendation algorithms that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards chosen by a subsequence of past agents.
+One trivial message of this form contains the full history; a recommendation algorithm that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.
+Our main result is a recommendation algorithm using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.
+We also exhibit simpler policies with higher, but still sublinear, regret.
+These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.
 \end{abstract}
@@
 
+\input{intro}
 \input{model}

### 2018-11-02 3levelproofs.tex
clean up appendix C

@@
 \begin{lemma}[Concentration of empirical means in the first level]\label{3levelw2}
-  For any $t_1, t_2\in [T]$ such that $t_1 < t_2$, $s\in [\NG]$, and
-  $a\in \{1,2\}$, let $W_2^{s,a,t_1,t_2}$ be the event that the mean
-  among the cells indexed by $t_1, (t_1+1), \ldots, t_2$ in the tape
-  $\cT^1_{a, s}$ is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away
+  For any $\z_1, \z_2\in [T]$ such that $\z_1 < \z_2$, $s\in [\NG]$, and
+  $a\in \{1,2\}$, let $W_2^{s,a,\z_1,\z_2}$ be the event that the mean
+  among the cells indexed by $\z_1, (\z_1+1), \ldots, \z_2$ in the tape
+  $\cT^1_{a, s}$ is at most $\sqrt{\frac{2\log(T)}{\z_2-\z_1+1}}$ away
   from $\mu_a$.  Let $W_2$ be the intersection of all these events
-  (i.e.  $W_2 = \bigcap_{a,s,t_1,t_2} W_2^{s,a,t_1,t_2}$). Then
+  (i.e.  $W_2 = \bigcap_{a,s,\z_1,\z_2} W_2^{s,a,\z_1,\z_2}$). Then
   \[
@@
 \[
-\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
+\Pr[W_2^{s,a,\z_1,\z_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
 \]
@@
   empirical mean of the first $\fdpN  T_1$ cells in tape $\cT^1_{a, s}$.
-  Let $W_4^{s,a,\text{high}}$ be the event
+  Let $W_3^{s,a,\text{high}}$ be the event
   $\tilde\mu_{a, s} \geq \mu_a + 1/\sqrt{\fdpN  T_1}$ and let
-  $W_4^{s,a,\text{low}}$ be the event that
-  $\tilde\mu_{a, s} \leq \mu_a - 1/\sqrt{\fdpN  T_1}$.  Let $W_4$ be the
+  $W_3^{s,a,\text{low}}$ be the event that
+  $\tilde\mu_{a, s} \leq \mu_a - 1/\sqrt{\fdpN  T_1}$.  Let $W_3$ be the
   event that for every $a\in \{1, 2\}$, there exists a group
-  $s_a\in [\NG]$ in the first level such that both $W_4^{s_a,a,\text{high}}$
-  and $W_4^{s_a,3-a,\text{low}}$ occur. Then
+  $s_a\in [\NG]$ in the first level such that both $W_3^{s_a,a,\text{high}}$
+  and $W_3^{s_a,3-a,\text{low}}$ occur. Then
   \[
-    \Pr[W_4]\geq 1 -2 /T.
+    \Pr[W_3]\geq 1 -2 /T.
   \]
@@
 \[
-\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{\fdpN T_1}} > 1/4.
+\Pr[W_3^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{\fdpN T_1}} > 1/4.
 \]
@@
 \[
-\Pr[W_4^{s,a,low}] > 1/4.
+\Pr[W_3^{s,a,low}] > 1/4.
 \]
-Since $W_4^{s,a,high}$ is independent with $W_4^{s,3-a,low}$, we have
+Since $W_3^{s,a,high}$ is independent with $W_3^{s,3-a,low}$, we have
 \[
-\Pr[W_4^{s,a,high} \cap W_4^{s,3-a,low}] =\Pr[W_4^{s,a,high}] \cdot  \Pr[W_4^{s,3-a,low}]>(1/4)^2 = 1/16.
+\Pr[W_3^{s,a,high} \cap W_3^{s,3-a,low}] =\Pr[W_3^{s,a,high}] \cdot  \Pr[W_3^{s,3-a,low}]>(1/4)^2 = 1/16.
 \]
-Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent
+Notice that $(W_3^{s,a,high} \cap W_3^{s,3-a,low})$ are independent
 across different $s$'s. By union bound, we have
 \[
-\Pr[W_4] \geq 1- 2(1-1/16)^\NG \geq 1 -2 /T.
+\Pr[W_3] \geq 1- 2(1-1/16)^\NG \geq 1 -2 /T.
 \]
@@
   With probability at least $1 - \frac{4}{T^3}$, the following event
-  $W_3$ holds: for all $a\in \{1, 2\}$ and $m \in [N_{T, a}]$, the
-  empirical means of the first $t$ \nicomment{what is $t$ here; you mean $m$? in which case please replace $m$ with $t$ in the conditioning and bound} arm $a$ pulls is at most
-  $\sqrt{\frac{2\log(T)}{m}}$ away from $\mu_a$, where $N_{T, a}$ is
+  $W_4$ holds: for all $a\in \{1, 2\}$ and $\z \in [N_{T, a}]$, the
+  empirical means of the first $\z$ 
+  %\nicomment{what is $t$ here; you mean $m$? in which case please replace $m$ with $t$ in the conditioning and bound} 
+  arm $a$ pulls is at most
+  $\sqrt{\frac{2\log(T)}{\z}}$ away from $\mu_a$, where $N_{T, a}$ is
   the total number of arm $a$ pulls by the end of $T$ rounds.
@@
   is chosen in the first two levels, its reward is taken from the
-  $j$-th cell in the tape. Define $W_3^{a,t}$ to be the event that the
+  $j$-th cell in the tape. Define $W_4^{a,\z}$ to be the event that the
   mean of the first $t$ pulls in the tape is at most
-  $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. By Chernoff bound,
+  $\sqrt{\frac{2\log(T)}{\z}}$ away from $\mu_a$. By Chernoff bound,
 \[
-\Pr[W_3^{a,t}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
+\Pr[W_4^{a,\z}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
 \]
@@
 \[
-\Pr[W_3] \geq 1- \frac{4}{T^3}.
+\Pr[W_4] \geq 1- \frac{4}{T^3}.
 \]
@@
 \begin{proof}
-  The events $W_1$ and $W_2^{a,s,1,t}$ for
-  $t = \fdpN T_1- \GdT \sqrt{T_1\log(T)},...,\fdpN T_1 + \GdT
+  The events $W_1$ and $W_2^{a,s,1,\z}$ for
+  $\z = \fdpN T_1- \GdT \sqrt{T_1\log(T)},...,\fdpN T_1 + \GdT
   \sqrt{T_1\log(T)}$ together imply that
@@
 \begin{proof}
-The events $W_1$ and $W_3^{a,t}$ for $t \geq  (\fdpN T_1- \GdT \sqrt{T_1\log(T)})\NG$ together imply that
+The events $W_1$ and $W_4^{a,\z}$ for $\z \geq  (\fdpN T_1- \GdT \sqrt{T_1\log(T)})\NG$ together imply that
   \[
@@
 \begin{proof}% [Proof of Lemma~\ref{lem:luck}]
-  For each $a \in \{1,2\}$, $W_4$ implies that there exists $s_a$ such
-  that both $W_4^{s_a,a,high}$ and $W_4^{s_a,3-a,low}$ happen.  The
-  events $W_4^{s_a,a,high}$, $W_1$, $W_2^{s_a,a,t, \fdpN T_1}$
-  for $t = \fdpN T_1- \GdT \sqrt{T_1\log(T)}+1, ...,\fdpN T_1-1$ and
-  $W_2^{s_a,a,\fdpN T_1,t}$ for
-  $t= \fdpN T_1,...,\fdpN T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
+  For each $a \in \{1,2\}$, $W_3$ implies that there exists $s_a$ such
+  that both $W_3^{s_a,a,high}$ and $W_3^{s_a,3-a,low}$ happen.  The
+  events $W_3^{s_a,a,high}$, $W_1$, $W_2^{s_a,a,\z, \fdpN T_1}$
+  for $\z = \fdpN T_1- \GdT \sqrt{T_1\log(T)}+1, ...,\fdpN T_1-1$ and
+  $W_2^{s_a,a,\fdpN T_1,\z}$ for
+  $\z= \fdpN T_1,...,\fdpN T_1+ \GdT \sqrt{T_1\log(T)}$ together imply that
 \begin{align*}

### 2018-11-02 app-warmup.tex
clean up appendix C

@@
 each cell containing an independent draw of the realized reward from
-the distribution $\cD_a$. Then for each arm $a$ and any $m\in [T]$, we
-can think of the sequence of the first $m$ realized rewards of $a$
-coming from the prefix of $m$ cells in its reward tape. Define
-$W^{a,m}_2$ to be the event that the empirical mean of the first $m$
+the distribution $\cD_a$. Then for each arm $a$ and any $\z\in [T]$, we
+can think of the sequence of the first $\z$ realized rewards of $a$
+coming from the prefix of $\z$ cells in its reward tape. Define
+$W^{a,\z}_2$ to be the event that the empirical mean of the first $\z$
 realized rewards in the tape of arm $a$ is at most
-$\sqrt{\frac{2\log(T)}{m}}$ away from $\mu_a$. Define $W_2$ to be the
-intersection of these events (i.e.  $\bigcap_{a,m\in[T]} W^{a,m}_2$).  By
+$\sqrt{\frac{2\log(T)}{\z}}$ away from $\mu_a$. Define $W_2$ to be the
+intersection of these events (i.e.  $\bigcap_{a,\z\in[T]} W^{a,\z}_2$).  By
 Chernoff bound,%\swcomment{$t$ may be confusing here}
 \[
-\Pr[W^{a,m}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
+\Pr[W^{a,\z}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
 \]

### 2018-11-02 intro-intro.tex

@@
+\nicomment{a proposed abstract since i don't have the token on main.tex:}
+
+In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world.
+A sequence of agents each choose an action with the goal of maximizing payoff given estimates of the state of the world.
+A recommendation algorithm tries to coordinate the choices of the agents by sending messages about the history of past actions.
+The goal of the algorithm is to minimize the regret of the action sequence.
+
+In this paper, we study a particular class of recommendation algorithms that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards chosen by a subsequence of past agents.
+One trivial message of this form contains the full history; a recommendation algorithm that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.
+Our main result is a recommendation algorithm using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.
+We also exhibit simpler policies with higher, but still sublinear, regret.
+These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.
+
+\nicomment{and now for the intro to the intro.}
+
+In {\em incentivized exploration}, a recommendation algorithm presents a sequence of agents
+
+In social learning, a sequence of individuals choose actions based on observations of past choices.
+Incentivized exploration algorithms coordinate social learning, hiding inducing sufficient exploration
+
 \ascomment{Nicole, it is all yours ..}

### 2018-11-02 intro.tex

@@
 
-\ascomment{stable text up to here.}
-
 \xhdr{Our contributions.}
-We build one such conceptual framework for a particular type of disclosure policies.
-Consider the \emph{full-disclosure policy} that reveals the full history of observations from the previous users.
+We start by revisiting the \emph{full-disclosure policy} that reveals the full history of observations from the previous users.
 We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it.
 Unfortunately, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}.
-However, for the sake of the argument, what if the policy reveals the history for every other agent, rather than the history for all agents?
+However, for the sake of the argument, what if a disclosure policy reveals the outcomes for every other agent, rather than the outcomes for all agents?
 We posit that users would trust such policy, too.
 Given a large volume of data, we posit that users would not be too unhappy with having access to only a fraction this data.
-A crucial aspect of our intuition here is that the ``subhistory" revealed to a given user is chosen in advance, without looking at the observations.
-In particular, the disclosure policy cannot subsample the observations that make a particular action look good.
+A crucial aspect of our intuition here is that the ``subhistory" revealed to a given user comes from a subset of previous users that is chosen in advance, without looking at what happens during the execution.
+In particular, the subhistory is not ``biased", in the sense that the disclosure policy cannot subsample the observations in favor of a particular action.
+
+With this intuition in mind, we define the class of \emph{unbiased-subhistory policies}: disclosure policies that reveal, to each arriving agent $t$, a subhistory  consisting of the outcomes for a subset $S_t$ of previous agents, where $S_t$ is chosen ahead of time.
+Further, we impose a transitivity property: if $t' \in S_t$, for some previous agent $t'$, then $S_{t'}\subset S_t$.
+So, agent $t$ has all information that agent $t'$ had at the time she chose her action.
+In particular, agent $t$ does not need to second-guess which message has caused aget $t'$ to make choose that action.
+
+\ascomment{stable text up to here.}
 

### 2018-11-02 llevel.tex
ll
notation change in llevel proof

@@
  For each agent $t$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in agent $t$'s observed history pull arm $a$.
-Define $W_2^{t,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{3\log(T)}{t_2-t_1+1}}$ away from $\mu_a$.
+Define $W_2^{t,a,\z_1,\z_2}$ to be the event that the mean of $\z_1$-th to $\z_2$-th pulls in the tape is at most $\sqrt{\frac{3\log(T)}{\z_2-\z_1+1}}$ away from $\mu_a$.
 By Chernoff bound,
 \[
-\Pr[W_2^{t,a,t_1,t_2}] \geq 1 - 2\exp(-6\log(T)) \geq 1- 2/T^6.
+\Pr[W_2^{t,a,\z_1,\z_2}] \geq 1 - 2\exp(-6\log(T)) \geq 1- 2/T^6.
 \]
 
-Define $W_2$ to be the intersection of all these events (i.e. $W_2 = \bigcap_{t,a,t_1,t_2} W_2^{t,a,t_1,t_2}$). By union bound, we have
+Define $W_2$ to be the intersection of all these events (i.e. $W_2 = \bigcap_{t,a,\z_1,\z_2} W_2^{t,a,\z_1,\z_2}$). By union bound, we have
 \[
@@
 $W_1,W_2,W_3,W_4$) in Theorem \ref{thm:llevel} to the case when $K$ is larger than 2.
-$W_1$ and $W_2$ extend naturally: we still set $W_1 = \bigcap_{a,s}W_1^{a,s}$ and $W_2 = \bigcap_{t,a,t_1,t_2} W_2^{t,a,t_1,t_2}$.
+$W_1$ and $W_2$ extend naturally: we still set $W_1 = \bigcap_{a,s}W_1^{a,s}$ and $W_2 = \bigcap_{t,a,\z_1,\z_2} W_2^{t,a,\z_1,\z_2}$.
 The difference is that now $a$ is taken over $K$ arms instead of 2 arms.
@@
 \qed
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2018-11-02 intro.tex
minor edit.

@@
 
-\xhdr{Our contributions.}
-We start by revisiting the \emph{full-disclosure policy} that reveals the full history of observations from the previous users.
+\xhdr{Our model.}
+For the sake of intuition, let us revisit the \emph{full-disclosure policy} that reveals the full history of observations from the previous users.
 We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it.
 Unfortunately, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}.
-However, for the sake of the argument, what if a disclosure policy reveals the outcomes for every other agent, rather than the outcomes for all agents?
+However, what if a disclosure policy reveals the outcomes for every other agent, rather than the outcomes for all agents?
 We posit that users would trust such policy, too.
@@
 So, agent $t$ has all information that agent $t'$ had at the time she chose her action.
-In particular, agent $t$ does not need to second-guess which message has caused aget $t'$ to make choose that action.
+In particular, agent $t$ does not need to second-guess which message has caused agent $t'$ to make choose that action.
 

### 2018-11-02 intro-intro.tex
intro to intro

--- 2018-11-02 intro-intro.tex
@@
-\ascomment{Nicole, it is all yours ..}
+In the classic literature on multi-armed bandits, an agent repeatedly selects one of a set of actions, each of which has a payoff drawn from an unknown fixed distribution.
+Over time, she can trade off {\em exploitation}, in which she picks an action to maximize her expected reward, with {\em exploration}, in which she takes potentially sub-optimal actions to learn more about their rewards.
+By coordinating her actions across time, she can guarantee an average reward which converges to that of the optimal action in hindsight at a rate proportional to the inverse square-root of the time horizon.
+
+In many decision problems of interest, the actions are not chosen by a single agent, as above, but rather a sequence of agents.
+In such settings, each agent will choose an exploitive action as the benefits of explorative actions are only accrued by future agents.
+For example, in online retail, products are purchased by a sequence of customers, each of which buys what she estimates to be the best available product.
+This behavior can cause herding, in which all agents eventually take a sub-optimal action of maximum expected payoff given the available information.
+
+This situation can be circumvented by a centralized algorithm that induces agents to take explorative actions, a line of work called {\em incentivizing exploration}.
+One way to induce exploration is to introduce payments~\cite{}.
+For example, an online retailer can give coupons to agents for trying certain products.
+When payments are financially or technologically infeasible, another alternative is to rely on {\em information asymmetry}~\cite{Kremer-JPE14}.
+Here the idea is that the centralized algorithm can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.
+Importantly, agents can not directly observe the past, but only learn about it through this message.
+The agent then chooses an action, using the content of the message as input.
+These systems are often referred to as {\em recommendation systems} as the content of the message can be interpreted as a recommendation for a particular action.
+
+\ascomment{Nicole, it is all yours ..} \nicomment{So now I propose skipping from here to the ``Our scope'' part.
+BTW I'd be in favor of deleting those headers (except for the related work one).
+Just breaks the flow imo.}
 

### 2018-11-02 intro-intro.tex
Commented out my old text.

@@
 
-\ascomment{Nicole, it is all yours ..} \nicomment{So now I propose skipping from here to the ``Our scope'' part.
-BTW I'd be in favor of deleting those headers (except for the related work one).
-Just breaks the flow imo.}
-
+\OMIT{ %%% Alex's original text
 Recommendation systems are ubiquitous, providing recommendations for movies (\eg  Netflix), products (\eg  Amazon), restaurants (\eg  Yelp), vacations (\eg Tripadvisor), etc.
@@
 A single round of this model is a version of a well-known ``Bayesian Persuasion game" \cite{Kamenica-aer11}.
-
-\ascomment{ ... up to here.}
+} %%%%%%%%

### 2018-11-02 2level.tex
Minor edit in figure.
Moved the assn back to prelims.

@@
   \node at(8,0.5){$\cdots$};
-  \node at(5,2.5){$T -T_1 \cdot \fdpL$ rounds};
+  \node at(5,2.5){all remaining rounds};
   \node at(0.5,0.5){$\fdpL$};
@@
 
-The proofs can be found in Appendix~\ref{app:warmup}. To simplify presentation, here and elsewhere we make the following assumption (which can be removed at the cost of a somewhat lengthier proofs).
-
-\begin{assumption}\label{ass:simplifying}
-In each round $t$, the estimates $\hat{\mu}_{t,a}$ depend only on the multiset
-    $\left\{\; (a_s,r_s):\;s\in S_t \;\right\}$,
-called \emph{anonymized subhistory}. Each agent $t$ forms its estimates according to the same \emph{estimate function}: a function $f_t$ from subhistories to $[0,1]^K$, so that the estimate vector
-        $(\hat{\mu}_{t,a}:\, a\in\A)$
-equals $f_t(m_t)$. This function is drawn from some fixed distribution over estimate functions.
-\end{assumption}
-
-Among other things, this assumption allows us to the define the expected number of samples of a given arm $a$ collected by a full-disclosure path $S$ of length $\fdpL$ (\ie present in the subhistory $\SubH{S}$.
+The proofs can be found in Appendix~\ref{app:warmup}.
+One important quantity is the expected number of samples of a given arm $a$ collected by a full-disclosure path $S$ of length $\fdpL$ (\ie present in the subhistory $\SubH{S}$.
 Indeed, this number, denoted $\fdpN$, is the same for all such paths.

### 2018-11-02 model.tex
some edit.
Moved the assn back to prelims.

@@
 \label{sec:model}
-\cite{Perchet2015BatchedBP} gives regret guarantees for mult-armed bandit in $M$ batches. They have 2 upper bounds which are similar to our Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2}.
 
@@
 
-We allow a much more permissive model that allows each agent to form arbitrary reward estimates as long as they lie within some ``confidence range" of the sample average.
-Formally, the model is characterized by the following assumption (which we make without further notice).
+We allow a much more permissive model that allows agents to form arbitrary reward estimates as long as they lie within some ``confidence range" of the sample average.
+Formally, the model is characterized by the following assumptions (which we make without further notice).
 
@@
 (NB: we make no assumption if $1\leq N_{t,a}<\estN$.)
+\end{assumption}
+
+\begin{assumption}\label{ass:simplifying}
+In each round $t$, the estimates $\hat{\mu}_{t,a}$ depend only on the multiset
+    $\left\{\; (a_s,r_s):\;s\in S_t \;\right\}$,
+called \emph{anonymized subhistory}. Each agent $t$ forms its estimates according to an \emph{estimate function} $f_t$ from anonymized subhistories to $[0,1]^K$, so that the estimate vector
+        $(\hat{\mu}_{t,a}:\, a\in\A)$
+equals $f_t(m_t)$. This function is drawn from some fixed distribution over estimate functions.
 \end{assumption}

### 2018-11-02 intro.tex
Pushed intro/our model.

@@
 However, these assumptions appear quite problematic in the context of recommendation systems.
-In particular, disclosure policies studied in prior work merely recommend an action to each agent, without any other supporting information, and moreover recommend exploratory actions to some randomly selected users.
+In particular, much of the prior work suggests disclosure policies that merely recommend an action to each agent, without any other supporting information, and moreover recommend exploratory actions to some randomly selected users.
 This works out extremely well in theory, but it is very unclear whether users would trust the principal to implement the stated policy and, even if they do, whether they would react to it rationally.
@@
 Then we arrive at a concrete mathematical problem: design policies from this class so as to optimize performance, \ie  the induced explore-exploit tradeoff.
-Our goal in terms of performance is as ambitious as the one in prior work on incentivizing exploration: essentially, to approach the performance of the social planner.
+Our goal in terms of performance is to approach the performance of the social planner.
 
@@
 
-\ascomment{stable text up to here.}
+Following much of the prior work on incentivizing exploration, we do not attempt to model heterogenous agent preferences and non-stationarity.
+Formally, we assume that the expected reward of taking a given action $a$, denoted $\mu_a$, is the same for all agents, and does not change over time.
+Then the crucial parameter of interest, for a given action $a$, are the number of samples $N_a$ and the empirical mean reward $\bar{\mu}_a$ in the observed subhistory.
+We consider a flexible model of agent response: for each action $a$ an agent forms an estimate $\hat{\mu}_a$ of the mean reward $\mu_a$, roughly following $\bar{\mu}_a$ but taking into account the uncertainty due to a small number of samples, and chooses an action with a largest reward estimate.
+We allow the reward estimates to be arbitrary otherwise, and not known to the principal.
+
+We measure the machine learning performance of a disclosure policy in terms of \emph{regret}, a standard notion from online machine learning.
+Regret is defined as the difference in the total expected reward between the best fixed action and actions induced by the policy.
+
+\xhdr{Our results.}
+We design transitive unbiased-subhistory policies with near-optimal regret.
+
+\ascomment{stable-ish text up to here.}
 

### 2018-11-02 intro-intro.tex
added a comment.

@@
 These systems are often referred to as {\em recommendation systems} as the content of the message can be interpreted as a recommendation for a particular action.
+
+\ascomment{Nicole: It would be good to introduce "disclosure policy" (= online algorithm that chooses messages, in the context of incentivizing exploration).
+And also talk about recommendation system as smth that exists regardless of incentivizing exploration, and is very common/important out there.}
 

### 2018-11-02 3level.tex
,
Edits for a slightly better notation in construction.

@@
 
-\jmcomment{$\NG$ is also used in Lemma 3.6.
+\jmcomment{$N_2$ is also used in Lemma 3.6.
 We need to find another notation.
@@
 Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot \NG\cdot \fdpL$ rounds in the first layer.
-There is a 1-1 correspondence between first-level groups $S_1$ and second-level groups $S_2$, whereby each agent $t\in S_2$ observes the full history from the corresponding group $S_1$.
-More formally, agent $t$ is connected to the last node of each full-disclosure path in $S_1$.
+There is a 1-1 correspondence between first-level groups $G$ and second-level groups $G'$, whereby each agent in $G'$ observes the full history from the corresponding group $G$.
+More formally, agent in $G'$ is connected to the last node of each full-disclosure path in $G$.
 In other words, this agent receives message
-    $m_t = \SubH{V(S_1)}$,
-where $V(S_1)$ is the set of all rounds in $S_1$.
+    $\SubH{S}$,
+where $S$ is the set of all rounds in $G$.
 \end{construction}

### 2018-11-02 3level.tex
One more minor edit.

@@
 
-The middle level consists of $\NG$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}. Each second-level group $S$ has the following property:
+The middle level consists of $\NG$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}. Each second-level group $G$ has the following property:
 \begin{align}\label{eq:group-defn}
-\text{all nodes in $S$ are connected to the same nodes outside of $S$, but not to one another.}
+\text{all nodes in $G$ are connected to the same nodes outside of $G$, but not to one another.}
 \end{align}

### 2018-11-02 llevel-overview.tex
in the middle

@@
 \ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$.  It
-also has the desirable property that the policy does not conceal too
+also has the desirable property that the policy does not withhold too
 much information from agents---any agent $t$ observes a good fraction
@@
 \end{theorem}
-\swcomment{think the theorem statement implies independence of
-  $\Delta$}
 
-In this section, we present the main techniques in our solution, and the 
-full proofs of Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2} will be deferred to Appendix \ref{sec:llevel-details}.
-Similarly as Section \ref{sec:3level}, we first prove them in the case of 2 arms (Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel}).
-We then extend them to the case of constant number of arms (Theorem \ref{thm:constarm}).
+Note for constant number of arms, this result mathches the optimal
+regret rate (given in \Cref{eq:model-OptRegret}) for stochastic
+bandits, up to logarithmic factors.
 
-We will now present the main idea of extending from 3-level to
+In this section, we present the main techniques in our solution, and
+the full proofs of Theorem \ref{thm:llevel-1} and Theorem
+\ref{thm:llevel-2} will be deferred to Appendix
+\ref{sec:llevel-details}. Similarly as Section \ref{sec:3level}, we
+first prove them in the case of 2 arms (Theorem \ref{thm:llevel} and
+Corollary \ref{cor:llevel}). We then extend them to the case of
+constant number of arms (Theorem \ref{thm:constarm}).
+
+A natural idea to extend the three-level policy is to insert more
+levels as multiple ``check points", so the policy can incentivize the
+agents to perform more adaptive exploration. However, we need to
+introduce two main modifications in the info-graph two accomendate
+some new challenges. We will first informally describe our techniques
+the two-arm case.
+
+% \begin{description}
+% \item[Challenge 1] \emph{Exponentially growing number of groups.} 
+% \item[Challenge 2] \emph{Uncertain number of arm pulls.}  
+% \end{description}
+
+\OMIT{We will now present the main idea of extending from 3-level to
   $L$-level is that instead of using the second level as one
-``check-point'', we use more levels to have multiple ``check points''.
-Some new challenges appear in this process. Here we give an overview
-of the additional techniques we use to get our $L$-level results.
+  ``check-point'', we use more levels to have multiple ``check
+  points''.  Some new challenges appear in this process. Here we give
+  an overview of the additional techniques we use to get our $L$-level
+  results.}
 
-\xhdr{Connecting structures between levels.} In our 3-level
-policy, the second level has $\NG = \Theta(\log(T))$ groups. We do so to
-ensure that in the small gap case (Lemma \ref{3levelsmallcase}), with
-high probability, both arms are pulled enough times in the second
-level. The argument relies on the fact that agents in different
-second-level groups observe disjoint histories of the first level and
-the independent randomness in first level groups guarantees each arm
-$a$ to have a ``lucky'' second-level group such that agents in that
-group all pull arm $a$ with high probability.
+\paragraph{Interlacing connections between levels.}A tempted approach
+to generalize the three-level policy is to build an $L$-level
+info-graph with the structure of a $\NG$-ary tree: for every
+$l\in \{2, \ldots , L\}$, each $l$-level group observes the
+sub-history from a disjoint set $\NG$ groups in level $(l-1)$. The
+disjoint sub-histories observed by all the groups in level $l$ are
+independent, and under the small gap regime (similar to
+Lemma~\ref{3levelsmallcase}) it ensures that each arm $a$ has a
+``lucky'' $l$-level group of agents that only pull $a$. This ``lucky''
+property is crucial for ensuring that both arms will be explored in
+level $l$.
 
-Simply generalizing this idea to an $L$-level policy would give us a $\NG$-ary tree like structure and the first level will have $\NG^{L-1}$ groups.
-It incurs an extra $\NG^{\Omega(L)}$ factor in the regret.
-If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor super poly-logarithmic.
-If we use $\log(T)/\log\log(T)$ levels as in Theorem \ref{thm:llevel-2}, this factor goes up to polynomial in $T$.
+However, in this construction, the first level will have $\NG^{L-1}$
+groups, which incurs $\NG^{\Omega(L)}$ regret. The exponential
+dependence in $L$ will heavily limit the adaptivity of the policy, and
+prevents having the number of levels for obtaining the result in
+\Cref{thm:llevel-2}. To overcome this, we will design an info-graph
+structure such that the number of groups at each level stays as
+$\sigma^2 = \Theta(\log^2(T))$.
 
-In order to avoid this undesirable factor, we design a slightly different connecting structure between levels in our $L$-level policy.
-The key observation is that, for any level $l \in \{3,...,L-1\}$, we do want agents in different $l$-th level groups to see disjoint histories of the $(l-1)$-th level to ensure that there is some ``lucky'' group for each arm whose mean is close enough to the best arm.
-However, it does not matter much if pulls in levels below $l-1$ get observed by agents in different $l$-th level groups because group sizes in lower levels are much smaller than group sizes of level $l-1$ and the independent randomness in level $l-1$ is sufficient.
+We will leverage the following key observation: in order to maintain
+the ``lucky'' property, it suffices to have agents in different $l$-th
+level groups to observe disjoint sub-histories that takes place in
+level $(l - 1)$. Moreover, as long as the group size in levels lower
+than $(l-1)$ are substantially smaller than group size of level $l-1$,
+the ``lucky'' property does not break even if different groups in
+level $l$ observe overlapping sub-history from levels
+$\{1, \ldots, l-2\}$.
+
+\OMIT{In our 3-level policy, the second level has
+  $\NG = \Theta(\log(T))$ groups. We do so to ensure that in the small
+  gap case (Lemma \ref{3levelsmallcase}), with high probability, both
+  arms are pulled enough times in the second level. The argument
+  relies on the fact that agents in different second-level groups
+  observe disjoint histories of the first level and the independent
+  randomness in first level groups guarantees each arm $a$ to have a
+  ``lucky'' second-level group such that agents in that group all pull
+  arm $a$ with high probability.
+
+  Simply generalizing this idea to an $L$-level policy would give us a
+  $\NG$-ary tree like structure and the first level will have
+  $\NG^{L-1}$ groups. It incurs an extra $\NG^{\Omega(L)}$ factor in
+  the regret. If we use $\log\log(T)$ levels as in Theorem
+  \ref{thm:llevel-1}, this factor super poly-logarithmic. If we use
+  $\log(T)/\log\log(T)$ levels as in Theorem \ref{thm:llevel-2}, this
+  factor goes up to polynomial in $T$.
+
+  In order to avoid this undesirable factor, we design a slightly
+  different connecting structure between levels in our $L$-level
+  policy.  The key observation is that, for any level
+  $l \in \{3,...,L-1\}$, we do want agents in different $l$-th level
+  groups to see disjoint histories of the $(l-1)$-th level to ensure
+  that there is some ``lucky'' group for each arm whose mean is close
+  enough to the best arm. However, it does not matter much if pulls in
+  levels below $l-1$ get observed by agents in different $l$-th level
+  groups because group sizes in lower levels are much smaller than
+  group sizes of level $l-1$ and the independent randomness in level
+  $l-1$ is sufficient.}
 
@@
 They get ``lucky'' for some arm at the same time.\\
-(iii) For each set of groups in level $l-1$, agents in level $l$ see the history of agents in one of these groups.
-Therefore, for each arm $a$, we just need one set of groups in level $l-1$ to get ``lucky'' and then all agents in level $l$ will see enough pulls of arm $a$.
+(iii) For each set of groups in level $l-1$, agents in level $l$ see
+the history of agents in one of these groups. Therefore, for each arm
+$a$, we just need one set of groups in level $l-1$ to get ``lucky''
+and then all agents in level $l$ will see enough pulls of arm $a$.
 

### 2018-11-02 llevel-overview.tex
editing...

@@
 some new challenges. We will first informally describe our techniques
-the two-arm case.
+for the two-arm case.
 
@@
 We will leverage the following key observation: in order to maintain
-the ``lucky'' property, it suffices to have agents in different $l$-th
-level groups to observe disjoint sub-histories that takes place in
-level $(l - 1)$. Moreover, as long as the group size in levels lower
-than $(l-1)$ are substantially smaller than group size of level $l-1$,
-the ``lucky'' property does not break even if different groups in
-level $l$ observe overlapping sub-history from levels
+the ``lucky'' property, it suffices to have the agents in different
+$l$-th level groups to observe disjoint sub-histories that takes place
+in level $(l - 1)$. Moreover, as long as the group size in levels
+lower than $(l-1)$ are substantially smaller than group size of level
+$l-1$, the ``lucky'' property does not break even if different groups
+in level $l$ observe overlapping sub-history from levels
 $\{1, \ldots, l-2\}$.

### 2018-11-02 3level.tex
a typo

@@
 We need to ensure that both arms continue to be explored in the second level.
-To achieve this, we leverage \event[4], which implies
+To achieve this, we leverage \event{4}, which implies
 that each arm $a$ has a first-level group $s_a$ where it gets ``lucky", in the sense that its empirical mean reward is slightly higher than $\mu_a$, while the empirical mean reward of the other arm is slightly lower than its true mean.

### 2018-11-02 llevel-overview.tex
editing...

@@
 
-For each level, our $L$-level policy has $\NG^2$ groups for some $\NG = \Theta(\log(T))$.
+This motivates the following interlacing connection structure between levels.
+For each level in the info-graph, there are  $\NG^2$ groups for some $\NG = \Theta(\log(T))$.
 The groups in the $l$-th level are labeled as $G_{l,u,v}$ for $u,v\in[\NG]$.
@@
 See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level).
-This connecting structure has three nice properties: \\
-(i) The number of groups does not grow with $L$ and stays as $\NG^2 = \Theta(\log^2(T))$ in each level. Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\
-(ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,\NG,v}$ (e.g.
+
+This connecting structure has the following nice properties: \\
+\OMIT{(i) The number of groups does not grow with $L$ and stays as $\NG^2 = \Theta(\log^2(T))$ in each level.
+Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
+(i) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,\NG,v}$ (e.g.
 $G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l-1$ and $v$.
@@
 They get ``lucky'' for some arm at the same time.\\
-(iii) For each set of groups in level $l-1$, agents in level $l$ see
+(ii) For each set of groups in level $l-1$, agents in level $l$ see
 the history of agents in one of these groups. Therefore, for each arm

### 2018-11-02 llevel-overview.tex
editing...

@@
 
-This motivates the following interlacing connection structure between levels.
-For each level in the info-graph, there are  $\NG^2$ groups for some $\NG = \Theta(\log(T))$.
-The groups in the $l$-th level are labeled as $G_{l,u,v}$ for $u,v\in[\NG]$.
-For any $l \in \{2,...,L\}$ and $u,v,w\in [\NG]$, agents in group $G_{l,u,v}$ see the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$).
-See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level).
+This motivates the following interlacing connection structure between
+levels. For each level in the info-graph, there are $\NG^2$ groups for
+some $\NG = \Theta(\log(T))$. The groups in the $l$-th level are
+labeled as $G_{l,u,v}$ for $u,v\in[\NG]$. For any $l \in \{2,...,L\}$
+and $u,v,w\in [\NG]$, agents in group $G_{l,u,v}$ see the history of
+agents in group $G_{l-1,v,w}$ (and by transitivity all agents in
+levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a
+visualization of simple case with $\sigma = 2$).
 
 This connecting structure has the following nice properties: \\
-\OMIT{(i) The number of groups does not grow with $L$ and stays as $\NG^2 = \Theta(\log^2(T))$ in each level.
-Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
+\OMIT{(i) The number of groups does not grow with $L$ and stays as
+  $\NG^2 = \Theta(\log^2(T))$ in each level. Having these groups only
+  incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
 (i) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,\NG,v}$ (e.g.
-$G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l-1$ and $v$.
+$G_{l-1,1,1}$ and $G_{l-1,2,1}$ circled in the Figure \ref{fig:llevel-connecting}) as a set of groups indexed by $l-1$ and $v$.
 The agents in a set of groups see the same history.

### 2018-11-02 llevel-overview.tex
editing...

@@
 levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a
-visualization of simple case with $\sigma = 2$).
+visualization of simple case with $\sigma = 2$). Two observations are
+in order:
+% \OMIT{(i) The number of groups does not grow with $L$ and stays as
+%   $\NG^2 = \Theta(\log^2(T))$ in each level. Having these groups only
+%   incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
+\begin{description}
 
-This connecting structure has the following nice properties: \\
-\OMIT{(i) The number of groups does not grow with $L$ and stays as
-  $\NG^2 = \Theta(\log^2(T))$ in each level. Having these groups only
-  incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
-(i) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,\NG,v}$ (e.g.
-$G_{l-1,1,1}$ and $G_{l-1,2,1}$ circled in the Figure \ref{fig:llevel-connecting}) as a set of groups indexed by $l-1$ and $v$.
+\item(i) For any level $l \geq 2$, fix the last group index to be $v$, and consider the groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,\NG,v}$ (e.g.
+$G_{l-1,1,1}$ and $G_{l-1,2,1}$ circled in the Figure \ref{fig:llevel-connecting}).
 The agents in a set of groups see the same history.
 They get ``lucky'' for some arm at the same time.\\
-(ii) For each set of groups in level $l-1$, agents in level $l$ see
+\item(ii) For each set of groups in level $l-1$, agents in level $l$ see
 the history of agents in one of these groups. Therefore, for each arm
@@
 and then all agents in level $l$ will see enough pulls of arm $a$.
-
+\end{description}
 \begin{figure}[H]

### 2018-11-02 3level.tex
fix 3level

@@
 
-\jmcomment{$N_2$ is also used in Lemma 3.6.
+%\jmcomment{$N_2$ is also used in Lemma 3.6.
 We need to find another notation.
@@
   $ \Delta \geq 4 \sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}$
-then all agents in Levels 2 and 3 pull arm 1.
+then all agents in the second and the third levels pull arm 1.
 \end{lemma}
@@
 In the \emph{medium gap} case, the data collected in a given first-level group is no longer guaranteed to determine the best arm.
-However, the data collected by the second-level groups enables all agents in the third level to correctly identify the best arm.
+However, agents in the third level see the history of not only one but all first-level groups and the data collected by all first-level groups enables agents in the third level to correctly identify the best arm.
 
@@
 is more challenging since even aggregating the data from all $\NG$
-first-level groups is not sufficient for identify the best arm.
+first-level groups is not sufficient for identifying the best arm.
 We need to ensure that both arms continue to be explored in the second level.

### 2018-11-02 llevel-overview.tex
editing...

@@
 structure such that the number of groups at each level stays as
-$\sigma^2 = \Theta(\log^2(T))$.
+$\NG^2 = \Theta(\log^2(T))$.
 
@@
   policy.  The key observation is that, for any level
-  $l \in \{3,...,L-1\}$, we do want agents in different $l$-th level
+  $l \in \{3,\ldots,L-1\}$, we do want agents in different $l$-th level
   groups to see disjoint histories of the $(l-1)$-th level to ensure
@@
 some $\NG = \Theta(\log(T))$. The groups in the $l$-th level are
-labeled as $G_{l,u,v}$ for $u,v\in[\NG]$. For any $l \in \{2,...,L\}$
+labeled as $G_{l,u,v}$ for $u,v\in[\NG]$. For any $l \in \{2,\ldots,L\}$
 and $u,v,w\in [\NG]$, agents in group $G_{l,u,v}$ see the history of
@@
 levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a
-visualization of simple case with $\sigma = 2$). Two observations are
+visualization of simple case with $\NG = 2$). Two observations are
 in order:
@@
 
-\item(i) For any level $l \geq 2$, fix the last group index to be $v$, and consider the groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,\NG,v}$ (e.g.
+\item(i) For any level $l \geq 2$, fix the last group index to be $v$, and consider the set of  groups $\{G_{l-1,i,v}\mid i \in [\NG]\}$ (e.g.
 $G_{l-1,1,1}$ and $G_{l-1,2,1}$ circled in the Figure \ref{fig:llevel-connecting}).

### 2018-11-02 llevel-overview.tex
editing...

@@
 
-\item(i) For any level $l \geq 2$, fix the last group index to be $v$, and consider the set of  groups $\{G_{l-1,i,v}\mid i \in [\NG]\}$ (e.g.
-$G_{l-1,1,1}$ and $G_{l-1,2,1}$ circled in the Figure \ref{fig:llevel-connecting}).
-The agents in a set of groups see the same history.
-They get ``lucky'' for some arm at the same time.\\
+\item(i) For any level $l \geq 2$, fix the last group index to be $v$,
+  and consider the set of groups
+  $\cG_{l-1, v}=\{G_{l-1,i,v}\mid i \in [\NG]\}$ (e.g. $G_{l-1,1,1}$
+  and $G_{l-1,2,1}$ circled in the Figure
+  \ref{fig:llevel-connecting}). The agents in this set of groups
+  observe the same sub-history. They get ``lucky'' for some arm at the
+  same time.
 \item(ii) For each set of groups in level $l-1$, agents in level $l$ see

### 2018-11-02 intro-intro.tex
Inserted some citations.

@@
 This situation can be circumvented by a centralized algorithm that induces agents to take explorative actions, a line of work called {\em incentivizing exploration}.
-One way to induce exploration is to introduce payments~\cite{}.
+One way to induce exploration is to introduce payments~\cite{Frazier-ec14,Kempe-colt18}.
 For example, an online retailer can give coupons to agents for trying certain products.
-When payments are financially or technologically infeasible, another alternative is to rely on {\em information asymmetry}~\cite{Kremer-JPE14}.
+When payments are financially or technologically infeasible, another alternative is to rely on {\em information asymmetry}, \eg \cite{Kremer-JPE14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17}.
 Here the idea is that the centralized algorithm can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.

### 2018-11-02 llevel-overview.tex
editing...

@@
 %   incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
-\begin{description}
-
-\item(i) For any level $l \geq 2$, fix the last group index to be $v$,
-  and consider the set of groups
+\begin{itemize}
+\item[(i)] Consider level $(l - 1)$ and fix the last group index to be
+  $v$, and consider the set of groups
   $\cG_{l-1, v}=\{G_{l-1,i,v}\mid i \in [\NG]\}$ (e.g. $G_{l-1,1,1}$
   and $G_{l-1,2,1}$ circled in the Figure
-  \ref{fig:llevel-connecting}). The agents in this set of groups
-  observe the same sub-history. They get ``lucky'' for some arm at the
-  same time.
-\item(ii) For each set of groups in level $l-1$, agents in level $l$ see
-the history of agents in one of these groups. Therefore, for each arm
-$a$, we just need one set of groups in level $l-1$ to get ``lucky''
-and then all agents in level $l$ will see enough pulls of arm $a$.
-\end{description}
+  \ref{fig:llevel-connecting}). The agents in any group of
+  $\cG_{l-1, v}$ observe the same sub-history. If the empirical mean
+  of arm $a$ is sufficiently high in their shared sub-history, then all groups in $\cG_{l-1, v}$ will become ``lucky'' groups for $a$.
+
+\item[(ii)] Every agent in level $l$ observes the sub-history from
+  $\NG$ $(l-1)$-th level groups, each of which belonging to a
+  different set $\cG_{l-1, v}$. Thus, for each arm $a$, we just need
+  one set of groups $\cG_{l-1, v}$ in level $l-1$ to be ``lucky'' for
+  $a$ and then all agents in level $l$ will see sufficient arm $a$
+  pulls.
+ \OMIT{For each set of groups
+    in level $l-1$, agents in level $l$ see the history of agents in
+    one of these groups. Therefore, for each arm $a$, we just need one
+    set of groups in level $l-1$ to get ``lucky'' and then all agents
+    in level $l$ will see enough pulls of arm $a$.}
+\end{itemize}
+
 \begin{figure}[H]
@@
 \end{figure}
-\xhdr{Additional groups for boundary cases.} Recall in our 3-level policy, the medium gap case (Lemma \ref{3levelmedium}) is the boundary case when the gap $|\mu_1-\mu_2|$ is $\Omega\left(\sqrt{\frac{1}{T_1}}\right)$ and $O\left(\sqrt{\frac{\log(T)}{T_1}}\right)$.
-In this case, the gap is not large enough to conclude that with high probability agents in both the second level and the third level all pull the best arm.
-The gap is also not small enough to conclude that with high probability both arms are explored enough times in the second level.
-We need to worry about the situation in which the sub-optimal arm does not get pulled enough times in the first two levels and some agents in the third level may pull the sub-optimal arm.
-Such situation is naturally ruled out in our 3-level policy for the following reason.
-Agents in the third level observe the history of the entire first level while agents in the second level only observes the history of a single first-level group.
-For each arm, even if it is not explored enough times in the second level, its empirical mean concentrates closer to its actual mean in the history observed by a third-level agent than the one observed by a second-level agent.
-Therefore, although the gap in the medium gap case is just not large enough for agents in the second level to all pull the best arm, it is large enough for agents in the third level to all pull the best arm.
+
+\paragraph{Amplifying groups for boundary cases.} Recall in our
+3-level policy, the medium gap case (Lemma \ref{3levelmedium}) is the
+boundary case when the gap $|\mu_1-\mu_2|$ is
+$\Omega\left(\sqrt{\frac{1}{T_1}}\right)$ and
+$O\left(\sqrt{\frac{\log(T)}{T_1}}\right)$. In this case, the gap is
+not large enough to conclude that with high probability agents in both
+the second level and the third level all pull the best arm. The gap is
+also not small enough to conclude that with high probability both arms
+are explored enough times in the second level. We need to worry about
+the situation in which the sub-optimal arm does not get pulled enough
+times in the first two levels and some agents in the third level may
+pull the sub-optimal arm. Such situation is naturally ruled out in our
+3-level policy for the following reason. Agents in the third level
+observe the history of the entire first level while agents in the
+second level only observes the history of a single first-level
+group. For each arm, even if it is not explored enough times in the
+second level, its empirical mean concentrates closer to its actual
+mean in the history observed by a third-level agent than the one
+observed by a second-level agent. Therefore, although the gap in the
+medium gap case is just not large enough for agents in the second
+level to all pull the best arm, it is large enough for agents in the
+third level to all pull the best arm.
 

### 2018-11-02 llevel-overview.tex
editing...

@@
 We will leverage the following key observation: in order to maintain
-the ``lucky'' property, it suffices to have the agents in different
-$l$-th level groups to observe disjoint sub-histories that takes place
-in level $(l - 1)$. Moreover, as long as the group size in levels
-lower than $(l-1)$ are substantially smaller than group size of level
-$l-1$, the ``lucky'' property does not break even if different groups
-in level $l$ observe overlapping sub-history from levels
-$\{1, \ldots, l-2\}$.
+the ``lucky'' property, it suffices to have $\NG$ $l$-th level groups
+that observe disjoint sub-histories that take place in level
+$(l - 1)$. Moreover, as long as the group size in levels lower than
+$(l-1)$ are substantially smaller than group size of level $l-1$, the
+``lucky'' property does not break even if different groups in level
+$l$ observe overlapping sub-history from levels $\{1, \ldots, l-2\}$.
 

### 2018-11-02 llevel-overview.tex
editing...

@@
 We will leverage the following key observation: in order to maintain
-the ``lucky'' property, it suffices to have $\NG$ $l$-th level groups
-that observe disjoint sub-histories that take place in level
-$(l - 1)$. Moreover, as long as the group size in levels lower than
-$(l-1)$ are substantially smaller than group size of level $l-1$, the
-``lucky'' property does not break even if different groups in level
-$l$ observe overlapping sub-history from levels $\{1, \ldots, l-2\}$.
+the ``lucky'' property, it suffices to have $\Theta(\log T)$ $l$-th
+level groups that observe disjoint sub-histories that take place in
+level $(l - 1)$. Moreover, as long as the group size in levels lower
+than $(l-1)$ are substantially smaller than group size of level $l-1$,
+the ``lucky'' property does not break even if different groups in
+level $l$ observe overlapping sub-history from levels
+$\{1, \ldots, l-2\}$.
 

### 2018-11-02 intro-intro.tex
delineated recommendation vs disclosure policy

--- 2018-11-02 intro-intro.tex
@@
 
-This situation can be circumvented by a centralized algorithm that induces agents to take explorative actions, a line of work called {\em incentivizing exploration}.
-One way to induce exploration is to introduce payments~\cite{}.
-For example, an online retailer can give coupons to agents for trying certain products.
-When payments are financially or technologically infeasible, another alternative is to rely on {\em information asymmetry}~\cite{Kremer-JPE14}.
-Here the idea is that the centralized algorithm can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.
+This situation can be circumvented by a centralized algorithm that induces agents to take explorative actions, an idea called {\em incentivizing exploration}.
+In practice, such algorithms are often encountered in the form of recommendations.
+One way to induce exploration is to introduce payments, \eg~\cite{Frazier-ec14,Kempe-colt18}.
+For example, the recommendation system of an online retailer might offer coupons to agents for trying certain products.
+When payments are financially or technologically infeasible, another alternative is to rely on information asymmetry, \eg~\cite{Kremer-JPE14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17}.
+Here the idea is that the centralized algorithm, often called a {\em disclosure policy}, can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.
+For example, the recommendation system of an online retailer might disclose past reviews or product rankings to the agents.
 Importantly, agents can not directly observe the past, but only learn about it through this message.
 The agent then chooses an action, using the content of the message as input.
-These systems are often referred to as {\em recommendation systems} as the content of the message can be interpreted as a recommendation for a particular action.
 

### 2018-11-02 main.tex
clean up appendix C
adding authors
byebye bayesian
typo
main
delineated recommendation vs disclosure policy

@@
 \newcommand{\event}[1]{\ensuremath{\mathtt{event}_{#1}}\xspace}
+\newcommand{\cG}{\mathcal{G}}
 
@@
 
-%index on the tap
-\def\z{z}
+%index on the tape
+\def\z{\tau}
 \title{Incentivizing Exploration with Unbiased History}
@@
 \author{
+Nicole Immorlica
+\and
+Jieming Mao
+\and
+Aleksandrs Slivkins
+\and
+Zhiwei Steven Wu
 }
@@
 In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world.
-A sequence of agents each choose an action with the goal of maximizing payoff given estimates of the state of the world.
-A recommendation algorithm tries to coordinate the choices of the agents by sending messages about the history of past actions.
+A sequence of agents each chooses an action with the goal of maximizing payoff given estimates of the state of the world.
+A disclosure policy tries to coordinate the choices of the agents by sending messages about the history of past actions.
 The goal of the algorithm is to minimize the regret of the action sequence.
 
-In this paper, we study a particular class of recommendation algorithms that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards chosen by a subsequence of past agents.
-One trivial message of this form contains the full history; a recommendation algorithm that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.
-Our main result is a recommendation algorithm using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.
+In this paper, we study a particular class of disclosure policies that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards chosen by a subsequence of past agents.
+One trivial message of this form contains the full history; a disclosure policy that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.
+Our main result is a disclosure policy using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.
 We also exhibit simpler policies with higher, but still sublinear, regret.
@@
 \input{llevel}
-\input{posterior}
+
+%\input{posterior}
 \end{document}

### 2018-11-02 llevel-overview.tex
editing...

@@
   $\cG_{l-1, v}=\{G_{l-1,i,v}\mid i \in [\NG]\}$ (e.g. $G_{l-1,1,1}$
-  and $G_{l-1,2,1}$ circled in the Figure
+  and $G_{l-1,2,1}$ circled in red in the Figure
   \ref{fig:llevel-connecting}). The agents in any group of
-  $\cG_{l-1, v}$ observe the same sub-history. If the empirical mean
-  of arm $a$ is sufficiently high in their shared sub-history, then all groups in $\cG_{l-1, v}$ will become ``lucky'' groups for $a$.
+  $\cG_{l-1, v}$ observe the same sub-history. As a result, if the
+  empirical mean of arm $a$ is sufficiently high in their shared
+  sub-history, then all groups in $\cG_{l-1, v}$ will become ``lucky''
+  for $a$.
 

### 2018-11-02 related-work.tex
Splitted related work into a separate file.

--- 2018-11-02 intro.tex
@@
-\section{Introduction}
-\label{sec:intro}
-
-\input{intro-intro.tex}
-
-\xhdr{Our scope.} Prior work on incentivizing exploration, with or without monetary incentives, achieves much progress (more on this in ``related work"), but relies heavily on the standard assumptions of Bayesian rationality and the ``power to commit" (\ie users trust that the principal actually implements the policy that it claims to implement).
-However, these assumptions appear quite problematic in the context of recommendation systems.
-In particular, disclosure policies studied in prior work merely recommend an action to each agent, without any other supporting information, and moreover recommend exploratory actions to some randomly selected users.
-This works out extremely well in theory, but it is very unclear whether users would trust the principal to implement the stated policy and, even if they do, whether they would react to it rationally.
-Several issues are in play: to wit, whether the principal intentionally uses a different disclosure policy than the claimed one (\eg because its incentives are not quite aligned with the users'), whether the principal correctly implements the policy that it wants to implement, whether the users trust the principal to make correct inferences on their behalf, and whether they find it acceptable that they may be singled out for exploration.
-Furthermore, regardless of how the users react to such disclosure policies, they may prefer not to be subjected to them, and leave the system.
-
-We strive to design disclosure policies which mitigate these issues and (still) incentivize a good balance between exploration and exploitation.
-While some assumptions on human behavior are unavoidable, we are looking for a class of disclosure policies for which we can make plausible behavioral assumptions.
-Then we arrive at a concrete mathematical problem: design policies from this class so as to optimize performance, \ie  the induced explore-exploit tradeoff.
-Our goal in terms of performance is as ambitious as the one in prior work on incentivizing exploration: essentially, to approach the performance of the social planner.
-
-\xhdr{Our model.}
-For the sake of intuition, let us revisit the \emph{full-disclosure policy} that reveals the full history of observations from the previous users.
-We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it.
-Unfortunately, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}.
-However, what if a disclosure policy reveals the outcomes for every other agent, rather than the outcomes for all agents?
-We posit that users would trust such policy, too.
-Given a large volume of data, we posit that users would not be too unhappy with having access to only a fraction this data.
-A crucial aspect of our intuition here is that the ``subhistory" revealed to a given user comes from a subset of previous users that is chosen in advance, without looking at what happens during the execution.
-In particular, the subhistory is not ``biased", in the sense that the disclosure policy cannot subsample the observations in favor of a particular action.
-
-With this intuition in mind, we define the class of \emph{unbiased-subhistory policies}: disclosure policies that reveal, to each arriving agent $t$, a subhistory  consisting of the outcomes for a subset $S_t$ of previous agents, where $S_t$ is chosen ahead of time.
-Further, we impose a transitivity property: if $t' \in S_t$, for some previous agent $t'$, then $S_{t'}\subset S_t$.
-So, agent $t$ has all information that agent $t'$ had at the time she chose her action.
-In particular, agent $t$ does not need to second-guess which message has caused agent $t'$ to make choose that action.
-
-\ascomment{stable text up to here.}
-
 \xhdr{Related work.}

### 2018-11-02 intro.tex
OK some more of the intro is there.

@@
 
-We measure the machine learning performance of a disclosure policy in terms of \emph{regret}, a standard notion from online machine learning.
+\xhdr{Regret.} We measure the performance of a disclosure policy in terms of \emph{regret}, a standard notion from the literature on multi-armed bandits.
 Regret is defined as the difference in the total expected reward between the best fixed action and actions induced by the policy.
+Regret is typically studied as a function of the time horizon $T$, which in our model is the number of agents.
+For multi-armed bandits, $o(T)$ regret bounds are deemed non-trivial, and $O(\sqrt{T})$ regret bounds are optimal in the worst case.
+Regret bounds that depend on a particular problem instance are also considered.
+A crucial parameter then is the \emph{gap} $\Delta$, the difference between the best and second best expected reward.
+One can achieve $O(\tfrac{1}{\Delta}\; \log T)$ regret rate, without knowing the $\Delta$.
 
-\xhdr{Our results.}
-We design transitive unbiased-subhistory policies with near-optimal regret.
+\xhdr{Our results and discussion.}
+Our main result is a transitive, unbiased-subhistory policy which attains near-optimal $\tilde{O}(\sqrt{T})$ regret rate for a constant number of actions.
+This policy also obtains the optimal instance-dependent regret rate
+    $\tilde{O}(\tfrac{1}{\Delta})$
+for problem instances with gap $\Delta$, without knowing the $\Delta$ in advance.
+In particular, we match the regret rate achieved for incentivizing exploration with unrestricted disclosure policies \cite{ICexploration-ec15-working}.
+
+The main challenge is that the agents still follow exploitation-only behavior, just like they do for the full-disclosure policy, albeit based only on a portion of history.
+A disclosure policy controls the flow of information (who sees what), but not the \emph{content} of that information.
+
+The first step is to obtain any substantial improvement over the full-disclosure policy.
+We accomplish this with a relatively simple policy which runs the full-disclosure policy ``in parallel" on several disjoint subsets of agents,  collects all data from these runs and discloses it to all remaining agents.
+While any single run of the full-disclosure policy may get stuck on a suboptimal arm, having these parallel runs ensure that sufficiently many of them will ``get lucky" and provide some exploration.
+This simple policy achieves $\tilde{O}(T^{2/3})$ regret.
+Conceptually, it implements a basic bandit algorithm that explores uniformly for a pre-set number of rounds, then picks one arm for exploitation and stays with it for the remaining rounds.
+We think of this policy  as having two ``levels": Level 1 contains the parallel runs, and Level 2 is everything else.
+
+The next step is to implement \emph{adaptive exploration}, when exploration schedule is adapted to previous observations.
+This is needed to improve over the $\tilde{O}(T^{2/3})$ regret.
+We upgrade the simple two-level policy with a middle level, where agents receive the data collected in some (but not all) runs from the first level.
+Essentially, this new level provides exploration only if the gap $\Delta$ is small (and therefore more exploration is needed).
+
+The main result extends this construction to multiple levels, connected in fairly intricate ways. \ascomment{add more}.
 
@@
 
-\xhdr{Related work.}
-
-\cite{Perchet2015BatchedBP} gives regret guarantees for mult-armed bandit in $M$ batches. They have 2 upper bounds which are similar to our Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2}.
+\input{related-work}

### 2018-11-02 llevel-overview.tex
editing...

@@
 However, in this construction, the first level will have $\NG^{L-1}$
-groups, which incurs $\NG^{\Omega(L)}$ regret. The exponential
-dependence in $L$ will heavily limit the adaptivity of the policy, and
-prevents having the number of levels for obtaining the result in
-\Cref{thm:llevel-2}. To overcome this, we will design an info-graph
-structure such that the number of groups at each level stays as
-$\NG^2 = \Theta(\log^2(T))$.
+groups, which introduces a multiplicative factor of $\NG^{\Omega(L)}$
+in the regret rate. The exponential dependence in $L$ will heavily
+limit the adaptivity of the policy, and prevents having the number of
+levels for obtaining the result in \Cref{thm:llevel-2}. To overcome
+this, we will design an info-graph structure such that the number of
+groups at each level stays as $\NG^2 = \Theta(\log^2(T))$.
 

### 2018-11-02 llevel-overview.tex
typo

@@
 \end{tikzpicture}
-\caption{Connectiing structures between levels for the $L$-level policy.}
+\caption{Connecting structures between levels for the $L$-level policy.}
 \label{fig:llevel-connecting}
@@
 Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$.
-The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$ groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels.
+The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$-groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels.
 When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm.

### 2018-11-02 3level.tex
event 3

@@
 \item[(\event{2})] \emph{Concentration in Level 1:} Within each first-level group, empirical mean rewards of each arm $a$ concentrate around $\mu_a$.
-\item[(\event{3})] \emph{Anti-concentration in Level 1:} For each arm, some first-level subgroup collects data which makes this arm look much better than the other.
+\item[(\event{3})] \emph{Anti-concentration in Level 1:} For each arm, some first-level subgroup collects data which makes this arm look much better than its actual mean and other arms look worse than their actual means.
 \item[(\event{4})] \emph{Concentration in prefix:}

### 2018-11-02 llevel-overview.tex
editing...

@@
 
-\paragraph{Amplifying groups for boundary cases.} Recall in our
-3-level policy, the medium gap case (Lemma \ref{3levelmedium}) is the
-boundary case when the gap $|\mu_1-\mu_2|$ is
-$\Omega\left(\sqrt{\frac{1}{T_1}}\right)$ and
-$O\left(\sqrt{\frac{\log(T)}{T_1}}\right)$. In this case, the gap is
-not large enough to conclude that with high probability agents in both
-the second level and the third level all pull the best arm. The gap is
-also not small enough to conclude that with high probability both arms
-are explored enough times in the second level. We need to worry about
-the situation in which the sub-optimal arm does not get pulled enough
-times in the first two levels and some agents in the third level may
-pull the sub-optimal arm. Such situation is naturally ruled out in our
-3-level policy for the following reason. Agents in the third level
-observe the history of the entire first level while agents in the
-second level only observes the history of a single first-level
-group. For each arm, even if it is not explored enough times in the
-second level, its empirical mean concentrates closer to its actual
-mean in the history observed by a third-level agent than the one
-observed by a second-level agent. Therefore, although the gap in the
-medium gap case is just not large enough for agents in the second
-level to all pull the best arm, it is large enough for agents in the
-third level to all pull the best arm.
+\paragraph{Amplifying groups for boundary cases.} Recall in the
+three-level policy, the medium gap case (Lemma \ref{3levelmedium})
+corresponds to the case where the gap $\Delta$ is between
+$\Omega\left({{1}/{T_1}}\right)$ and
+$O\left(\sqrt{{\log(T)}/{T_1}}\right)$. This is a boundary case since
+$\Delta$ is neither large enough to conclude that with high
+probability agents in both the second level and the third level all
+pull the best arm, nor small enough to conclude that both arms are
+explored enough times in the second level (due to
+anti-concentration). In this case, we need to ensure that agents in
+the third level can eliminate the inferior arm. This issue is easily
+resolved in the three-level policy since the agents in the third level
+observe the history of the entire first level, which provides
+sufficiently accurate reward estimates for both arms.
+
+\OMIT{about the situation in which the sub-optimal arm does not get
+  pulled enough times in the first two levels and some agents in the
+  third level may pull the sub-optimal arm.  Such situation is
+  naturally ruled out in our 3-level policy for the following
+  reason. Agents in the third level observe the history of the entire
+  first level while agents in the second level only observes the
+  history of a single first-level group. For each arm, even if it is
+  not explored enough times in the second level, its empirical mean
+  concentrates closer to its actual mean in the history observed by a
+  third-level agent than the one observed by a second-level
+  agent. Therefore, although the gap in the medium gap case is just
+  not large enough for agents in the second level to all pull the best
+  arm, it is large enough for agents in the third level to all pull
+  the best arm.}
 

### 2018-11-02 intro.tex
intro

@@
 
-\input{intro-intro.tex}
+In the classic literature on multi-armed bandits, an agent repeatedly selects one of a set of actions, each of which has a payoff drawn from an unknown fixed distribution.
+Over time, she can trade off {\em exploitation}, in which she picks an action to maximize her expected reward, with {\em exploration}, in which she takes potentially sub-optimal actions to learn more about their rewards.
+By coordinating her actions across time, she can guarantee an average reward which converges to that of the optimal action in hindsight at a rate proportional to the inverse square-root of the time horizon.
+
+In many decision problems of interest, the actions are not chosen by a single agent, as above, but rather a sequence of agents.
+This is particularly common in social learning settings such as online websites, where a population of users try to learn about the content of the site.
+In such settings, each agent will choose an exploitive action as the benefits of explorative actions are only accrued by future agents.
+For example, in online retail, products are purchased by a sequence of customers, each of which buys what she estimates to be the best available product.
+This behavior can cause herding, in which all agents eventually take a sub-optimal action of maximum expected payoff given the available information.
+
+This situation can be circumvented by a centralized algorithm that induces agents to take explorative actions, an idea called {\em incentivizing exploration}.
+Such algorithms are often encountered in the form of recommendations and are quite common in practice.
+Many online websites, like Amazon, Reddit, Yelp, and Tripadvisor, among many others, use recommendation policies of some sort to help users navigate their offerings.
+%
+One way recommendation policies induce exploration is to introduce payments, \eg~\cite{Frazier-ec14,Kempe-colt18}.
+For example, the recommendation system of an online retailer might offer coupons to agents for trying certain products.
+When payments are financially or technologically infeasible, another alternative is to rely on information asymmetry, \eg~\cite{Kremer-JPE14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17}.
+Here the idea is that the centralized algorithm, often called a {\em disclosure policy}, can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.
+For example, the recommendation system of an online retailer might disclose past reviews or product rankings to the agents.
+Importantly, agents can not directly observe the past, but only learn about it through this message.
+The agent then chooses an action, using the content of the message as input.
 
 \xhdr{Our scope.} Prior work on incentivizing exploration, with or without monetary incentives, achieves much progress (more on this in ``related work"), but relies heavily on the standard assumptions of Bayesian rationality and the ``power to commit" (\ie users trust that the principal actually implements the policy that it claims to implement).
-However, these assumptions appear quite problematic in the context of recommendation systems.
+However, these assumptions appear quite problematic in the context of recommendation systems of actual online websites such as those mentioned above.
 In particular, much of the prior work suggests disclosure policies that merely recommend an action to each agent, without any other supporting information, and moreover recommend exploratory actions to some randomly selected users.
-This works out extremely well in theory, but it is very unclear whether users would trust the principal to implement the stated policy and, even if they do, whether they would react to it rationally.
+This works out extremely well in theory, but it is very unclear whether users would even know some complicated policy of the principal, let alone trust the principal to implement the stated policy.
+Even if they do know the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally.
+%
 Several issues are in play: to wit, whether the principal intentionally uses a different disclosure policy than the claimed one (\eg because its incentives are not quite aligned with the users'), whether the principal correctly implements the policy that it wants to implement, whether the users trust the principal to make correct inferences on their behalf, and whether they find it acceptable that they may be singled out for exploration.
@@
 We interpret it as the ``gold standard": we posit that users would trust such policy, even if they cannot verify it.
-Unfortunately, the full-disclosure policy is not good for our purposes, essentially because rational users would \emph{exploit} rather than \emph{explore}.
-However, what if a disclosure policy reveals the outcomes for every other agent, rather than the outcomes for all agents?
+Unfortunately, the full-disclosure policy is not good for our purposes, essentially because we expect users to \emph{exploit} rather than \emph{explore}.
+However, what if a disclosure policy reveals the outcomes for every tenth agent, rather than the outcomes for all agents?
 We posit that users would trust such policy, too.
@@
 
-The next step is to implement \emph{adaptive exploration}, when exploration schedule is adapted to previous observations.
+The next step is to implement \emph{adaptive exploration}, where the exploration schedule is adapted to previous observations.
 This is needed to improve over the $\tilde{O}(T^{2/3})$ regret.
 We upgrade the simple two-level policy with a middle level, where agents receive the data collected in some (but not all) runs from the first level.
-Essentially, this new level provides exploration only if the gap $\Delta$ is small (and therefore more exploration is needed).
-
-The main result extends this construction to multiple levels, connected in fairly intricate ways. \ascomment{add more}.
+Essentially, this new level provides exploration only if the gap $\Delta$ between the best and second-best arm is small, but not small enough to be insignificant to the regret guarantee.
+When this happens, the runs in the first level do not have sufficient time to distinguish the two arms before herding on one of them.
+However, for each of these arms, there is some chance that it has an empirical mean reward significantly above its actual mean while the other one has empirical mean reward significantly below its actual mean in any given first-level run.
+The second level agents observing such runs will be induced to further explore that arm, allowing the third level agents to get enough samples to distinguish the arms.
+%
+The main result extends this construction to multiple levels, connected in fairly intricate ways, obtaining optimal regreat of $\tilde{O}(T^{1/2})$.
+\ascomment{add more}.
+\nicomment{don't think it's necessary; at least i can't crystalize the key idea it adds over the 3level; mostly it just takes the 3level idea to its extreme}
 

### 2018-11-02 llevel-overview.tex
editing...

@@
 
-When we extend the 3-level policy to an $L$-level policy, we have such boundary case for each intermediate level.
-Moreover, the worry mentioned above does not get naturally resolved as in some of these boundary cases, the ratios between the upper and lower bounds of the gap rise from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$.
-The reason for such rise is that, except the first level, we don't have good enough guarantee of the number of pulls of each arm.
-For example, in Figure \ref{fig:llevel-connecting}, when we talk about having enough arm $a$ pulls in the history observed by agents in $G_{l,1,1}$, it could be that  only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm $a$.
-Therefore our estimate of the number of arm $a$ pulls can be off by an $\NG=\Theta(\log(T))$ multiplicative factor.
-This finally makes the boundary cases harder to deal with.
+In the $L$-level policy, such boundary case occurs for each
+intermediate level $l\in \{\}$. Moreover, the worry mentioned above does not get
+naturally resolved as in some of these boundary cases, the ratios
+between the upper and lower bounds of the gap rise from
+$\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$. The reason for such
+rise is that, except the first level, we don't have good enough
+guarantee of the number of pulls of each arm. For example, in Figure
+\ref{fig:llevel-connecting}, when we talk about having enough arm $a$
+pulls in the history observed by agents in $G_{l,1,1}$, it could be
+that only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it
+also could be that most agents in groups
+$G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm
+$a$. Therefore our estimate of the number of arm $a$ pulls can be off
+by an $\NG=\Theta(\log(T))$ multiplicative factor. This finally makes
+the boundary cases harder to deal with.
 

### 2018-11-02 related-work.tex

@@
 \xhdr{Related work.}
+The problem of incentivizing exploration via information asymmetry was introduced in \cite{Kremer-JPE14}, under the Bayesian rationality and the (implicit) power-to-commit assumptions.
+The original problem -- essentially, a version of our model with unrestricted disclosure policies -- was largely resolved in \cite{Kremer-JPE14} and the subsequent work \cite{ICexploration-ec15,ICexplorationGames-ec16}.
+Several extensions were considered: to contextual bandits \cite{ICexploration-ec15}, to repeated games
+\cite{ICexplorationGames-ec16}, and to social networks \cite{Bahar-ec16}.
 
-\cite{Perchet2015BatchedBP} gives regret guarantees for mult-armed bandit in $M$ batches. They have 2 upper bounds which are similar to our Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2}.
+Several other papers study related, but technically different models: same model with time-discounted utilities \cite{Bimpikis-exploration-ms17}; a version with monetary incentives \cite{Frazier-ec14} and moreover with heterogenous agents \cite{Kempe-colt18}; a version with a continuous information flow and a continuum of agents \cite{Che-13}; coordination of costly exploration decisions when they are separate from the ``payoff-generating" decisions \cite{Bobby-Glen-ec16,Annie-ec18-traps,Liang-ec18}.
+Scenarios with long-lived, exploring agents and no principal to coordinate them have been studied in \cite{Bolton-econometrica99,Keller-econometrica05}.
+
+Full-disclosure policy, and closely related ``greedy" (exploitation-only) algorithm in multi-armed bandits, have been a subject of a recent line of work \cite{Sven-aistats18,kannan2018smoothed,bastani2017exploiting,externalities-colt18,practicalCB-arxiv18}.
+A common theme is that the greedy algorithm performs well in theory, under  substantial heterogeneity assumptions, and sometimes it works well in practice.
+Yet, it suffers $\Omega(T)$ regret in the worst case.%
+\footnote{This is a well-known folklore result; \eg see \cite{CompetingBandits-itcs16} for a concrete example.}
+
+Exploration-exploitation tradeoff received much attention over the past decades, usually under the rubric of ``multi-armed bandits"; see  \cite{Bubeck-survey12,Gittins-book11} for background. 
+Exploration-exploitation problems with incentives issues arise in several other scenarios: dynamic pricing
+    \cite{KleinbergL03,BZ09,BwK-focs13},
+dynamic auctions
+    \cite{AtheySegal-econometrica13,DynPivot-econometrica10,Kakade-pivot-or13},
+pay-per-click ad auctions
+    \cite{MechMAB-ec09,DevanurK09,Transform-ec10-jacm},
+and human computation
+    \cite{RepeatedPA-ec14,Ghosh-itcs13,Krause-www13}.

### 2018-11-02 llevel-overview.tex
editing...

@@
 corresponds to the case where the gap $\Delta$ is between
-$\Omega\left({{1}/{T_1}}\right)$ and
+$\Omega\left(\sqrt{{1}/{T_1}}\right)$ and
 $O\left(\sqrt{{\log(T)}/{T_1}}\right)$. This is a boundary case since
@@
 In the $L$-level policy, such boundary case occurs for each
-intermediate level $l\in \{\}$. Moreover, the worry mentioned above does not get
-naturally resolved as in some of these boundary cases, the ratios
-between the upper and lower bounds of the gap rise from
-$\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$. The reason for such
-rise is that, except the first level, we don't have good enough
-guarantee of the number of pulls of each arm. For example, in Figure
+intermediate level $l\in \{2, \ldots, l-1\}$, but issue mentioned
+above does not get naturally resolved as in some of these boundary
+cases---the ratios between the upper and lower bounds of $\Delta$ rise
+from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$, and it would
+require more observations from level $(l-2)$ to distinguish two arms
+at level $l$. The reason for this larger disparity is that, except the
+first level, we can no longer guarantee sufficient number of pulls of
+each arm. For example, in as shown in Figure
 \ref{fig:llevel-connecting}, when we talk about having enough arm $a$

### 2018-11-02 llevel-overview.tex
rm shit

@@
 first level, we can no longer guarantee sufficient number of pulls of
-each arm. For example, in as shown in Figure
-\ref{fig:llevel-connecting}, when we talk about having enough arm $a$
-pulls in the history observed by agents in $G_{l,1,1}$, it could be
-that only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it
-also could be that most agents in groups
-$G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm
-$a$. Therefore our estimate of the number of arm $a$ pulls can be off
-by an $\NG=\Theta(\log(T))$ multiplicative factor. This finally makes
-the boundary cases harder to deal with.
+each arm. For example, as shown in Figure \ref{fig:llevel-connecting},
+when we talk about having enough arm $a$ pulls in the history observed
+by agents in $G_{l,1,1}$, it could be that only agents in group
+$G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most
+agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are
+pulling arm $a$. Therefore our estimate of the number of arm $a$ pulls
+can be off by an $\NG=\Theta(\log(T))$ multiplicative factor. This
+finally makes the boundary cases harder to deal with.
 

### 2018-11-02 model.tex
Minor edit to save a line.

@@
 Any such algorithm suffers from $\Omega(T^{2/3})$ regret in the worst case.%
-\footnote{The first explicit reference we are aware of is \cite{MechMAB-ec09,DevanurK09}, but this fact has been known in the community for much longer.}
+\footnote{The first explicit reference we know of is \cite{MechMAB-ec09,DevanurK09}, but this fact has been known in the community for much longer.}
 

### 2018-11-02 llevel-overview.tex
editing...

@@
 \end{tikzpicture}
-\caption{Connecting structures between levels for the $L$-level policy.}
+\caption{Interlacing connections between levels for the $L$-level policy.}
 \label{fig:llevel-connecting}
@@
 can be off by an $\NG=\Theta(\log(T))$ multiplicative factor. This
-finally makes the boundary cases harder to deal with.
+ultimately makes the boundary cases harder to deal with.
 
-In our $L$-level policy, after understanding the boundary cases well, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups.
+We resolve this problem by introducing an additional type of \emph{amplifying groups}: $\Gamma$-groups.
 For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$.

### 2018-11-02 main.tex
Added explanation of unbiased to the abstract.

@@
 
-In this paper, we study a particular class of disclosure policies that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards chosen by a subsequence of past agents.
+In this paper, we study a particular class of disclosure policies that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards from by a subsequence of past agents, where the subsequence is chosen ahead of time.
 One trivial message of this form contains the full history; a disclosure policy that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.

### 2018-11-02 3level.tex
event3

@@
 
-For the sake of intuition, consider the framework of bandit algorithms with limited adaptivity.
+For the sake of intuition, consider the framework of bandit algorithms with limited adaptivity \cite{Perchet2015BatchedBP}.
 Suppose a bandit algorithm outputs a distribution $p_t$ over arms in each round $t$, and the arm $a_t$ is then drawn independently from $p_t$.
@@
 We need to ensure that both arms continue to be explored in the second level.
-To achieve this, we leverage \event{4}, which implies
+To achieve this, we leverage \event{3}, which implies
 that each arm $a$ has a first-level group $s_a$ where it gets ``lucky", in the sense that its empirical mean reward is slightly higher than $\mu_a$, while the empirical mean reward of the other arm is slightly lower than its true mean.

### 2018-11-02 intro.tex
Added a sentence on focus groups.
Some edits in intro/3Level

@@
 We accomplish this with a relatively simple policy which runs the full-disclosure policy ``in parallel" on several disjoint subsets of agents,  collects all data from these runs and discloses it to all remaining agents.
+In practice, these subsets may correspond to multiple ``focus groups".
 While any single run of the full-disclosure policy may get stuck on a suboptimal arm, having these parallel runs ensure that sufficiently many of them will ``get lucky" and provide some exploration.
@@
 This is needed to improve over the $\tilde{O}(T^{2/3})$ regret.
-We upgrade the simple two-level policy with a middle level, where agents receive the data collected in some (but not all) runs from the first level.
-Essentially, this new level provides exploration only if the gap $\Delta$ between the best and second-best arm is small, but not small enough to be insignificant to the regret guarantee.
-When this happens, the runs in the first level do not have sufficient time to distinguish the two arms before herding on one of them.
-However, for each of these arms, there is some chance that it has an empirical mean reward significantly above its actual mean while the other one has empirical mean reward significantly below its actual mean in any given first-level run.
-The second level agents observing such runs will be induced to further explore that arm, allowing the third level agents to get enough samples to distinguish the arms.
-%
+As a proof of concept, we focus on the case of two actions, and upgrade the simple two-level policy with a middle level.
+The agents in this new level receive the data collected in some (but not all) runs from the first level.
+What happens is that these agents explore only if the gap $\Delta$ between the best and second-best arm is sufficiently small, and exploit otherwise.
+When $\Delta$ is small, the runs in the first level do not have sufficient time to distinguish the two arms before herding on one of them.
+However, for each of these arms, there is some chance that it has an empirical mean reward significantly above its actual mean while the other arm has empirical mean reward significantly below its actual mean in any given first-level run.
+The middle-level agents observing such runs will be induced to further explore that arm, collecting enough samples for the third-level agents to distinguish the two arms.
 The main result extends this construction to multiple levels, connected in fairly intricate ways, obtaining optimal regreat of $\tilde{O}(T^{1/2})$.
-\ascomment{add more}.
-\nicomment{don't think it's necessary; at least i can't crystalize the key idea it adds over the 3level; mostly it just takes the 3level idea to its extreme}
-
-\ascomment{stable-ish text up to here.}
 

### 2018-11-02 main.tex
final

@@
 % a very useful package for edits and comments, from David Kempe (USC)
-\usepackage{color-edits}
+%\usepackage{color-edits}
 %\usepackage[suppress]{color-edits}  % use this to suppress the package
-\addauthor{as}{red}      % as for Alex
-\addauthor{jm}{blue}     % jm for Jieming
-\addauthor{ni}{magenta}     % ni for Nicole
-\addauthor{sw}{brown}     % sw for Steven
+%\addauthor{as}{red}      % as for Alex
+%\addauthor{jm}{blue}     % jm for Jieming
+%\addauthor{ni}{magenta}     % ni for Nicole
+%\addauthor{sw}{brown}     % sw for Steven
 % e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.
@@
 \author{
-Nicole Immorlica
+Nicole Immorlica \thanks{Microsoft Research, email: nicimm@microsoft	.com.}
 \and
-Jieming Mao
+Jieming Mao \thanks{University of Pennsylvania, email: maojm517@gmail.com.}
 \and
-Aleksandrs Slivkins
+Aleksandrs Slivkins  \thanks{Microsoft Research, email: slivkins@microsoft.com.}
 \and
-Zhiwei Steven Wu
+Zhiwei Steven Wu  \thanks{University of Minnesota, email: zsw@umn.edu.}
 }

### 2018-11-02 model.tex
final

@@
 \xhdr{Preliminaries.}
-\asedit{We assume that $K$ is constant, and focus on the dependence on $T$. However, we explicitly state the dependence on $K$, \eg using the $O_K()$ notation.}
+We assume that $K$ is constant, and focus on the dependence on $T$. However, we explicitly state the dependence on $K$, \eg using the $O_K()$ notation.
 
@@
 
-\asedit{We use the notion of \emph{reward tape} to simplify the application of (anti-)concentration inequalities.
+We use the notion of \emph{reward tape} to simplify the application of (anti-)concentration inequalities.
 This is a $K\times T$ random matrix with rows and columns corresponding to arms and rounds, respectively.
 For each arm $a$ and round $t$, the value in cell $(a,t)$ is drawn independently from Bernoulli distribution $\mD_a$.
-W.l.o.g., rewards in our model are defined by the rewards tape: namely, the reward for the $j$-th pull of arm $a$ is taken from the $(a,j)$-th entry of the reward matrix.}
+W.l.o.g., rewards in our model are defined by the rewards tape: namely, the reward for the $j$-th pull of arm $a$ is taken from the $(a,j)$-th entry of the reward matrix.
 

### 2018-11-02 llevel-overview.tex
editing...

@@
 corresponds to the case where the gap $\Delta$ is between
-$\Omega\left(\sqrt{{1}/{T_1}}\right)$ and
-$O\left(\sqrt{{\log(T)}/{T_1}}\right)$. This is a boundary case since
+$\Omega\left(\sqrt{{1}/({\log(T) T_1)}}\right)$ and
+$O\left(\sqrt{{1}/{T_1}}\right)$. This is a boundary case since
 $\Delta$ is neither large enough to conclude that with high
@@
 resolved in the three-level policy since the agents in the third level
-observe the history of the entire first level, which provides
-sufficiently accurate reward estimates for both arms.
+observe the entire first-level history, which consists of
+$\Omega(\log(T) T_1)$ pulls of each arm and provides sufficiently
+accurate reward estimates to distinguish the two arms.
 
@@
 
-In the $L$-level policy, such boundary case occurs for each
-intermediate level $l\in \{2, \ldots, l-1\}$, but issue mentioned
-above does not get naturally resolved as in some of these boundary
-cases---the ratios between the upper and lower bounds of $\Delta$ rise
-from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$, and it would
-require more observations from level $(l-2)$ to distinguish two arms
-at level $l$. The reason for this larger disparity is that, except the
-first level, we can no longer guarantee sufficient number of pulls of
-each arm. For example, as shown in Figure \ref{fig:llevel-connecting},
-when we talk about having enough arm $a$ pulls in the history observed
-by agents in $G_{l,1,1}$, it could be that only agents in group
-$G_{l-1,1,1}$ are pulling arm $a$ and it also could be that most
-agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are
-pulling arm $a$. Therefore our estimate of the number of arm $a$ pulls
-can be off by an $\NG=\Theta(\log(T))$ multiplicative factor. This
-ultimately makes the boundary cases harder to deal with.
+In the $L$-level policy, such boundary cases occur for each
+intermediate level $l\in \{2, \ldots, l-1\}$, but the issue mentioned
+above does not get naturally resolved since the ratios between the
+upper and lower bounds of $\Delta$ rise from $\Theta(\sqrt{\log(T)})$
+to $\Theta(\log(T))$, and it would require more observations from
+level $(l-2)$ to distinguish two arms at level $l$. The reason for
+this larger disparity is that, except the first level, we can no
+longer guarantee sufficient number of pulls of each arm. For example,
+as shown in Figure \ref{fig:llevel-connecting}, when we talk about
+having enough arm $a$ pulls in the history observed by agents in
+$G_{l,1,1}$, it could be that only agents in group $G_{l-1,1,1}$ are
+pulling arm $a$ and it also could be that most agents in groups
+$G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,\NG}$ are pulling arm
+$a$. Therefore our estimate of the number of arm $a$ pulls can be off
+by an $\NG=\Theta(\log(T))$ multiplicative factor. This ultimately
+makes the boundary cases harder to deal with.
 
-We resolve this problem by introducing an additional type of \emph{amplifying groups}: $\Gamma$-groups.
+We resolve this problem by introducing an additional type of \emph{amplifying groups}, called $\Gamma$-groups.
 For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$.

### 2018-11-02 llevel-overview.tex
update

@@
 one in Theorem \ref{thm:llevel-1}, but requires a higher number of
-levels $L = O(\log(T/\log\log(T)))$ and larger group sizes. We will
+levels $L = O(\log(T/\log\log(T)))$ and different group sizes. We will
 bound its regret as a function of the gap parameter $\Delta$ even
@@
 \label{thm:llevel-2}
-There exists a $O(\log(T)/\log\log(T))$-level policy such that for
+There exists an $O(\log(T)/\log\log(T))$-level policy such that for
 every multi-armed bandit instance with gap parameter $\Delta$, the
@@
 
-Note for constant number of arms, this result mathches the optimal
+Note for constant number of arms, this result matches the optimal
 regret rate (given in \Cref{eq:model-OptRegret}) for stochastic
@@
 agents to perform more adaptive exploration. However, we need to
-introduce two main modifications in the info-graph two accomendate
+introduce two main modifications in the info-graph to accommodate
 some new challenges. We will first informally describe our techniques
@@
 corresponds to the case where the gap $\Delta$ is between
-$\Omega\left(\sqrt{{1}/({\log(T) T_1)}}\right)$ and
-$O\left(\sqrt{{1}/{T_1}}\right)$. This is a boundary case since
+$\Omega\left(\sqrt{{1}/({T_1})}\right)$ and
+$O\left(\sqrt{{\log(T)}/{T_1}}\right)$. This is a boundary case since
 $\Delta$ is neither large enough to conclude that with high
@@
 observe the entire first-level history, which consists of
-$\Omega(\log(T) T_1)$ pulls of each arm and provides sufficiently
+$\Omega(T_1\log(T))$ pulls of each arm and provides sufficiently
 accurate reward estimates to distinguish the two arms.
@@
 level $(l-2)$ to distinguish two arms at level $l$. The reason for
-this larger disparity is that, except the first level, we can no
-longer guarantee sufficient number of pulls of each arm. For example,
+this larger disparity is that, except the first level, our guarantee on 
+the number of pulls of each arm is no longer tight. For example,
 as shown in Figure \ref{fig:llevel-connecting}, when we talk about
@@
 For each $l \in [L], u,v \in [\NG]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$.
-Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$.
-The main difference between the $G$-groups and $\Gamma$-groups is that the history of $\Gamma$-groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels.
-When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm.
+Agents in $\Gamma_{l,u,v}$ observe the same history as the one observed by agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T))$ times the number of agents in $G_{l,u,v}$.
+The main difference between $G$-groups and $\Gamma$-groups is that the history of $\Gamma$-groups in level $l$ is not sent to agents in level $l+1$ but agents in higher levels.
+When we are in the boundary case in which we don't have good guarantees about the $l+1$ level agents' pulls, the new construction makes sure that agents in levels higher than $l+1$ get to see enough pulls of each arm and all pull the best arm.
 %%% Local Variables:

### 2018-11-02 llevel-overview.tex
lol

@@
 corresponds to the case where the gap $\Delta$ is between
-$\Omega\left(\sqrt{{1}/({T_1})}\right)$ and
+$\Omega\left(\sqrt{{1}/{T_1}}\right)$ and
 $O\left(\sqrt{{\log(T)}/{T_1}}\right)$. This is a boundary case since
@@
 above does not get naturally resolved since the ratios between the
-upper and lower bounds of $\Delta$ rise from $\Theta(\sqrt{\log(T)})$
+upper and lower bounds of $\Delta$ increase from $\Theta\left(\sqrt{\log(T)}\right)$
 to $\Theta(\log(T))$, and it would require more observations from

### 2018-11-03 main.tex
.
title
Expanded title notes.

@@
 \def\z{\tau}
-\title{Incentivizing Exploration with Unbiased History}
+\title{Incentivizing Exploration with Unbiased Histories}
 
 \author{
-Nicole Immorlica \thanks{Microsoft Research, email: nicimm@microsoft	.com.}
+Nicole Immorlica \thanks{Microsoft Research, Cambridge, MA. Email: nicimm@microsoft.com.}
 \and
-Jieming Mao \thanks{University of Pennsylvania, email: maojm517@gmail.com.}
+Jieming Mao \thanks{University of Pennsylvania, Philadelphia, PA. email: maojm517@gmail.com. Results in this paper were obtained while J. Mao was an intern at Microsoft Research NYC.}
 \and
-Aleksandrs Slivkins  \thanks{Microsoft Research, email: slivkins@microsoft.com.}
+Aleksandrs Slivkins  \thanks{Microsoft Research, New York, NY. email: slivkins@microsoft.com.}
 \and
-Zhiwei Steven Wu  \thanks{University of Minnesota, email: zsw@umn.edu.}
+Zhiwei Steven Wu  \thanks{University of Minnesota, Minneapolis, MN. Email: zsw@umn.edu. Results in this paper were obtained while Z.S. Wu was a postdoc at Microsoft Research NYC.}
 }

### 2019-01-30 COLT 2019 Submission/algg.tex
COLT submission

%!TEX root = main.tex
\section{\ALGG: Revealing Full History}

\swedit{Before we describe our algorithms, we will first analyze a
  simple policy \ALGG \nicomment{as jieming and i discussed offline, this is a bad name for a policy; policies just determine the history and so aren't ``greedy'' in any sense i can see} that fully discloses the history over all
  previous rounds\nidelete{, and lets the agents make the ``greedy'' choices
  across all rounds}. Even though the algorithm does not guarantee low
  regret, it will be used as a subroutine in our main algorithms.  In
  particular, we show that because of the randomness in the rewards,
  with constant probability, \ALGG will induce the agents to
  play each arm at least once.} \nicomment{as we're talking about behavioral agents and not necessarily rational ones, i find it strange to talk about ``greedy'' agents -- which suggests to me that agents use an estimator equal to the empirical mean -- and to use the word ``incentivize'' (i changed it to ``induce'' in the previous paragraph).}

\begin{lemma}
\label{lem:greedy}
Under Assumption \ref{ass:embehave}, there exist two constants $\GdT = O_K(1)$
and $\GdP = \Omega_K(1)$ such that for any arm $a$, with probability
at least $\GdP$, \ALGG of $\GdT$ rounds pulls this arm at least
once.\footnote{The notations $O_k$ and $\Omega_K$ hide the dependence
  on the number of arms $K$.} \nicomment{If we change the name of the policy, we might also want to change the subscripts of these constants.}
\end{lemma}

\begin{proof}
  Fix any arm $a$. Let $\GdT = (K-1) \cdot c_T + 1$ and
  $\GdP = (1/3)^{\GdT}$. \swedit{We will condition on the event that
    all the realized rewards in $\GdT$ rounds are 0, which occurs with
    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.}
  In this case, we want to show that arm $a$ is pulled at least
  once. We prove this by contradiction. Suppose arm $a$ is not pulled. By
  the pigeonhole principle, we know that there is some other arm $a'$
  that is pulled at least $c_T + 1$ rounds. Let $t$ be the round in
  which arm $a'$ is pulled exactly $c_T + 1$ times. By Assumption
  \ref{ass:embehave}, we know
  \[
    \hat{\mu}_{a'}^t \leq 0 + c_m / \sqrt{c_T} < 1/3. 
  \]
  \nicomment{Wait, where did we set $c_T$?} On the other hand, we have
  $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
  the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
  \swdelete{ In addition, we know that this case happens with
    probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is
    at most $2/3$. To sum up, we know that with probability at least
    $\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.}
   \jmcomment{Agree with these changes.}
\end{proof}

\swedit{In our policies presented in the next sections, we will use
  \ALGG of $T_G$ rounds as a subroutine for initial exploration. For
  any $a$, let $q_a$ \nicomment{$q$ sounds like a fraction; maybe $n^G_a$ or $N^G_a$} be the expected number of arm $a$ pulls in one
  run of \ALGG of $T_G$ rounds.} \nicomment{\ALGG of $T_G$ rounds is a mouthful; what about using notation like \ALGG($T_G$)? or if we will always use $T_G$ rounds, then just define the policy to be that from now on?}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2019-01-30 COLT 2019 Submission/posterior.tex
COLT submission

%!TEX root = main.tex
\section{Posterior Mean}
\jmcomment{Do we want this section?} In this section, we give an example to show that for certain natural prior, when agents use this prior to compute the posterior means and use them as the estimators, Assumption \ref{ass:embehave} holds.

In the following example, it shows that the empirical mean and the posterior mean is really close (i.e. the difference is $O(1/n) = o(1/\sqrt{n})$). It's a special case of conjugate prior Beta distributions (i.e. this prior is just $Beta(1,1)$). Similar guarantees hold for Beta distribution with other parameters. For more details, see \cite{https://en.wikipedia.org/wiki/Conjugate_prior}.
\begin{example}
Let the prior distribution be the distribution over Bernoulli distributions $Ber(p)$ where $p$ is uniformly randomly sampled from $[0,1]$. Suppose there are $a$ 1's in $n$ samples. Then the posterior mean is $\frac{a+1}{n+2}$ and the empirical mean is $\frac{a}{n}$. Their difference is at most $\frac{1}{n+2}$. 
\end{example}

%\jmcomment{This example is against us. Should delete later.}
%\begin{example}
%Let the prior distribution be the uniform distribution over Bernoulli distributions with mean between $1/3$ and $2/3$. Suppose we have $n$ samples. With probability at least $\Omega(1/\sqrt{n})$, the difference between empirical mean and posterior mean is larger than $1/\sqrt{n}$.
%\end{example}

%jmcomment{this is not binary}
%\begin{example}
%Let the prior distribution be the sum of two independent 0-mean Gaussians. The first Gaussian is sampled once and has variance $\alpha^2$. The second Gaussian is sampled for each sample and has variance $\beta^2$. Suppose there are $n$ samples with empirical mean $m$. The posterior mean is $\frac{n \cdot m \cdot \alpha^2}{n \cdot \alpha^2 + \beta^2}$. The difference between the posterior mean and the empirical mean is $\frac{m\beta^2}{n\cdot \alpha^2 + \beta^2}$.
%\end{example}

%\jmcomment{Too many assumptions.}
%\begin{assumption}
%\label{ass:post}
%For any arm $i$ and any $m >0$, let $H_m$ be the random variables of $m$ pulls of arm $i$. Let $\emn(H_m)$ be the empirical mean and $\pmn(H_m)$ be the posterior mean. With probability at least $1 - \exp(m)$, we have $|\emn(H_m) - \pmn(H_m)| \leq \frac{1}{m}$. 
%\end{assumption}

In the above example, the samples of arm $a$ are chosen non-adaptively. Now think about the case when arms are chosen adaptively (i.e. in each round, which arm to choose is based on the history). Clearly, empirical means do not depend on whether samples are chosen adaptively. We show in the following lemma that it is also true for posterior means. It's a folklore and we include the proof for the completeness of our paper.
\begin{lemma}
\label{lem:post}
For any arbitrary strategy of pulling arms for $T$ rounds, let its history to be $G_T$. We allow this strategy to be adaptive based on history. Fix an arm $i$. Let $m_i(G_T)$ be the number of pulls of arm $i$, $\pmn_i(G_T)$ be the posterior mean of arm $i$. Let $H_{m(G_T)}$ be the sub history of arm $i$ in $G_T$. Then $\pmn_i(G_T)$ is the same as the posterior mean of seeing $H_{m_i(G_T)}$ after $m_i(G_T)$ non-adaptive pulls of arm $i$.
\end{lemma}

\begin{proof}
Let's assume there are $m^0_i(G_T)$ 0's and $m^1_i(G_T)$ 1's among of $m_i(G_T)$ pulls of arm $i$ in $G_T$. By the definition of posterior mean, we have
\[
\pmn_i(G_T) = \E[\mu_i|G_T] = \frac{\sum_{x_i} x_i \cdot \Pr[\mu_i=x_i, G_T]}{\sum_{x_i} \Pr[\mu_i=x_i, G_T]}.
\]

We also know that 
\[
\frac{\Pr[\mu_i = x_i, G_T]}{\Pr[\mu_i = x_i', G_T]} = \frac{\Pr[\mu_i = x_i] \cdot  (1-x_i)^{m^0_i(G_T)}x_i^{m^1_i(G_T)}}{\Pr[\mu_i = x_i'] \cdot (1-x_i)^{m^0_i(G_T)}(x_i')^{m^1_i(G_T)} }.
\]

Therefore ,
\[
\pmn_i(G_T) = \frac{\sum_{x_i} x_i \cdot \Pr[\mu_i = x_i] \cdot  (1-x_i)^{m^0_i(G_T)}x_i^{m^1_i(G_T)}}{\sum_{x_i}\Pr[\mu_i = x_i] \cdot  (1-x_i)^{m^0_i(G_T)}x_i^{m^1_i(G_T)}}
\]

Finally, by the definition of posterior mean, the posterior mean of seeing $H_{m_i(G_T)}$ after $m_i(G_T)$ pulls of arm $i$ is
\[
\frac{\sum_{x_i} x_i \cdot \Pr[\mu_i = x_i] \cdot  (1-x_i)^{m^0_i(G_T)}x_i^{m^1_i(G_T)}}{\sum_{x_i}\Pr[\mu_i = x_i] \cdot  (1-x_i)^{m^0_i(G_T)}x_i^{m^1_i(G_T)}} = \pmn_i(G_T).
\]
\end{proof}

%\begin{corollary}
%\label{cor:post}
%For any arbitrary strategy of pulling arms for $T$ rounds, let its history to be $G_T$. We allow this strategy to be adaptive based on history. Fix an arm $i$. Let $m(G_T)$ be the number of pulls of arm $i$, $\emn(G_T)$ be the empirical mean of arm $i$ and $\pmn(G_T)$ be the posterior mean of arm $i$. Let $p_0$ be the probability that $m(G_T) \geq m_0$. With probability $p_0 - 2\exp(m_0)$, $|\emn(G_T) - \pmn(G_T)| \leq \frac{1}{m(G_T)}$.
%\end{corollary}

%\begin{proof}
%Simply by applying Assumption \ref{ass:post}, Lemma \ref{lem:post} and union bound, we can prove the corollary.
%\end{proof}

### 2019-01-30 COLT 2019 Submission/related-work.tex
COLT submission

--- 2018-11-02 related-work.tex
@@
 
-Full-disclosure policy, and closely related ``greedy" (exploitation-only) algorithm in multi-armed bandits, have been a subject of a recent line of work \cite{Sven-aistats18,kannan2018smoothed,bastani2017exploiting,externalities-colt18,practicalCB-arxiv18}.
-A common theme is that the greedy algorithm performs well in theory, under  substantial heterogeneity assumptions, and sometimes it works well in practice.
-Yet, it suffers $\Omega(T)$ regret in the worst case.%
-\footnote{This is a well-known folklore result; \eg see \cite{CompetingBandits-itcs16} for a concrete example.}
+Full-disclosure policy, and closely related ``greedy" (exploitation-only) algorithm in multi-armed bandits, have been a subject of a recent line of work \cite{Sven-aistats18,kannan2018smoothed,bastani2017exploiting,externalities-colt18}.
+A common theme is that the greedy algorithm performs well in theory, under  substantial assumptions on heterogeneity of the agents. Yet, it suffers $\Omega(T)$ regret in the worst case.%
+\footnote{This is a well-known folklore result; \eg see \cite{CompetingBandits-itcs18} for a concrete example.}
 

### 2019-01-30 COLT 2019 Submission/main.tex
COLT submission
update author name format

--- 2018-11-02 main.tex
@@
-\documentclass[11pt]{article}
+\documentclass[anon,12pt]{colt2019}
 \usepackage{fullpage}
@@
 % ======    PACKAGES
-\usepackage{slivkins-setup,slivkins-theorems}
+\usepackage{slivkins-setup}
+%,slivkins-theorems}
 %\usepackage{amsmath, amsfonts, amssymb, amsthm, amsbsy, amscd, bm, bbm}
@@
 \usepackage{array}
-\usepackage{booktabs}
+%\usepackage{booktabs}
 \usepackage{graphicx}
-\usepackage[small,bf]{caption}
-\setlength{\captionmargin}{30pt}
-\usepackage{subcaption}
-\captionsetup[sub]{margin=10pt,font=small}
+%\usepackage[small,bf]{caption}
+%\setlength{\captionmargin}{30pt}
+%\usepackage{subcaption}
+%\captionsetup[sub]{margin=10pt,font=small}
 \usepackage{color}
@@
 \usepackage{algorithm}
-\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
+%\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
 \usepackage{url}
-\usepackage{tocbibind}
+%\usepackage{tocbibind}
 \usepackage{enumerate}
@@
 
+\newtheorem{assumption}[theorem]{Assumption}
+\newtheorem{construction}[theorem]{Construction}
+\newtheorem{claim}[theorem]{Claim}
 \DeclareMathOperator*{\argmin}{argmin}
@@
 \def\z{\tau}
-\title{Incentivizing Exploration with Unbiased History}
+\title{Incentivizing Exploration with Unbiased Histories}
+\usepackage{times}
 
-\author{
-Nicole Immorlica \thanks{Microsoft Research, email: nicimm@microsoft	.com.}
+% Authors with different addresses:
+\coltauthor{
+\Name{Nicole Immorlica} \Email{nicimm@microsoft.com}\\
+\addr Microsoft Research, Cambridge, MA. 
 \and
-Jieming Mao \thanks{University of Pennsylvania, email: maojm517@gmail.com.}
+\Name{Jieming Mao} \Email{maojm517@gmail.com}\\
+\addr University of Pennsylvania, Philadelphia, PA.
 \and
-Aleksandrs Slivkins  \thanks{Microsoft Research, email: slivkins@microsoft.com.}
+\Name{Aleksandrs Slivkins}  \Email{slivkins@microsoft.com}\\
+\addr Microsoft Research, New York, NY.
 \and
-Zhiwei Steven Wu  \thanks{University of Minnesota, email: zsw@umn.edu.}
+\Name{Zhiwei Steven Wu} \Email{zsw@umn.edu}\\
+\addr University of Minnesota, Minneapolis, MN.
 }
@@
 \end{abstract}
+\begin{keywords}%
+  incentivizing exploration, multi-armed bandit, social learning
+\end{keywords}
 \end{titlepage}
-
 \input{intro}
@@
 
-\bibliographystyle{plain}
+%\bibliographystyle{plain}
+%
+
+%\acks{We would like to thank Robert Kleinberg for discussions in the early stage of this project.}
 \bibliography{bib-abbrv,bib-AGT,bib-bandits,bib-ML,bib-random,bib-slivkins}
-
-\section*{Acknowledgment}
-We would like to thank Robert Kleinberg for discussions in the early stage of this project.
-
 \appendix

### 2019-01-30 COLT 2019 Submission/llevel.tex
COLT submission
remove fullpage

--- 2018-11-02 llevel.tex
@@
 \label{thm:llevel}
-The $L$-level recommendation policy gets regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(\NG^4))$.
+The $L$-level recommendation policy gets regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for \\ $L \leq \log(\ln(T)/\log(\NG^4))$.
 In particular, if we pick $L = \log(\ln(T)/\log(\NG^4))$, the regret is $O(T^{1/2} polylog(T))$.
@@
 \begin{align*}
-\bar{\mu}_a ^t &\geq \mu_a + \left(\fdpN T_1\NG \cdot \frac{1}{\sqrt{\fdpN T_1\NG}} - \GdT \sqrt{T_1\log(T)} \NG\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}\NG}} \right) \cdot \frac{1}{(\fdpN T_1+ \GdT \sqrt{T_1\log(T)})\NG} \\
+\bar{\mu}_a ^t &\geq \mu_a + \left(\fdpN T_1\NG \cdot \frac{1}{\sqrt{\fdpN T_1\NG}} - \GdT \sqrt{T_1\log(T)} \NG\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}\NG}} \right) \\
+&~~~~~~~~~~~\cdot \frac{1}{(\fdpN T_1+ \GdT \sqrt{T_1\log(T)})\NG} \\
 &> \mu_a + \frac{1}{4\sqrt{\fdpN T_1\NG}}.
@@
 &\geq \mu_1 -\mu_2-\sqrt{\frac{3\log(T)}{\NG\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{\NG\fdpN[2]T_1/2}}- \frac{\estC}{\sqrt{\NG\fdpN[1]T_1/2}} -  \frac{\estC}{\sqrt{\NG\fdpN[2]T_1/2}}\\
-&\geq\frac{\sqrt{\NG}}{4\sqrt{\fdpN[1]T_1}} +  \frac{\sqrt{\NG}}{4\sqrt{\fdpN[2]T_1}}-\sqrt{\frac{3\log(T)}{\NG\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{\NG\fdpN[2]T_1/2}}- \frac{\estC}{\sqrt{\NG\fdpN[1]T_1/2}} -  \frac{\estC}{\sqrt{\NG\fdpN[2]T_1/2}}\\
+&\geq\frac{\sqrt{\NG}}{4\sqrt{\fdpN[1]T_1}} +  \frac{\sqrt{\NG}}{4\sqrt{\fdpN[2]T_1}}-\sqrt{\frac{3\log(T)}{\NG\fdpN[1]T_1/2}} - \sqrt{\frac{3\log(T)}{\NG\fdpN[2]T_1/2}}\\
+&~~~~~~- \frac{\estC}{\sqrt{\NG\fdpN[1]T_1/2}} -  \frac{\estC}{\sqrt{\NG\fdpN[2]T_1/2}}\\
 &>0.
@@
 \begin{align*}
-\hat{\mu}_1^t - \hat{\mu}_2^t &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{\estC}{\sqrt{\NG^2\fdpN[1]T_1/2}}-\frac{\estC}{\sqrt{\NG^2\fdpN[2]T_1/2}}  \\
+&~~~\hat{\mu}_1^t - \hat{\mu}_2^t\\
+ &\geq \bar{\mu}_1^t - \bar{\mu}_2^t - \frac{\estC}{\sqrt{\NG^2\fdpN[1]T_1/2}}-\frac{\estC}{\sqrt{\NG^2\fdpN[2]T_1/2}}  \\
 &\geq \mu_1 -\mu_2 -  \sqrt{\frac{3\log(T)}{\NG^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{\NG^2\fdpN[2]T_1/2}}- \frac{\estC}{\sqrt{\NG^2\fdpN[1]T_1/2}}-\frac{\estC}{\sqrt{\NG^2\fdpN[2]T_1/2}}  \\
-&\geq\frac{1}{4\sqrt{\NG\fdpN[1]T_1}} + \frac{1}{4\sqrt{\NG\fdpN[2]T_1}}  -  \sqrt{\frac{3\log(T)}{\NG^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{\NG^2\fdpN[2]T_1/2}}- \frac{\estC}{\sqrt{\NG^2\fdpN[1]T_1/2}}-\frac{\estC}{\sqrt{\NG^2\fdpN[2]T_1/2}}  \\
+&\geq\frac{1}{4\sqrt{\NG\fdpN[1]T_1}} + \frac{1}{4\sqrt{\NG\fdpN[2]T_1}}  -  \sqrt{\frac{3\log(T)}{\NG^2\fdpN[1]T_1/2}}- \sqrt{\frac{3\log(T)}{\NG^2\fdpN[2]T_1/2}}\\
+&~~~~~~~~- \frac{\estC}{\sqrt{\NG^2\fdpN[1]T_1/2}}-\frac{\estC}{\sqrt{\NG^2\fdpN[2]T_1/2}}  \\
 &>0.
@@
 This will blow up the regret by a factor of $(K-1)$ which is a constant.
-\qed
+%\qed
 

### 2019-02-01 COLT 2019 Submission/2level.tex
Minor edits to save space.

--- 2018-11-02 2level.tex
@@
 
-We prove that for a constant number of arms, with constant probability, a full-disclosure path of constant length suffices to sample each arm at least once. We will build on this fact throughout.
+We prove that for a constant number of arms, with constant probability, a full-disclosure path of constant length suffices to sample each arm once. We use this fact throughout.
 
@@
 In the ``exploitation phase", each agent $t>N$ receives the full subhistory from exploration, \ie $m_t = \SubH{[N]}$.
-The info-graph for this disclosure policy is shown in Figure~\ref{fig:2level}.
+The info-graph for this disclosure policy is in Figure~\ref{fig:2level}.
 
@@
 Indeed, this number, denoted $\fdpN$, is the same for all such paths.
-Then,
 

### 2019-02-01 COLT 2019 Submission/3level.tex
Minor edits to save space.

--- 2018-11-02 3level.tex
@@
 \begin{description}
-\item[(\event{1})] \emph{Exploration in Level 1:} Every first-level group collects at least $\Omega(T_1)$ samples of each arm.
+\item[(\event{1})] \emph{Exploration in Level 1:} Every first-level group collects  $\Omega(T_1)$ samples of each arm.
 \item[(\event{2})] \emph{Concentration in Level 1:} Within each first-level group, empirical mean rewards of each arm $a$ concentrate around $\mu_a$.
@@
 \item[(\event{4})] \emph{Concentration in prefix:}
-The empirical mean reward of each arm $a$ concentrates around $\mu_a$ in any prefix of its pulls. (This ensures accurate reward estimates in exploitation.)
+Empirical mean reward of each arm $a$ concentrates around $\mu_a$ in any prefix of its pulls (ensuring accurate reward estimates in exploitation.)
 \end{description}
@@
 We break down the regret analysis into four cases, based on the magnitude the gap parameter $\Delta = \mu_1-\mu_2$.
-As a shorthand, denote
+As a shorthand,
     $\conf{n} = \sqrt{\log(T)/n}$.
 In words, this is a confidence term, up to constant factors, for $n$ independent random samples.
-
 The simplest case is very small gap, which trivially yields an upper bound on regret.
@@
 
-Another simple case is when $\Delta$ is sufficiently large, so that
+The second case is when $\Delta$ is sufficiently large, so that
 the data collected in any first-level group suffices to determine the best arm. The proof follows from \event{1} and \event{2}.

### 2019-02-01 COLT 2019 Submission/llevel-overview.tex
remove fullpage
Minor edits to save space.

--- 2018-11-02 llevel-overview.tex
@@
 \label{sec:llevel}
-In this section, we give an overview of how we extend our three-level
+
+We give an overview of how we extend our three-level
 policy to a more adaptive $L$-level policy for $L > 3$ in order to
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 \centering
-\begin{tikzpicture}  
+\begin{tikzpicture} [scale = 0.9]
  \foreach \x in {0,3,6,9}

### 2019-02-01 COLT 2019 Submission/model.tex
Minor edits to save space.
Minor edits.

--- 2018-11-02 model.tex
@@
 We are interested in \emph{regret}, defined as
-\begin{align}\label{eq:intro-regret-defn}
-\textstyle
-  \reg(T)
+%\begin{align}\label{eq:intro-regret-defn}
+%\textstyle
+ $ \reg(T)
   %= \reg(a_1, \ldots , a_T)
   = T \max_{a\in \A} \mu_a -
-  \sum_{t\in [T]} \E[\mu_{a_t}].
-\end{align}
+  \sum_{t\in [T]} \E[\mu_{a_t}].$
+%\end{align}
 (The expectation is over the chosen arms $a_t$, which depend on randomness in rewards, and possibly in the algorithm.)
@@
 \end{align}
-Accordingly, $\SubH{[t-1]}$ is called the \emph{full history} at time $t$.
+$\SubH{[t-1]}$ is called the \emph{full history} at time $t$.
 The \emph{outcome} for agent $t$ is the tuple $(t,a_t,r_t)$.
 
-We focus on disclosure policies of a particular form, where the message in each round $t$ is $m_t = \SubH{S_t}$ for some subset $S_t\subset [t-1]$.
-We assume that the subset $S_t$ is chosen ahead of time, before round $1$ (and therefore does not depend on the observations $\SubH{t-1}$).
+We focus on disclosure policies of a particular form: the message in each round $t$ is $m_t = \SubH{S_t}$ for some subset $S_t\subset [t-1]$.
+We assume that $S_t$ is chosen ahead of time, before round $1$ (and therefore does not depend on the observations $\SubH{t-1}$).
 Such message is called \emph{unbiased subhistory}, and the resulting disclosure policy is called an \emph{unbiased-history policy}.
@@
 
-We allow a much more permissive model that allows agents to form arbitrary reward estimates as long as they lie within some ``confidence range" of the sample average.
-Formally, the model is characterized by the following assumptions (which we make without further notice).
+We allow a much more permissive model which allows agents to form arbitrary reward estimates as long as they lie within some ``confidence range" of the sample average.
+The model is characterized by the following assumptions (made without further notice).
 
@@
 Let $N_{t,a}$ and $\bar{\mu}_{t,a}$ denote the number of pulls and the empirical mean reward of arm $a$ in subhistory $m_t$.
-Then for some absolute constant $\estN\in \N$ and $\estC=\tfrac{1}{16}$, and for all agents $t\in [T]$ and arms $a\in\A$ it holds that
+Then for some absolute constant $\estN\in \N$ and $\estC=\tfrac{1}{16}$, and for all agents $t\in [T]$ and arms $a\in\A$ we have
 \[
@@
     \left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
-		\frac{\estC}{\sqrt{N_{t,a}}}.
+		\estC/\sqrt{N_{t,a}}.
 \]

### 2019-02-01 COLT 2019 Submission/intro.tex
Minor edit.

--- 2018-11-02 intro.tex
@@
 %
-One way recommendation policies induce exploration is to introduce payments, \eg~\cite{Frazier-ec14,Kempe-colt18}.
+One way recommendation policies induce exploration is to introduce payments, \eg~\cite{Frazier-ec14,KKMPRVW17,Kempe-colt18}.
 For example, the recommendation system of an online retailer might offer coupons to agents for trying certain products.
@@
 for problem instances with gap $\Delta$, without knowing the $\Delta$ in advance.
-In particular, we match the regret rate achieved for incentivizing exploration with unrestricted disclosure policies \cite{ICexploration-ec15-working}.
+In particular, we match the regret rate achieved for incentivizing exploration with unrestricted disclosure policies \citep{ICexploration-ec15-working}.
 

### 2019-02-01 COLT 2019 Submission/related-work.tex
Added one more citation. Changed \cite -> \citep in various places.

--- 2018-11-02 related-work.tex
@@
 \xhdr{Related work.}
+The problem of incentivizing exploration via information asymmetry was introduced in \cite{Kremer-JPE14}, under the Bayesian rationality and the (implicit) power-to-commit assumptions.
+The original problem -- essentially, a version of our model with unrestricted disclosure policies -- was largely resolved in \cite{Kremer-JPE14} and the subsequent work \citep{ICexploration-ec15,ICexplorationGames-ec16}.
+Several extensions were considered: to contextual bandits \citep{ICexploration-ec15}, to repeated games
+\citep{ICexplorationGames-ec16}, and to social networks \citep{Bahar-ec16}.
 
-\cite{Perchet2015BatchedBP} gives regret guarantees for mult-armed bandit in $M$ batches. They have 2 upper bounds which are similar to our Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2}.
+Several other papers study related, but technically different models: same model with time-discounted utilities \citep{Bimpikis-exploration-ms17}; a version with monetary incentives \citep{Frazier-ec14} and moreover with heterogenous agents \citep{Kempe-colt18}; a version with a continuous information flow and a continuum of agents \citep{Che-13}; coordination of costly exploration decisions when they are separate from the ``payoff-generating" decisions \citep{Bobby-Glen-ec16,Annie-ec18-traps,Liang-ec18}.
+Scenarios with long-lived, exploring agents and no principal to coordinate them have been studied in \citep{Bolton-econometrica99,Keller-econometrica05}.
+
+Full-disclosure policy, and closely related ``greedy" (exploitation-only) algorithm in multi-armed bandits, have been a subject of a recent line of work \citep{Sven-aistats18,kannan2018smoothed,bastani2017exploiting,externalities-colt18}.
+A common theme is that the greedy algorithm performs well in theory, under  substantial assumptions on heterogeneity of the agents. Yet, it suffers $\Omega(T)$ regret in the worst case.%
+\footnote{This is a well-known folklore result; \eg see \citep{CompetingBandits-itcs18} for a concrete example.}
+\citet{Baransi-ecml14} use the ``greedy" algorithm on randomly sub-sampled subhistories to achieve optimal regret rate for two arms.
+However, their result is insufficient for our motivation, as the subhistories are not \emph{unbiased} or \emph{transitive}, in the sense defined earlier in the Introduction.
+In particular, the sub-sampling scheme depends on the current history, which may distort agents' incentives.
+
+Exploration-exploitation tradeoff received much attention over the past decades, usually under the rubric of ``multi-armed bandits"; see  \citep{Bubeck-survey12,Gittins-book11} for background.
+Exploration-exploitation problems with incentives issues arise in several other scenarios: dynamic pricing
+    \citep{KleinbergL03,BZ09,BwK-focs13},
+dynamic auctions
+    \citep{AtheySegal-econometrica13,DynPivot-econometrica10,Kakade-pivot-or13},
+pay-per-click ad auctions
+    \citep{MechMAB-ec09,DevanurK09,Transform-ec10-jacm},
+and human computation
+    \citep{RepeatedPA-ec14,Ghosh-itcs13,Krause-www13}.

### 2019-02-01 COLT 2019 Submission/intro.tex
\cite -> \citep in some places.

@@
 %
-One way recommendation policies induce exploration is to introduce payments, \eg~\cite{Frazier-ec14,KKMPRVW17,Kempe-colt18}.
+One way recommendation policies induce exploration is to introduce payments, \eg~\citep{Frazier-ec14,KKMPRVW17,Kempe-colt18}.
 For example, the recommendation system of an online retailer might offer coupons to agents for trying certain products.
-When payments are financially or technologically infeasible, another alternative is to rely on information asymmetry, \eg~\cite{Kremer-JPE14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17}.
+When payments are financially or technologically infeasible, another alternative is to rely on information asymmetry, \eg~\citep{Kremer-JPE14,Che-13,ICexploration-ec15,Bimpikis-exploration-ms17}.
 Here the idea is that the centralized algorithm, often called a {\em disclosure policy}, can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.

### 2019-02-01 COLT 2019 Submission/3level.tex
Lots of minor space-saving edits.

@@
 achieves regret
-\[ \reg(T) \leq O\left( T^{4/7}\, \log T \right).\]
+$ \reg(T) \leq O\left( T^{4/7}\, \log T \right)$.
 This is achieved with parameters
@@
 \xhdr{The ``good events".}
-We establish four ``good events" each of which occurs with high probability.
+We establish four ``good events" which occur with high probability.
 \begin{description}

### 2019-02-01 COLT 2019 Submission/intro.tex
Lots of minor space-saving edits.

@@
 
-The main challenge is that the agents still follow exploitation-only behavior, just like they do for the full-disclosure policy, albeit based only on a portion of history.
+The main challenge is that the agents still follow exploitation-only behavior, as for the full-disclosure policy, albeit based only on a portion of history.
 A disclosure policy controls the flow of information (who sees what), but not the \emph{content} of that information.

### 2019-02-01 COLT 2019 Submission/llevel-overview.tex
Lots of minor space-saving edits.

@@
 \label{thm:llevel-1}
-For any $L > 3$, there exists an $L$-level disclosure policy with
-regret $$O_K\left(T^{2^{L-1}/(2^L-1)} \cdot \polylog(T) \right).$$ In
-particular, there exists a $O(\log\log(T))$-level recommendation
+For any $L > 3$, there is an $L$-level disclosure policy with
+regret 
+    $O_K\left(T^{2^{L-1}/(2^L-1)} \cdot \polylog(T) \right)$.
+ In particular, there is a $O(\log\log(T))$-level recommendation
 policy with regret $O_K(T^{1/2} \polylog(T))$.
@@
 every multi-armed bandit instance with gap parameter $\Delta$, the
-policy has regret $$O_K(\min(1/\Delta, T^{1/2}) \cdot \polylog(T))$$
+policy has regret 
+    $O_K(\min(1/\Delta, T^{1/2}) \cdot \polylog(T))$
 Moreover, under this policy, each agent $t$ observes a subhistory of

### 2019-02-01 COLT 2019 Submission/related-work.tex
Lots of minor space-saving edits.

@@
 \citet{Baransi-ecml14} use the ``greedy" algorithm on randomly sub-sampled subhistories to achieve optimal regret rate for two arms.
-However, their result is insufficient for our motivation, as the subhistories are not \emph{unbiased} or \emph{transitive}, in the sense defined earlier in the Introduction.
-In particular, the sub-sampling scheme depends on the current history, which may distort agents' incentives.
+However, their result is insufficient for our motivation, as the subhistories are not \emph{unbiased} or \emph{transitive}, in the sense defined earlier.
+In particular, the sub-sampling scheme depends on the history, which may distort agents' incentives.
 

### 2019-02-01 COLT 2019 Submission/llevel-overview.tex
A bit more space-saving.

@@
 
-Note for constant number of arms, this result matches the optimal
-regret rate (given in \Cref{eq:model-OptRegret}) for stochastic
-bandits, up to logarithmic factors.
-
-In this section, we present the main techniques in our solution, and
+For constant number of arms, this result matches the optimal
+regret rate \eqref{eq:model-OptRegret} for stochastic
+bandits, up to logarithmic factors. Below we present the main techniques in our solution, and
 the full proofs of Theorem \ref{thm:llevel-1} and Theorem
@@
 levels as multiple ``check points", so the policy can incentivize the
-agents to perform more adaptive exploration. However, we need to
-introduce two main modifications in the info-graph to accommodate
-some new challenges. We will first informally describe our techniques
+agents to perform more adaptive exploration. However, we need two key modifications in the info-graph to accommodate
+some new challenges. We first informally describe our techniques
 for the two-arm case.
@@
 agents in group $G_{l-1,v,w}$ (and by transitivity all agents in
-levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a
-visualization of simple case with $\NG = 2$). Two observations are
-in order:
+levels below $l-1$). See Figure \ref{fig:llevel-connecting} for the simple case with $\NG = 2$).
+
+Two observations are in order.
 % \OMIT{(i) The number of groups does not grow with $L$ and stays as
@@
 %   incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
-\begin{itemize}
-\item[(i)] Consider level $(l - 1)$ and fix the last group index to be
+%\begin{itemize}
+%\item[(i)] 
+(i) Consider level $(l - 1)$ and fix the last group index to be
   $v$, and consider the set of groups
@@
   for $a$.
-
-\item[(ii)] Every agent in level $l$ observes the sub-history from
+%\item[(ii)] 
+(ii) Every agent in level $l$ observes the sub-history from
   $\NG$ $(l-1)$-th level groups, each of which belonging to a
@@
     in level $l$ will see enough pulls of arm $a$.}
-\end{itemize}
+%\end{itemize}
 
-\begin{figure}[h]
+\begin{figure}[t]
 \centering

### 2019-02-01 COLT 2019 Submission/2level.tex
Lots of minor space-saving edits.
A bit more space-saving.
figure =>appendix
Some more space-saving.

@@
 We use this policy as a ``gadget" in our constructions.
-Hence, we formulate it slightly more generally:
+Hence, we formulate it more generally:
 
@@
 
-\begin{figure}[H]
+%\iffalse
+\begin{figure}[t]
 \centering
-\begin{tikzpicture}
+\begin{tikzpicture}[scale =0.8]
  \filldraw[fill=blue!20!white]
@@
 \end{figure}
+%\fi
 
@@
 \begin{theorem}\label{thm:2level}
-The \2LEVEL with parameter $T_1 = T^{2/3}\,\log(T)^{1/3}$ achieves regret
-\[ \reg(T) \leq O_K\left( T^{2/3}\, (\log T)^{1/3} \right).\]
+The \2LEVEL with parameter 
+    $T_1 = \tilde{O}(T^{2/3})$ 
+%    $T_1 = T^{2/3}\,\log(T)^{1/3}$ 
+achieves regret
+     $\tilde{O}_K (T^{2/3})$.
+%\[ \reg(T) \leq O_K\left( T^{2/3}\, (\log T)^{1/3} \right).\]
 \end{theorem}
@@
 Suppose the info-graph contains $T_1$ full-disclosure paths of $\fdpL$ rounds each. Let $N_a$ be the number of samples of arm $a$ collected by all paths. Then with probability at
-  least $1-\delta$, for all $a\in \A$,
+  least $1-\delta$,
   \[
-    \left| N_a - \fdpN T_1\right| \leq \fdpL\cdot \sqrt{T_1 \log(2K/\delta) / 2}.
+    \left| N_a - \fdpN T_1\right| \leq \fdpL\cdot \sqrt{T_1 \log(2K/\delta) / 2},\quad
+    \text{for all $a\in \A$}.
   \]

### 2019-02-01 COLT 2019 Submission/model.tex
Lots of minor space-saving edits.
Some more space-saving.

@@
 The \emph{subhistory} for a subset of rounds $S\subset [T]$ is defined as
-\begin{align} \label{eq:model-subhistory}
+\begin{align*} %\label{eq:model-subhistory}
     \SubH{S} = \left\{\; (s,a_s,r_s):\;s\in S \;\right\}.
-\end{align}
+\end{align*}
 $\SubH{[t-1]}$ is called the \emph{full history} at time $t$.
@@
 This regret bound can only be achieved using \emph{adaptive exploration}: \ie when exploration schedule is adapted to the observations.
-A simple example of \emph{non}-adaptive exploration is the \emph{explore-then-exploit} algorithm which samples arms uniformly at random for the first $N$ rounds, for some pre-set number $N$, then chooses one arm and sticks with it till the end.
-More generally,
-\emph{exploration-separating} algorithms have a property that in each round $t$, either the choice of an arm does not depend on the observations so far, or the reward collected in this round is not used in the subsequent rounds.
+A simple example of \emph{non}-adaptive exploration is the \emph{explore-then-exploit} algorithm which samples arms uniformly at random for the first $N$ rounds, for some pre-set $N$, then chooses one arm and sticks with it till the end.
 Any such algorithm suffers from $\Omega(T^{2/3})$ regret in the worst case.%
-\footnote{The first explicit reference we know of is \cite{MechMAB-ec09,DevanurK09}, but this fact has been known in the community for much longer.}
+\footnote{More generally, this lower bound applies to \emph{exploration-separating} algorithms, where in each round $t$, either the choice of an arm does not depend on the observations so far, or the reward collected in this round is not used in the subsequent rounds.
+The first explicit reference we know of is \cite{MechMAB-ec09,DevanurK09}, but this fact has been known in the community for much longer.}
 
@@
 
-Throughout the paper, we use the standard concentration and anti-concentration inequalities: respectively, Chernoff Bounds and Berry-Esseen Theorem.
+Throughout the paper, we use the standard concentration and anti-concentration inequalities: resp., Chernoff Bounds and Berry-Esseen Theorem (see Appendix~\ref{sec:prelim}).
 The former states that that a sum of independent random variables converges to its expectation quickly.
@@
 In particular, the average strays far enough from its expectation with some guaranteed probability.
-The theorem statements are moved to Appendix~\ref{sec:prelim}.
+%The theorem statements are moved to Appendix~\ref{sec:prelim}.
 
-We use the notion of \emph{reward tape} to simplify the application of (anti-)concentration inequalities.
-This is a $K\times T$ random matrix with rows and columns corresponding to arms and rounds, respectively.
+We use the notion of \emph{reward tape} to simplify applications of (anti-)concentration inequalities.
+This is a $K\times T$ random matrix with rows and columns corresponding to arms and rounds.
 For each arm $a$ and round $t$, the value in cell $(a,t)$ is drawn independently from Bernoulli distribution $\mD_a$.
-W.l.o.g., rewards in our model are defined by the rewards tape: namely, the reward for the $j$-th pull of arm $a$ is taken from the $(a,j)$-th entry of the reward matrix.
+W.l.o.g., rewards in our model are defined by the rewards tape: the reward for the $j$-th pull of arm $a$ is taken from cell $(a,j)$ of the reward tape.
 

### 2019-02-01 COLT 2019 Submission/3level.tex
figure =>appendix
Some more space-saving.
Added pageref's to references to figures.

@@
 \begin{construction}
-The \emph{three-level policy} is defined as follows.
+The \emph{three-level policy} is defined as follows (see Figure~\ref{fig:3level} on page \pageref{fig:3level}).
 The info-graph consists of three levels: the first two correspond to \emph{exploration}, and the third implements \emph{exploitation}.
-Like in the two-level policy, the first level consists of multiple full-disclosure paths of length $\fdpL$ each, and each agent $t$ in the exploitation level sees full history from exploration  (see Figure~\ref{fig:3level}).
-
-The middle level consists of $\NG$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}. Each second-level group $G$ has the following property:
+Like in the two-level policy, the first level consists of multiple full-disclosure paths of length $\fdpL$ each, and each agent $t$ in the exploitation level sees full history from exploration.
+The middle level consists of $\NG$ disjoint subsets of $T_2$ agents each, called \emph{second-level groups}.
+Each second-level group $G$ has the following property:
 \begin{align}\label{eq:group-defn}
@@
 \end{construction}
-
+\iffalse
 \begin{figure}[t]
@@
 \end{figure}
-
+\fi
 The key idea is as follows.
@@
 first and second levels, so
-\[ \textstyle
-\reg(T) \leq (\NG\,T_1\cdot \GdT + \NG\, T_2)
-\cdot 4\,\sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}
-= O(T^{4/7} \log^{6/7}(T)).
-\]
+%\[ \textstyle
+$\reg(T) \leq (\NG\,T_1\cdot \GdT + \NG\, T_2)
+\cdot 4\,\sum_{a\in\A}\; \conf{\fdpN[a]\cdot T_1}$,
+which is at most 
+$O(T^{4/7} \log^{6/7}(T))$.
+%\]
 Therefore, we obtain the stated regret bound in all cases.

### 2019-02-01 COLT 2019 Submission/related-work.tex
A bit more space-saving.

@@
 
-Full-disclosure policy, and closely related ``greedy" (exploitation-only) algorithm in multi-armed bandits, have been a subject of a recent line of work \citep{Sven-aistats18,kannan2018smoothed,bastani2017exploiting,externalities-colt18}.
+Full-disclosure policy, and closely related ``greedy" (exploitation-only) bandit algorithm have been a subject of a recent line of work \citep{Sven-aistats18,kannan2018smoothed,bastani2017exploiting,externalities-colt18}.
 A common theme is that the greedy algorithm performs well in theory, under  substantial assumptions on heterogeneity of the agents. Yet, it suffers $\Omega(T)$ regret in the worst case.%
@@
 
-Exploration-exploitation tradeoff received much attention over the past decades, usually under the rubric of ``multi-armed bandits"; see  \citep{Bubeck-survey12,Gittins-book11} for background.
+Exploration-exploitation tradeoff received much attention over the past decades,
+%, usually under the rubric of ``multi-armed bandits"; 
+see  \citep{Bubeck-survey12,Gittins-book11} for background.
 Exploration-exploitation problems with incentives issues arise in several other scenarios: dynamic pricing

### 2019-02-01 COLT 2019 Submission/related-work.tex
cut..

--- 2019-02-01 COLT 2019 Submission/related-work.tex
@@
 \footnote{This is a well-known folklore result; \eg see \citep{CompetingBandits-itcs18} for a concrete example.}
-\citet{Baransi-ecml14} use the ``greedy" algorithm on randomly sub-sampled subhistories to achieve optimal regret rate for two arms.
+\citet{Baransi-ecml14} use the ``greedy" algorithm on sub-sampled subhistories to achieve optimal regret rate for two arms.
 However, their result is insufficient for our motivation, as the subhistories are not \emph{unbiased} or \emph{transitive}, in the sense defined earlier.
@@
 
-Exploration-exploitation tradeoff received much attention over the past decades, usually under the rubric of ``multi-armed bandits"; see  \citep{Bubeck-survey12,Gittins-book11} for background.
-Exploration-exploitation problems with incentives issues arise in several other scenarios: dynamic pricing
+Exploration-exploitation tradeoff received much attention over the past decades, usually under the rubric of ``multi-armed bandits"; see  \citep{Bubeck-survey12% ,Gittins-book11
+} for background.
+Exploration-exploitation problems with incentives issues arise in other scenarios, including dynamic pricing
     \citep{KleinbergL03,BZ09,BwK-focs13},

### 2019-03-25 COLT 2019 Submission/COLT rebuttal.txt
rebuttal

AnonReviewer1:
Q: Why does it matter if agent t' knows which observations agent t got if all agent t' does is essentially compute the sample mean from its observations?
A: First of all, they may not computing exactly sample means. Second, even if they are computing sample means, it matters to know if these are means from which sets of agents.

Q: I was surprised that the proof of Lemma 7 is not included
A: It could be proved using Chernoff bound and union bound. We will include it in the next version for completeness.

Q: Relatedly, in the proof of Lemma 18 when Lemma 7 is used to bound W^{a, s}_1, where does the middle inequality come from 
A: Sorry for the confusion. Lemma 7 is stated after applying union bound. And in Lemma 18, we are using Lemma 7 before the union bound step. We will make it more clear in the next version.

PC3: 
Q: I found the motivation behind the “unbiased subhistories” model not convincing: I don’t see why users, who wouldn’t trust minimal disclosure policies, should trust policies based on subhistories.  Even if the subhistories revealed to the agents are “unbiased”, the principal might still behave very differently (e.g., employ exploration) on the other rounds that are never disclosed.  Further, users do NOT know in advance whether they will be part of future subhistories.  Why would they react rationally in this setting?
A:

Q: The behaviour of agents in the model is also weird: the authors assume that the true mean reward of each arm is in the interval [1/3,2/3] (which is already suspicious), but then posit that agents make decisions according to empirical averages over revealed subhistories, which might fall out of this interval (granted, this happens only with a small probability, but precisely when exploration is needed).  So, it seems that agents in this model are not behaving very rationally.
A:

Q: The regret bounds in the paper are exponential in the number of arms K and other parameters of the problem.  Furthermore, the authors never mention this caveat explicitly in the paper, and only after browsing through the appendix (proof of Thm 5, with definitions from proof of Lem 4) did I realize that. (The authors do hint that their bounds are suboptimal w.r.t. K, but that is of course unsatisfactory.)
A:

AnonReviewer2: 
Q: In "Our scope" you assume that the info-graph is common knowledge. Do you mean that it is known by the agents? If so, where do they use it and is that reasonable to assume?
A:

Q: The authors claim that Assumption 1 is "much more permissive" than just assuming that the agents maximize their empirical averages. It seems a bit of an overstatement. Pulling each arm at least N_est ensures that the estimate used by the agents is at most 1/256N the empirical everage, where N is the number of pulls of the chosen arm up to the current round. It does not seem to change generality. If that is the case, can the authors elaborate on exactly why? 
A:

Q:In all the policies proposed in the paper, the constant L_K^FDP, used by the algorithm, depends on N_est (see proof of Lemma 4, page 15). This would imply that the algorithm knows N_est. It should be clearly stated as an assumption for the model.
A:

Q: In section 4 the authors set the number K of actions to 2. Is this without loss of generality? How do bounds depend on K if K is arbitrary?
A:

Q: Page 5, rewards are Bernoulli. Is this necessary? Do things work for arbitrary distributions on [0,1]?
A:

Q: Page 5, means are in [1/3, 2/3]. Is this necessary? Where do things break down if means are in [0,1]?
A:

### 2019-03-27 COLT 2019 Submission/COLT rebuttal.txt
Full draft of rebuttal.

@@
-AnonReviewer1:
+============ Review 1 (AnonReviewer1) ===============
+
+Thanks for the positive comments!
+
 Q: Why does it matter if agent t' knows which observations agent t got if all agent t' does is essentially compute the sample mean from its observations?
-A: First of all, they may not computing exactly sample means. Second, even if they are computing sample means, it matters to know if these are means from which sets of agents.
+
+A: Indeed, it doesn't matter once the behavioral model is fixed.
+But it helps to justify this model.
+As we explain (page 3, para 1), due to this "transitivity property" agent t' does not need to worry why agent t chose a particular action.
+Essentially, t' can just treat the subhistory as a set of data points, and not worry where they came from.
 
 Q: I was surprised that the proof of Lemma 7 is not included
-A: It could be proved using Chernoff bound and union bound. We will include it in the next version for completeness.
+
+A: It has a fairly standard proof via Chernoff bounds. But good point, we will include it in a revision.
 
 Q: Relatedly, in the proof of Lemma 18 when Lemma 7 is used to bound W^{a, s}_1, where does the middle inequality come from
-A: Sorry for the confusion. Lemma 7 is stated after applying union bound. And in Lemma 18, we are using Lemma 7 before the union bound step. We will make it more clear in the next version.
 
-PC3: 
-Q: I found the motivation behind the “unbiased subhistories” model not convincing: I don’t see why users, who wouldn’t trust minimal disclosure policies, should trust policies based on subhistories.
-Even if the subhistories revealed to the agents are “unbiased”, the principal might still behave very differently (e.g., employ exploration) on the other rounds that are never disclosed.
-Further, users do NOT know in advance whether they will be part of future subhistories.
-Why would they react rationally in this setting?
-A:
+A: Good catch, thanks! Lemma 7 is stated after applying union bound, and in Lemma 18, we are using Lemma 7 before the union bound step. We will fix this in a revision.
 
-Q: The behaviour of agents in the model is also weird: the authors assume that the true mean reward of each arm is in the interval [1/3,2/3] (which is already suspicious), but then posit that agents make decisions according to empirical averages over revealed subhistories, which might fall out of this interval (granted, this happens only with a small probability, but precisely when exploration is needed).
-So, it seems that agents in this model are not behaving very rationally.
-A:
+============== Review 2 (PC Member3) =================
 
-Q: The regret bounds in the paper are exponential in the number of arms K and other parameters of the problem.
-Furthermore, the authors never mention this caveat explicitly in the paper, and only after browsing through the appendix (proof of Thm 5, with definitions from proof of Lem 4) did I realize that.
-(The authors do hint that their bounds are suboptimal w.r.t.
-K, but that is of course unsatisfactory.)
-A:
+Thanks for raising several important conceptual concerns.
+We believe these concerns can be easily addressed via a more careful discussion, as per the below.
+Note that a version of this discussion appeared in our response to STOC reviews, which we provided early on.
+Unfortunately, we didn't received STOC reviews until after the COLT submission deadline.
 
-AnonReviewer2: 
-Q: In "Our scope" you assume that the info-graph is common knowledge. Do you mean that it is known by the agents? If so, where do they use it and is that reasonable to assume?
-A:
+"why users, who wouldn’t trust minimal disclosure policies, should trust policies based on subhistories."
 
-Q: The authors claim that Assumption 1 is "much more permissive" than just assuming that the agents maximize their empirical averages.
-It seems a bit of an overstatement.
-Pulling each arm at least N_est ensures that the estimate used by the agents is at most 1/256N the empirical everage, where N is the number of pulls of the chosen arm up to the current round.
-It does not seem to change generality.
-If that is the case, can the authors elaborate on exactly why?
-A:
+We argue that our mechanism requires substantially weaker trust/rationality assumptions compared to the minimal-disclosure policies.
 
-Q:In all the policies proposed in the paper, the constant L_K^FDP, used by the algorithm, depends on N_est (see proof of Lemma 4, page 15).
-This would imply that the algorithm knows N_est.
-It should be clearly stated as an assumption for the model.
-A:
+There are several distinct issues here: that the agents (i) sufficiently understanding the announced policy, (ii) trusting the principal to want to implement it, (iii) trust him to actually implement it without bugs, and (iv) react to the policy in the way that we want.
 
-Q: In section 4 the authors set the number K of actions to 2. Is this without loss of generality? How do bounds depend on K if K is arbitrary?
-A:
+Re (i), we only need an agent to understand that he is given an unbiased history -- doesn't matter which one  -- and it sees the entire message received by each agent in this subhistory.
+This is arguably pretty accessible, compared to a full-blown spec of a bandit algorithm.
+
+Re (iii), faithfully revealing a subhistory is arguably easy, whereas debugging an actual bandit algorithm in a production-level system tends to be tricky.
+
+Re (ii), a third party can, at least in principle, check collect subhistories from multiple agents and check them for consistency (e.g., that arms' average rewards are within the statistical deviations).
+Such checks appear virtually impossible for minimal-disclosure policies.
+
+Re (iv), the agent should react to his subhistory as if it was just given a dataset, not thinking where this data came from.
+Whereas verifying that a minimal-disclosure policy is indeed incentive-compatible typically requires a sophisticated Bayesian reasoning.
+
+"... the principal might still behave very differently ... on the other rounds that are never disclosed."
+
+What happens outside of the revealed subhistory should not matter to the agent, because it does not affect the revealed subhistory.
+
+"users do NOT know in advance whether they will be part of future subhistories."
+
+It doesn't really matter for our model, but they do know: the info-flow graph is public.
+
+"... mean reward of each arm is in the interval [1/3,2/3] (which is already suspicious), but ... agents make decisions according to empirical averages"
+
+Indeed, our agents do not take into account that mean rewards lie in [1/3, 2/3].
+Our justification is two-fold.
+First, we could posit incomplete information: agents simply do not know that mean rewards are restricted.
+Second, typical users are unlikely to implement a fully rational model.
+Following empirical averages appears much more natural.
+In particular, a realistic user should not estimate mean rewards as 1/3 if it keeps getting 0 rewards.
+
+That the mean rewards lie in [1/3, 2/3] is a fairly mild assumption -- even for a bandit problem, let alone an incentivized exploration problem where NOTHING is known (without very strong trust/rationality assumptions).
+
+Of course, [1/3, 2/3] can be replaced with [eps,1-eps] for any constant eps>0, which then propagates into the regret bounds.
+
+"The regret bounds ... are exponential in [#arms]"
+
+Indeed.
+However, such dependence is state-of-art in all prior work on incentivized exploration (see Mansour et al., 2015).
+We conjecture this is an inevitable "price of incentives".
+Note that this whole issue is irrelevant for two arms (which could be a paper on its own).
+
+====== Review 3 (AnonReviewer2) ============
+
+Thanks for raising several important conceptual concerns.
+We believe these concerns can be easily addressed via a more careful discussion, as per the below.
+Note that a version of this discussion appeared in our response to STOC reviews, which we provided early on.
+Unfortunately, we didn't received STOC reviews until after the COLT submission deadline.
+
+"Overall, assumptions seem a bit heavy compared to the results obtained. "
+
+A relevant comparison, in our opinion, is the state-of-art on incentivized exploration, where NOTHING was known without very strong trust/rationality assumptions.
+
+"... you assume that the info-graph is common knowledge. Do you mean that it is known by the agents?"
+
+Yes.
+It is reasonable, in the sense that the mechanism can "publish" whatever it wants.
+However, we don't need this assumption, neither formally nor to justify our model.
+We only need "unbiased history" with "transitivity".
+
+"Assumption 1 is "much more permissive" than just assuming that the agents maximize their empirical averages."
+
+We allow reward estimates to be within constant*ConfidenceRadius from the empirical averages, and we only make this assumption if N>N_est.
+
+Put simply: rewards estimates are can differ from the empirical average, but not too much, and users reliably form such estimates only if they have sufficiently many samples.
+
+"the algorithm knows N_est. It should be clearly stated." 
+Agreed!
+
+"In section 4 the authors set the number K of actions to 2." 
+Section 4 is a graceful intro to the general result in Section 5. So, it posits K=2 for simplicity only.
+
+"How do bounds depend on K if K is arbitrary?"
+
+Our regret bounds are exponential in K (which we should make clearer).
+However, such dependence is state-of-art in all prior work on incentivized exploration (see Mansour et al., 2015).
+We conjecture this is an inevitable "price of incentives".
+Note that this whole issue is irrelevant for two arms (which could be a paper on its own).
 
 Q: Page 5, rewards are Bernoulli. Is this necessary? Do things work for arbitrary distributions on [0,1]?
-A:
 
-Q: Page 5, means are in [1/3, 2/3]. Is this necessary? Where do things break down if means are in [0,1]?
-A:
+Bernoulli rewards is arguably the most important special case.
+However, this restriction is just for ease of exposition.
+Essentially, we only need {reward>3/4} and {reward<1/4} to happen with constant probability.
+%%% Jieming, is this true? I don't see why not.
+
+"means are in [1/3, 2/3]. Is this necessary? Where do things break down  if means are in [0,1]?"
+
+Yes, this seems essential for our analysis. 
+%%% Jieming, can you concisely explain why?
+
+Of course, [1/3, 2/3] can be replaced with [eps,1-eps] for any constant eps>0, which then propagates into the regret bounds.
+
+Somewhat controversially, our behavioral model for agents does not take this fact into account.
+Our justification is two-fold.
+First, we could posit incomplete information: agents simply do not know that mean rewards are restricted.
+Second, typical users are unlikely to implement a fully rational model.
+Following empirical averages appears much more natural.
+In particular, a realistic user should not estimate mean rewards as 1/3 if it keeps getting 0 rewards.

### 2019-03-27 COLT 2019 Submission/COLT rebuttal.txt
Update COLT rebuttal.txt
Minor edit in reb3.

@@
 Essentially, we only need {reward>3/4} and {reward<1/4} to happen with constant probability.
-%%% Jieming, is this true? I don't see why not.
 
@@
 Yes, this seems essential for our analysis.
-%%% Jieming, can you concisely explain why?
+When arms' means can get closer to 1, for example, let's say some arm has mean 1-1/T^{0.1}.
+Then in our solution, this arm will with high probability stop agents from exploring other arms with small initial estimates (e.g.
+0.5) and better actual means (e.g.
+1).
 
 Of course, [1/3, 2/3] can be replaced with [eps,1-eps] for any constant eps>0, which then propagates into the regret bounds.
-
-Somewhat controversially, our behavioral model for agents does not take this fact into account.
-Our justification is two-fold.
-First, we could posit incomplete information: agents simply do not know that mean rewards are restricted.
-Second, typical users are unlikely to implement a fully rational model.
-Following empirical averages appears much more natural.
-In particular, a realistic user should not estimate mean rewards as 1/3 if it keeps getting 0 rewards.

### 2019-04-15 intro.tex
king of self-citation
Revised to address reviewers' comments, as per our rebuttals.

@@
 However, these assumptions appear quite problematic in the context of recommendation systems of actual online websites such as those mentioned above.
-In particular, much of the prior work suggests disclosure policies that merely recommend an action to each agent, without any other supporting information, and moreover recommend exploratory actions to some randomly selected users.
+In particular, much of the prior work suggests disclosure policies that merely recommend an action to each user, without any other supporting information, and moreover recommend exploratory actions to some randomly selected users.
 This works out extremely well in theory, but it is very unclear whether users would even know some complicated policy of the principal, let alone trust the principal to implement the stated policy.
@@
 %
-Several issues are in play: to wit, whether the principal intentionally uses a different disclosure policy than the claimed one (\eg because its incentives are not quite aligned with the users'), whether the principal correctly implements the policy that it wants to implement, whether the users trust the principal to make correct inferences on their behalf, and whether they find it acceptable that they may be singled out for exploration.
-Furthermore, regardless of how the users react to such disclosure policies, they may prefer not to be subjected to them, and leave the system.
+Several issues are in play: to wit, whether the principal intentionally uses a different disclosure policy than the claimed one (\eg because its incentives are not quite aligned with the users'), whether the principal correctly implements the policy that it wants to implement,%
+\footnote{\asedit{Large-scale systems that implement bandit algorithms can be notoriously difficult to debug \cite{DS-arxiv}.}}
+ whether the users trust the principal to make correct inferences on their behalf, and whether they find it acceptable that they may be singled out for exploration.
+Regardless of how the users react to such disclosure policies, they may prefer not to be subjected to them, and leave the system.
 
 We strive to design disclosure policies which mitigate these issues and (still) incentivize a good balance between exploration and exploitation.
-While some assumptions on human behavior are unavoidable, we are looking for a class of disclosure policies for which we can make plausible behavioral assumptions.
+While some assumptions on human behavior are unavoidable, we are looking for a class of disclosure policies for which \asedit{they are (more) plausible}.
 Then we arrive at a concrete mathematical problem: design policies from this class so as to optimize performance, \ie  the induced explore-exploit tradeoff.
@@
 Unfortunately, the full-disclosure policy is not good for our purposes, essentially because we expect users to \emph{exploit} rather than \emph{explore}.
-However, what if a disclosure policy reveals the outcomes for every tenth agent, rather than the outcomes for all agents?
+However, what if a disclosure policy reveals the outcomes for every tenth user, rather than the outcomes for all users?
 We posit that users would trust such policy, too.
-Given a large volume of data, we posit that users would not be too unhappy with having access to only a fraction this data.
+Given a large volume of data, users would not be too unhappy with having access to only a fraction this data.
+
 A crucial aspect of our intuition here is that the ``subhistory" revealed to a given user comes from a subset of previous users that is chosen in advance, without looking at what happens during the execution.
-In particular, the subhistory is not ``biased", in the sense that the disclosure policy cannot subsample the observations in favor of a particular action.
+In particular, the subhistory is not ``biased", in the sense that the disclosure policy cannot subsample the observations so as to make a particular action look good.
+\asedit{(If a subhistory is subsampled in favor of some action, revealing is essentially no better than just issuing a recommendation without any supporting evidence.)}
+With this intuition in mind, we define the class of \emph{unbiased-subhistory policies}: disclosure policies that reveal, to each arriving agent $t$, a subhistory  consisting of the outcomes for a subset $S_t$ of previous agents, where $S_t$ is chosen ahead of time.
+\asedit{(From here on, we will use ``users" and ``agents" interchangeably.)}
 
-With this intuition in mind, we define the class of \emph{unbiased-subhistory policies}: disclosure policies that reveal, to each arriving agent $t$, a subhistory  consisting of the outcomes for a subset $S_t$ of previous agents, where $S_t$ is chosen ahead of time.
 Further, we impose a transitivity property: if $t' \in S_t$, for some previous agent $t'$, then $S_{t'}\subset S_t$.
-So, agent $t$ has all information that agent $t'$ had at the time she chose her action.
-In particular, agent $t$ does not need to second-guess which message has caused agent $t'$ to make choose that action.
+In words, agent $t$ has all information that agent $t'$ had at the time she chose her action.
+\asedit{Agent $t$ does not need to second-guess which message has caused agent $t'$ to choose that action, since such second-guessing cannot possibly yield any additional information.
+Essentially, agent $t$ can treat the subhistory as a set of data points collected by an algorithm, and not worry how these data points has been affected by other agents' choices.}
 
 Following much of the prior work on incentivizing exploration, we do not attempt to model heterogenous agent preferences and non-stationarity.
-Formally, we assume that the expected reward of taking a given action $a$, denoted $\mu_a$, is the same for all agents, and does not change over time.
-Then the crucial parameter of interest, for a given action $a$, are the number of samples $N_a$ and the empirical mean reward $\bar{\mu}_a$ in the observed subhistory.
-We consider a flexible model of agent response: for each action $a$ an agent forms an estimate $\hat{\mu}_a$ of the mean reward $\mu_a$, roughly following $\bar{\mu}_a$ but taking into account the uncertainty due to a small number of samples, and chooses an action with a largest reward estimate.
-We allow the reward estimates to be arbitrary otherwise, and not known to the principal.
+We assume that the expected reward of taking a given action $a$, denoted $\mu_a$, is the same for all agents, and does not change over time.
+
+We consider a flexible model of agent response.
+For each action $a$, the crucial statistics are the number of samples $N_a$ and the empirical mean reward $\bar{\mu}_a$ in the observed subhistory.
+An agent forms an estimate $\hat{\mu}_a$ of the mean reward $\mu_a$, roughly following $\bar{\mu}_a$ but taking into account the uncertainty due to a small number of samples, and chooses an action with a largest reward estimate.
+We allow the reward estimates to be arbitrary otherwise.
+\asedit{The way they depend on the observed statistics may differ from one agent to another.
+This dependence, as well as the statistics and the reward estimates, are not known to the principal.
+We make no assumptions whatsoever unless an agent has sufficiently many samples from a given arm.}
+
+\asedit{Our model of agent response is justified by the assumption of unbiased, transitive subhistory.
+This assumption is no longer needed once the model is assumed.
+The model is justified regardless of what the agents know about the subsets $(S_{t}: t\in [T])$.
+In particular, we could posit that these subsets are common knowledge, or that the agents do not know them, not even their own subset.}
 
@@
 
-\xhdr{Our results and discussion.}
+\xhdr{Our results and techniques.}
 Our main result is a transitive, unbiased-subhistory policy which attains near-optimal $\tilde{O}(\sqrt{T})$ regret rate for a constant number of actions.
@@
 for problem instances with gap $\Delta$, without knowing the $\Delta$ in advance.
-In particular, we match the regret rate achieved for incentivizing exploration with unrestricted disclosure policies \cite{ICexploration-ec15-working}.
+In particular, we match the best possible regret rates for the multi-armed bandit problem (same as the prior work on unrestricted disclosure policies \cite{ICexploration-ec15-working}).
+\asedit{Each agent $t$ sees a substantial fraction of history available at time $t$: namely, our policy reveals a subhistory of
+size at least $\Omega( t/\polylog(T))$.
+Our regret bounds scale exponentially in the number of actions; this dependence is grossly suboptimal for multi-armed bandits, but matches the state-of-art for unrestricted disclosure policies \cite{ICexploration-ec15-working}, and is conjectured to be unavoidable for incentivized exploration.}
 
@@
 
+\ascomment{The following xhdr is new}
+
+\xhdr{Discussion.}
+We argue that our subhistory-based policies require substantially weaker trust and rationality assumptions compared to the minimal-disclosure policies in prior work.
+There are several distinct issues here:
+
+\begin{itemize}
+
+\item \emph{Whether agents sufficiently understand the announced policy.} We only need an agent to understand that he is given some unbiased history.
+It does not matter what is the subset of rounds and how it is related to the other agents' subsets.
+This is arguably quite comprehensible, compared to a full-blown spec of a bandit algorithm.
+
+\item \emph{Whether agents trust the principal's intent to implement the stated policy.} A third party can, at least in principle, collect subhistories from multiple agents and check them for consistency (e.g., that arms' average rewards are within the statistical deviations).
+This should create incentives for the principal not to manipulate the policy.
+Note that similar checks appear virtually impossible for minimal-disclosure policies.
+
+\item \emph{Whether agents trust the principal to implement the stated policy without bugs.}
+    Faithfully revealing a subhistory is arguably easy, whereas (as noted above) debugging an actual bandit algorithm in a large-scale production-level system tends to be quite complicated.
+
+\item \emph{Whether agents react to the policy in a way that we assume.}
+In our framework, an agent should react to the subhistory as if it was a set of data points collected by an algorithm, free from other agents' influence.
+The system can provide summary statistics, so that agents would not need to actually look at the raw data.%
+\footnote{Trusting the summary statistics is a relatively minor issue, one where "cheating" can, in principle, be easily verified.}
+Whereas verifying that a minimal-disclosure policy is indeed incentive-compatible typically requires a sophisticated Bayesian reasoning.
+
+\end{itemize}
+
+Even though we are not showing full histories, even a small fraction of history would realistically contain a large number of datapoints.
+Besides, a user usually looks at a small sample of reviews.
+In our case, one could say that these reviews are just pre-selected by the algorithm (in an ``unbiased" and ``transitive" way, as explained above).
+
+For the sake of the analysis, we assume that the mean rewards lie in the interval
+    $[\nicefrac{1}{3}, \nicefrac{2}{3}]$,
+whereas the agents' response model does not take this fact into account.% 
+\footnote{Of course, the $[\nicefrac{1}{3}, \nicefrac{2}{3}]$ restriction can be replaced with $[\eps,1-\eps]$ for any given global constant $\eps>0$ (which would then propagate into the regret bounds).}
+Our justification is two-fold.
+First, agents may operate under incomplete information: they simply do not know that mean rewards are restricted.
+Second, typical users of a recommendation system are unlikely to be fully rational (whether Bayesian or not).
+Following empirical averages appears much more natural.
+In particular, a realistic user should not estimate mean rewards as $\nicefrac{1}{3}$ if it keeps getting $0$ rewards.
+
+On a final note, we emphasize that we provide the first result on incentivized exploration that does not rely on the strong assumptions of trust and rationality.
+
 \input{related-work}

### 2019-04-16 model.tex
Moved (anti)concentration theorems back to prelims.

@@
 
-Throughout the paper, we use the standard concentration and anti-concentration inequalities: respectively, Chernoff Bounds and Berry-Esseen Theorem.
-The former states that that a sum of independent random variables converges to its expectation quickly.
-The latter states that the CDF of an appropriately scaled average of IID random variables converges to the CDF of the standard normal distribution pointwise.
+Throughout the paper, we use the standard concentration and anti-concentration inequalities: respectively, Chernoff Bounds and Berry-Esseen Theorem. The former states that 
+    $\bar{X} = \frac{1}{n}\sum_{i=1}^n X_i$, 
+the average of $n$ independent random variables $X_1 \LDOTS X_n$, converges to its expectation quickly.
+The latter states that the CDF of an appropriately scaled average $\bar{X}$ converges to the CDF of the standard normal distribution pointwise.
 In particular, the average strays far enough from its expectation with some guaranteed probability.
-The theorem statements are moved to Appendix~\ref{sec:prelim}.
+The theorem statements are as follows:
+
+\begin{theorem}
+Fix $n$. Let $X_1,...,X_n$  be independent random variables, and let $\bar{X} = \frac{1}{n}\sum_{i=1}^n X_i$. Then:
+
+\begin{itemize}
+\item[(a)] \emph{(Chernoff Bounds)} %\label{thm:prelims-chernoff}
+Assume $X_i \in [0,1]$ for all $i$. Then
+\[
+\Pr[ |\bar{X} - \E[\bar{X}]| > \varepsilon] \leq 2\exp(-2n\varepsilon^2).
+\]
+
+\item[(b)] \emph{(Berry-Esseen Theorem)} %\label{thm:prelims-Berry}
+Assume $X_1 \LDOTS X_n$ are identically distributed, with 
+\[ 
+    \sigma^2 := \E[ (X_1 - \E[X_1])^2] = \sigma^2
+    \quad\text{and}\quad
+    \rho := \E[ |X_1 - \E[X_1]|^3] <\infty.\]
+Let $F_n$ be the cumulative distribution function of $\frac{(\bar{X} - \E[\bar{X}]) \sqrt{n}}{\sigma}$ and $\Phi$ be the cumulative distribution function of the standard normal distribution. 
+\[
+|F_n(x) - \Phi(x) | \leq \frac{\rho}{2\sigma^3\sqrt{n}}
+\quad \forall x\in \R.
+\]
+\end{itemize}
+\end{theorem}
 

### 2019-04-16 2level.tex
Proofs in the warmup section: moved the short proof back to the body; the longer proof, made it the last subsection in the section.

@@
 
-\OMIT{ %%%%%%
-\begin{proof}[Proof Sketch]
-\ascomment{Jieming, pls add a brief proof sketch if you can.}
-\jmcomment{The main idea of the proof is to consider the case when all pulled arms have bad realized rewards (i.e. 0). }
-\jmcomment{Actually, not clear about how to write a sketch for a proof of 8 lines.}
+\begin{proof}
+  Fix any arm $a$. Let $\GdT = (K-1) \cdot \estN + 1$ and
+  $\GdP = (1/3)^{\GdT}$. We will condition on the event that
+    all the realized rewards in $\GdT$ rounds are 0, which occurs with
+    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.
+  In this case, we want to show that arm $a$ is pulled at least
+  once. We prove this by contradiction. Suppose arm $a$ is not pulled. By
+  the pigeonhole principle, we know that there is some other arm $a'$
+  that is pulled at least $\estN + 1$ rounds. Let $t$ be the round in
+  which arm $a'$ is pulled exactly $\estN + 1$ times. By Assumption
+  \ref{ass:embehave}, we know
+  \[
+    \hat{\mu}_{a'}^t \leq 0 + \estC / \sqrt{\estN}  \leq \estC < 1/3.
+  \]
+  On the other hand, we have
+  $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
+  the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
 \end{proof}
-} %%%%%%
 
@@
 
-The proofs can be found in Appendix~\ref{app:warmup}.
+The proof can be found in Section~\ref{app:warmup}.
 One important quantity is the expected number of samples of a given arm $a$ collected by a full-disclosure path $S$ of length $\fdpL$ (\ie present in the subhistory $\SubH{S}$.
@@
 
+\input{app-warmup}
+
 %%% Local Variables:

### 2019-04-16 app-warmup.tex
Proofs in the warmup section: moved the short proof back to the body; the longer proof, made it the last subsection in the section.

@@
 %!TEX root = main.tex
-\section{Proofs from Section~\ref{sec:warmup}}
+\subsection{Proof of Theorem~\ref{thm:2level}}
 \label{app:warmup}
 
-\begin{proof}[Proof of Lemma~\ref{lem:greedy}]
-  Fix any arm $a$. Let $\GdT = (K-1) \cdot \estN + 1$ and
-  $\GdP = (1/3)^{\GdT}$. We will condition on the event that
-    all the realized rewards in $\GdT$ rounds are 0, which occurs with
-    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.
-  In this case, we want to show that arm $a$ is pulled at least
-  once. We prove this by contradiction. Suppose arm $a$ is not pulled. By
-  the pigeonhole principle, we know that there is some other arm $a'$
-  that is pulled at least $\estN + 1$ rounds. Let $t$ be the round in
-  which arm $a'$ is pulled exactly $\estN + 1$ times. By Assumption
-  \ref{ass:embehave}, we know
-  \[
-    \hat{\mu}_{a'}^t \leq 0 + \estC / \sqrt{\estN}  \leq \estC < 1/3.
-  \]
-  %\nicomment{Wait, where did we set $\estN$?} 
-  On the other hand, we have
-  $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
-  the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
-  %\swdelete{ In addition, we know that this case happens with
-    %probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is
-    %at most $2/3$. To sum up, we know that with probability at least
-    %$\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.}
-  % \jmcomment{Agree with these changes.}
-\end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{thm:2level}]
   We will set $T_1$ later in the proof, depending on whether the gap
@@
 By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get regret $O(T^{2/3}\log(T)^{1/3})$.
-\OMIT{Notice that if we know the gap parameter is known to be larger than
-$\Delta$, we can set
-\[
-T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
-\]
-In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total regret is at most
-\[
-T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
-\]
-This completes the proof.}
-\end{proof}

### 2019-04-26 main.tex
Added a ToC.
Proofs in the warmup section: moved the short proof back to the body; the longer proof, made it the last subsection in the section.
warmup: moved the \input statement for the proofs back into the main file.
Moved \input for details of L-level stuff into the right place.
Revised /expanded the abstract.

@@
 \usepackage{float}
+
 % ======    PACKAGES
@@
 %\usepackage{amsbsy,amscd, bm, bbm}
+\usepackage{nicefrac}
 \usepackage{kpfonts}
@@
 \usepackage{algorithm}
-\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
+%\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
+\usepackage[breaklinks]{hyperref}
 \usepackage{url}
@@
 % a very useful package for edits and comments, from David Kempe (USC)
-%\usepackage{color-edits}
+\usepackage{color-edits}
 %\usepackage[suppress]{color-edits}  % use this to suppress the package
-%\addauthor{as}{red}      % as for Alex
-%\addauthor{jm}{blue}     % jm for Jieming
-%\addauthor{ni}{magenta}     % ni for Nicole
-%\addauthor{sw}{brown}     % sw for Steven
+\addauthor{as}{red}      % as for Alex
+\addauthor{jm}{blue}     % jm for Jieming
+\addauthor{ni}{magenta}     % ni for Nicole
+\addauthor{sw}{brown}     % sw for Steven
 % e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.
@@
 
+\date{First version: November 2018\\This version: April 2019}
+
 \author{
@@
 }
+
 \begin{document}
-\begin{titlepage}
+
 \maketitle
 
-\thispagestyle{empty}
 \begin{abstract}
@@
 A disclosure policy tries to coordinate the choices of the agents by sending messages about the history of past actions.
-The goal of the algorithm is to minimize the regret of the action sequence.
+The goal of the disclosure policy is to minimize the regret of the action sequence \asedit{chosen by the agents.
+Prior work achieves much progress with disclosure policies that merely recommend an action to each user.
+However, all this work relies heavily on trust and rationality assumptions, which are standard and yet quite problematic in the context of recommendation systems.}
 
-In this paper, we study a particular class of disclosure policies that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards from by a subsequence of past agents, where the subsequence is chosen ahead of time.
-One trivial message of this form contains the full history; a disclosure policy that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.
-Our main result is a disclosure policy using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.
+\asedit{In this paper, we design disclosure policies which incentivize good performance under more plausible behavioral assumptions.
+Conceptually, we would like to retain the trustworthiness of revealing the full history, while avoiding the herding behavior induced by such disclosure policy (which may lead to regret linear in the time horizon).
+We focus on messages, called {\em unbiased subhistories}, consisting of the actions and rewards from a subsequence of past agents, where the subsequence is chosen ahead of time.
+We further require these messages to be \emph{transitive}: if a message includes action and reward from a particular agent, then it also includes the message sent to that agent.
+We posit a flexible model of agent response, which we argue is plausible for this class of disclosure policies.}
+
+Our main result is a disclosure policy using unbiased, transitive subhistories that obtains regret $\tilde{O}(\sqrt{T})$, where $T$ is the time horizon.
 We also exhibit simpler policies with higher, but still sublinear, regret.
@@
 \end{abstract}
-\end{titlepage}
+
+\thispagestyle{empty}
+\addtocontents{toc}{\setcounter{tocdepth}{0}}
+\newpage
+\thispagestyle{empty}
+\tableofcontents
+\newpage
+\addtocontents{toc}{\setcounter{tocdepth}{2}}
 
@@
 \input{2level}
-
+\input{app-warmup}
 \input{3level}
-
-%l-level in the 10page
+\input{3levelproofs}
 \input{llevel-overview}
+\input{llevel}
 
@@
 \appendix
-\input{prelim}
-\input{app-warmup}
-\input{3levelproofs}
-\input{llevel}
+%\input{prelim}
+%\input{app-warmup}
+%\input{3levelproofs}
+%\input{llevel}
 

### 2019-04-26 main.tex
Minor edit in the abstract.

@@
 Prior work achieves much progress with disclosure policies that merely recommend an action to each user.
-However, all this work relies heavily on trust and rationality assumptions, which are standard and yet quite problematic in the context of recommendation systems.}
+However, all this work relies heavily on trust and rationality assumptions, standard in economic theory, yet quite problematic in the context of the motivating applications.}
 

### 2019-04-26 main.tex
More edits in abstract.

--- 2019-04-26 main.tex
@@
 \begin{abstract}
-In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world.
-A sequence of agents each chooses an action with the goal of maximizing payoff given estimates of the state of the world.
+In a social learning setting, there is a set of actions, each of which has a \asedit{fixed but unknown expected payoff}.
+\asedit{Agents arrive one by one, each chooses} an action with the goal of maximizing the payoff.
 A disclosure policy tries to coordinate the choices of the agents by sending messages about the history of past actions.
@@
 Prior work achieves much progress with disclosure policies that merely recommend an action to each user.
-However, all this work relies heavily on trust and rationality assumptions, which are standard and yet quite problematic in the context of recommendation systems.}
+(Absent agents' incentives, such policy is a multi-armed bandit algorithm.) However, all this work relies heavily on trust and rationality assumptions, standard in economic theory, yet quite problematic in the context of the motivating applications.}
 

### 2019-04-26 ec19 workshop/cover.tex
Started the draft.

--- 2019-04-26 main.tex
@@
-\documentclass[11pt]{article}
-\usepackage{fullpage}
-\usepackage{mathrsfs}
-\usepackage{float}
+\documentclass[11pt,letterpaper]{article}
 
-% ======    PACKAGES
-\usepackage{slivkins-setup,slivkins-theorems}
-%\usepackage{amsmath, amsfonts, amssymb, amsthm, amsbsy, amscd, bm, bbm}
-%\usepackage{amsbsy,amscd, bm, bbm}
-\usepackage{nicefrac}
-\usepackage{kpfonts}
-\usepackage{array}
-\usepackage{booktabs}
-\usepackage{graphicx}
-\usepackage[small,bf]{caption}
-\setlength{\captionmargin}{30pt}
-\usepackage{subcaption}
-\captionsetup[sub]{margin=10pt,font=small}
-\usepackage{color}
-\usepackage{ifthen}
-\usepackage{xspace}
-\usepackage[noend]{algorithmic}
-\usepackage{algorithm}
-%\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
-\usepackage[breaklinks]{hyperref}
-\usepackage{url}
-\usepackage{tocbibind}
-\usepackage{enumerate}
-\usepackage{mdframed}
-\usepackage{comment}
-\usepackage{tikz}
-\usetikzlibrary{decorations.pathreplacing}
-\usepackage{cleveref}
-
-\DeclareMathOperator*{\argmin}{argmin}
+\usepackage{fullpage,times}
 
@@
 %\usepackage[suppress]{color-edits}  % use this to suppress the package
+%\addauthor{ab}{green}   % ab for Ashwin
+%\addauthor{bk}{magenta} % bk for Bobby
 \addauthor{as}{red}      % as for Alex
-\addauthor{jm}{blue}     % jm for Jieming
-\addauthor{ni}{magenta}     % ni for Nicole
-\addauthor{sw}{brown}     % sw for Steven
+%\addauthor{mb}{blue}    % mb for Moshe
 % e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \newtheorem{theorem}{Theorem}[section]
-% \newtheorem{corollary}[theorem]{Corollary}
-% \newtheorem{conjecture}[theorem]{Conjecture}
-% \newtheorem{proposition}[theorem]{Proposition}
-% \newtheorem{definition}[theorem]{Definition}
-% \newtheorem{lemma}[theorem]{Lemma}
-% \newtheorem{remark}{Remark}[section]
-% \newtheorem{claim}{Claim}[section]
-% \newtheorem{example}{Example}[section]
+\begin{document}
+%\vspace{-30mm}
 
-\newcommand{\term}[1]{\ensuremath{\mathtt{#1}}\xspace}
-\newcommand{\thread}{\term{thread}}
-\newcommand{\ALGG}{full-disclosure path }
-\newcommand{\ALGPG}{\term{Parallel Greedy}}
+\section*{Summary: Incentivizing Exploration with Unbiased Histories}
 
-% Alex's notation!
-\newcommand{\SubH}[1]{\mathcal{H}_{#1}} % subhistory
-\newcommand{\AnonSubH}[1]{H^{\texttt{anon}}_{#1}} % subhistory
+In a social learning setting, there is a set of actions, each of which has a fixed but unknown expected payoff.
+Agents arrive one by one, each chooses an action with the goal of maximizing the payoff.
+A disclosure policy tries to coordinate the choices of the agents by sending messages about the history of past actions.
+The goal of the disclosure policy is to minimize the regret of the action sequence chosen by the agents.
+Prior work achieves much progress with disclosure policies that merely recommend an action to each user.
+(Absent agents' incentives, such policy is a multi-armed bandit algorithm.) However, all this work relies heavily on trust and rationality assumptions, standard in economic theory, yet quite problematic in the context of the motivating applications.
+However, all this work relies heavily on trust and rationality assumptions, standard in economic theory, yet quite problematic in the context of the motivating applications.
 
-% new notation for FDPs (full-disclosure paths)
-\newcommand{\fdp}{\term{FDP}}
-\newcommand{\fdpL}{L^\fdp_K} % sufficient length of greedy path
-\newcommand{\fdpP}{p^\fdp_K} % success prob for greedy path
-\newcommand{\fdpN}[1][a]{N^\fdp_{K,#1}}
-    % Exp #pulls for arm $a$ in greedy path of length L_K.
-
-% new notation for low-deviation assumption on agents' reward estimates
-\newcommand{\estN}{N_{\term{est}}}
-\newcommand{\estC}{C_{\term{est}}}
-
-% notation for 3level section
-\newcommand{\conf}[1]{\mathtt{conf}\left(#1\right)}
-\newcommand{\event}[1]{\ensuremath{\mathtt{event}_{#1}}\xspace}
-\newcommand{\cG}{\mathcal{G}}
-
-% Greedy notation
-\def\GdT{L^\fdp_K} % sufficient length of greedy path
-\def\GdP{p^\fdp_K} % success prob for greedy path
-
-\def\2LEVEL{two-level policy}
-
-\newcommand{\DT}{\mD} % Alex' notation for distribution over types.
-
-%number of groups
-\def\NG{\sigma}
-
-\def\DKL{\textbf{D}_{\term{KL}}}
-\def\D{\mathbb{D}}
-\def\E{\mathbb{E}}
-\def\reg{\mathrm{Reg}}
-\def\A{\mathcal{A}}
-\def\M{\mathcal{M}}
-\def\S{\mathcal{S}}
-\def\X{\mathcal{X}}
-\def\EX{\term{EX}}
-\def\Ds{*}
-\def\EE{\mathcal{E}}
-\def\varTheta{\bold{\Theta}}
-\def\varOmega{\bold{\Omega}}
-\def\cD{\mathcal{D}}
-\def\cT{\mathcal{T}}
-\def\Ber{\emph{Ber} }
-
-\def\pmn{\hat{\mu}}
-\def\emn{\bar{\mu}}
-%\def\q_a{\fdpN}
-%\def\ell{l}
-
-%index on the tape
-\def\z{\tau}
-\title{Incentivizing Exploration with Unbiased Histories}
-
-\date{First version: November 2018\\This version: April 2019}
-
-\author{
-Nicole Immorlica \thanks{Microsoft Research, Cambridge, MA. Email: nicimm@microsoft.com.}
-\and
-Jieming Mao \thanks{University of Pennsylvania, Philadelphia, PA. email: maojm517@gmail.com. Results in this paper were obtained while J. Mao was an intern at Microsoft Research NYC.}
-\and
-Aleksandrs Slivkins  \thanks{Microsoft Research, New York, NY. email: slivkins@microsoft.com.}
-\and
-Zhiwei Steven Wu  \thanks{University of Minnesota, Minneapolis, MN. Email: zsw@umn.edu. Results in this paper were obtained while Z.S. Wu was a postdoc at Microsoft Research NYC.}
-}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world.
-A sequence of agents each chooses an action with the goal of maximizing payoff given estimates of the state of the world.
-A disclosure policy tries to coordinate the choices of the agents by sending messages about the history of past actions.
-The goal of the disclosure policy is to minimize the regret of the action sequence \asedit{chosen by the agents.
-Prior work achieves much progress with disclosure policies that merely recommend an action to each user.
-However, all this work relies heavily on trust and rationality assumptions, which are standard and yet quite problematic in the context of recommendation systems.}
-
-\asedit{In this paper, we design disclosure policies which incentivize good performance under more plausible behavioral assumptions.
+In this paper, we design disclosure policies which incentivize good performance under more plausible behavioral assumptions.
 Conceptually, we would like to retain the trustworthiness of revealing the full history, while avoiding the herding behavior induced by such disclosure policy (which may lead to regret linear in the time horizon).
@@
 We further require these messages to be \emph{transitive}: if a message includes action and reward from a particular agent, then it also includes the message sent to that agent.
-We posit a flexible model of agent response, which we argue is plausible for this class of disclosure policies.}
-
+We posit a flexible model of agent response, which we argue is plausible for this class of disclosure policies.
 Our main result is a disclosure policy using unbiased, transitive subhistories that obtains regret $\tilde{O}(\sqrt{T})$, where $T$ is the time horizon.
@@
 These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.
-\end{abstract}
 
-\thispagestyle{empty}
-\addtocontents{toc}{\setcounter{tocdepth}{0}}
-\newpage
-\thispagestyle{empty}
-\tableofcontents
-\newpage
-\addtocontents{toc}{\setcounter{tocdepth}{2}}
-
-\input{intro}
-\input{model}
-
-%\input{algg}
-
-\input{2level}
-\input{app-warmup}
-\input{3level}
-\input{3levelproofs}
-\input{llevel-overview}
-\input{llevel}
-
-\bibliographystyle{plain}
-\bibliography{bib-abbrv,bib-AGT,bib-bandits,bib-ML,bib-random,bib-slivkins}
-
-\section*{Acknowledgment}
-We would like to thank Robert Kleinberg for discussions in the early stage of this project.
-
-\appendix
-%\input{prelim}
-%\input{app-warmup}
-%\input{3levelproofs}
-%\input{llevel}
-
-%\input{posterior}
 \end{document}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2019-04-26 ec19 workshop/cover.tex
Full draft?

@@
 
-\section*{Summary: Incentivizing Exploration with Unbiased Histories}
+\section*{Summary: Incentivizing Exploration with Unbiased Histories
+\\{\large (by Nicole Immorlica, Jieming Mao, Aleksandrs Slivkins and Zhiwei Steven Wu)}}
 
@@
 Agents arrive one by one, each chooses an action with the goal of maximizing the payoff.
-A disclosure policy tries to coordinate the choices of the agents by sending messages about the history of past actions.
-The goal of the disclosure policy is to minimize the regret of the action sequence chosen by the agents.
+A disclosure policy coordinates the choices of the agents by sending messages about the history of past actions.
+These messages can alter agents' incentives towards \emph{exploration}, taking potentially sub-optimal actions for the sake of learning more about their rewards.
+The goal of the disclosure policy is to incentivize exploration so as  to maximize social welfare; more specifically, so as to minimize the regret of the action sequence chosen by the agents.
 Prior work achieves much progress with disclosure policies that merely recommend an action to each user.
 (Absent agents' incentives, such policy is a multi-armed bandit algorithm.) However, all this work relies heavily on trust and rationality assumptions, standard in economic theory, yet quite problematic in the context of the motivating applications.
-However, all this work relies heavily on trust and rationality assumptions, standard in economic theory, yet quite problematic in the context of the motivating applications.
 
@@
 
+\vspace{2mm}
+
+This paper continues the line of work on ``incentivized exploration": bandit learning in applications such as recommendation systems, in the presence of strategic behavior of self-interested users whose incentives are skewed in favor of exploitation.
+As such, this paper continues a broader theme of ``exploration and incentives", and is firmly positioned in the area of ``learning in the presence of strategic behavior".
+
+This is the first paper in the literature on ``exploration and incentives" (and possibly in the broader literature on ``learning and incentives") which attempts to mitigate the limitations of standard economic assumptions on rational behavior.
 \end{document}

### 2019-04-29 ec19 workshops/cover-straregic-learning.tex
renamed file.

--- 2019-04-26 ec19 workshop/cover.tex
@@
 
-This paper continues the line of work on ``incentivized exploration": bandit learning in applications such as recommendation systems, in the presence of strategic behavior of self-interested users whose incentives are skewed in favor of exploitation.
+This paper continues the line of work on ``incentivized exploration": essentially, bandit learning in applications such as recommendation systems, in the presence of strategic behavior of self-interested users whose incentives are skewed in favor of exploitation.
 As such, this paper continues a broader theme of ``exploration and incentives", and is firmly positioned in the area of ``learning in the presence of strategic behavior".
-
 This is the first paper in the literature on ``exploration and incentives" (and possibly in the broader literature on ``learning and incentives") which attempts to mitigate the limitations of standard economic assumptions on rational behavior.

### 2019-04-29 ec19 workshops/cover-straregic-learning.tex
Expanded a bit more.

@@
 
-\section*{Summary: Incentivizing Exploration with Unbiased Histories
-\\{\large (by Nicole Immorlica, Jieming Mao, Aleksandrs Slivkins and Zhiwei Steven Wu)}}
+\section*{Submission: Incentivizing Exploration with Unbiased Histories \\
+{\large (by Nicole Immorlica, Jieming Mao, Aleksandrs Slivkins and Zhiwei Steven Wu)}\\
+{\large Workshop: Learning in the Presence of Strategic Behavior}
+}
 
@@
 These messages can alter agents' incentives towards \emph{exploration}, taking potentially sub-optimal actions for the sake of learning more about their rewards.
-The goal of the disclosure policy is to incentivize exploration so as  to maximize social welfare; more specifically, so as to minimize the regret of the action sequence chosen by the agents.
-Prior work achieves much progress with disclosure policies that merely recommend an action to each user.
-(Absent agents' incentives, such policy is a multi-armed bandit algorithm.) However, all this work relies heavily on trust and rationality assumptions, standard in economic theory, yet quite problematic in the context of the motivating applications.
+The goal of the disclosure policy is to incentivize exploration so as  to maximize social welfare; specifically, so as to minimize the regret of the chosen action sequence.
+
+Prior work achieves much progress with disclosure policies that merely recommend an action to each user, without any other supporting information, and sometimes recommend exploratory actions.
+(Absent agents' incentives, such policy is a multi-armed bandit algorithm.) All this work relies heavily on trust and rationality assumptions, standard in economic theory.
+However, these assumptions are quite problematic in the context of the motivating applications such as recommendation systems.
+It is very unclear whether users would know and understand some complicated disclosure policy announced  by the principal, let alone trust the principal to faithfully implement this policy.
+Even if they do know the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally, particularly regarding the possibility of being singled out for exploration.
 

### 2019-04-29 ec19 workshops/cover-straregic-learning.tex
Added a bit more.

@@
 It is very unclear whether users would know and understand some complicated disclosure policy announced  by the principal, let alone trust the principal to faithfully implement this policy.
-Even if they do know the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally, particularly regarding the possibility of being singled out for exploration.
+(The principal may deviate from the announced policy either intentionally, or due to insufficient information about the users, or because of bugs in implementation.) Even if the users understand the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally, particularly regarding the lack of supporting information and the possibility of being singled out for exploration.
+For example, users may find such disclosure policies unacceptable and leave the system.
 

### 2019-04-29 intro.tex
Minor edit.

@@
 However, these assumptions appear quite problematic in the context of recommendation systems of actual online websites such as those mentioned above.
-In particular, much of the prior work suggests disclosure policies that merely recommend an action to each user, without any other supporting information, and moreover recommend exploratory actions to some randomly selected users.
-This works out extremely well in theory, but it is very unclear whether users would even know some complicated policy of the principal, let alone trust the principal to implement the stated policy.
-Even if they do know the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally.
+In particular, much of the prior work suggests disclosure policies that merely recommend an action to each user, without any other supporting information, and \asedit{sometimes recommend exploratory actions}.
+This works out extremely well in theory, but it is very unclear whether users would know and  understand some complicated policy deployed by the principal, let alone trust the principal to implement this policy.
+Even if they do understand the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally.
 %

### 2019-04-29 ec19 workshops/cover-straregic-learning.tex
Minor edit.

@@
 As such, this paper continues a broader theme of ``exploration and incentives", and is firmly positioned in the area of ``learning in the presence of strategic behavior".
-This is the first paper in the literature on ``exploration and incentives" (and possibly in the broader literature on ``learning and incentives") which attempts to mitigate the limitations of standard economic assumptions on rational behavior.
+To the best of our knowledge, this is the first paper in the literature on ``exploration and incentives" (and possibly in the broader literature on ``learning and incentives") which attempts to mitigate the limitations of standard economic assumptions on rational behavior.
 \end{document}

### 2019-04-29 ec19 workshops/cover-behavioral-EC.tex
Added a cover letter for the behavioral EC workshop.

--- 2019-04-29 ec19 workshops/cover-straregic-learning.tex
@@
 {\large (by Nicole Immorlica, Jieming Mao, Aleksandrs Slivkins and Zhiwei Steven Wu)}\\
-{\large Workshop: Learning in the Presence of Strategic Behavior}
+{\large Workshop: Behavioral EC}
 }
@@
 
-This paper continues the line of work on ``incentivized exploration": essentially, bandit learning in applications such as recommendation systems, in the presence of strategic behavior of self-interested users whose incentives are skewed in favor of exploitation.
-As such, this paper continues a broader theme of ``exploration and incentives", and is firmly positioned in the area of ``learning in the presence of strategic behavior".
-This is the first paper in the literature on ``exploration and incentives" (and possibly in the broader literature on ``learning and incentives") which attempts to mitigate the limitations of standard economic assumptions on rational behavior.
+This paper continues the line of work on ``incentivized exploration": essentially, multi-armed bandit learning in applications such as recommendation systems, in the presence of strategic behavior of self-interested users whose incentives are skewed in favor of exploitation.
+As such, this paper continues a broader theme of ``exploration and incentives", and an even broader theme of ``machine learning and incentives".
+To the best of our knowledge, this is the first paper in the literature on ``exploration and incentives" (and one of the few such papers in the broader literature on ``learning and incentives") which attempts to mitigate the limitations of standard economic assumptions on rational behavior.
 \end{document}

### 2019-04-29 ec19 workshops/18pp version/main.tex
Copied the files.

--- 2019-04-26 main.tex
@@
 \begin{abstract}
-In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world.
-A sequence of agents each chooses an action with the goal of maximizing payoff given estimates of the state of the world.
-A disclosure policy tries to coordinate the choices of the agents by sending messages about the history of past actions.
-The goal of the disclosure policy is to minimize the regret of the action sequence \asedit{chosen by the agents.
+\ascomment{rewrote the abstract.}
+
+In a social learning setting, there is a set of actions, each of which has a fixed but unknown expected payoff.
+Agents arrive one by one, each chooses an action with the goal of maximizing the payoff.
+A disclosure policy coordinates the choices of the agents by sending messages about the history of past actions.
+These messages can alter agents' incentives towards \emph{exploration}, taking potentially sub-optimal actions for the sake of learning more about their rewards.
+The goal of the disclosure policy is to incentivize exploration so as  to maximize social welfare; more specifically, so as to minimize the regret of the action sequence chosen by the agents.
 Prior work achieves much progress with disclosure policies that merely recommend an action to each user.
-However, all this work relies heavily on trust and rationality assumptions, which are standard and yet quite problematic in the context of recommendation systems.}
+(Absent agents' incentives, such policy is a multi-armed bandit algorithm.) However, all this work relies heavily on trust and rationality assumptions, standard in economic theory, yet quite problematic in the context of the motivating applications.
 
-\asedit{In this paper, we design disclosure policies which incentivize good performance under more plausible behavioral assumptions.
+In this paper, we design disclosure policies which incentivize good performance under more plausible behavioral assumptions.
 Conceptually, we would like to retain the trustworthiness of revealing the full history, while avoiding the herding behavior induced by such disclosure policy (which may lead to regret linear in the time horizon).

### 2019-04-29 ec19 workshops/18pp version/related-work.tex
Copied the files.

--- 2018-11-02 related-work.tex
@@
 
-Full-disclosure policy, and closely related ``greedy" (exploitation-only) algorithm in multi-armed bandits, have been a subject of a recent line of work \cite{Sven-aistats18,kannan2018smoothed,bastani2017exploiting,externalities-colt18,practicalCB-arxiv18}.
-A common theme is that the greedy algorithm performs well in theory, under  substantial heterogeneity assumptions, and sometimes it works well in practice.
-Yet, it suffers $\Omega(T)$ regret in the worst case.%
-\footnote{This is a well-known folklore result; \eg see \cite{CompetingBandits-itcs16} for a concrete example.}
+Full-disclosure policy, and closely related ``greedy" (exploitation-only) algorithm in multi-armed bandits, have been a subject of a recent line of work \cite{Sven-aistats18,kannan2018smoothed,bastani2017exploiting,externalities-colt18}.
+A common theme is that the greedy algorithm performs well in theory, under  substantial assumptions on heterogeneity of the agents. Yet, it suffers $\Omega(T)$ regret in the worst case.%
+\footnote{This is a well-known folklore result; \eg see \cite{CompetingBandits-itcs18} for a concrete example.}
 
-Exploration-exploitation tradeoff received much attention over the past decades, usually under the rubric of ``multi-armed bandits"; see  \cite{Bubeck-survey12,Gittins-book11} for background. 
+Exploration-exploitation tradeoff received much attention over the past decades, usually under the rubric of ``multi-armed bandits"; see books \cite{CesaBL-book,Bubeck-survey12,Gittins-book11} for background.
 Exploration-exploitation problems with incentives issues arise in several other scenarios: dynamic pricing

### 2019-04-29 main.tex
Moved acks to before the bib.

--- 2019-04-26 main.tex
@@
 
+\section*{Acknowledgment}
+We would like to thank Robert Kleinberg for discussions in the early stage of this project.
+
 \bibliographystyle{plain}
 \bibliography{bib-abbrv,bib-AGT,bib-bandits,bib-ML,bib-random,bib-slivkins}
-
-\section*{Acknowledgment}
-We would like to thank Robert Kleinberg for discussions in the early stage of this project.
 

### 2019-06-17 EC2019 Poster/main.tex
poster

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Landscape Poster
% LaTeX Template
% Version 1.0 (29/03/13)
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final]{beamer}

\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster

%\usepackage[orientation=portrait,size=custom,width=91.44,height=121.92,scale=1.9]{beamerposter}

\usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamercolor{block title}{fg=white,bg=dblue!70} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{36in} % A0 width: 46.8in
\setlength{\textwidth}{35in} % A0 width: 46.8in
\setlength{\paperheight}{48in} % A0 height: 33.1in
\setlength{\sepwid}{0\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.30\paperwidth} % Width of one column
\setlength{\twocolwid}{0.624\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

\usepackage{graphicx}  % Required for including images

\usepackage{booktabs} % Top and bottom rules for tables
\usepackage{exscale}

\setbeamertemplate{itemize/enumerate body begin}{\normalsize}
\setbeamertemplate{itemize/enumerate subbody begin}{\normalsize}
\usepackage{slivkins-setup,slivkins-theorems}

\newcommand{\term}[1]{\ensuremath{\mathtt{#1}}}

\def\varTheta{\bold{\Theta}}
\def\varOmega{\bold{\Omega}}
\def\ell{l}

% exploration sets
\newcommand{\AExp}{\mA} % actions
\newcommand{\MExp}{\mM}  % menus

% benchmarks
\def\OPT{\term{OPT}}
\newcommand{\OPTpub}{\OPT_{\term{pub}}}
\newcommand{\OPTpri}{\OPT_{\term{pri}}}
%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------

\title{Incentivizing Exploration with Unbiased Histories} % Poster title

\author{Nicole Immorlica$^1$, Jieming Mao$^2$, Aleksandrs Slivkins$^1$, Zhiwei Steven Wu$^3$} % Author(s)

\institute{Microsoft Research$^1$, University of Pennsylvania$^2$, University of Minnesota$^3$} % Institution(s)

%----------------------------------------------------------------------------------------

\begin{document}

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t]
 % The whole poster is enclosed in one beamer frame

\begin{columns}[t]
 % The whole poster consists of two major columns, each of which can be
 % subdivided further with another \begin{columns} block - the [t] argument
 % aligns each column's content to the top

\begin{column}{.01\textwidth}\end{column} % Empty spacer column

\begin{column}{.44\textwidth} % The first column

\begin{alertblock}{Problem}
\begin{itemize}
\item Incentivizing Exploration: 
\begin{itemize}
\item Agents arrive sequentially in a social learning setting 
\item The principal balances exploration and exploitation by controlling the information each agent receives
\end{itemize}
\item Prior work achieves much progress but relies heavily on trust and rationality assumptions (e.g. direct recommendation of an action)
\item We would like to retain the trustworthiness of revealing the full history but it is impossible without using information asymmetry 
\item Achieve low-regret with messages called \emph{unbiased subhistories} 
\begin{itemize}
\item Actions and rewards from a subsequence of past agents 
\item The subsequence is chosen ahead of time
\end{itemize}
\end{itemize}
\end{alertblock}

\begin{block}{Model}
~\\
A game consists of $T$ rounds between a principal and $T$ agents. Each round $t \in[T]$ proceeds as follows:
\begin{itemize}
\item Agent $t$ receives message $m_t$ from the principal
\item Agent $t$ chooses action $a_t \in \mathcal{A}$, $|\mathcal{A}| = $ constant $K$
\item Agent $t$ obtains reward $r_t \in \{0,1\}$ sampled from Bernoulli $\mu_{a_t} \in [1/3,2/3]$ 
\item Agent $t$ reports $r_t$ back to the principal
\end{itemize}
\textbf{Unbiased subhistories:} the subhistory for a subset of rounds $S \subset [T]$
$$\mathcal{H}_{S} = \{ (s,a_s,r_s): s \in S \}$$
with two properties:
\begin{itemize}
\item Unbiased: $S_t$ is chosen before round 1
\item Transitive: $t \in S_{t'} \Rightarrow S_t \subset S_{t'}$
\end{itemize}
\textbf{Agents' behavior:} Agent $t$ forms an estimate $\hat{\mu}_a^t$ for each arm $a$  and chooses the one with the highest estimate. Estimates are close to empirical averages in the subhistories:
\[
|\hat{\mu}_a^t- \bar{\mu}_a^t| < \frac{C}{\sqrt{N_{t,a}}}. 
\]
\textbf{Regret:}
\[
Reg(T) = T\cdot \max_{a \in \mathcal{A}} \mu_a - \sum_{t \in [T]} \mathbb{E}[\mu_{a_t}].
\]
\end{block}

\begin{block}{Warm-up: Two-level Policy}
~\\
\textbf{Full-disclosure Path:} reveal the full history in each round\\
\textbf{Lemma:} a full-disclosure path of some constant length samples each arm at least once with constant probability \\
~\\
\textbf{Two-level Policy:}
\begin{center}
\includegraphics[width=0.99\linewidth]{2l.png} 
\end{center}
\textbf{Theorem:}
\[
Reg(T) \leq O_K (T^{2/3} (\log(T))^{1/3})
\]
\end{block}

\end{column} % End of the first column

\begin{column}{.01\textwidth}\end{column} % Empty spacer column

\begin{column}{.44\textwidth} % The second column
\begin{block}{Three-level Policy}

\begin{center}
\includegraphics[width=0.99\linewidth]{3l.png} 
\end{center}
\textbf{Theorem:}
\[
Reg(T) \leq O_K (T^{4/7} \log(T))
\]
\textbf{Proof Sketch} (for 2 arms): Wlog $\mu_1 \geq \mu_2$,  $\Delta = \mu_1 - \mu_2$\\
$T_1 = T^{4/7} \log^{-1/7}(T)$, $T_2 = T^{6/7}\log^{-5/7}(T)$, $\sigma= \log(T)$\\
Case analysis based on $\Delta$:
\begin{itemize}
\item (Negligible gap) $\Delta < T^{-3/7}\log^{6/7}(T)$: \\picking any arm gives small regret\\
~
\item (Large gap) $\Delta > \sqrt{\log(T)/T_1} = T^{-2/7} \log^{4/7}(T)$:\\ concentration in the first level \\$\Rightarrow$ all agents in the second and the third levels pull arm 1\\~
\item (Small gap) $\Delta \in (T^{-3/7}\log^{6/7}(T), \sqrt{1/T_1})$:\\ anti-concentration in the first level \\$\Rightarrow$ both arms are pulled $\geq T_2$ times, concentration in the second level\\ $\Rightarrow$ all agents in the third level pull arm 1\\~
\item (Medium gap) $\Delta \in (\sqrt{1/T_1}, \sqrt{\log(T)/T_1})$:\\ concentration in the first level \\$\Rightarrow$ all agents in the third level pull arm 1
\end{itemize}
\end{block}

\begin{block}{$L$-level Policy}
\begin{center}
\includegraphics[width=0.99\linewidth]{ll.png} 
\end{center}
\textbf{Interlacing connection:} Agents in Group $G_{l,u,v}$ sees history of agents in group $G_{l-1,v,w}$ for all $u,v,w \in [\log(T)]$\\
~\\
\textbf{Theorem:}
$L$-level policy:
\[
Reg(T) \leq O_K (T^{2^{L-1} / (2^L-1)} \text{poly}\log(T))
\]
$O(\log(T)/\log\log(T))$-level policy:
\[
Reg(T) \leq O_K(T^{1/2} \text{poly} \log(T))
\]
\end{block}

\end{column} % End of the second column

\begin{column}{.01\textwidth}\end{column} % Empty spacer column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}
